### 2009-03-29 methods/ms.tex
added methods folder for the paper

% calibration
% you should look @ calibration/plot_dcfluxes.pro in my publish/ directory, and /usb/scratch1/planets/planet_dcfluxes.txt is the actual raw data
%/home/milkyway/student/ginsbura/bgps_pipeline/calibration/plot_dcfluxes.pro?

% glitches
% I can't send you raw data for the glitches, but the best way I can think of dealing with them is taking one of my postiter.sav files in some directory and grabbing ac_bolos[where(flags)]...... except that include hand-flagged stuff too

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                       % 
%       Bolocam Galactic Plane Survey Description       %
%                                                       % 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,preprint]{aastex}
%{emulateapj}

\usepackage{rotating}

\citestyle{aa}

\bibliographystyle{apj_w_etal}

\newcommand{\vect}[1]{\mathbf{#1}}
\newcommand{\xad}{\vect{x}}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{jaguirre@nrao.edu}
\newcommand{\lsim}{{_{<}\atop^{\sim}}}
\newcommand{\gsim}{{_{>}\atop^{\sim}}}
\newcommand{\etal}{{et al.\/}}
\newcommand{\ie}{{\em ie.\/}}
\newcommand{\cmq}{cm{$^{-3}$}}
\newcommand{\per}{$^{\rm{-1}}$}
\newcommand{\tc}{{$\theta^1$~Orionis~C}}
%\newcommand{\msol}{M{$_{\odot}$}}
\def\msol{\ifmmode {\>M_\odot}\else {$M_\odot$}\fi}
\newcommand{\lsol}{L{$_{\odot}$}}
\newcommand{\kms}{km~s{$^{-1}$}}
\newcommand{\hii}{H~{\sc ii}}
\newcommand{\Hii}{H~{\sc ii}}
\newcommand{\Ha}{\mbox{H$\alpha$}}
\newcommand{\sii}{S~{\sc ii}}
\newcommand{\Feii}{Fe~{\sc ii}}
\newcommand{\oi}{O~{\sc i}}
\newcommand{\nii}{N~{\sc ii}}
\newcommand{\oiii}{O~{\sc iii}}
\newcommand{\mgii}{Mg~{\sc ii}}
\newcommand{\tco}{{$^{13}$CO}}
\newcommand{\CO}{{$^{12}$CO}}
\newcommand{\Tco}{{$^{12}$CO}}
\newcommand{\co}{C{$^{18}$O}}
\newcommand{\Lsol}{L$_{\odot}$}
\newcommand{\Msol}{M$_{\odot}$}
%\newcommand{\C18o}{C$^{18}$O($1\rightarrow 0$)}
\newcommand{\Check}{{\bf ???}}
\newcommand{\mum}{\ensuremath{\mu \mathrm{m}}}
\newcommand{\flux}{flux density}
\newcommand{\solar}{\ensuremath{\odot}}

\newcommand{\epsi}{\varepsilon}

\newcommand{\bgpsarea}{150}
\newcommand{\bcamfwhm}{31.2\arcsec}
\newcommand{\ncores}{$10^4$}
\newcommand{\bgpsdepthlow}{20}
\newcommand{\bgpsdepthhigh}{50}

\newcommand{\TBD}{{\bf TBD}}

\def\Figure#1#2#3#4{
\begin{figure}[htb]
\epsscale{#4}
\plotone{#1}
\caption{#2}
\label{#3}
\end{figure}
}

\def\Table#1#2#3#4#5{
\begin{deluxetable}{#1}
\tablewidth{0pt}
\tablecaption{#2}
\tablehead{#3}
\startdata
\label{#4}
#5
\enddata
\end{deluxetable}
}

\newcommand{\penn}{1}
\newcommand{\casa}{2}
\newcommand{\cso}{3}
\newcommand{\utexas}{4}
\newcommand{\virginia}{5}
\newcommand{\ubc}

	% End definitions

\slugcomment{DRAFT: \today}

\shorttitle{BGPS}
\shortauthors{Aguirre et al.}

\begin{document}

\title{The Bolocam Galactic Plane Survey: Survey Description and Data
Reduction}

%\newpage
%\pagebreak

%\tableofcontents

%\newpage
%\pagebreak

\author{James Aguirre\altaffilmark{\penn},
        Adam Ginsburg\altaffilmark{\casa},
        Miranda Nordhaus\altaffilmark{\utexas},
	Meredith Drosback\altaffilmark{4},
        John Bally\altaffilmark{\casa}, 
	Cara Battersby\altaffilmark{\casa},
	Eric Todd Bradley\altaffilmark{5},
%        Richard Chamberlin\altaffilmark{\cso},
	Claudia Cyganowski\altaffilmark{6},
	Darren Dowell\altaffilmark{7}
	Neal J. Evans II\altaffilmark{\utexas},
        Jason Glenn\altaffilmark{\casa},
        Paul Harvey\altaffilmark{1,7},
        Erik Rosolowsky\altaffilmark{8},
%        Wayne Schlingman\altaffilmark{9},
%        Yancy Shirley\altaffilmark{9},
        Guy S. Stringfellow\altaffilmark{\casa},
        Josh Walawender\altaffilmark{10}, and 
        Jonathan Williams\altaffilmark{11}
}

%\author{James Aguirre\altaffilmark{\penn},
%  Adam Ginsburg\altaffilmark{\casa},
%  John Bally\altaffilmark{\casa},

%  Meredith Drosback\altaffilmark{\virginia},
%  Neal J. Evans\altaffilmark{\utexas},
%  Jason Glenn\altaffilmark{\casa},
%  Miranda Nordhaus\altaffilmark{\utexas},
%  Erik Rosolowsky\altaffilmark{\ubc},
%  Josh Walawender\altaffilmark{\virginia},
%  Jonathan Williams\altaffilmark{\virginia}
%}

\email{jaguirre@sas.upenn.edu}

\altaffiltext{\penn}{University of Pennsylvania, Philadelphia, PA 19104}
%Jansky Fellow, National Radio Astronomy Observatory} 
\altaffiltext{\casa}{CASA, University of Colorado, CB 389, Boulder, CO 80309}
\altaffiltext{\utexas}{Department of Astronomy, University of Texas, 
       1 University Station C1400, Austin, TX 78712}
\altaffiltext{4}{Caltech Submillimeter Observatory, Hilo, HI}
\altaffiltext{5}{Institute for Astronomy (IfA), University of Hawaii
640 N. Aohoku Pl., Hilo, HI 96720}

\begin{abstract}

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm
continuum survey of \bgpsarea\ square degrees of the Galactic Plane in
the 1st, 2nd, and 3rd quadrants.  The BGPS represents the first large
area, systematic survey of the Galactic Plane in the (sub)millimeter
continuum without pre-selected targets.  The survey has detected
\ncores\ cores to a limiting depth of between \bgpsdepthlow\ and
\bgpsdepthhigh\ mJy RMS.  This paper details the survey observations
and methods.  We treat carefully the comparison of the survey pointing
and flux calibration and and serves as a companion to the public data
release through NASA's Infrared Processing and Analysis Center (IPAC).
We anticipate that the BGPS will be useful as a finder chart for ALMA
and as a long-wavelength complement to {\em Herschel}-HiGAL.

\end{abstract}

\keywords{
ISM: - molecular clouds --
stars: formation -- high mass
millimeter continuum
}

%\include{bgps_methods_introduction}

\section{Introduction}

Millimeter-wavelength continuum surveys of the Galactic plane provide
the best way to identify high-column density cores and clumps where
planets, stars, and star clusters form.  Such data can locate and lead
to the measurement of the physical properties of cores un-biased by
selection effects such as the presence of embedded stars, star
clusters, infrared sources, masers, or radio continuum emission.
Galaxy-wide surveys are essential for measuring the impacts of the
environment on core properties and star formation activity.  Do core
properties vary with location in or out of spiral arms?  Do core
properties vary with Galactocentric distance?  Do they depend on the
level of nearby star formation activity?  Galactic plane surveys of
mm-wavelength dust continuum emission provide the most efficient tool
for the identification of potential or active sites of star formation,
including the rare objects where the most massive stars and cluster
are, or soon will be, forming.  Dust continuum surveys of the Galaxy
provide essential ``ground truth'' required for the analysis of distant
galaxies where where individual clouds and cores are not resolved and
only galaxy-wide average quantities can be measured.

The advent of focal plane arrays containing hundreds of individual
bolometers sensitive to millimeter and sub-millimeter (sub-mm)
radiation has enabled large-scale surveys of mm-wavelength continuum
emission from Galactic interstellar dust.  The 144 element Bolocam
focal plane array, mounted at the Cassegrain focus of the 10 meter
diameter sub-mm telescope at the Caltech Sub-millimeter Observatory
(CSO) was use to survey over \bgpsarea\ square degrees of the northern
Galactic plane at a wavelength of 1.1 mm in the dust-continuum.  The
Bolocam Galactic Plane Survey (BGPS) presented here has detected about
\ncores\ cores in the surveyed fields, providing an unbiased sample of
cores suitable for multi-wavelength and high-resolution studies with
existing telescopes and future facilities.  The core catalog is
described in a companion paper \citep{rosolowsky09}.

Dust continuum emission near a wavelength of 1 mm is the best tracer
of the material most directly associated with the formation of
planetary systems, stars, and star clusters
\citep{johnstone06}.  Galactic dust continuum radiation at
this wavelength is optically-thin almost everywhere, and at typical
dust temperatures of order 10 K or more, is observed on the
Rayleigh-Jeans tail of the Planck function.  Thus, the determination
of column densities is relatively straight forward if the dust
temperature is known.

A crucial step in the observational study of star and cluster
formation is identification and characterization of the cloud cores
which will soon form or are actively forming stars.  Massive stars and
clusters form from high-density cloud cores with very large column
densities and extinctions $A_V > $ 100.  Thus, such cloud cores are
best investigated at millimeter and sub-millimeter wavelengths.
However, the interpretation of various gas tracers that produce
emission lines in this portion of the spectrum is very difficult.
Although in principle, spectral lines provide excellent diagnostics of
line-of-sight motions, temperatures, and densities in a cloud,
variations in tracer abundances caused by depletions and complex
chemical processing, uncertainties in excitation conditions, and the
impacts of radiation fields and shocks make the derivation of column
densities, masses, and other physical properties of cloud cores very
difficult.  The continuum emission from warm dust provides a more
reliable tracer of the column densities and core masses.

The great advantage of continuum observations at 1.1mm is that the
mass column density does not depend strongly on the dust temperature
$T_d$ (varying only linearly unless $T_d$ is less than about 10 K) and
is independent of the gas volume density.  Using the same dust opacity
as \citet{enoch06} and \citet{young06}, and assuming a gas-to-dust
mass ratio $X$ of 100, the mass sensitivity can be written as
\begin{equation} 
\label{eq:Mass}
M_{gas}\approx
0.22\left( e^{12.9/T_d}-1 \right) \left({S_\nu\over 15\; {\rm mJy}} \right)
D^{2}_{kpc} \msol 
\end{equation}
where $D_{kpc}$ is the distance to the source in kpc.  (At $S_\nu =
15$~mJy this corresponds to an RMS extinction sensitivity of $A_V\sim
1$ mag, with the same $T_d$ dependence).  It is thus possible with a
wide area, relatively shallow 1.1~mm survey to provide an unmatched,
uniform inventory of massive star-forming and starless condensations.

A number of (sub)millimeter surveys of the Galactic Plane are ongoing
or planned.  The BGPS is the first.

The outline of the paper is as follows. Section \ref{sec:Observations}
describes the instrument and the observations.  Section
\ref{sec:FluxCalibration} describes the flux calibration and errors.
Section \ref{sec:Astrometry} describes the construction of an absolute
reference frame for the observations and verification against

%BGPS will identify regions of high-mass star and cluster formation
%throughout the Galaxy and sites of low-mass star formation within a
%few kpc of the Sun (Figure 1).  Their physical properties may then be
%constrained by comparison with data in other wavebands.  The
%distribution of these regions will be compared with other tracers of
%the interstellar medium (ISM) such as molecular clouds, supershells,
%HII regions, supernova remnants, and supershells.  The 1.1 mm data
%together with dust continuum maps at shorter wavelengths taken by us
%with SHARC~II or with other telescopes will constrain temperature and
%reveal what surrounding material may be feeding the formation of dense
%cores. Star formation efficiencies may be obtained by detailed
%comparison of the NIR-MIR observations of stars with the BGPS
%observations.  This will also constrain the extinction law and dust
%properties, essential to refining mass estimates.  By comparing the
%distribution of 1.1mm cores with HII regions, supernova remnants, and
%IR emission as seen by {\it Spitzer}, we will constrain the mode of
%core and star formation, i.e., is it predominantly triggered by
%advancing shock and ionization fronts, by converging flows in a
%turbulent medium, or by spontaneous gravitational collapse?  The
%former models predict a close correlation between fronts and cores
%while the latter predicts the correlation will be poor.

%\Figure{mass_limits}{The limiting gas mass of cores detectable
%with at a flux limit of 15 mJy RMS. Detection thresholds at 3 (dashed)
%and 5 (solid) $\sigma$ are shown for a range of dust temperatures.
%Dust temperatures $<20$~K are most interesting for this survey, since
%these are the sources most likely to be pre- or proto-stellar
%condensations.}{fig:mass_limits}{1.0}
%
\Figure{coverage_moll} {The coverage of the BGPS.  The background
greyscale is IRAS 100 \mum.  
%The Bolocam coverage is shown with white
%solid lines in the top two panels and black in the bottom three.
%Major regions of Galactic star formation are labeled.  The coverage of
%{\em Spitzer}-GLIMPSE \citep{benjamin03} and the FCRAO $^{13}$CO GRS
%\citep{jackson06} are shown.
}{fig:coverage}{1.0}

%\include{bgps_methods_observations}
\section{Observations}
\label{sec:Observations}

%\subsection{Instrument}

Bolocam\footnote{{\tt http://www.cso.caltech.edu/bolocam}} is the
facility 144-element bolometer array camera operating from the 10.4 m
dish of the Caltech Submillimeter Observatory (CSO) on the summit of
Mauna Kea.  We used the filter configuration with a bandcenter of
268~GHz (hereafter 1.1~mm) and fractional bandwidth $\Delta \nu/\nu =
0.17$.  The passband is constructed to exclude the $^{12}\mathrm{CO}(2
\to 1)$ emission line.  Figure \ref{fig:Passband} shows the passband.
We compute color corrections for sources of varying spectral index in
Appendix \ref{app:ColorCorrections}.

The array field-of-view is 7\arcmin.5, with individual detectors
having nearly Gaussian beams of \bcamfwhm\ FWHM.  The spacing of the
pixels at 1.1 mm is 1.6$f\lambda$, so the focal plane is not
instantaneously sampled.  The Bolocam instrument is described in greater
detail in \citet{haig04} and \citet{glenn03}.

%\subsection{Observations}

The observations described here were acquired during six separate
observing sessions at the CSO over the course of two years.  The
observing epochs are given in Table \ref{tab:Observing}, along with
corresponding ranges for the zenith opacity $\tau_{225}$ of the CSO
tipper tau.  Because of the CSO weather multiplexing policy, Bolocam
observations were typically scheduled when $\tau_{225} > 0.06$.
Between each observing epoch, Bolocam was removed from its mount at
the re-imaged Cassegrain focus and stored warm.  Thus the flux
calibration and pointing model must be re-computed for each epoch to
allow for changes in the instrument and optics.

%\subsection{Observing Strategy}

% xraster 120 11280 23 /step_size=162 /equatorial /position_angle=36.753118 /alternate_direction /rot /settling_time = 03

Our basic observing strategy was to raster scan Bolocam by moving the
primary mirror of the CSO to modulate the astrophysical signal faster
than fluctuations in atmospheric opacity.  Each field was scanned with
alternating raster scans along $l$ and $b$.  Starting with Epoch III,
the fundamental scan unit was a $3\arcdeg \times 1\arcdeg$ block.
Each block was scanned with 23 scans along lines of constant $b$, and
67 scans along lines of constant $l$.  In both cases, the spacing
between adjacent rasters was 162\arcsec.  The total time for such a
scan was between 39 and 48 minutes.  In order to fill in the
instanteously undersampled focal plane, we began using in Epoch II a
field rotator to mechanically align the focal plane at an optimal
orientation along the scan direction to improve the sampling
orthogonal to the scan direction.  This is shown in Figure
\ref{fig:Array}.  The data were electronically sampled at 10 Hz along
the scan direction, slightly higher than the Nyquist rate for the scan
speed of 120\arcsec\ s$^{-1}$.  
%CHECK
Without the field rotator, the coverage shows variations of 100\% from
pixel to pixel in a single raster of a field.  With the rotator

The resulting coverage using the
above scan pattern and the field rotator, is typically uniform to
% per Adam, 2009/3/26

 with only a single pass across the field.

% FIGURES AND TABLES

\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright
molecular emission lines are shown at their rest frequencies.  Note
that the Bolocam passband rejects $>90\%$ of the $^{12}$CO flux, leaving our
continuum measurements largely uncontaminated.  SO and CH3OH lines are probably
the dominant contributors to line flux in the passband.  \citet{nummelin1998}
found that 22\% of the  flux in one pointing towards Sgr B2 was from lines, and
\citet{yoshida2005} reported >40\% in Orion A from line emission}
{fig:Passband}{1.0}

\Table
{llll}
{Observing Epochs for the BGPS}
{Begin (UT) & End (UT) & Nights & $\tau_{225}$ }
{tab:Observing}
{
2005 Jul 03 & 2005 Jul 13 & 5 & 0.1 \\
2005 Sep 04 & 2005 Sep 12 & 5 & 0.1 \\
2006 Jul 01 & 2006 Jul 13 & 5 & 0.1 \\
2006 Sep 01 & 2006 Sep 09 & 5 & 0.1 \\
2007 Jul 01 & 2007 Jul 13 & 5 & 0.1 \\
2007 Sep 01 & 2007 Sep 09 & 5 & 0.1 \\
}

\Figure{scan_10deg}{The effect of field rotation on the coverage
obtained via Bolocam raster scans.  (could also use this figure to
show the distortion map)}{fig:Array}{1.0}

%\begin{sidewaysfigure}[h]
\begin{center}
  \begin{figure}[t]
%    \includegraphics[width=6in,height=9.5in]{fig1_pg1_bw_inv_bar_label} 
    \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
    \caption{$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
      sources, e.g. Sgr B2, Sgr A, and sources near $l=10$ and
      $l=13$, appear to be saturated, but this is only a display
      artifact.  The noise is more pronounced from $l=-7$ to $l=-2$
      because this region was observed less.}
    \label{fig:galplane_p1}
  \end{figure}
    %\end{sidewaysfigure}

    %\begin{sidewaysfigure}[h]
  \begin{figure} 
%    \includegraphics[width=6in,height=9.5in]{fig1_pg2_bw_inv_bar_label} 
    \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
    \caption{$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
      51, W 43, W 49, and M 17 appear to be saturated, but this is
      only a display artifact}
    \label{fig:galplane_p2}
    %\end{sidewaysfigure}
  \end{figure}
\end{center}

%\begin{sidewaysfigure}[h]
%\begin{center}
%\includegraphics[scale=0.5]{bgps_montage}
%\end{center}
%\caption{ The coverage of the Bolocam Northern Galactic Plane Survey.
%as of September 2007.  The negative greyscale is the IRAS 100 \mum\
%survey.  Dashed lines indicate coverage between 15 and 100 mJy RMS;
%solid lines indicate areas covered more deeply than 30 mJy RMS.}
%\label{fig:coverage_sep06}
%\end{sidewaysfigure}

%\include{bgps_methods_flux_calibration}
\section{Flux Density and Surface Brightness Calibration}

The absolute flux calibration is obtained from observations of Mars,
Uranus and Neptune (the ``primary calibrators'').  The millimeter-wave
flux of these planets is known to $\sim 5\%$
\citep{orton86,griffin93}.  Calibrations at (sub)millimeter
wavelengths are strongly affected by atmospheric opacity corrections.
Further, the detector responsivity of Bolocam's bolometers is a
non-linear function of the mean atmospheric loading.

To relate observations of the primary calibrators to observations of
the BGPS fields, we make use of the following relation.  The
calibration ${\cal S}$, referred to the detectors, is given by
\begin{equation}
\label{eq:Calibration}
{\cal S} \, \left[\mathrm{\frac{V}{Jy}}\right] = 
S(\tau) \eta A \exp{(-\tau)} \Delta\nu
\end{equation}
where $S$ is the bolometer responsivity ([V/W]), $\eta$ is the system
optical efficiency, $A$ is the effective telescope collecting area,
$\Delta \nu$ is the bandwidth, and $\tau$ is the line-of-sight,
in-band atmosphere opacity.  Under the assumption that the only power
variation on the detectors is due to the power from the atmosphere,
which may be parameterized by $\tau$, ${\cal S}$ is a single-valued
function of $\tau$.  We have used the mean bolometer resistance as a
proxy for $\tau$, since the bolometer resistance is a single-valued
function of loading.  {\it This quantity is monitored continuously for
all observations.}  Note that this calibration curve folds in both the
effects of changing atmospheric transmission, as well as changes in
the detector response with optical loading.

%Multiple observations of secondary calibrators suffice to give the
%shape of the curve.  To reference it to the absolute calibrators, the
%fluxes of the planets were held fixed and the fluxes of the secondary
%calibrators allowed to float to produce the best agreement with a
%second-order polynomial for all sources.  The values for the secondary
%calibrators agree well with previously obtained Bolocam values and
%with values in the literature \citep{sandell94,jenness02}.  
%%A fit of Equation \ref{eq:Calibration} 
%

A fit to the observed values for the primary calibrators was performed
for the each epoch separately.
%CHECK
The agreement between epochs was good, so a single combined
calibration was used for all data here.
%We have found that the calibration can differ
%between successive cooldowns of the instrument by $\sim10\%$ \Check\
%but is generally stable over the period of order a month which
%constitutes each of the observing epochs.  
The calibration curve is shown in Figure \ref{fig:Calibration}.  The
resulting error on the calibration curve fit is less than 
%CHECK
$5\%$ (statistical) over the observed range of $\tau$.  A tally of all
contributions to the flux density error is given in Table
\ref{tab:ErrorBudget}.

The above flux density calibration only accounts for the average
calibration of bolometer Volts to Janskys.  It is also necessary to
account for the variation of bolometer response across the focal
plane.  We do this by monitoring the response to the atmosphere
emission in all bolometers.  Since the atmosphere is common to all
detectors, any changes in response are due to the intrinsic properties
of the detectors.  The change in relative response with loading for a
typical detector is shown in Figure \ref{fig:Flatfield}.  The method
is discussed further in Section \ref{sec:Mapping}

The instrument beam size (PSF) is measured using the planets Uranus
and Neptune which are nearly point sources for Bolocam.
% For

%The semi-diameter of
%Mars over this period ranged from 2.3\arcsec\ to 2.9\arcsec, with
%Neptune $\sim1.1\arcsec$.  Relative to the \bcamfwhm~FWHM Bolocam
%beam, these may be regarded as point sources; the finite size of Mars
%results in a $< 1.5\%$ correction of the observed flux.
The beam area is that averaged over all detectors, and is ?$1.71\times10^{-6}$\TBD\ ($35.6$\farcs)
steradians.  This allows conversion of the maps, calibrated in Jy
beam$^{-1}$, into surface brightness (MJy sr$^{-1}$).  The uncertainty
in the beam size is ?$.7\%$\TBD\  (number quoted is the uncertainty in the 
mean beam size), leading to an uncertainty in the surface
brightness calibration of \TBD.

\subsection{Comparison to Other Surveys}

Comparison of the accuracy of the Bolocam flux density calibration
with the SCUBA 850 \mum\ results is complicated by the unknown effect
of the dust spectral index.  However, there are several large-area
surveys with the MAMBO instrument at 1.2 mm with which we can compare.
For example, there is \citet{motte07}.

\Figure{fluxcal_errorbars}
%{calibration_plot_2004}
{Average calibration curve [V/Jy] versus the mean detector voltage, a
proxy for atmospheric loading.}{fig:Calibration}{1.0}

\Figure{rel_flux_cal_050303_ob3_to_050405_o66}{Scaling of the
relative calibration with atmospheric loading for bolocam
143. {\em To be replaced with new figure}}{fig:Flatfield}{1.0}

\Figure{relsens_cal}{Relative sensitivity calibration.  Black is the median over
all bolometers, red and green are individual bolometers. a. before
b. after}{fig:relsens_cal}{1.0}

\begin{deluxetable}{lc}
\tablewidth{0pt}
\tablecaption{Flux density error budget}
\tablehead{
\colhead{Source} & \colhead{Contribution}
}
\startdata
\label{tab:ErrorBudget}
Pointing error uncertainty & 2\% \\
Calibration curve (Eq. \ref{eq:Calibration}) uncertainty & $<5\%$ \\  % formal statistical error is probably less than real effect...?
PCA flux reduction uncertainty & 4\% \\   % is this an uncertainty?  Or systematic loss?
Absolute Mars flux uncertainty &  5\% \\
Beam size uncertainty (surface brightness) & X\% \\
\hline
Total & 7\% (random) + 5\% (systematic)
\enddata
\end{deluxetable}

\section{Astrometry}

\subsection{Absolute Reference Sources and Pointing Model}

We constructed an absolute reference system for the BGPS by observing
bright quasars and blazars near the Galactic Plane.

The distribution of sources over the sky is shown in Figure \ref{fig:astrometry}

Pointing observations were performed approximately once every two
hours over the night.  These sources were then mapped in alt/az
coordinates relative to the nominal telescope boresight.  The
elevation offsets showed a deviation from zero which was empirically
well-modeled by a quadratic function of elevation and a linear
function of azimuth.  No systematic deviation was observed for the
azimuth offsets.

Because the Galactic Plane appears over much of the sky, the pointing
model necessarily encompasses a large range of elevation and azimuth.
Nevertheless, an RMS scatter of $\sim 6\arcsec$ for the model over the
entire observed range was achieved, with the scatter somewhat worse at
the highest ZA.  A separate model was constructed for each epoch.  The
residuals are nearly Gaussian, with an RMS of $\sim6\arcsec$.

Further details of the pointing calculation are given in Appendix
\ref{sec:PointingCalculation}.

\subsection{Pixel Positions in the FOV}

In addition to the model for the pointing center, it is necessary to
empirically determine actual projected pattern of the array on the
sky, and measure the offset angle between the focal plane and the sky
coordinate system.  This is done by making observations which track
all detectors across a bright source (a planet) and making maps from each
bolometer individually.

A mean focus offset for the secondary is determined once per observing
run.  An elevation-dependent correction is applied via a
CSO-determined look-up table between raster scans.  We do not see any
evidence that more frequent focus checks improve the quality of the
PSF.

\subsection{Relative Alignment and Mosaicing}

Relative alignment was performed by finding the peak of the
cross-correlation between images and a pointing master selected from
the epoch with the best-constrained pointing model for that
field. Each observation was initially mapped individually, then all
observations of a given field were cross-correlated with a selected
master image of that field. The cross-correlation peak was fit with a
gaussian and the difference between the gaussian peak and the image
center was used as the pixel offset. The offsets were recorded and
written to the timestreams. Finally, all observations of a field were
merged into a single timestream with pointing offsets applied to
create the field mosaic.

This method of alignment avoids the ambiguities inherent in using
extracted sources to align fields, as the Bolocam sources are rarely
point-like.  It further avoids the pointing smearing and loss of peak
flux density which would result if the the maps were coadded using the
pointing model alone.

TBD: In low s/n fields, specifically l=65 to 75, there was not enough signal to
acquire a pointing offset using cross-correlation.  In these fields the
relative pointing offset is larger and the beam is slightly larger.

{\em Show a cross-correlation map?}

\subsection{Comparison to SCUBA and SHARC-II Positions}

The same cross-correlation procedure was used to compare to SCUBA maps where
available.  The morphological correlation between SCUBA and BGPS sources is
excellent, so cross-correlation maps could be used to test our pointing model.

{\em Miranda's data here}

\Figure{plane_astrometry}{The distribution of absolute reference
sources (crosses) and in-plane millimeter sources (x's) in the
Galactic Plane.}{fig:astrometry}{1.0}

\Figure{pointing_model}{The pointing model correction (left) and
residuals (right) for Epoch V, from which the master reference images
were derived for subsequent alignment. {\em To be replaced with newer
figure?}}{fig:PointingModel}{1.0}

\Figure{pointing_model_residuals}{The residuals of the pointing
model.  Note the Gaussian distribution.}{fig:PointingModelResiduals}{1.0}

\Figure{pointing_model_skydist}{The distribution of the PCAL
sources across the local sky in Hawaii.  Notice the good sampling of
the entire region used for the Survey.}{fig:PCALSkydist}{1.0}

\section{Mapping Algorithm}
\label{sec:Mapping}

The essential signal-processing problem to be solved by the mapping
algorithm is the estimation and removal of a signal due to fluctuating
atmosphere emission which is $>\sim$100's of times stronger than the typical
sources in our maps.  We implement an iterative procedure for
estimating both the atmosphere fluctuations and the astrophysical
signal without {\it a priori} knowledge of either.

We assume the raw timestream data $d$ for each bolometer (indexed by
$i$) can be written as
\begin{equation}
d_i(t) = s_i(t)+a_i(t)+e_i(t)+\epsi_i(t)
\end{equation}
where $s$ is the astrophysical signal, $a$ is atmospheric fluctuation
noise, $e$ are non-random signals due to the instrument itself, and
$\epsi$ is irreducible Gaussian noise due to photon shot and detector
noise.  The process of making a maximum likelihood map in the presence
of Gaussian noise is well-understood, and if the only contributions to
the data were $s$ and $\epsi$, then the minimum variance estimator of
the true astrophysical map is given by
\begin{equation}
\label{eq:LSMap}
m = (A^T W A) A^T W d
\end{equation}
where $A$ encodes the pointing information and $W$ is the covariance
matrix of the noise $\epsi$.  Note that the mapping from data to map
is a linear operator, $M =(A^T W A) A^T W$.  For compactness, Equation
\ref{eq:LSMap} will be written as $M[d] = m$.  Note that the mapping
operation is not invertible.  However, note that given a map $m$,
there exists a linear operation which makes predictions about the
observed timestreams, namely $d = A m$; this will be denoted $T[m] =
d$.

The goal is to produce a time series for each bolometer which as
closely as possible approximates $s + \epsi$ so that we may produce
the best estimate of the astrophysical signal $m = M[s+\epsi] = S + N$.

We proceed iteratively as follows. 
\begin{equation}
\label{eq:FirstIterStep}
\tilde{a}^{(n)}(t) = 
\sum_i{d_i(t)-\tilde{s}^{(n)}_i(t) - \tilde{e}^{(n)}_i(t)}
\end{equation}
where $\tilde{s}^{(0)}_i(t)=0$.  This mean atmosphere model is then
fit to each bolometer to obtain the relative gains (flat field) of the
detectors
\begin{equation}
\tilde{a}^{(n)}_i(t) = \frac{d_i(t) \cdot a(t)}{d_i(t)^2} a(t) = r_i a(t)
\end{equation}
The instrument errors, which are typically smaller than the
atmosphere, are then estimated
\begin{equation}
\tilde{e}^{(n)}_i(t) = some models
\end{equation}
and both the atmosphere and instrument models are subtracted from the
raw time series
\begin{equation}
d_i(t) - \tilde{a}^{(n)}_i(t) - \tilde{e}^{(n)}_i(t)
\approx s_i(t) + \epsi_i(t)
\end{equation}
This is the best estimate of signal plus irreducible noise at
iteration step $n$, and is made into a map
\begin{equation}
M[d_i(t) - \tilde{a}^{(n)}_i(t) - \tilde{e}^{(n)}_i(t)] = \tilde{m}^{(n)}
\end{equation}
The current best map $\tilde{m}^{(n)}$ is then deconvolved to provide
a relatively low-noise, smooth map from which to generate a timestream
\begin{equation}
T[{\cal D}[\tilde{m}^{(n)}]] = \tilde{s}^{(n)}_i(t)
\end{equation}
We note that it is possible to produce an ``error map''
\begin{equation}
N = M[d_i(t) - \tilde{s}^{(n)}_i(t) - \tilde{a}^{(n)}_i(t) - 
\tilde{e}^{(n)}_i(t)]
\end{equation}
The process then begins again with Equation \ref{eq:FirstIterStep}.

%\Figure{eachpca}{The effect of the number of iterations on
%the reduction process.}{fig:Iter}{1.0}

\subsection{Atmosphere Fluctuation Noise Model}

The simplest model for the atmosphere fluctations makes use of the
fact that the beams for all of the detectors pass through a nearly
identical atmosphere, thus implying that atmosphere fluctuations will
be highly correlated between detectors.

\subsection{Instrument Error Signals}

Most of the instrument error signals have characteristic features
which allow them to be identified, though not always removed.  The
error signals include the following:
\begin{enumerate}

\item Pickup from the 60 Hz AC power.  This appears as narrow lines in
the PSD of the data.  The second harmonic of 60 Hz is aliased via
beating against the 130 Hz bolometer bias frequency into 10 Hz with
sidebands split at $\sim1$ Hz.

\item Spikes in voltage due to cosmic ray strikes on the bolometers
(``glitches'').

\item Microphonic pickup due to vibrations of the receiver.  The most
noticeable microphonics occur at the end of each scan when the
telescope is turning around and the field rotator is adjusting.  This
leads to broad spikes in the time series, whose long decay must be
removed from the data, particularly during the beginnings of scans.

%\item Others?

\end{enumerate}

Fortunately, most of the AC powerline pick-up occurs at frequencies
where there is no astrophysical signal, given the beam size and scan
speed.  Thus this error is dealt with by first notch filtering at the
line frequencies and then low-pass filtering the data.  Because of the
low correlation with astrophysical signal, this step is performed only
once and is not iterated.

Both glitches and microphonic pickup from the scan turnarounds are
degenerate with astrophysical signal and must be estimated as part of
the iterative process.  Glitches are identified as large excursions
from the RMS level after subtraction of the best atmosphere and bright
source model, and the data there is excluded from inclusion in
subsequent maps.  The turnaround microphonics are modeled as decaying
exponentials at the beginnings and ends of scans.

\Figure{flagger_plots}{An illustration of a ``glitch'' in a single
bolometer timestream due to a cosmic ray strike.  Note the acausal
ringing due to the application of the downsampling filter.  The time
series for a physically adjacent bolometer is shown in red.  The high
level of correlation due to atmospheric fluctuations is readily
apparent, as well as the lack of correlation due to the
glitch.}{fig:CosmicRayGlitch}{1.0}

\Figure{crs}{The distribution of glitch amplitudes flagged and
removed from the data.  The expected contribution to the noise from
the unremoved glitches below the detection threshold is
\TBD.}{fig:GlitchDistribution}{1.0}

\subsection{Data Flagging}

Due to the large volume of data generated by the survey, it was
necessary to develop new tools to quickly visualize the data and
ensure data quality.  We used a ``waterfall''

\Figure{flagger_withglitch}{An illustration of the flagging process using the
waterfall plot.  In this image, an anomaly which affects all
bolometers for a brief period of time is evident near the top of the
image.}{fig:Flag1}{1.0}

\Figure{flagger_glitchboxflagged}{A box is drawn around the bad data and it is
removed from subsequent analysis.}{fig:Flag2}{1.0}

\Figure{flagger_glitchgone}{A rescaled version of the data with the bad data
removed.}{fig:Flag3}{1.0}

An automated flagger was also created that flags out outlier data on a per-pixel
basis.  In order to make a robust measurement of the variance of the fluxes
assigned to each pixel, we used the median average deviation over the data in
the pixel and rejected high and low outliers at the 3-sigma level.  Pixels with
too little data to compute a deviation, i.e. those with $<3$ data points, were
also flagged out - these scan-edge pixels are the dominant contribution to the
total number of flagged data points.

\subsection{Creation of the Astrophysical Model}

WRITTEN POORLY: 
The timestream data is made into a spatial map using the pointing data 
corresponding to each time point for each bolometer.  The data is weighted
by inverse variance across a single scan and then drizzled into a map with
$7.2$\farcs pixels using a nearest-neighbor algorithm.  The nearest-neighbor
matching allows the map to be returned to a timestream in the same manner, 
but with the S/N improved by averaging over all hits on a given pixel.

%\Figure{l001_deconvolutionkernelcompare}{The effect of
%deconvolution on the iterative process can be seen in its effect on
%the residuals. From left to right: map, noise, smoothmap, model. Top
%to bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
%7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which
%has the result of leaving no flux in the residual at the location of
%Sgr B2, and does not ``dig a hole'' in the residual map, as the
%7.2\arcsec\ kernel does.}{fig:Deconvolution}{1.0}

\section{Noise and Systematic Effects}
\label{sec:Noise}

The error maps produced by the iterative mapping provide a natural way
of estimating the systematic error resulting from imperfect
subtraction of bright sources.  This results in ``ghosts'' of the
bright sources in the error maps $E$.

% this is not true.  I can't do jackknifing....
% To estimate the size of this
% residual error, we also construct jackknife maps for each field, in
% which the astrophysical signal is made to exactly cancel.  This
% provides an estimate of the noise-only RMS in the maps, to which
% deviations from the ``ghosts'' may be compared.

The noise is correlated between adjacent pixels.

The final per-pixel error estimate is given as ...

Because observing conditions varied widely during the survey, the RMS
noise levels obtained in the various fields of the BGPS also varies.

\Figure{survey_depth}{The depth of the BGPS in the first quadrant
as a function of Galactic longitude.  Black is the standard deviation
of $0.9\arcdeg \times 0.9\arcdeg$ degree blocks centered on $b=0$ and
the longitude indicated; red is similar, but the estimator is
median(1/sqrt(weight map).}{fig:Depth}{1.0}

The depth can be converted into an estimate of mass via standard
estimates.

\section{Photometry}

To do accurate and meaningful photometry on the Bolocam maps requires
a good estimate of the noise (Section \ref{sec:Noise}) but also an
understanding of the spatial filtering imposed by the observing
strategy and the cleaning and mapping of the data.

The Bolocam maps produced are the convolution of the (nearly Gaussian)
primary beam $G(\xad)$, together with an effective high-pass
spatial filter $F(\xad)$,
\[
M'(\xad) = (G(\xad) \otimes F(\xad)) \otimes M(\xad)
\]
The effect of the high pass filter is that the effective PSF $B=G
\otimes F$ has the non-intuitive property that its area is {\em zero}:
\[
\int{B(\Omega) d\Omega} = 0
\]
Clearly, this complicates the definition of surface brightness, and
also imposes a limit on the size of features for which photometry may
be meaningfully performed.

\Figure{aper_phot_hpf_beam}{The effect of performing aperture
photometry on a point source of unit flux observed with the effective
Bolocam PSF $B$.  The black curve shows the area (measured in pixels)
as a function of the aperture radius for the filter measured via
simulation.  This is compared to the equivalent case for a Gaussian
beam (green).  The vertical lines show radii of $n/2 \times FWHM$ for
$n=1,2,3$.  One can see that the Gaussian beam has nearly reached a
constant area of $2 \pi \sigma^2$ by a radius of $3/2 \times FWHM$, at
which point any larger aperture would recover the full flux of the
source.  The actual Bolocam beam reaches its maximum effective area
sooner, and then drops precipitously as the size of the aperture is
increased.  }{fig:ESF}{1.0}

%\Figure{esf}{The effective spatial filter applied to the Bolocam
%maps due to atmospheric cleaning.}{fig:ESF}{1.0}

\clearpage

\Figure{pca_comparison}{The fractional flux lost as a function of
source size for well-separated Gaussian sources with the FWHM as
indicated. Legend: number of PCA components }{fig:PCA_filter}{1.0}

\clearpage

\Figure{deconvolution_comparison}{The fractional flux lost as a function of
source size for well-separated Gaussian sources with the FWHM as
indicated.  Legend: Size of deconvolution kernel used to make model }{fig:deconv_filter}{1.0}

\section{Final Maps}

The final maps are produced by coadding all observations of a single
square degree centered on a particular Galactic coordinate
$(l_0,b_0)$.  The maps are made in Galactic coordinates using a plate
carr\'{e} (FITS header CAR) projection.  As these maps are near the
coordinate system equator, the difference between truly equiareal
pixels and the pixels used is at most X\%.  The pixel size is
7.2\arcsec, chosen to be much smaller than the Bolocam beam, and
producing data squares 500 pixels on a side.

Noise maps are produced for each map, containing ...

\section{Public Data Release}

All processed maps are made available through
IPAC\footnote{http://irsa.ipac.caltech.edu/Missions/bolocam.html}.

%\citet{moore07}
%\citet{zinchenko97}

\section{Summary}

% first millimeter....
The BGPS is the first (sub)millimeter survey of a substantial fraction
of the Galactic Plane, providing an unbiased look at the high-density
gas most intimately associated with the earliest phases of star
formation.

\acknowledgments

We would like to acknowledge the staff and day crew of the CSO for their
assistance. The BGPS project is supported by the National Science Foundation
through NSF grant AST-0708403. J.A. was supported by a Jansky Fellowship from
the National Radio Astronomy Observatory (NRAO). The first observing runs for
BGPS were supported by travel funds provided by NRAO. Support for the
development of Bolocam was provided by NSF grants AST-9980846 and AST-0206158.
Team support was provided in part by NSF grant AST-0607793 to the
University of Texas at Austin.

We recognize and acknowledge the cultural role and reverence that the
summit of Mauna Kea has within the Hawaiian community. We are
fortunate to conduct observations from this mountain.

{\it Facilities:} \facility{CSO (Bolocam)}

\appendix

\section{Pointing Calculation}
\label{sec:PointingCalculation}

To calculate the position at which to point the telescope, the CSO
antenna computer computes an alt/az derived from the RA/Dec J2000
(heliocentric) catalog position.  It performs the following
calculation:

\begin{enumerate}

\item Precess catalog coordinates to current epoch.  The CSO by
default stores catalog positions in B1950.

\item Add aberration and nutation corrections.  This is the
``requested apparent'' RA and Dec reported by the antenna computer.

\item The equatorial coordinates are transformed to horizon
coordinates using the current local apparent sidereal time.

\item A 11-term model (``$C$-terms'') based on the optical pointing of
the telescope is then applied to $A$ and $Z$ along with $t$-terms (?),
the tilt of the alidade, and a refraction correction to obtain the
necessary mechanical pointing of the telescope to acquire the source.

\item The telescope then attempts to follow this track; the difference
between the requested $A$,$Z$ and the actual, measured angles of the
encoders (a result of servo errors) are also reported.

% are c4 and c5 different from the alidade_x,y tilt that are in the RPC file?

%char	32   pointing_file_name
%double	11   pointing_constant
%double	6    t_term_constant
%double	1    alidade_x_tilt
%double	1    alidade_y_tilt
%double	1    azimuth_t_term_offset
%double	1    elevation_t_term_offset
%double	1    tropospheric_refraction

\end{enumerate}

The CSO antenna computer reports this pointing information, including
geocentric RA/Dec, at a rate of 100 Hz.  This time series, along with
the field rotator encoder information from Bolocam is merged with the
bolometer time series and aligned.

To calculate the pointing used in the map from the telescope inputs,
the Bolocam software does the following:

\begin{enumerate}

\item Start with the reported $\alpha',\delta'$ from the CSO.  Remove
aberration and nutation corrections.  Precess from current epoch to
J2000.  This gives $\alpha,\delta$.

\item Apply the $\Delta A,\Delta E$ terms to $\alpha,\delta$ to
account for the difference between commanded and actual positions of
the telescope.

\end{enumerate}

After this is done, the remaining

\section{Table of Absolute and In-Plane Pointing Sources}

\Table
{llrrrrc}
{Absolute Pointing Calibrators}
{Number & Alias & RA(J2000) & Dec(J2000) & l & b  & Flux (Jy)}
{tab:PCAL}
{
         1 &   1622-253 & 16 25 46.9 & -25 27 38.3 & 352.14 &  16.32 &  0.18 \\
         2 & 16293-2422 & 16 32 22.9 & -24 28 35.6 & 353.94 &  15.84 &  8.40 \\
         3 &   1657-261 & 17 00 53.2 & -26 10 51.7 & 356.70 &   9.75 &  0.07 \\
         4 &   NGC6334I & 17 20 53.4 & -35 47  1.7 & 351.42 &   0.64 &  2.50 \\
         5 &    NRAO530 & 17 33 02.7 & -13 04 49.5 &  12.03 &  10.81 &  2.70 \\
         6 &   1741-038 & 17 43 58.8 &  -3 50  4.6 &  21.59 &  13.13 &  1.44 \\
         7 &   1749+096 & 17 51 32.8 &   9 39  0.7 &  34.92 &  17.65 &  2.70 \\
         8 &      G5.89 & 18 00 30.4 & -24 04  0.5 &   5.89 &  -0.39 &  3.57 \\
         9 &        M8E & 18 04 53.0 & -24 26 39.4 &   6.05 &  -1.45 &  3.92 \\
        10 &     G10.62 & 18 10 28.7 & -19 55 49.8 &  10.62 &  -0.38 & 17.20 \\
        11 &   1830-211 & 18 33 39.9 & -21 03 40.0 &  12.17 &  -5.71 &  1.70 \\
        12 &      G34.3 & 18 53 18.6 &   1 14 58.3 &  34.26 &   0.15 & 31.30 \\
        13 &   1908-202 & 19 11 09.6 & -20 06 55.0 &  16.87 & -13.22 &  1.00 \\
        14 &      G45.1 & 19 13 22.1 &  10 50 53.4 &  45.07 &   0.13 &  3.70 \\
        15 &      OV236 & 19 24 51.0 & -29 14 29.8 &   9.34 & -19.61 &  8.60 \\
        16 &   1923+210 & 19 25 59.6 &  21 06 26.1 &  55.56 &   2.26 &  0.32 \\
        17 &   1954+513 & 19 55 42.7 &  51 31 48.6 &  85.30 &  11.76 &  0.60 \\
        18 &       CYGA & 19 59 28.5 &  40 44  1.7 &  76.19 &   5.75 &  0.25 \\
        19 &      K3-50 & 20 01 45.7 &  33 32 43.5 &  70.29 &   1.60 &  8.45 \\
        20 &   2005+403 & 20 07 44.9 &  40 29 48.6 &  76.82 &   4.30 &  0.40 \\
        21 &        ON1 & 20 10 09.1 &  31 31 37.7 &  69.54 &  -0.98 &  2.90 \\
        22 &    2013+37 & 20 15 28.7 &  37 10 59.6 &  74.87 &   1.22 &  1.40 \\
        23 &   2021+317 & 20 23 19.0 &  31 53  2.4 &  71.40 &  -3.10 &  0.54 \\
        24 &   2023+336 & 20 25 10.8 &  33 43  0.3 &  73.13 &  -2.37 &  0.92 \\
        25 &     GL2591 & 20 29 24.7 &  40 11 18.9 &  78.89 &   0.71 &  2.07 \\
        26 &    MWC 349 & 20 32 45.5 &  40 39 36.7 &  79.64 &   0.47 &  1.67 \\
        27 &       W75N & 20 38 36.4 &  42 37 34.5 &  81.87 &   0.78 &  4.46 \\
        28 &      3C418 & 20 38 37.0 &  51 19 12.7 &  88.81 &   6.04 &  0.62 \\
        29 &   CRL 2688 & 21 02 18.8 &  36 41 37.7 &  80.17 &  -6.50 &  1.90 \\
        30 &    NGC7027 & 21 07 01.6 &  42 14 10.2 &  84.93 &  -3.50 &  9.27 \\
        31 &   2201+315 & 22 03 15.0 &  31 45 38.4 &  85.96 & -18.78 &  0.35 \\
}

\Table
{llrrrrc}
{In-plane Millimeter Sources}
{Number & Alias & RA(J2000) & Dec(J2000) & l & b  & Flux (mJy)}
{tab:PPS}
{
   l351pps &            & 17 23 50.2 & -36 38 58.8 & 351.04 &  -0.34 &  -999.0 \\
   l354pps &            & 18 00 50.0 & -23 20 33.0 &   6.55 &  -0.10 &  -999.0 \\
   l357pps &            & 17 40 57.3 & -31 10 48.0 & 357.56 &  -0.32 &  -999.0 \\
   l000pps &            & 17 46 37.1 & -29 10 21.5 & 359.91 &  -0.31 &  -999.0 \\
  l000pps2 &            & 17 47 10.3 & -28 46 11.8 &   0.32 &  -0.20 &  -999.0 \\
   l002pps &            & 17 50 36.3 & -27 06  2.8 &   2.14 &   0.01 &  -999.0 \\
   l006pps &            & 17 57 34.4 & -23 58 12.0 &   5.64 &   0.24 &   989.0 \\
   l009pps &            & 18 06 14.2 & -20 31 58.0 &   9.61 &   0.19 &  1187.0 \\
  l009pps2 &            & 18 06 15.5 & -20 32  8.0 &   9.61 &   0.19 &  1189.0 \\
   l012pps &            & 18 10 50.5 & -17 55 54.0 &  12.42 &   0.51 &  1205.0 \\
   l015pps &            & 18 14 35.3 & -16 45 45.0 &  13.87 &   0.28 &  1085.0 \\
  l015pps2 &            & 18 21 08.5 & -14 31 48.0 &  16.58 &  -0.05 &   748.0 \\
   l018pps &            & 18 25 42.0 & -13 10 13.0 &  18.30 &  -0.39 &  1544.0 \\
   l020pps &            & 18 28 09.9 & -11 28 47.0 &  20.08 &  -0.13 &  1650.0 \\
   l021pps &            & 18 30 34.0 &  -9 34 54.0 &  22.04 &   0.22 &   993.0 \\
   l023pps &            & 18 34 54.6 &  -8 49 18.0 &  23.20 &  -0.38 &  1681.0 \\
   l024pps &            & 18 36 05.1 &  -7 31 21.0 &  24.49 &  -0.04 &  1851.0 \\
   l025pps &            & 18 36 16.7 &  -6 43  8.7 &  25.23 &   0.29 &  -999.0 \\
   l026pps &            & 18 37 18.4 &  -6 38 38.4 &  25.41 &   0.10 &  -999.0 \\
  l026pps2 &            & 18 39 04.9 &  -6 24 23.6 &  25.82 &  -0.18 &  -999.0 \\
   l027pps &            & 18 41 51.1 &  -5 01 48.0 &  27.36 &  -0.17 &  3478.0 \\
   l028pps &            & 18 44 19.0 &  -4 40 52.0 &  27.95 &  -0.55 &  -999.0 \\
  l028pps2 &            & 18 42 51.8 &  -4 00  1.9 &  28.39 &   0.08 &  -999.0 \\
   l029pps &            & 18 42 15.6 &  -3 34 44.5 &  28.70 &   0.41 &  -999.0 \\
  l028pps2 &            & 18 42 50.8 &  -3 59 46.1 &  28.40 &   0.09 &  -999.0 \\
   l033pps &            & 18 52 25.1 &   0 14 53.0 &  33.26 &  -0.11 &  -999.0 \\
   l035pps &            & 18 53 39.1 &   1 50 32.0 &  34.82 &   0.35 &   756.0 \\
   l037pps &            & 18 59 10.0 &   4 12 10.0 &  37.55 &   0.20 &  1045.0 \\
   l038pps &            & 19 01 53.2 &   4 12 51.0 &  37.87 &  -0.40 &  1487.0 \\
   l040pps &            & 19 05 40.9 &   6 26  5.0 &  40.28 &  -0.22 &  1700.0 \\
   l042pps &            & 19 10 33.5 &   9 08  7.0 &  43.23 &  -0.05 &  1247.0 \\
   l044pps &            & 19 11 54.4 &   9 35 53.0 &  43.80 &  -0.13 &  1829.0 \\
  l044pps2 &            & 19 13 28.4 &  10 53 41.0 &  45.12 &   0.13 &  1999.0 \\
   l048pps &            & 19 23 10.8 &  14 26 31.0 &  49.37 &  -0.30 &  1903.0 \\
   l050pps &            & 19 23 11.1 &  14 26 34.0 &  49.37 &  -0.30 &  2088.0 \\
   l079pps &            & 20 29 25.3 &  40 11 28.0 &  78.89 &   0.71 &  1390.0 \\
   l079pps &            & 20 29 25.2 &  40 11 30.0 &  78.89 &   0.71 &  2014.0 \\
  l079pps2 &            & 20 31 13.3 &  40 03 33.0 &  78.99 &   0.35 &   790.0 \\
   l080pps &            & 20 34 42.8 &  39 44 45.0 &  79.13 &  -0.37 &  1104.0 \\
  l080pps2 &            & 20 40 05.3 &  41 31 48.0 &  81.17 &  -0.11 &   961.0 \\
   l080pps &            & 20 30 28.7 &  41 16  6.0 &  79.88 &   1.18 &  1024.0 \\
   l082pps &            & 20 40 26.8 &  41 56 54.0 &  81.54 &   0.10 &   805.0 \\
l110.5npps &            & 23 05 10.7 &  60 14 50.6 & 110.11 &   0.05 &  -999.0 \\
   l111pps &            & 23 15 31.5 &  61 07 39.7 & 111.62 &   0.38 &  -999.0 \\
    l134p1 &            & 02 29 02.8 &  61 33 31.2 & 134.28 &   0.86 &  -999.0 \\
  l134p1-2 &            & 02 27 06.9 &  61 52 20.8 & 133.95 &   1.07 &  -999.0 \\
  l134p1-3 &            & 02 27 02.4 &  61 52 32.9 & 133.94 &   1.07 &  -999.0 \\
    l135p1 &            & 02 34 45.1 &  61 46 23.0 & 134.83 &   1.31 &  -999.0 \\
   l136p15 &            & 02 50 08.4 &  61 59 56.7 & 136.38 &   2.27 &  -999.0 \\
   l137p15 &            & 02 29 03.2 &  60 43 26.9 & 134.59 &   0.08 &  -999.0 \\
    IC1396 &            & 21 40 11.5 &  58 16 11.7 &  99.93 &   4.21 &  -999.0 \\
  IC1396-2 &            & 21 36 36.8 &  57 30 50.0 &  99.07 &   3.97 &  -999.0 \\
  IC1396-3 &            & 21 35 38.4 &  57 26 40.5 &  98.93 &   4.00 &  -999.0 \\
   l189pps &            & 06 08 50.1 &  21 38 19.0 & 188.94 &   0.87 &  -999.0 \\
 l189pps-2 &            & 06 08 49.7 &  21 38  5.7 & 188.95 &   0.87 &  -999.0 \\
   l192pps &            & 06 12 51.5 &  18 00 39.3 & 192.58 &  -0.05 &  -999.0 \\
 l192pps-2 &            & 06 12 51.5 &  17 59 36.3 & 192.59 &  -0.05 &  -999.0 \\
 l192pps-3 &            & 06 12 50.1 &  18 00 35.8 & 192.58 &  -0.05 &  -999.0 \\
 l192pps-4 &            & 06 12 50.3 &  17 59 28.8 & 192.59 &  -0.06 &  -999.0 \\
 l192pps-5 &            & 06 07 43.9 &  20 39 29.6 & 189.67 &   0.17 &  -999.0 \\
}

\section{Calculation of Color Corrections}
\label{app:ColorCorrections}

If an experiment has finite bandwidth ($t(\nu) \ne \delta(\nu -
\nu_c)$), to report a source surface brightness at a single
frequency, one must assume a source spectrum.  The power detected from
that source is assumed to be
\begin{equation}
P_{in} = \eta \; A \Omega \; \int I_0(\nu) t(\nu) d \nu
\end{equation}
(Here $\eta$ and $A \Omega$ are the optical efficiency and throughput
of the instrument, $I_0(\nu)$ is the nominal (assumed) surface
brightness of the source, and $t(\nu)$ is the bandpass transmission
normalized to $1.0$ at its peak.)  The effective band center $\nu_c$
is usually chosen such that
\begin{equation}
I_0(\nu_c) \simeq \frac{\int I_0(\nu) t(\nu) d \nu}
{\int t(\nu) d \nu} 
\end{equation}
The band centers for TopHat are calculated assuming a Rayleigh-Jeans
(RJ) source spectrum
\begin{eqnarray}
I_0(\nu_c) & = & I_{RJ}(\nu_c) \\
\nonumber & = & \tau \; 2 k T \; \frac{\nu_c^2}{c^2},
\end{eqnarray}
where $\tau$ is the optical depth of the source and $k$ is Boltzmann's
constant.  Since the detected power is assumed to be
\begin{equation}
P_{in} = \eta \; A \Omega \; \int \tau \; 2 k T \; \frac{\nu^2}{c^2}
\; t(\nu) d \nu,
\end{equation}
we can write
\begin{equation}
I_0(\nu_c) = \frac{P_{in}}{\eta \; A \Omega \int \nu^2 \; t(\nu) d \nu} \; \nu_c^2
\end{equation}
Now if we assume a different source spectrum, for example a greybody
with power-law emissivity, the assumed input power is
\begin{eqnarray}
P_{in} & = & \eta \; A \Omega \; \int I_{GB}(\nu) t(\nu) d \nu \\
\nonumber & = & \eta \; A \Omega \; \int \tau(\nu_0) (\nu / \nu_0)^\alpha B_\nu(T) t(\nu) d \nu
\end{eqnarray}
and the source spectrum inferred from the detected power is
\begin{eqnarray}
I_{GB}(\nu_c) & = & \tau(\nu_0) (\nu_c / \nu_0)^\alpha B_{\nu_c}(T) \\
\nonumber & = & \frac{P_{in}}{\eta \; A \Omega \int \nu^\alpha B_\nu(T) t(\nu) d \nu} \; \nu_c^\alpha B_{\nu_c}(T) \\
\nonumber & = & \frac{\int \nu^2 t(\nu) d \nu}{\int \nu^\alpha B_\nu(T) t(\nu) d \nu} \; \nu_c^{\alpha-2} B_{\nu_c}(T) \; I_{RJ}(\nu_c) \\
\nonumber & \equiv & \frac{I_{RJ}(\nu_c)}{K}.
\end{eqnarray}
This defines the color correction $K$ to apply to the reported TopHat
flux from a source if the source is assumed to have a greybody
spectrum with power-law emissivity.

We make a similar calculation for DIRBE, for which the band centers are 
computed assuming a spectrum with $\nu I(\nu)$ constant.  In this case, 
the correction is given by 
\begin{eqnarray}
K &=& \frac{\nu_c^{-1}}{\int \nu^{-1} t(\nu) d \nu} \left[\frac{\tau(\nu_0) (\nu_c / \nu_0)^\alpha B_{\nu_c}(T)}{\int \tau(\nu_0) (\nu / \nu_0)^\alpha B_{\nu}(T) t(\nu) d \nu} \right]^{-1} \\
\nonumber &=& \frac{\int \nu^\alpha B_{\nu}(T) t(\nu) d \nu}{\int \nu^{-1} t(\nu) d \nu} \; \nu_c^{-(\alpha+1)} B_{\nu_c}(T)
\end{eqnarray}
For an arbitrary experiment with bandpass $t(\nu)$ that reports its
surface brightness measurements assuming a spectrum $I_0(\nu)$, the
surface brightness assuming a different source spectrum $I_1(\nu)$ is
given by
\begin{eqnarray}
I_1(\nu_c) &=& I_0(\nu_c) / K \\
\nonumber &=& I_0(\nu_c) \frac{I_1(\nu_c)}{\int I_1(\nu) t(\nu) d \nu} \left[\frac{I_0(\nu_c)}{\int I_0(\nu) t(\nu) d \nu} \right]^{-1}
\end{eqnarray}

\bibliography{milkyway}

\end{document}

### 2009-03-29 analysis/example_waterfalls.py
added pyflagger

@@ -8,6 +8,7 @@ f = pyflagger.Flagger('/usb/scratch1/super_gc/050703_o15_raw_ds5.nc_indiv13pca',
 f.plotscan(12)
 f.scannum = 12
 f.flags[f.scannum,:,:] -= (f.flags[f.scannum,:,:] > 0)
+ytitle()
 figure(1); savefig(figure_path+'flagger_withglitch.ps')
 
 f.flag_box(97,123,97,132,1)

### 2009-03-29 cleaning/flagging/pyflagger.py

@@ -1,0 +1,678 @@
+
+import math
+
+import pylab
+from pylab import *
+import matplotlib
+import pyfits
+from numpy import isnan
+from mad import MAD,nanmedian
+#from matplotlib import patches
+from matplotlib.patches import Rectangle,FancyArrow
+from matplotlib.lines import Line2D
+from matplotlib.widgets import Cursor, MultiCursor
+import matplotlib.cm as cm
+from Scientific.IO import NetCDF
+import time
+import re
+import os
+import copy
+
+
+matplotlib.defaultParams['image.origin']='lower'
+matplotlib.defaultParams['image.interpolation']='nearest'
+matplotlib.defaultParams['image.aspect']=.1
+
+class Flagger:
+  """
+  Write out a file with appropriate flagging commands for use in IDL / later editing
+  Example:
+
+      import pyflagger
+      f = pyflagger.Flagger('050906_o11_raw_ds5.nc')
+      f.plotscan(0)
+      f.close()
+  """
+
+  def __init__(self, filename, ncfilename='', flagfile='', mapnum='', axis=None):
+    fnsearch = re.compile(
+            '([0-9]{6}_o[0-9b][0-9]_raw_ds5.nc)(_indiv[0-9]{1,2}pca)(_MARS)?').search(filename)
+    ncsearch = re.compile(
+            '[0-9]{6}_o[0-9b][0-9]_raw_ds5.nc').search(ncfilename)
+    if fnsearch is None:
+        print "Couldn't find the correct prefix in the filename" \
+                +" - expected form like 050906_o11_raw_ds5.nc_indiv13pca_timestream00.fits"
+        return
+    mapnumsearch = re.compile('([0-9]{2})(\.fits)').search(filename)
+    if mapnumsearch is not None and mapnum=='':
+        mapnum = mapnumsearch.groups()[0]
+    elif mapnum=='':
+        mapnum = '01'
+
+    self.fileprefix = fnsearch.group()
+    self.pathprefix = filename[:fnsearch.start()]
+
+    if ncsearch is not None and fnsearch.groups()[0] == ncsearch.group():
+        self.ncfilename = ncfilename # self.pathprefix+fnsearch.groups()[0]
+        self.readncfile()
+    else:
+        print "Warning: the NCDF filename doesn't match the input fits file name."\
+                + "You'll probably get errors and your work won't be saved."
[…]

### 2009-03-29 analysis/example_waterfalls.py
pyflagger / example waterfalls updated

@@ -5,16 +5,15 @@ figure_path = '/home/milkyway/student/ginsbura/paper_figures/'
 
 f = pyflagger.Flagger('/usb/scratch1/super_gc/050703_o15_raw_ds5.nc_indiv13pca',mapnum='01',ncfilename='/scratch/sliced/l000/050703_o15_raw_ds5.nc')
 
-f.plotscan(12)
+f.plotscan(12,seconds=1)
 f.scannum = 12
 f.flags[f.scannum,:,:] -= (f.flags[f.scannum,:,:] > 0)
-ytitle()
 figure(1); savefig(figure_path+'flagger_withglitch.ps')
 
 f.flag_box(97,123,97,132,1)
 figure(1); savefig(figure_path+'flagger_glitchboxflagged.ps')
 
-f.plotscan(12)
+f.plotscan(12,seconds=1)
 figure(1); savefig(figure_path+'flagger_glitchgone.ps')
 
 figure(3)

### 2009-03-29 cleaning/flagging/pyflagger.py

@@ -193,7 +193,7 @@ class Flagger:
         self.flags = reshape(ft[:,self.bolo_indices],[self.nscans,self.scanlen,self.ngoodbolos])
 
 
-  def plotscan(self, scannum, fignum=1, button=1):
+  def plotscan(self, scannum, fignum=1, button=1, seconds=0):
     if self.connected:
         self.dcon()
     self.connected = 1
@@ -204,15 +204,25 @@ class Flagger:
     clf()
     #subplot(122)
     title("Flags for Scan "+str(self.scannum)+" in "+self.ncfilename);
-    xlabel('Bolometer number'); ylabel('Time (.02s)')
+    if seconds:
+        aspect_mult = 20
+        extent = [0,self.plane.shape[1],0,self.plane.shape[0]/20.]
+        my_ylabel='Time (s)'
+    else:
+        aspect_mult = 1
+        extent = [0,self.plane.shape[1],0,self.plane.shape[0]]
+        my_ylabel='Time (.02s)'
+    xlabel('Bolometer number'); ylabel(my_ylabel)
     imshow(self.flags[scannum,:,:],interpolation='nearest',
-            origin='lower',aspect=self.aspect)
+            origin='lower',aspect=self.aspect*aspect_mult,
+            extent=extent)
     colorbar()
     self.datafig = figure(fignum);clf(); #subplot(121)
     title("Scan "+str(self.scannum)+" in "+self.ncfilename);
-    xlabel('Bolometer number'); ylabel('Time (.02s)')
+    xlabel('Bolometer number'); ylabel(my_ylabel)
     imshow(self.plane,interpolation='nearest',
-            origin='lower',aspect=self.aspect)
+            origin='lower',aspect=self.aspect*aspect_mult,
+            extent=extent)
     colorbar()
     self.showrects()
     self.showlines()

### 2009-03-30 methods/ms.tex
One more time, baby ...

@@
+% Figure list
+% 1) fig:Coverage
+% 2) fig:BGPSMontage
+% 3) fig:Bandpass
+% 4) fig:Array
+% 5) fig:CalibrationCurves
+% 6) fig:Flatfield
+% 7) fig:CygnusComparison
+% 8) fig:PointingCalibrators
+
 % calibration
@@
 \usepackage{rotating}
+\usepackage{subfigure}
 
@@
 
+\def\bgps{BGPS}
 \newcommand{\bgpsarea}{150}
@@
 \label{#3}
+\end{figure}
+}
+
+\def\FigureTwo#1#2#3#4#5{
+\begin{figure}[htb]
+\epsscale{#5}
+\plottwo{#1}{#2}
+\caption{#3}
+\label{#4}
 \end{figure}
@@
 \newcommand{\casa}{2}
-\newcommand{\cso}{3}
-\newcommand{\utexas}{4}
-\newcommand{\virginia}{5}
-\newcommand{\ubc}
+\newcommand{\utexas}{3}
+\newcommand{\virginia}{4}
+\newcommand{\ucf}{5}
+\newcommand{\wisc}{6}
+\newcommand{\jpl}{7}
+\newcommand{\ubc}{8}
+\newcommand{\hawaiihilo}{9}
+\newcommand{\hawaiimain}{10}
+\newcommand{\arizona}{11}
 
@@
         Miranda Nordhaus\altaffilmark{\utexas},
-	Meredith Drosback\altaffilmark{4},
+	Meredith Drosback\altaffilmark{\virginia},
         John Bally\altaffilmark{\casa}, 
 	Cara Battersby\altaffilmark{\casa},
-	Eric Todd Bradley\altaffilmark{5},
+	Eric Todd Bradley\altaffilmark{\ucf},
 %        Richard Chamberlin\altaffilmark{\cso},
-	Claudia Cyganowski\altaffilmark{6},
-	Darren Dowell\altaffilmark{7}
+	Claudia Cyganowski\altaffilmark{\wisc},
+	Darren Dowell\altaffilmark{\jpl}
 	Neal J. Evans II\altaffilmark{\utexas},
         Jason Glenn\altaffilmark{\casa},
-        Paul Harvey\altaffilmark{1,7},
-        Erik Rosolowsky\altaffilmark{8},
+        Paul Harvey\altaffilmark{\utexas,\casa},
+        Erik Rosolowsky\altaffilmark{\ubc},
 %        Wayne Schlingman\altaffilmark{9},
@@
         Guy S. Stringfellow\altaffilmark{\casa},
-        Josh Walawender\altaffilmark{10}, and 
-        Jonathan Williams\altaffilmark{11}
+        Josh Walawender\altaffilmark{\hawaiihilo}, and 
+        Jonathan Williams\altaffilmark{\hawaiimain}
 }
 
-%\author{James Aguirre\altaffilmark{\penn},
-%  Adam Ginsburg\altaffilmark{\casa},
-%  John Bally\altaffilmark{\casa},
-
-%  Meredith Drosback\altaffilmark{\virginia},
-%  Neal J. Evans\altaffilmark{\utexas},
-%  Jason Glenn\altaffilmark{\casa},
-%  Miranda Nordhaus\altaffilmark{\utexas},
-%  Erik Rosolowsky\altaffilmark{\ubc},
-%  Josh Walawender\altaffilmark{\virginia},
-%  Jonathan Williams\altaffilmark{\virginia}
-%}
-
-\email{jaguirre@sas.upenn.edu}
-
-\altaffiltext{\penn}{University of Pennsylvania, Philadelphia, PA 19104}
-%Jansky Fellow, National Radio Astronomy Observatory} 
-\altaffiltext{\casa}{CASA, University of Colorado, CB 389, Boulder, CO 80309}
-\altaffiltext{\utexas}{Department of Astronomy, University of Texas, 
-       1 University Station C1400, Austin, TX 78712}
-\altaffiltext{4}{Caltech Submillimeter Observatory, Hilo, HI}
-\altaffiltext{5}{Institute for Astronomy (IfA), University of Hawaii
-640 N. Aohoku Pl., Hilo, HI 96720}
-
+\affil{{$^\penn$}{\it{Department of Physics and Astronomy, University of
+      Pennsylvania, Philadelphia, PA }}}
+\email{\tt jaguirre@sas.upenn.edu}
+
+\affil{{$^\casa$}{\it{CASA, University of Colorado, CB 389, Boulder, CO 80309}}}
+%, \email{John.Bally@casa.colorado.edu}
+%      \email{adam.ginsburg@colorado.edu}
+%      \email{cara.battersby@colorado.edu}
+%      \email{Jason.Glenn@colorado.edu} \email{pmh@astro.as.utexas.edu}
+%      \email{Guy.Stringfellow@colorado.edu} }}
+
+\affil{{$^\utexas$}{\it{Department of Astronomy, University of Texas,
+      1 University Station C1400, Austin, TX 78712}}}
+%,            
+%      \email{nje@astro.utexas.edu},
+%      \email{nordhaus@astro.utexas.edu}}}
+
+\affil{{$^\virginia$}{\it{Department of Astronomy, University of
+Virginia, P.O. Box 400325, Charlottesville, VA 22904}}}
+%, 
+%    \email{meredith.drosback@origins.colorado.edu}}}
+
+\affil{{$^\ucf$}{\it{Department of Physics, University of Central
+Florida}}}
+%,           
+%                                              } ,   \email{tbradley@physics.ucf.edu}} }
+
+\affil{{$^\wisc$}{\it{Department of Astronomy, University of Wisconsin,
+       Madison, WI 53706}}}
+% , \email{cyganow@astro.wisc.edu}}}
+
+\affil{{$^\jpl$}{\it{Jet Propulsion Laboratory, California Institute
+   of Technology, 4800 Oak Grove Dr., Pasadena, CA 91104}}}
+%,
+%       \email{cdd@submm.caltech.edu}}}
+
+\affil{{$^{\ubc}$}{\it{Department of Physics and Astronomy, University
+       of British Columbia, Okanagan }}}
+% ,               \email{erik.rosolowsky@ubc.ca}}}
+
+%\affil{{$^{\arizona}$}{\it{ Steward Observatory, University of
+%Arizona, 933 North Cherry Avenue, Tucson, AZ 85721 }}}
+%%\email{yshirley@as.arizona.edu} \email{wschlingman@as.arizona.edu}}}
+
+\affil{{$^{\hawaiihilo}$}{\it{Institute for Astronomy, University of
+        Hawaii,640 N. Aohoku Pl., Hilo, HI 96720}}}
+%\email{joshw@ifa.hawaii.edu} }}
+
+\affil{{$^{\hawaiimain}$}{\it{Institute for Astronomy, University of
+Hawaii,680 Woodlawn Drive, Honolulu, HI 96822}}}
+%\email{jpw@ifa.hawaii.edu}}
+
+%\altaffiltext{\penn}{University of Pennsylvania, Philadelphia, PA 19104}
+%%Jansky Fellow, National Radio Astronomy Observatory} 
+%\altaffiltext{\casa}{CASA, University of Colorado, CB 389, Boulder, CO 80309}
+%\altaffiltext{\utexas}{Department of Astronomy, University of Texas, 
+%       1 University Station C1400, Austin, TX 78712}
+%\altaffiltext{4}{Caltech Submillimeter Observatory, Hilo, HI}
+%\altaffiltext{5}{Institute for Astronomy (IfA), University of Hawaii
+%640 N. Aohoku Pl., Hilo, HI 96720}
+%
 \begin{abstract}
@@
 
-The advent of focal plane arrays containing hundreds of individual
-bolometers sensitive to millimeter and sub-millimeter (sub-mm)
-radiation has enabled large-scale surveys of mm-wavelength continuum
-emission from Galactic interstellar dust.  The 144 element Bolocam
-focal plane array, mounted at the Cassegrain focus of the 10 meter
-diameter sub-mm telescope at the Caltech Sub-millimeter Observatory
-(CSO) was use to survey over \bgpsarea\ square degrees of the northern
-Galactic plane at a wavelength of 1.1 mm in the dust-continuum.  The
-Bolocam Galactic Plane Survey (BGPS) presented here has detected about
-\ncores\ cores in the surveyed fields, providing an unbiased sample of
-cores suitable for multi-wavelength and high-resolution studies with
-existing telescopes and future facilities.  The core catalog is
-described in a companion paper \citep{rosolowsky09}.
-
 Dust continuum emission near a wavelength of 1 mm is the best tracer
@@
 
-The great advantage of continuum observations at 1.1mm is that the
-mass column density does not depend strongly on the dust temperature
-$T_d$ (varying only linearly unless $T_d$ is less than about 10 K) and
-is independent of the gas volume density.  Using the same dust opacity
-as \citet{enoch06} and \citet{young06}, and assuming a gas-to-dust
-mass ratio $X$ of 100, the mass sensitivity can be written as
+The advent of focal plane arrays containing hundreds of individual
+bolometers sensitive to millimeter and sub-millimeter (sub-mm)
+radiation has enabled large-scale surveys of mm-wavelength continuum
+emission from Galactic interstellar dust.  The great advantage of
+continuum observations at 1.1mm is that the mass column density does
+not depend strongly on the dust temperature $T_d$ (varying only
+linearly unless $T_d$ is less than about 10 K) and is independent of
+the gas volume density.  Using the same dust opacity as
+\citet{enoch06} and \citet{young06}, and assuming a gas-to-dust mass
+ratio $X$ of 100, the mass sensitivity can be written as
 \begin{equation} 
@@
 
-A number of (sub)millimeter surveys of the Galactic Plane are ongoing
-or planned.  The BGPS is the first.
+This survey presents the results of one of the first wide-area,
+untargeted surveys of the Galactic Plane in the millimeter continuum.
+We have used the 144 element Bolocam focal plane array, mounted at the
+Cassegrain focus of the 10 meter diameter sub-mm telescope at the
+Caltech Sub-millimeter Observatory (CSO), to survey over \bgpsarea\
+square degrees of the northern Galactic plane at a wavelength of 1.1
+mm in the dust continuum.  Figure \ref{fig:Coverage} shows the
+coverage of the \bgps.  Maps of the entire BGPS are presented in
+Figure \ref{fig:BGPSMontage}.  We have detected \ncores\ cores in the
+surveyed fields, providing an unbiased sample of cores suitable for
+multi-wavelength and high-resolution studies with existing telescopes
+and future facilities.  The core catalog is described in a companion
+paper \citep{rosolowsky09}.
 
@@
 %\citep{jackson06} are shown.
-}{fig:coverage}{1.0}
+}{fig:Coverage}{1.0}
+
+% TEST
+% Useful, but not here
+%\begin{figure}
+%  \subfigure[$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
+%	sources, e.g. Sgr B2, Sgr A, and sources near $l=10$ and
+%	$l=13$, appear to be saturated, but this is only a display
+%	artifact.  The noise is more pronounced from $l=-7$ to $l=-2$
+%	because this region was observed less.]{\label{fig:BGPSMontage-a}\includegraphics[scale=0.75]{fig1_pg1_bw_inv_bar_label}}\\
+%\pagebreak
+%\subfigure[$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
+%	51, W 43, W 49, and M 17 appear to be saturated, but this is
+%	only a display artifact.]
+%{\label{fig:BGPSMontage-b}\includegraphics[scale=0.75]{fig1_pg2_bw_inv_bar_label}}
+%
+%\end{figure}
+%% --------------------------------
+%
+
+\newcounter{subfig}
+\setcounter{subfig}{1}
+\renewcommand{\thefigure}{\arabic{figure}\alph{subfig}}
+
+%\begin{sidewaysfigure}[h]
+\begin{figure}
+  \begin{minipage}{6.5in}
+    \begin{center}
+      \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
+      \caption{$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
+	sources, e.g. Sgr B2, Sgr A, and sources near $l=10$ and
+	$l=13$, appear to be saturated, but this is only a display
+	artifact.  The noise is more pronounced from $l=-7$ to $l=-2$
+	because this region was observed less.}
+    \end{center}
+    \label{fig:BGPSMontage}
+  \end{minipage}
+\end{figure}
+
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
+
+\begin{figure}
+  \begin{minipage}{6.5in} 
+    \begin{center}
+      \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
+      \caption{$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
+	51, W 43, W 49, and M 17 appear to be saturated, but this is
+	only a display artifact}
+    \end{center}
+  \end{minipage}
+\end{figure}
+
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
+
+\begin{figure}
+  \begin{minipage}{6.5in} 
+    \begin{center}
+      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
+      \caption{$l=49.5$ to $l=74.5$.}
+    \end{center}
+  \end{minipage}
+\end{figure}
+
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
+
+\begin{figure}
+  \hspace{-1in}
+  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
+  \caption{The Cygnus Arm.}
+\end{figure}
+%  \vspace{-4in}
+
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
+
+\begin{figure}
+\hspace{-0.5in}
+  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
+  \caption{Cloud complexes centered at $l=111$ in the Perseus Arm.}
+\end{figure}
+
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
+
+\begin{figure}
+  \hspace{-1in}
+  \includegraphics[scale=0.8]{fig1_pg6_bw_inv_bar_label} 
+  \caption{W3/4/5}
+\end{figure}
+
+\renewcommand{\thefigure}{\arabic{figure}}
+
+\clearpage
 
@@
 0.17$.  The passband is constructed to exclude the $^{12}\mathrm{CO}(2
-\to 1)$ emission line.  Figure \ref{fig:Passband} shows the passband.
+\to 1)$ emission line.  Figure \ref{fig:Bandpass} shows the passband.
 We compute color corrections for sources of varying spectral index in
@@
 molecular emission lines are shown at their rest frequencies.  Note
-that the Bolocam passband rejects $>90\%$ of the $^{12}$CO flux, leaving our
-continuum measurements largely uncontaminated.  SO and CH3OH lines are probably
-the dominant contributors to line flux in the passband.  \citet{nummelin1998}
-found that 22\% of the  flux in one pointing towards Sgr B2 was from lines, and
-\citet{yoshida2005} reported >40\% in Orion A from line emission}
-{fig:Passband}{1.0}
+that the Bolocam passband rejects $>90\%$ of the $^{12}$CO flux,
+leaving our continuum measurements largely uncontaminated.  SO and
+CH3OH lines are probably the dominant contributors to line flux in the
+passband.  \citet{nummelin1998} found that 22\% of the flux in one
+pointing towards Sgr B2 was from lines, and \citet{yoshida2005}
+reported $>40\%$ in Orion A from line emission} {fig:Bandpass}{1.0}
 
@@
 
-\Figure{scan_10deg}{The effect of field rotation on the coverage
-obtained via Bolocam raster scans.  (could also use this figure to
-show the distortion map)}{fig:Array}{1.0}
-
-%\begin{sidewaysfigure}[h]
-\begin{center}
-  \begin{figure}[t]
-%    \includegraphics[width=6in,height=9.5in]{fig1_pg1_bw_inv_bar_label} 
-    \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
-    \caption{$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
-      sources, e.g. Sgr B2, Sgr A, and sources near $l=10$ and
-      $l=13$, appear to be saturated, but this is only a display
-      artifact.  The noise is more pronounced from $l=-7$ to $l=-2$
-      because this region was observed less.}
-    \label{fig:galplane_p1}
-  \end{figure}
-    %\end{sidewaysfigure}
-
-    %\begin{sidewaysfigure}[h]
-  \begin{figure} 
-%    \includegraphics[width=6in,height=9.5in]{fig1_pg2_bw_inv_bar_label} 
-    \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
-    \caption{$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
-      51, W 43, W 49, and M 17 appear to be saturated, but this is
-      only a display artifact}
-    \label{fig:galplane_p2}
-    %\end{sidewaysfigure}
-  \end{figure}
-\end{center}
-
-%\begin{sidewaysfigure}[h]
-%\begin{center}
-%\includegraphics[scale=0.5]{bgps_montage}
-%\end{center}
-%\caption{ The coverage of the Bolocam Northern Galactic Plane Survey.
-%as of September 2007.  The negative greyscale is the IRAS 100 \mum\
-%survey.  Dashed lines indicate coverage between 15 and 100 mJy RMS;
-%solid lines indicate areas covered more deeply than 30 mJy RMS.}
-%\label{fig:coverage_sep06}
-%\end{sidewaysfigure}
-
-%\include{bgps_methods_flux_calibration}
+\FigureTwo{bolosens050904_o32}{scan_10deg}{Left: the position,
+ellipticity and relative response of the detectors in the Bolocam
+focal plane as mapped to the sky.  Right: The effect of field rotation
+on the coverage obtained via Bolocam raster scans.}{fig:Array}{1.0}
+
 \section{Flux Density and Surface Brightness Calibration}
 
-The absolute flux calibration is obtained from observations of Mars,
-Uranus and Neptune (the ``primary calibrators'').  The millimeter-wave
-flux of these planets is known to $\sim 5\%$
-\citep{orton86,griffin93}.  Calibrations at (sub)millimeter
-wavelengths are strongly affected by atmospheric opacity corrections.
-Further, the detector responsivity of Bolocam's bolometers is a
-non-linear function of the mean atmospheric loading.
+The absolute flux calibration is obtained from observations of Mars
+and Uranus
+% no good observations, per AG
+%and Neptune 
+(the ``primary calibrators'').  The millimeter-wave flux of these
+planets is known to $\sim 5\%$ \citep{orton86,griffin93}.
+Calibrations at (sub)millimeter wavelengths are strongly affected by
+atmospheric opacity corrections.  Further, the detector responsivity
+of Bolocam's bolometers is a non-linear function of the mean
+atmospheric loading.
 
@@
 %constitutes each of the observing epochs.  
-The calibration curve is shown in Figure \ref{fig:Calibration}.  The
+The calibration curve is shown in Figure \ref{fig:CalibrationCurves}.  The
 resulting error on the calibration curve fit is less than 
@@
 of the detectors.  The change in relative response with loading for a
-typical detector is shown in Figure \ref{fig:Flatfield}.  The method
-is discussed further in Section \ref{sec:Mapping}
+typical detector is shown in Figure \ref{fig:CalibrationCurves}.  The
+actual application of the the method to the time series of the
+bolometer data is shown in Figure \ref{fig:Flatfield}, and is
+discussed further in Section \ref{sec:Mapping}.
 
@@
 and Neptune which are nearly point sources for Bolocam.
-% For
-
 %The semi-diameter of
@@
 %results in a $< 1.5\%$ correction of the observed flux.
-The beam area is that averaged over all detectors, and is ?$1.71\times10^{-6}$\TBD\ ($35.6$\farcs)
-steradians.  This allows conversion of the maps, calibrated in Jy
-beam$^{-1}$, into surface brightness (MJy sr$^{-1}$).  The uncertainty
-in the beam size is ?$.7\%$\TBD\  (number quoted is the uncertainty in the 
-mean beam size), leading to an uncertainty in the surface
-brightness calibration of \TBD.
+The maps of the planets, including all detectors, are fit to a
+Gaussian profile.  The beam area is that averaged over all detectors,
+and is ?$1.71\times10^{-6}$\TBD\ ($35.6$\farcs) steradians.  This
+allows conversion of the maps, calibrated in Jy beam$^{-1}$, into
+surface brightness (MJy sr$^{-1}$).  The uncertainty in the beam size
+is ?$.7\%$\TBD\ (number quoted is the uncertainty in the mean beam
+size), leading to an uncertainty in the surface brightness calibration
+of \TBD.
 
@@
 surveys with the MAMBO instrument at 1.2 mm with which we can compare.
-For example, there is \citet{motte07}.
-
-\Figure{fluxcal_errorbars}
+Figure \ref{fig:CygnusComparison} shows the comparison of fluxes
+extracted from our map in the Cygnus Arm with those of
+\citet{motte07}.
+
+\FigureTwo{fluxcal_errorbars}{rel_flux_cal_050303_ob3_to_050405_o66}
 %{calibration_plot_2004}
-{Average calibration curve [V/Jy] versus the mean detector voltage, a
-proxy for atmospheric loading.}{fig:Calibration}{1.0}
-
-\Figure{rel_flux_cal_050303_ob3_to_050405_o66}{Scaling of the
+{Left: Average calibration curve [V/Jy] versus the mean detector
+voltage, a proxy for atmospheric loading.  Red points are observations
+of Mars and black of Uranus.  Right: Scaling of the
 relative calibration with atmospheric loading for bolocam
-143. {\em To be replaced with new figure}}{fig:Flatfield}{1.0}
-
-\Figure{relsens_cal}{Relative sensitivity calibration.  Black is the median over
-all bolometers, red and green are individual bolometers. a. before
-b. after}{fig:relsens_cal}{1.0}
+143. {\em To be replaced with new figure}}{fig:CalibrationCurves}{1.0}
+
+\Figure{relsens_cal}{An illustration of the relative sensitivity
+calibration using the atmosphere as a calibrator.  Black is the median
+over all bolometers (the atmosphere model), red and green are
+individual bolometers. a. before and b. after applying the relative
+calibration.  Note the improved agreement.}{fig:Flatfield}{1.0}
+
+\Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
+in the same aperture from the \citet{motte07} MAMBO map and the
+Bolocam map of this paper.}{fig:CygnusComparison}{1.0}
 
@@
 We constructed an absolute reference system for the BGPS by observing
-bright quasars and blazars near the Galactic Plane.
-
-The distribution of sources over the sky is shown in Figure \ref{fig:astrometry}
+bright quasars and blazars near the Galactic Plane.  The distribution
+of sources over the sky is shown in Figure
+\ref{fig:PointingCalibrators} and the list is given in Appendix
+\ref{app:PointingCalibrators}.
 
@@
 
+For the purposes of comparison with other surveys, we present in
+Appendix \ref{app:ReferenceSources} a selection
+
 {\em Miranda's data here}
 
-\Figure{plane_astrometry}{The distribution of absolute reference
-sources (crosses) and in-plane millimeter sources (x's) in the
-Galactic Plane.}{fig:astrometry}{1.0}
-
-\Figure{pointing_model}{The pointing model correction (left) and
-residuals (right) for Epoch V, from which the master reference images
-were derived for subsequent alignment. {\em To be replaced with newer
-figure?}}{fig:PointingModel}{1.0}
-
-\Figure{pointing_model_residuals}{The residuals of the pointing
-model.  Note the Gaussian distribution.}{fig:PointingModelResiduals}{1.0}
-
-\Figure{pointing_model_skydist}{The distribution of the PCAL
-sources across the local sky in Hawaii.  Notice the good sampling of
-the entire region used for the Survey.}{fig:PCALSkydist}{1.0}
+\FigureTwo{plane_astrometry}{pointing_model_skydist}{Left: The
+distribution of absolute reference sources (crosses) in the Galactic
+Plane (Appendix \ref{app:PointingCalibrators}).  Also shown (crosses)
+are the locations of bright, isolated, compact sources for comparison
+with other surveys, as given in Appendix \ref{app:ReferenceSources}.
+Right: The distribution of the pointing calibration sources across the
+local sky in Hawaii.  Notice the good sampling of the entire region
+used for the Survey.}{fig:PointingCalibrators}{1.0}
+
+\begin{figure}
+  \subfigure[The pointing model correction (left) and residuals
+(right) for Epoch V, from which the master reference images were
+derived for subsequent alignment. {\em To be replaced with newer
+figure?}]
+{\label{fig:PointingModel-a}\includegraphics[scale=1.0]{pointing_model}}\\
+
+  \subfigure[The residuals of the pointing model.  Note the Gaussian
+distribution.]{\label{fig:PointingModel-b}\includegraphics[scale=0.7]{pointing_model_residuals}}
+
+\caption{Pointing model.}
+\end{figure}
 
@@
 \end{equation}
-The instrument errors, which are typically smaller than the
-atmosphere, are then estimated
+This is illustrated in Figure \ref{fig:Flatfield}.  The instrument
+errors, which are typically smaller than the atmosphere, are then
+estimated
 \begin{equation}
@@
 \Figure{flagger_plots}{An illustration of a ``glitch'' in a single
-bolometer timestream due to a cosmic ray strike.  Note the acausal
-ringing due to the application of the downsampling filter.  The time
-series for a physically adjacent bolometer is shown in red.  The high
-level of correlation due to atmospheric fluctuations is readily
-apparent, as well as the lack of correlation due to the
-glitch.}{fig:CosmicRayGlitch}{1.0}
+bolometer timestream (red) due to a cosmic ray strike.  Note the
+acausal ringing due to the application of the downsampling filter.
+The time series for a physically adjacent bolometer is shown in blue,
+and a bolometer which does not pass over a source in green.  The PCA
+model has already been subtracted from the
+data.}{fig:CosmicRayGlitch}{1.0}
 
@@
 
-\Figure{flagger_withglitch}{An illustration of the flagging process using the
-waterfall plot.  In this image, an anomaly which affects all
-bolometers for a brief period of time is evident near the top of the
-image.}{fig:Flag1}{1.0}
+\Figure{flagger_withglitch}{An illustration of the flagging process
+using the waterfall plot. The glitch apparent at middle right is the
+same one whose time series is shown in Figure
+\ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the effect
+of the glitch also propagates over the other bolometers, appearing as
+a horizontal stripe.}  {fig:Flag1}{1.0}
 
@@
 
-\Figure{flagger_glitchgone}{A rescaled version of the data with the bad data
-removed.}{fig:Flag3}{1.0}
-
-An automated flagger was also created that flags out outlier data on a per-pixel
-basis.  In order to make a robust measurement of the variance of the fluxes
-assigned to each pixel, we used the median average deviation over the data in
-the pixel and rejected high and low outliers at the 3-sigma level.  Pixels with
-too little data to compute a deviation, i.e. those with $<3$ data points, were
-also flagged out - these scan-edge pixels are the dominant contribution to the
-total number of flagged data points.
+\Figure{flagger_glitchgone}{A rescaled version of the data with the
+bad data removed.  The effect of the glitch on the other bolometers is
+now more apparent; this too is flagged out in subsequent
+analysis.}{fig:Flag3}{1.0}
+
+An automated flagger was also created that flags out outlier data on a
+per-pixel basis.  In order to make a robust measurement of the
+variance of the fluxes assigned to each pixel, we used the median
+average deviation over the data in the pixel and rejected high and low
+outliers at the 3-sigma level.  Pixels with too little data to compute
+a deviation, i.e. those with $<3$ data points, were also flagged out -
+these scan-edge pixels are the dominant contribution to the total
+number of flagged data points.
 
@@
 
-%\Figure{l001_deconvolutionkernelcompare}{The effect of
-%deconvolution on the iterative process can be seen in its effect on
-%the residuals. From left to right: map, noise, smoothmap, model. Top
-%to bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
-%7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which
-%has the result of leaving no flux in the residual at the location of
-%Sgr B2, and does not ``dig a hole'' in the residual map, as the
-%7.2\arcsec\ kernel does.}{fig:Deconvolution}{1.0}
+\Figure{l001_deconvolutionkernelcompare}{The effect of
+deconvolution on the iterative process can be seen in its effect on
+the residuals. From left to right: map, noise, smoothmap, model. Top
+to bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
+7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which
+has the result of leaving no flux in the residual at the location of
+Sgr B2, and does not ``dig a hole'' in the residual map, as the
+7.2\arcsec\ kernel does.}{fig:Deconvolution}{1.0}
 
@@
 % deviations from the ``ghosts'' may be compared.
+
+In some fields, flux from certain source spread out over the course of
+the iterative process using certain kernel sizes.  The cause of this
+artifact are not yet well-understood, but using a different kernel
+size was an effective workaround and did little to change the
+properties of the final map.
 
@@
 
+\section{Calculation of Color Corrections}
+\label{app:ColorCorrections}
+
+If an experiment has finite bandwidth ($t(\nu) \ne \delta(\nu -
+\nu_c)$), to report a source surface brightness at a single
+frequency, one must assume a source spectrum.  The power detected from
+that source is assumed to be
+\begin{equation}
+P_{in} = \eta \; A \Omega \; \int I_0(\nu) t(\nu) d \nu
+\end{equation}
+(Here $\eta$ and $A \Omega$ are the optical efficiency and throughput
+of the instrument, $I_0(\nu)$ is the nominal (assumed) surface
+brightness of the source, and $t(\nu)$ is the bandpass transmission
+normalized to $1.0$ at its peak.)  The effective band center $\nu_c$
+is usually chosen such that
+\begin{equation}
+I_0(\nu_c) \simeq \frac{\int I_0(\nu) t(\nu) d \nu}
+{\int t(\nu) d \nu} 
+\end{equation}
+The band centers for Bolocam are calculated assuming a Rayleigh-Jeans
+(RJ) source spectrum
+\begin{eqnarray}
+I_0(\nu_c) & = & I_{RJ}(\nu_c) \\
+\nonumber & = & \tau \; 2 k T \; \frac{\nu_c^2}{c^2},
+\end{eqnarray}
+where $\tau$ is the optical depth of the source and $k$ is Boltzmann's
+constant.  Since the detected power is assumed to be
+\begin{equation}
+P_{in} = \eta \; A \Omega \; \int \tau \; 2 k T \; \frac{\nu^2}{c^2}
+\; t(\nu) d \nu,
+\end{equation}
+we can write
+\begin{equation}
+I_0(\nu_c) = \frac{P_{in}}{\eta \; A \Omega \int \nu^2 \; t(\nu) d \nu} \; \nu_c^2
+\end{equation}
+Now if we assume a different source spectrum, for example a greybody
+with power-law emissivity, the assumed input power is
+\begin{eqnarray}
+P_{in} & = & \eta \; A \Omega \; \int I_{GB}(\nu) t(\nu) d \nu \\
+\nonumber & = & \eta \; A \Omega \; \int \tau(\nu_0) (\nu / \nu_0)^\alpha B_\nu(T) t(\nu) d \nu
+\end{eqnarray}
+and the source spectrum inferred from the detected power is
+\begin{eqnarray}
+I_{GB}(\nu_c) & = & \tau(\nu_0) (\nu_c / \nu_0)^\alpha B_{\nu_c}(T) \\
+\nonumber & = & \frac{P_{in}}{\eta \; A \Omega \int \nu^\alpha B_\nu(T) t(\nu) d \nu} \; \nu_c^\alpha B_{\nu_c}(T) \\
+\nonumber & = & \frac{\int \nu^2 t(\nu) d \nu}{\int \nu^\alpha B_\nu(T) t(\nu) d \nu} \; \nu_c^{\alpha-2} B_{\nu_c}(T) \; I_{RJ}(\nu_c) \\
+\nonumber & \equiv & \frac{I_{RJ}(\nu_c)}{K}.
+\end{eqnarray}
+This defines the color correction $K$ to apply to the reported Bolocam
+flux from a source if the source is assumed to have a greybody
+spectrum with power-law emissivity.
+
+%We make a similar calculation for DIRBE, for which the band centers are 
+%computed assuming a spectrum with $\nu I(\nu)$ constant.  In this case, 
+%the correction is given by 
+%\begin{eqnarray}
+%K &=& \frac{\nu_c^{-1}}{\int \nu^{-1} t(\nu) d \nu} \left[\frac{\tau(\nu_0) (\nu_c / \nu_0)^\alpha B_{\nu_c}(T)}{\int \tau(\nu_0) (\nu / \nu_0)^\alpha B_{\nu}(T) t(\nu) d \nu} \right]^{-1} \\
+%\nonumber &=& \frac{\int \nu^\alpha B_{\nu}(T) t(\nu) d \nu}{\int \nu^{-1} t(\nu) d \nu} \; \nu_c^{-(\alpha+1)} B_{\nu_c}(T)
+%\end{eqnarray}
+%
+We note that for an arbitrary experiment with bandpass $t(\nu)$ that
+reports its surface brightness measurements assuming a spectrum
+$I_0(\nu)$, the surface brightness assuming a different source
+spectrum $I_1(\nu)$ is given by
+\begin{eqnarray}
+I_1(\nu_c) &=& I_0(\nu_c) / K \\
+\nonumber &=& I_0(\nu_c) \frac{I_1(\nu_c)}{\int I_1(\nu) t(\nu) d \nu} \left[\frac{I_0(\nu_c)}{\int I_0(\nu) t(\nu) d \nu} \right]^{-1}
+\end{eqnarray}
+
 \section{Pointing Calculation}
@@
 
-After this is done, the remaining
-
-\section{Table of Absolute and In-Plane Pointing Sources}
+\section{Table of Absolute Pointing Sources}
+\label{app:PointingCalibrators}
+
+The absolute reference frame for the BGPS pointing model was chosen
+from a selection of bright quasars near the Galactic Plane.  Table
+\ref{tab:PointingCalibrators} gives the pointing sources used for this
+purpose.
 
@@
 {Number & Alias & RA(J2000) & Dec(J2000) & l & b  & Flux (Jy)}
-{tab:PCAL}
+{tab:PointingCalibrators}
 {
@@
 }
+
+\clearpage
+
+\section{Table of Reference Sources}
+\label{app:ReferenceSources}
 
@@
 
-\section{Calculation of Color Corrections}
-\label{app:ColorCorrections}
-
-If an experiment has finite bandwidth ($t(\nu) \ne \delta(\nu -
-\nu_c)$), to report a source surface brightness at a single
-frequency, one must assume a source spectrum.  The power detected from
-that source is assumed to be
-\begin{equation}
-P_{in} = \eta \; A \Omega \; \int I_0(\nu) t(\nu) d \nu
-\end{equation}
-(Here $\eta$ and $A \Omega$ are the optical efficiency and throughput
-of the instrument, $I_0(\nu)$ is the nominal (assumed) surface
-brightness of the source, and $t(\nu)$ is the bandpass transmission
-normalized to $1.0$ at its peak.)  The effective band center $\nu_c$
-is usually chosen such that
-\begin{equation}
-I_0(\nu_c) \simeq \frac{\int I_0(\nu) t(\nu) d \nu}
-{\int t(\nu) d \nu} 
-\end{equation}
-The band centers for TopHat are calculated assuming a Rayleigh-Jeans
-(RJ) source spectrum
-\begin{eqnarray}
-I_0(\nu_c) & = & I_{RJ}(\nu_c) \\
-\nonumber & = & \tau \; 2 k T \; \frac{\nu_c^2}{c^2},
-\end{eqnarray}
-where $\tau$ is the optical depth of the source and $k$ is Boltzmann's
-constant.  Since the detected power is assumed to be
-\begin{equation}
-P_{in} = \eta \; A \Omega \; \int \tau \; 2 k T \; \frac{\nu^2}{c^2}
-\; t(\nu) d \nu,
-\end{equation}
-we can write
-\begin{equation}
-I_0(\nu_c) = \frac{P_{in}}{\eta \; A \Omega \int \nu^2 \; t(\nu) d \nu} \; \nu_c^2
-\end{equation}
-Now if we assume a different source spectrum, for example a greybody
-with power-law emissivity, the assumed input power is
-\begin{eqnarray}
-P_{in} & = & \eta \; A \Omega \; \int I_{GB}(\nu) t(\nu) d \nu \\
-\nonumber & = & \eta \; A \Omega \; \int \tau(\nu_0) (\nu / \nu_0)^\alpha B_\nu(T) t(\nu) d \nu
-\end{eqnarray}
-and the source spectrum inferred from the detected power is
-\begin{eqnarray}
-I_{GB}(\nu_c) & = & \tau(\nu_0) (\nu_c / \nu_0)^\alpha B_{\nu_c}(T) \\
-\nonumber & = & \frac{P_{in}}{\eta \; A \Omega \int \nu^\alpha B_\nu(T) t(\nu) d \nu} \; \nu_c^\alpha B_{\nu_c}(T) \\
-\nonumber & = & \frac{\int \nu^2 t(\nu) d \nu}{\int \nu^\alpha B_\nu(T) t(\nu) d \nu} \; \nu_c^{\alpha-2} B_{\nu_c}(T) \; I_{RJ}(\nu_c) \\
-\nonumber & \equiv & \frac{I_{RJ}(\nu_c)}{K}.
-\end{eqnarray}
-This defines the color correction $K$ to apply to the reported TopHat
-flux from a source if the source is assumed to have a greybody
-spectrum with power-law emissivity.
-
-We make a similar calculation for DIRBE, for which the band centers are 
-computed assuming a spectrum with $\nu I(\nu)$ constant.  In this case, 
-the correction is given by 
-\begin{eqnarray}
-K &=& \frac{\nu_c^{-1}}{\int \nu^{-1} t(\nu) d \nu} \left[\frac{\tau(\nu_0) (\nu_c / \nu_0)^\alpha B_{\nu_c}(T)}{\int \tau(\nu_0) (\nu / \nu_0)^\alpha B_{\nu}(T) t(\nu) d \nu} \right]^{-1} \\
-\nonumber &=& \frac{\int \nu^\alpha B_{\nu}(T) t(\nu) d \nu}{\int \nu^{-1} t(\nu) d \nu} \; \nu_c^{-(\alpha+1)} B_{\nu_c}(T)
-\end{eqnarray}
-For an arbitrary experiment with bandpass $t(\nu)$ that reports its
-surface brightness measurements assuming a spectrum $I_0(\nu)$, the
-surface brightness assuming a different source spectrum $I_1(\nu)$ is
-given by
-\begin{eqnarray}
-I_1(\nu_c) &=& I_0(\nu_c) / K \\
-\nonumber &=& I_0(\nu_c) \frac{I_1(\nu_c)}{\int I_1(\nu) t(\nu) d \nu} \left[\frac{I_0(\nu_c)}{\int I_0(\nu) t(\nu) d \nu} \right]^{-1}
-\end{eqnarray}
-
 \bibliography{milkyway}

### 2009-03-30 analysis/example_waterfalls.py
example_waterfalls updated

@@ -7,13 +7,15 @@ f = pyflagger.Flagger('/usb/scratch1/super_gc/050703_o15_raw_ds5.nc_indiv13pca',
 
 f.plotscan(12,seconds=1)
 f.scannum = 12
-f.flags[f.scannum,:,:] -= (f.flags[f.scannum,:,:] > 0)
+f.flags[f.scannum,:,:] -= (f.flags[f.scannum,:,:] > 0) * f.flags[f.scannum,:,:]
 figure(1); savefig(figure_path+'flagger_withglitch.ps')
 
 f.flag_box(97,123,97,132,1)
+draw()
 figure(1); savefig(figure_path+'flagger_glitchboxflagged.ps')
 
 f.plotscan(12,seconds=1)
+draw()
 figure(1); savefig(figure_path+'flagger_glitchgone.ps')
 
 figure(3)

### 2009-03-30 analysis/example_waterfalls.py
example_waterfalls updated again

@@ -5,17 +5,16 @@ figure_path = '/home/milkyway/student/ginsbura/paper_figures/'
 
 f = pyflagger.Flagger('/usb/scratch1/super_gc/050703_o15_raw_ds5.nc_indiv13pca',mapnum='01',ncfilename='/scratch/sliced/l000/050703_o15_raw_ds5.nc')
 
-f.plotscan(12,seconds=1)
 f.scannum = 12
 f.flags[f.scannum,:,:] -= (f.flags[f.scannum,:,:] > 0) * f.flags[f.scannum,:,:]
+
+f.plotscan(12,seconds=1)
 figure(1); savefig(figure_path+'flagger_withglitch.ps')
 
 f.flag_box(97,123,97,132,1)
-draw()
 figure(1); savefig(figure_path+'flagger_glitchboxflagged.ps')
 
 f.plotscan(12,seconds=1)
-draw()
 figure(1); savefig(figure_path+'flagger_glitchgone.ps')
 
 figure(3)

### 2009-03-30 analysis/example_waterfalls.py
example_waterfalls - time flagged

@@ -12,6 +12,7 @@ f.plotscan(12,seconds=1)
 figure(1); savefig(figure_path+'flagger_withglitch.ps')
 
 f.flag_box(97,123,97,132,1)
+f.flag_time(,'t')
 figure(1); savefig(figure_path+'flagger_glitchboxflagged.ps')
 
 f.plotscan(12,seconds=1)

### 2009-03-30 analysis/example_waterfalls.py
example_waterfalls - time flagged

@@ -12,7 +12,7 @@ f.plotscan(12,seconds=1)
 figure(1); savefig(figure_path+'flagger_withglitch.ps')
 
 f.flag_box(97,123,97,132,1)
-f.flag_time(,'t')
+f.flag_time(128,'t')
 figure(1); savefig(figure_path+'flagger_glitchboxflagged.ps')
 
 f.plotscan(12,seconds=1)

### 2009-03-30 methods/ms.tex
ms.tex - removed middle flagger figure
example_waterfalls - times flagged

@@
 
-\Figure{flagger_withglitch}{An illustration of the flagging process
-using the waterfall plot. The glitch apparent at middle right is the
-same one whose time series is shown in Figure
-\ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the effect
-of the glitch also propagates over the other bolometers, appearing as
-a horizontal stripe.}  {fig:Flag1}{1.0}
-
-\Figure{flagger_glitchboxflagged}{A box is drawn around the bad data and it is
-removed from subsequent analysis.}{fig:Flag2}{1.0}
-
-\Figure{flagger_glitchgone}{A rescaled version of the data with the
-bad data removed.  The effect of the glitch on the other bolometers is
-now more apparent; this too is flagged out in subsequent
-analysis.}{fig:Flag3}{1.0}
+\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of the
+flagging process using the waterfall plot. Left: The glitch apparent at middle
+right is the same one whose time series is shown in Figure
+\ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the effect of the
+glitch also propagates over the other bolometers, appearing as a horizontal
+stripe. Right: The same data displayed with the time point including the glitch
+flagged out and rescaled}  {fig:Flag1}{1.0}
+
+%this figure failed to create automatically and wasn't really that useful
+%anyway
+% \Figure{flagger_glitchboxflagged}{A box is drawn around the bad data and it is
+% removed from subsequent analysis.}{fig:Flag2}{1.0}
+
+% \Figure{flagger_glitchgone}{A rescaled version of the data with the
+% bad data removed.  The effect of the glitch on the other bolometers is
+% now more apparent; this too is flagged out in subsequent
+% analysis.}{fig:Flag3}{1.0}
 

### 2009-03-30 analysis/example_waterfalls.py

@@ -11,8 +11,17 @@ f.flags[f.scannum,:,:] -= (f.flags[f.scannum,:,:] > 0) * f.flags[f.scannum,:,:]
 f.plotscan(12,seconds=1)
 figure(1); savefig(figure_path+'flagger_withglitch.ps')
 
-f.flag_box(97,123,97,132,1)
+#f.flag_box(97,123,97,132,1)
+f.flag_time(123,'t')
+f.flag_time(124,'t')
+f.flag_time(125,'t')
+f.flag_time(126,'t')
+f.flag_time(127,'t')
 f.flag_time(128,'t')
+f.flag_time(129,'t')
+f.flag_time(130,'t')
+f.flag_time(131,'t')
+f.flag_time(132,'t')
 figure(1); savefig(figure_path+'flagger_glitchboxflagged.ps')
 
 f.plotscan(12,seconds=1)

### 2009-03-31 methods/ms.tex
new paper draft - flagger text

@@
 be meaningfully performed.
+
+Figure \ref{fig:PCA_filter} shows the fraction of flux recovered in the map as a
+function of source size for a range of different PCA components subtracted in
+the cleaning.  These measurements were produced by inserting simulated gaussian
+sources at a range of peak flux densities and sizes spread out through the map
+and summing the flux in an ellipse on the final cleaned map.  The median
+fraction over all sources of a given size is plotted in the figure.
+
+Real data with the astrophysical source model removed were used as the
+background.  Because this is real data, at lower numbers of PCA components
+subtracted, the atmosphere still dominates the total measured flux, which is
+particularly evident for the largest sources.
+
+Figure \ref{fig:deconv_filter} shows the fraction of flux recovered in the maps
+as a function of the deconvolution kernel used to create the astrophysical model
+maps.  The differences at large source sizes are not yet well-understood
+(!!!!!!), but at the smallest source size, it is evident that a deconvolution
+kernel smaller than the source size does not fully recover the source flux.
+Therefore we chose a deconvolution kernel smaller than the beam but larger than
+the pixel size used. \ref{fig:Deconvolution} demonstrates the effects of using
+both too large and too small a kernel.
 

### 2009-03-31 methods/ms.tex
new paper draft - cores->clumps

@@
 continuum without pre-selected targets.  The survey has detected
-\ncores\ cores to a limiting depth of between \bgpsdepthlow\ and
+\ncores\ clumps to a limiting depth of between \bgpsdepthlow\ and
 \bgpsdepthhigh\ mJy RMS.  This paper details the survey observations
@@
 Millimeter-wavelength continuum surveys of the Galactic plane provide
-the best way to identify high-column density cores and clumps where
+the best way to identify high-column density clumps and clumps where
 planets, stars, and star clusters form.  Such data can locate and lead
-to the measurement of the physical properties of cores un-biased by
+to the measurement of the physical properties of clumps un-biased by
 selection effects such as the presence of embedded stars, star
@@
 Galaxy-wide surveys are essential for measuring the impacts of the
-environment on core properties and star formation activity.  Do core
-properties vary with location in or out of spiral arms?  Do core
+environment on clump properties and star formation activity.  Do clump
+properties vary with location in or out of spiral arms?  Do clump
 properties vary with Galactocentric distance?  Do they depend on the
@@
 provide essential ``ground truth'' required for the analysis of distant
-galaxies where where individual clouds and cores are not resolved and
+galaxies where where individual clouds and clumps are not resolved and
 only galaxy-wide average quantities can be measured.
@@
 A crucial step in the observational study of star and cluster
-formation is identification and characterization of the cloud cores
+formation is identification and characterization of the cloud clumps
 which will soon form or are actively forming stars.  Massive stars and
-clusters form from high-density cloud cores with very large column
-densities and extinctions $A_V > $ 100.  Thus, such cloud cores are
+clusters form from high-density cloud clumps with very large column
+densities and extinctions $A_V > $ 100.  Thus, such cloud clumps are
 best investigated at millimeter and sub-millimeter wavelengths.
@@
 impacts of radiation fields and shocks make the derivation of column
-densities, masses, and other physical properties of cloud cores very
+densities, masses, and other physical properties of cloud clumps very
 difficult.  The continuum emission from warm dust provides a more
-reliable tracer of the column densities and core masses.
+reliable tracer of the column densities and clump masses.
 
@@
 coverage of the \bgps.  Maps of the entire BGPS are presented in
-Figure \ref{fig:BGPSMontage}.  We have detected \ncores\ cores in the
-surveyed fields, providing an unbiased sample of cores suitable for
+Figure \ref{fig:BGPSMontage}.  We have detected \ncores\ clumps in the
+surveyed fields, providing an unbiased sample of clumps suitable for
 multi-wavelength and high-resolution studies with existing telescopes
-and future facilities.  The core catalog is described in a companion
+and future facilities.  The clump catalog is described in a companion
 paper \citep{rosolowsky09}.

### 2009-03-31 methods/ms.tex
Testing ...
deconv_map changed to deal with NANs better

@@
 
-For the purposes of comparison with other surveys, we present in
-Appendix \ref{app:ReferenceSources} a selection
+For the purposes of comparison of both flux and pointing with other
+surveys, we present in Appendix \ref{app:ReferenceSources} a selection
+of bright, compact, relatively isolated sources.
 
@@
 Therefore we chose a deconvolution kernel smaller than the beam but larger than
-the pixel size used. \ref{fig:Deconvolution} demonstrates the effects of using
+the pixel size used.  Figure \ref{fig:Deconvolution} demonstrates the effects of using
 both too large and too small a kernel.

### 2009-04-02 methods/ms.tex
plot_galplane

@@
 
-Figure \ref{fig:PCA_filter} shows the fraction of flux recovered in the map as a
+Figure \ref{fig:PCA_filter}a shows the fraction of flux recovered in the map as a
 function of source size for a range of different PCA components subtracted in
@@
 
-Figure \ref{fig:deconv_filter} shows the fraction of flux recovered in the maps
+Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered in the maps
 as a function of the deconvolution kernel used to create the astrophysical model
@@
 
-\Figure{pca_comparison}{The fractional flux lost as a function of
-source size for well-separated Gaussian sources with the FWHM as
-indicated. Legend: number of PCA components }{fig:PCA_filter}{1.0}
-
-\clearpage
-
-\Figure{deconvolution_comparison}{The fractional flux lost as a function of
-source size for well-separated Gaussian sources with the FWHM as
-indicated.  Legend: Size of deconvolution kernel used to make model }{fig:deconv_filter}{1.0}
+\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The fractional
+flux recovered as a function of source size for well-separated Gaussian sources with
+the FWHM as indicated. \emph{Left}: 3,7,10,13,16,21,26,31 PCA components subtracted }{fig:PCA_filter}{1.0}
+
+%\clearpage 
+%
+%\Figure{deconvolution_comparison}{The fractional flux lost as a function of
+%source size for well-separated Gaussian sources with the FWHM as
+%indicated.  Legend: Size of deconvolution kernel used to make model }{fig:deconv_filter}{1.0}
 

### 2009-04-02 methods/ms.tex
changed flagger figures

@@
 sources at a range of peak flux densities and sizes spread out through the map
-and summing the flux in an ellipse on the final cleaned map.  The median
-fraction over all sources of a given size is plotted in the figure.
+and summing the flux in an ellipse on the final cleaned map.
 
@@
 (!!!!!!), but at the smallest source size, it is evident that a deconvolution
-kernel smaller than the source size does not fully recover the source flux.
+kernel smaller than the source size does not reliably recover the source flux.
 Therefore we chose a deconvolution kernel smaller than the beam but larger than
@@
 flux recovered as a function of source size for well-separated Gaussian sources with
-the FWHM as indicated. \emph{Left}: 3,7,10,13,16,21,26,31 PCA components subtracted }{fig:PCA_filter}{1.0}
+the FWHM as indicated.
+\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13
+(orange),16 (red),21 (teal),26 (lime),31 (black) PCA components subtracted.
+\emph{Right}: 7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
+kernel for 13 PCA components subtracted
+}{fig:PCA_filter}{1.0}
 

### 2009-04-06 methods/ms.tex
Testing ...
Progress, of a sort.

@@
 % 8) fig:PointingCalibrators
+% 9) fig:PointingModel
+% 10) fig:SCUBAPointingComparison
+% 11) fig:IterativeMapping
+% 12) fig:Flagging
+% 13) fig:GlitchDistribution
+% 14) fig:PCA_Filter
+% 15) fig:Deconvolution
 
@@
 \section{Flux Density and Surface Brightness Calibration}
+\label{sec:FluxCalibration}
 
@@
 
+% 6
 \Figure{relsens_cal}{An illustration of the relative sensitivity
@@
 
+% 7
 \Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
@@
 \section{Astrometry}
+\label{sec:Astrometry}
 
@@
 
-{\em Show a cross-correlation map?}
-
-\subsection{Comparison to SCUBA and SHARC-II Positions}
-
-The same cross-correlation procedure was used to compare to SCUBA maps where
-available.  The morphological correlation between SCUBA and BGPS sources is
-excellent, so cross-correlation maps could be used to test our pointing model.
+\subsection{Comparison to SCUBA Legacy Source Positions}
+\label{sec:SCUBAPointingComparison}
+%and SHARC-II Positions}
+
+The same cross-correlation procedure was used to compare to the SCUBA
+maps from the Legacy Catalog.  The morphological correlation between
+SCUBA and BGPS sources is excellent, so cross-correlation maps could
+be used to test our pointing model.
+
+An example is shown in Figure \ref{fig:SCUBAPointingComparison}.
+
+{\it Do the negative bowls of either survey bunge up the
+cross-correlation?  If not, how do we deal with them?}
 
@@
 
-{\em Miranda's data here}
-
+%{\em Miranda's data here}
+
+% 8
+% -----------------------------------------------------------------------------
 \FigureTwo{plane_astrometry}{pointing_model_skydist}{Left: The
@@
 Right: The distribution of the pointing calibration sources across the
-local sky in Hawaii.  Notice the good sampling of the entire region
-used for the Survey.}{fig:PointingCalibrators}{1.0}
-
+local sky in Hawaii during the July 2007 epoch when the pointing model
+was constructed.  Notice the good sampling of the entire region used
+for the Survey.}{fig:PointingCalibrators}{1.0}
+% -----------------------------------------------------------------------------
+
+% 9
+% -----------------------------------------------------------------------------
 \begin{figure}
@@
   \subfigure[The residuals of the pointing model.  Note the Gaussian
-distribution.]{\label{fig:PointingModel-b}\includegraphics[scale=0.7]{pointing_model_residuals}}
-
-\caption{Pointing model.}
+distribution.]
+{\label{fig:PointingModel-b}\includegraphics[scale=0.5]{pointing_model_residuals}}
+
+\caption{The Bolocam pointing model for Epoch V.}
+\label{fig:PointingModel}
 \end{figure}
+% -----------------------------------------------------------------------------
+
+% 10
+% -----------------------------------------------------------------------------
+\begin{figure}
+
+  \subfigure[{\it Left}: the Bolocam map in a portion of the $l=30$
+  field.  {\it Right}: the SLC maps in the same region.  The green
+  contours on the Bolocam map indicate the positions of the SLC
+  sources.]
+  {\label{fig:SCUBAPointingComparison-a}\includegraphics[scale=0.8]
+  {scuba_bolocam_l030}}
+
+  \begin{tabular}{cc}
+
+  \subfigure[The cross-correlation map of the BGPS and SLC maps in
+  Figure \ref{fig:SCUBAPointingComparison-a}. {\bf to be replaced with
+  correct map}]
+  {\label{fig:SCUBAPointingComparison-b}\includegraphics[scale=0.45]
+  {xcorr_standin}}
+
+  \subfigure[The measured offset between Bolocam and SCUBA Legacy
+sources \citep{difrancesco08}, using the method described in Setion
+\ref{sec:SCUBAPointingComparison}.  The circle indicates the $1\sigma$
+region, which is also consistent with the error derived from the
+internal Bolocam pointing model.]
+{\label{fig:SCUBAPointingComparison-c}\includegraphics[scale=0.45]
+{scuba_pointing_offsets}}
+
+\end{tabular}
+
+\caption{Comparing the Bolocam positions to those of the SCUBA Legacy Catalog.}
+\label{fig:SCUBAPointingComparison}
+\end{figure}
+% -----------------------------------------------------------------------------
 
@@
 
-%\Figure{eachpca}{The effect of the number of iterations on
-%the reduction process.}{fig:Iter}{1.0}
-
 \subsection{Atmosphere Fluctuation Noise Model}
@@
 
-\Figure{flagger_plots}{An illustration of a ``glitch'' in a single
-bolometer timestream (red) due to a cosmic ray strike.  Note the
-acausal ringing due to the application of the downsampling filter.
-The time series for a physically adjacent bolometer is shown in blue,
-and a bolometer which does not pass over a source in green.  The PCA
-model has already been subtracted from the
-data.}{fig:CosmicRayGlitch}{1.0}
-
-\Figure{crs}{The distribution of glitch amplitudes flagged and
-removed from the data.  The expected contribution to the noise from
-the unremoved glitches below the detection threshold is
-\TBD.}{fig:GlitchDistribution}{1.0}
-
 \subsection{Data Flagging}
@@
 ensure data quality.  We used a ``waterfall''
-
-\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of the
-flagging process using the waterfall plot. Left: The glitch apparent at middle
-right is the same one whose time series is shown in Figure
-\ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the effect of the
-glitch also propagates over the other bolometers, appearing as a horizontal
-stripe. Right: The same data displayed with the time point including the glitch
-flagged out and rescaled}  {fig:Flag1}{1.0}
-
-%this figure failed to create automatically and wasn't really that useful
-%anyway
-% \Figure{flagger_glitchboxflagged}{A box is drawn around the bad data and it is
-% removed from subsequent analysis.}{fig:Flag2}{1.0}
-
-% \Figure{flagger_glitchgone}{A rescaled version of the data with the
-% bad data removed.  The effect of the glitch on the other bolometers is
-% now more apparent; this too is flagged out in subsequent
-% analysis.}{fig:Flag3}{1.0}
 
@@
 
-\Figure{l001_deconvolutionkernelcompare}{The effect of
-deconvolution on the iterative process can be seen in its effect on
-the residuals. From left to right: map, noise, smoothmap, model. Top
-to bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
+\setcounter{subfig}{1}
+\renewcommand{\thefigure}{\arabic{figure}\alph{subfig}}
+
+\begin{figure}
+  \begin{minipage}{6.5in}
+    \begin{center}
+      \includegraphics[scale=0.9]{iterative_mapping1}
+      \caption{An example of the change in the time series as
+      iterative mapping proceeds.}
+    \end{center}
+    \label{fig:IterativeMapping}
+  \end{minipage}
+\end{figure}
+
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
+
+\begin{figure}
+  \begin{minipage}{6.5in}
+    \begin{center}
+      \includegraphics[scale=0.9]{iterative_mapping2}
+      \caption{}
+    \end{center}
+    \label{fig:IterativeMapping-b}
+  \end{minipage}
+\end{figure}
+
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
+
+\begin{figure}
+  \begin{minipage}{6.5in}
+    \begin{center}
+      \includegraphics[scale=0.9]{iterative_mapping3}
+      \caption{}
+    \end{center}
+    \label{fig:IterativeMapping-c}
+  \end{minipage}
+\end{figure}
+
+% -----------------------------------------------------------------------------
+\setcounter{subfig}{1}
+\begin{figure}
+  \begin{minipage}{3.25in}
+    \begin{center}
+      \includegraphics[scale=0.5]{flagger_withglitch}
+    \end{center}
+  \end{minipage}
+  \begin{minipage}{3.25in}
+    \begin{center}
+      \includegraphics[scale=0.5]{flagger_glitchgone}
+    \end{center}
+  \end{minipage}
+  \caption{An illustration of the flagging process using the waterfall
+plot. Left: The glitch apparent at middle right is the same one whose
+time series is shown in Figure \ref{fig:CosmicRayGlitch}.  Because of
+the PCA subtraction, the effect of the glitch also propagates over the
+other bolometers, appearing as a horizontal stripe. Right: The same
+data displayed with the time point including the glitch flagged out
+and rescaled}
+
+  \label{fig:Flagger}
+
+  \addtocounter{figure}{-1} 
+  \addtocounter{subfig}{1}
+
+  \begin{minipage}{6.5in}
+    \begin{center}
+      \includegraphics[scale=0.5]{flagger_plots}
+      \caption{An illustration of a ``glitch'' in a single bolometer
+timestream (red) due to a cosmic ray strike.  Note the acausal ringing
+due to the application of the downsampling filter.  The time series
+for a physically adjacent bolometer is shown in blue, and a bolometer
+which does not pass over a source in green.  The PCA model has already
+been subtracted from the data.}
+    \end{center}
+  \end{minipage}
+
+\end{figure}
+
+% -----------------------------------------------------------------------------
+
+\renewcommand{\thefigure}{\arabic{figure}}
+
+%\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of
+%the flagging process using the waterfall plot. Left: The glitch
+%apparent at middle right is the same one whose time series is shown in
+%Figure \ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the
+%effect of the glitch also propagates over the other bolometers,
+%appearing as a horizontal stripe. Right: The same data displayed with
+%the time point including the glitch flagged out and rescaled}
+%{fig:Flaggin}{1.0}
+%
+\Figure{crs}{The distribution of glitch amplitudes flagged and removed
+from the data.  The expected contribution to the noise from the
+unremoved glitches below the detection threshold is
+\TBD.}{fig:GlitchDistribution}{1.0}
+
+\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution
+on the iterative process can be seen in its effect on the
+residuals. From left to right: map, noise, smoothmap, model. Top to
+bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
 7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which
@@
 7.2\arcsec\ kernel does.}{fig:Deconvolution}{1.0}
+
+\clearpage
 
@@
 
-Figure \ref{fig:PCA_filter}a shows the fraction of flux recovered in the map as a
+Figure \ref{fig:PCA_Filter}a shows the fraction of flux recovered in the map as a
 function of source size for a range of different PCA components subtracted in
@@
 
-Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered in the maps
-as a function of the deconvolution kernel used to create the astrophysical model
-maps.  The differences at large source sizes are not yet well-understood
-(!!!!!!), but at the smallest source size, it is evident that a deconvolution
-kernel smaller than the source size does not reliably recover the source flux.
-Therefore we chose a deconvolution kernel smaller than the beam but larger than
-the pixel size used.  Figure \ref{fig:Deconvolution} demonstrates the effects of using
-both too large and too small a kernel.
+Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered
+in the maps as a function of the deconvolution kernel used to create
+the astrophysical model maps.  The differences at large source sizes
+are not yet well-understood (!!!!!!), but at the smallest source size,
+it is evident that a deconvolution kernel smaller than the source size
+does not reliably recover the source flux.  Therefore we chose a
+deconvolution kernel smaller than the beam but larger than the pixel
+size used.  Figure \ref{fig:Deconvolution} demonstrates the effects of
+using both too large and too small a kernel.
 
@@
 
-%\Figure{esf}{The effective spatial filter applied to the Bolocam
-%maps due to atmospheric cleaning.}{fig:ESF}{1.0}
-
 \clearpage
 
-\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The fractional
-flux recovered as a function of source size for well-separated Gaussian sources with
-the FWHM as indicated.
-\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13
-(orange),16 (red),21 (teal),26 (lime),31 (black) PCA components subtracted.
-\emph{Right}: 7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
-kernel for 13 PCA components subtracted
-}{fig:PCA_filter}{1.0}
+\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The
+fractional flux recovered as a function of source size for
+well-separated Gaussian sources with the FWHM as indicated.
+\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13 (orange),16 (red),21
+(teal),26 (lime),31 (black) PCA components subtracted.  \emph{Right}:
+7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
+kernel for 13 PCA components subtracted }{fig:PCA_Filter}{1.0}
 

### 2009-04-06 methods/ms.tex
Test
More.

@@
 % 13) fig:GlitchDistribution
-% 14) fig:PCA_Filter
+% 14) fig:PCA_Graphical
 % 15) fig:Deconvolution
+% 16) fig:Noise
+% 17) fig:NoiseVsLongitude
+% 18) fig:PCA_Filter
+% 19) fig:AperturePhotometry
 
@@
 
-\FigureTwo{fluxcal_errorbars}{rel_flux_cal_050303_ob3_to_050405_o66}
+\FigureTwo{fluxcal_errorbars}{calib_vs_dc}
+%{rel_flux_cal_050303_ob3_to_050405_o66}
 %{calibration_plot_2004}
@@
 voltage, a proxy for atmospheric loading.  Red points are observations
-of Mars and black of Uranus.  Right: Scaling of the
-relative calibration with atmospheric loading for bolocam
-143. {\em To be replaced with new figure}}{fig:CalibrationCurves}{1.0}
+of Mars and black of Uranus.  Right: Scaling of the relative
+calibration with atmospheric loading for a single
+detector.}{fig:CalibrationCurves}{1.0}
 
@@
 
+\begin{figure}
+  \begin{minipage}{6.5in}
+    \begin{center}
+      \includegraphics[scale=0.8]{eachpca}
+    \end{center}
+  \end{minipage}
+\vspace{0.25in}
+  \begin{minipage}{6.5in}
+    \begin{center}
+      \includegraphics[scale=0.8]{eachpca_20iters}
+    \end{center}
+  \end{minipage}
+  \caption{{\it Top}: a grid of maps of the first 20 PCA components
+displayed at the same scale.  It is clear that NCG 7538, the object
+imaged, has correlated emission in each component.  There are varying
+levels of correlated noise in each component, with the first through
+third being the most obvious atmospheric components.  Most of the
+other noise components are probably various bits of correlated
+detector noise. {\it Bottom}: The same figure, but after 20
+iterations.  The figure is the breakdown of the atmosphere remainder
+(i.e. the raw data minus the astrophysical model) into eigenfunctions.
+Very little astrophysical flux remains at any level of correlation,
+though there is some at large (few arcminute) scales.}
+\label{fig:PCA_Graphical}
+
+\end{figure}
+
 \Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution
@@
 
-Figure \ref{fig:PCA_Filter}a shows the fraction of flux recovered in the map as a
-function of source size for a range of different PCA components subtracted in
-the cleaning.  These measurements were produced by inserting simulated gaussian
-sources at a range of peak flux densities and sizes spread out through the map
-and summing the flux in an ellipse on the final cleaned map.
+Figure \ref{fig:PCA_Filter}a shows the fraction of flux recovered in
+the map as a function of source size for a range of different PCA
+components subtracted in the cleaning.  These measurements were
+produced by inserting simulated gaussian sources at a range of peak
+flux densities and sizes spread out through the map and summing the
+flux in an ellipse on the final cleaned map.
 
@@
 using both too large and too small a kernel.
+
+\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The
+fractional flux recovered as a function of source size for
+well-separated Gaussian sources with the FWHM as indicated.
+\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13 (orange),16 (red),21
+(teal),26 (lime),31 (black) PCA components subtracted.  \emph{Right}:
+7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
+kernel for 13 PCA components subtracted }{fig:PCA_Filter}{1.0}
 
@@
 \clearpage
-
-\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The
-fractional flux recovered as a function of source size for
-well-separated Gaussian sources with the FWHM as indicated.
-\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13 (orange),16 (red),21
-(teal),26 (lime),31 (black) PCA components subtracted.  \emph{Right}:
-7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
-kernel for 13 PCA components subtracted }{fig:PCA_Filter}{1.0}
 
@@
 
+\section{FITS Header Information}
+\label{app:FITS_Header}
+
+\begin{verbatim}
+
+SIMPLE  =                    T / Written by IDL:  Sun Jan 18 01:21:05 2009      
+BITPIX  =                  -32 / Number of bits per data pixel                  
+NAXIS   =                    2 / Number of data axes                            
+NAXIS1  =                 3134 /                                                
+NAXIS2  =                  883 /                                                
+DATE    = '2009-01-18'         / Creation UTC (CCCC-MM-DD) date of FITS header  
+LONPOLE2=            180.00000 /lonpole                                         
+LATPOLE2=            0.0000000 /latpole                                         
+PPBEAM  =            21.276915 /pixels per beam                                 
+CALIB_0 =          -0.00333379 / 0th coefficient for flux cal                   
+CALIB_1 =             -2.92617 / 1st coefficient for flux cal                   
+CALIB_2 =              6.97269 / 2nd coefficient for flux cal                   
+ITERNUM =                    0 /Iteration number                                
+N_PCA   =                    0 /number of PCA components subtracted             
+COMMENT FITS (Flexible Image Transport System) format is defined in 'Astronomy  
+COMMENT and Astrophysics', volume 376, page 359; bibcode 2001A&A...376..359H    
+CTYPE1  = 'GLON-CAR'           / Coordinate Type                                
+CTYPE2  = 'GLAT-CAR'           / Coordinate Type                                
+EQUINOX =              2000.00 / Equinox of Ref. Coord.                         
+CD1_1   =    -0.00199999986216 / Degrees / Pixel                                
+CD2_1   =        0.00000000000 / Degrees / Pixel                                
+CD1_2   =       -0.00000000000 / Degrees / Pixel                                
+CD2_2   =     0.00199999986216 / Degrees / Pixel                                
+CRPIX1  =              1270.52 / Reference Pixel in X                           
+CRPIX2  =              366.367 / Reference Pixel in Y                           
+CRVAL1  =        191.092003456 / Galactic longitude of reference pixel          
+CRVAL2  =      0.0993870183708 / Galactic latitude of reference pixel           
+PV2_1   =        0.00000000000 /Projection parameter 1                          
+HISTORY PUTAST: Jan 18 01:10:42 2009 World Coordinate System parameters written 
+END
+
+\end{verbatim}
+
 \bibliography{milkyway}

### 2009-04-11 methods/ms.tex
Try again.

@@
 
+% Major Sections
+% sec:Introduction
+% sec:Observations
+% sec:FluxCalibration
+% sec:Astrometry
+% sec:Mapping
+
 % calibration
@@
 \newcommand{\vdag}{(v)^\dagger}
-\newcommand{\myemail}{jaguirre@nrao.edu}
+\newcommand{\myemail}{{\tt jaguirre@sas.upenn.edu}}
 \newcommand{\lsim}{{_{<}\atop^{\sim}}}
@@
 
-%\newpage
-%\pagebreak
-
-%\tableofcontents
-
-%\newpage
-%\pagebreak
+\newpage
+\pagebreak
+
+\tableofcontents
+
+\newpage
+\pagebreak
 
@@
       Pennsylvania, Philadelphia, PA }}}
-\email{\tt jaguirre@sas.upenn.edu}
+\email{\myemail}
 
@@
 \section{Introduction}
+\label{sec:Introduction}
 
@@
 emission from Galactic interstellar dust.  The great advantage of
-continuum observations at 1.1mm is that the mass column density does
-not depend strongly on the dust temperature $T_d$ (varying only
-linearly unless $T_d$ is less than about 10 K) and is independent of
-the gas volume density.  Using the same dust opacity as
-\citet{enoch06} and \citet{young06}, and assuming a gas-to-dust mass
-ratio $X$ of 100, the mass sensitivity can be written as
+continuum observations at 1.1mm is the low optical depth of the dust,
+permitting an estimate of the mass of the emitting region.  Further,
+the mass column density is independent of the gas volume density.
+
+Using the same dust opacity as \TBD\ ({\it put in original references})
+%\citet{enoch06} and \citet{young06},
+and assuming a gas-to-dust mass ratio $X$ of 100, the mass sensitivity
+can be written as
 \begin{equation} 
@@
 15$~mJy this corresponds to an RMS extinction sensitivity of $A_V\sim
-1$ mag, with the same $T_d$ dependence).  It is thus possible with a
-wide area, relatively shallow 1.1~mm survey to provide an unmatched,
-uniform inventory of massive star-forming and starless condensations.
+1$ mag, with the same $T_d$ dependence).  For Bolocam, $h\nu/k \approx
+13$~K, so for $T_d > XXX$ the dependence is approximately linear.  At
+the coldest temperatures expected, the mass changes a factor of 2.9
+between 20 and 10 K.  Far more important is the accurate determination
+of the distance to the clump.
+
+Thus it is thus possible with a wide area, relatively shallow 1.1~mm
+survey to provide an unmatched, uniform inventory of massive
+star-forming and starless condensations.
 
@@
 
+%\section{Overview of the Analysis}
+%\label{sec:Overview}
+
+{\it material from the Letter here}
+
+A number of different descriptions of the reduction of Bolocam data
+have been published \citep{laurent05,enoch06,sayers09}.  This work
+addresses the issues specific to the BGPS, significantly improving the
+method of \citet{enoch06} for generating maps and characterizing their
+properties.  It incorporates also some of the technical developments
+of \citet{sayers09}, though the exquisite control of systematics and
+noise of that analysis is neither necessary nor possible here.
+
 The outline of the paper is as follows. Section \ref{sec:Observations}
@@
 Section \ref{sec:Astrometry} describes the construction of an absolute
-reference frame for the observations and verification against
+reference frame for the observations and verification against other
+(sub)millimeter catalogs.  Section \ref{sec:Mapping}, \ref{sec:Noise},
+\ref{sec:Photometry}, \ref{sec:FinalMaps}, \ref{sec:Discussion}.
 
@@
     \begin{center}
-      \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
+ %     \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
       \caption{$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
@@
     \begin{center}
-      \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
+ %     \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
       \caption{$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
@@
     \begin{center}
-      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
-      \caption{$l=49.5$ to $l=74.5$.}
+%      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
+      \caption{$l=49.5$ to $l=74.5$.  \TBD\ Add annotations}
     \end{center}
@@
   \hspace{-1in}
-  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
-  \caption{The Cygnus Arm.}
+%  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
+  \caption{The Cygnus Arm. \TBD\ Add annotations}
 \end{figure}
@@
 \hspace{-0.5in}
-  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
-  \caption{Cloud complexes centered at $l=111$ in the Perseus Arm.}
+%  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
+  \caption{Cloud complexes centered at $l=111$ in the Perseus Arm. \TBD\ Add annotations}
 \end{figure}
@@
   \hspace{-1in}
-  \includegraphics[scale=0.8]{fig1_pg6_bw_inv_bar_label} 
-  \caption{W3/4/5}
+%  \includegraphics[scale=0.8]{fig1_pg6_bw_inv_bar_label} 
+  \caption{W3/4/5 \TBD\ Add annotations}
 \end{figure}
@@
 calibration and pointing model must be re-computed for each epoch to
-allow for changes in the instrument and optics.
+allow for variations in the instrument and optics.  We found that the
+flux calibration did not in fact differ significantly between epochs.
+For the pointing model, we computed a well-constrained version for
+Epoch V and aligned all images to this.
 
@@
 between adjacent rasters was 162\arcsec.  The total time for such a
-scan was between 39 and 48 minutes.  In order to fill in the
-instanteously undersampled focal plane, we began using in Epoch II a
-field rotator to mechanically align the focal plane at an optimal
-orientation along the scan direction to improve the sampling
-orthogonal to the scan direction.  This is shown in Figure
-\ref{fig:Array}.  The data were electronically sampled at 10 Hz along
-the scan direction, slightly higher than the Nyquist rate for the scan
-speed of 120\arcsec\ s$^{-1}$.  
+scan was between 39 and 48 minutes.  The data were electronically
+sampled at 10 Hz along the scan direction, slightly higher than the
+Nyquist rate for the scan speed of 120\arcsec\ s$^{-1}$.
+
+In order to fill in the instanteously undersampled focal plane, we
+began using in Epoch II a field rotator to mechanically align the
+focal plane at an optimal orientation along the scan direction to
+improve the sampling orthogonal to the scan direction.  This is shown
+in Figure \ref{fig:Array}.  Achieving good sampling is complicated by
+a number of missing pixels.  A simulation was performed to determine
+the optimal angle to rotate the array with respect to the scan
+direction to account for the beam spacing and missing pixels.  During
+the turnaround following a raster, the field rotator is adjusted to
+this optimum angle.
 %CHECK
+% per Adam, 2009/3/26
 Without the field rotator, the coverage shows variations of 100\% from
-pixel to pixel in a single raster of a field.  With the rotator
-
-The resulting coverage using the
-above scan pattern and the field rotator, is typically uniform to
-% per Adam, 2009/3/26
-
- with only a single pass across the field.
+pixel to pixel in a single raster of a field.  With the rotator, this
+is reduced to $\sim40\%$.
 
@@
 leaving our continuum measurements largely uncontaminated.  SO and
-CH3OH lines are probably the dominant contributors to line flux in the
-passband.  \citet{nummelin1998} found that 22\% of the flux in one
+CH$_3$OH lines are probably the dominant contributors to line flux in
+the passband.  \citet{nummelin1998} found that 22\% of the flux in one
 pointing towards Sgr B2 was from lines, and \citet{yoshida2005}
-reported $>40\%$ in Orion A from line emission} {fig:Bandpass}{1.0}
+reported $>40\%$ in Orion A from line emission. \TBD\ Other lines
+lying in the Bolocam passband include CS($5\to4$) and ($6\to5$) (245
+and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267 GHz).}
+{fig:Bandpass}{1.0}
 
 \Table
-{llll}
+{lllll}
 {Observing Epochs for the BGPS}
-{Begin (UT) & End (UT) & Nights & $\tau_{225}$ }
+{Number & Begin (UT) & End (UT) & Nights & $\tau_{225}$ }
 {tab:Observing}
 {
-2005 Jul 03 & 2005 Jul 13 & 5 & 0.1 \\
-2005 Sep 04 & 2005 Sep 12 & 5 & 0.1 \\
-2006 Jul 01 & 2006 Jul 13 & 5 & 0.1 \\
-2006 Sep 01 & 2006 Sep 09 & 5 & 0.1 \\
-2007 Jul 01 & 2007 Jul 13 & 5 & 0.1 \\
-2007 Sep 01 & 2007 Sep 09 & 5 & 0.1 \\
+I   & 2005 Jul 03 & 2005 Jul 13 & 5 & 0.1 \\
+II  & 2005 Sep 04 & 2005 Sep 12 & 5 & 0.1 \\
+III & 2006 Jul 01 & 2006 Jul 13 & 5 & 0.1 \\
+IV  & 2006 Sep 01 & 2006 Sep 09 & 5 & 0.1 \\
+V   & 2007 Jul 01 & 2007 Jul 13 & 5 & 0.1 \\
+VI  & 2007 Sep 01 & 2007 Sep 09 & 5 & 0.1 \\
 }
@@
 extracted from our map in the Cygnus Arm with those of
-\citet{motte07}.
+\citet{motte07} (M07).
+
+The figures of the Cygnus-X region presented by M07
+%Motte et al. (2009)
+, obtained at a central wavelength of 1.2 mm using the 30 meter IRAM
+telescope, appear nearly identical to the 1.1 mm Bolocam images.  The
+BGPS mapping strategy, larger beam, and field of view provides better
+recovery of the large scale structure of the dust continuum emission,
+but inferior angular resolution.  Nevertheless, there is excellent
+agreement between the structure revealed by the two data sets.
+
+The Bolocam and M07 data sets have flux calibration consistent within
+about 20\%.  However, direct comparison with the fluxes listed in M07
+is difficult due to the factor of three difference in the size of the
+beams used.  For example, the the brightest source in the Cyg-X region
+is DR 21.  While M07 quote a peak flux density per beam of
+4.2 Jy/beam for the brightest feature in the DR 21 complex (their peak
+N46) and 17.9 Jy/beam in a 0.19 x 0.14 pc box, BGPS measures a peak
+flux of 15.5 Jy/beam (the beam being roughly 31\arcsec\ in diameter).
+Fluxes are best compared using sources compact as observed with the
+beam of the IRAM 30 meter telescope.
+
+We have convolved the fits files\footnote{{\tt
+ftp://cdsarc.u-strasbg.fr/pub/cats/J/A+A/476/1243/fits/}} with a
+Gaussian kernel that generates an approximately 35\arcsec\ beam,
+matched to our images (mapped without application of the distortion
+correction).  The results are shown in Figure
+\ref{fig:CygnusComparison}.
+
+\Table
+{lll}
+{Flux density comparison with \citet{motte07}.}
+{
+Source  &   BGPS           &  Motte \\
+        &   peak mJy/beam  &  mJy in box (see Motte+ Table 1)
+}
+{tab:CygnusComparison}
+{
+ N11    &   350 - 550      &  340 \\
+ N12    &   1660-2200      &  1630 \\
+ N16    &   613            &  550 \\
+ N18    &   618            &  430 \\
+ N26    &   314            &  340 \\
+ N46    &   15500          &  17930  (DR21 S)
+}
 
@@
 
-Relative alignment was performed by finding the peak of the
-cross-correlation between images and a pointing master selected from
-the epoch with the best-constrained pointing model for that
-field. Each observation was initially mapped individually, then all
-observations of a given field were cross-correlated with a selected
-master image of that field. The cross-correlation peak was fit with a
-gaussian and the difference between the gaussian peak and the image
-center was used as the pixel offset. The offsets were recorded and
-written to the timestreams. Finally, all observations of a field were
-merged into a single timestream with pointing offsets applied to
-create the field mosaic.
+Relative alignment between different observations of the same field
+was performed by finding the peak of the cross-correlation between
+images and a pointing master selected from the epoch with the
+best-constrained pointing model for that field. (In almost all cases,
+this was from Epoch V.)  Each observation was initially mapped
+individually, then all observations of a given field were
+cross-correlated with a selected master image of that field. The
+cross-correlation peak was fit with a gaussian and the difference
+between the gaussian peak and the image center was used as the pixel
+offset. 
+%The offsets were recorded and written to the
+%timestreams. 
+Finally, all observations of a field were merged into a single
+timestream with pointing offsets applied to create the field mosaic.
 
@@
 flux density which would result if the the maps were coadded using the
-pointing model alone.
+pointing model alone, where each individual observation would be
+coadded with tthe 6\arcsec\ RMS uncertainty of the model.  The
+relative alignment using the correlation maps is typically accurate to
+\TBD\ $<1\arcsec$.
 
@@
 
-\subsection{Comparison to SCUBA Legacy Source Positions}
+\subsection{Comparison to SCUBA Legacy Catalog Source Positions}
 \label{sec:SCUBAPointingComparison}
@@
 
-The same cross-correlation procedure was used to compare to the SCUBA
-maps from the Legacy Catalog.  The morphological correlation between
-SCUBA and BGPS sources is excellent, so cross-correlation maps could
-be used to test our pointing model.
-
-An example is shown in Figure \ref{fig:SCUBAPointingComparison}.
-
-{\it Do the negative bowls of either survey bunge up the
-cross-correlation?  If not, how do we deal with them?}
-
-For the purposes of comparison of both flux and pointing with other
-surveys, we present in Appendix \ref{app:ReferenceSources} a selection
-of bright, compact, relatively isolated sources.
+All of the SCUBA 850 and 450 \mum\ data has been re-processed in a
+uniform manner and made publicly available as the SCUBA Legacy Catalog
+(hereafter SLC).  These maps provide an excellent cross-check on the
+accuracy of the BGPS pointing model.  We have used the same
+cross-correlation procedure as that used to obtain the relative
+alignment of Bolocam observations to compare to the SLC.  A number of
+concerns might arise in comparing the Bolocam to the SCUBA maps,
+including the differing scan strategies (SCUBA maps were typically
+taken in jiggle-map mode, which tends to remove extended structure)
+and the often restricted range of positions measured within an
+extended cloud for the SLC.  The cross-correlation technique actually
+mitigates these effects, since it does not require the establishment
+of a single position for an object (which may differ due to the change
+in wavlength between the surveys or due to the observing strategy) but
+rather makes use of all the information available.  In the event, the
+morphological correlation between SCUBA and BGPS sources is generally
+excellent, giving a high degree of confidence to the comparison and to
+the results obtained from the pointing model.  An example is shown in
+Figure \ref{fig:SCUBAPointingComparison}.  We find that the RMS offset
+between BGPS and SLC positions within a $3\arcdeg \times 1\arcdeg$
+bloc defined by the BGPS is \TBD\ a few arcseconds, consistent with
+the errors derived for the Bolocam pointing model.
+
+For the purposes of future comparison of both flux and pointing with
+other surveys, we present in Appendix \ref{app:ReferenceSources} a
+selection of bright, compact, relatively isolated sources.
 
@@
 local sky in Hawaii during the July 2007 epoch when the pointing model
-was constructed.  Notice the good sampling of the entire region used
-for the Survey.}{fig:PointingCalibrators}{1.0}
+was constructed.  Note the good sampling built up over the range of
+sky observed in the Survey.}{fig:PointingCalibrators}{1.0}
 % -----------------------------------------------------------------------------
@@
   contours on the Bolocam map indicate the positions of the SLC
-  sources.]
+  sources.  \TBD\ {\it Do the negative bowls of either survey bunge up
+  the cross-correlation?  If not, how do we deal with them?  The SCUBA
+  image here has been somewhat doctored because of a large DC offset
+  in the diagonal filament at center}]
   {\label{fig:SCUBAPointingComparison-a}\includegraphics[scale=0.8]
@@
 \end{equation}
-where $A$ encodes the pointing information and $W$ is the covariance
-matrix of the noise $\epsi$.  Note that the mapping from data to map
-is a linear operator, $M =(A^T W A) A^T W$.  For compactness, Equation
-\ref{eq:LSMap} will be written as $M[d] = m$.  Note that the mapping
-operation is not invertible.  However, note that given a map $m$,
+where $A$ encodes the pointing information and $W$ is the inverse of
+the covariance matrix of the time domain noise $\epsi$,
+\begin{equation}
+W = {\langle \epsi_i \epsi_j \rangle}^{-1}
+\end{equation}
+In this case, the mapping from data to map is a linear operator, $M
+=(A^T W A) A^T W$.  For compactness, Equation \ref{eq:LSMap} will be
+written as $M[d] = m$.  Note that the mapping operation is not
+invertible.  However, given a map $m$ and an observing matrix $A$,
 there exists a linear operation which makes predictions about the
@@
 
-We proceed iteratively as follows. 
+We proceed iteratively, estimating $a$ and $e$ in the order of their
+relative strengths, beginning with the atmosphere.  The first
+iteration step is then
 \begin{equation}
@@
 \end{equation}
-We note that it is possible to produce an ``error map''
+where ${\cal D}$ represents the deconvolution operation.  At this
+stage, the iterative process could begin again with Equation
+\ref{eq:FirstIterStep}, though it is highly useful to produce an
+``error map''
 \begin{equation}
-N = M[d_i(t) - \tilde{s}^{(n)}_i(t) - \tilde{a}^{(n)}_i(t) - 
+E = M[d_i(t) - \tilde{s}^{(n)}_i(t) - \tilde{a}^{(n)}_i(t) - 
 \tilde{e}^{(n)}_i(t)]
 \end{equation}
-The process then begins again with Equation \ref{eq:FirstIterStep}.
+This error map serves as a straightforward visualization of the
+progress of the iterative method, since in a perfect process it would
+be map of $\epsi$.
 
@@
 be highly correlated between detectors.
+
+To further remove the atmosphere (and other correlated instrument
+noise) without a detailed physical model, we use a principal component
+analysis (PCA) as given in \citet{laurent05}.
 
@@
 low correlation with astrophysical signal, this step is performed only
-once and is not iterated.
+once and is not iterated (c.f. Figure XXX of \citet{sayers09}).
 
@@
 necessary to develop new tools to quickly visualize the data and
-ensure data quality.  We used a ``waterfall''
+ensure data quality.  A common tool in radio astronomy is the
+so-called ``waterfall'' plot, which is an image with frequency on the
+x-axis, time on the y, and an intensity proportional to the
+interferometer visibility amplitude or phase.  We have used a variant
+on this to visualize the Bolocam data by displaying bolometer number
+(related to the bolometer position in the focal plane) on the x-axis
+and time on the y, with the intensity given by the bolometer's
+response (in Jy) at that time.  An example of this is shown in Figure
+\ref{fig:Flagger}.  With practice, anomalies such as the glitch shown
+can be detected and manually and iteractively flagged out.
 
@@
 variance of the fluxes assigned to each pixel, we used the median
-average deviation over the data in the pixel and rejected high and low
+average deviation (MAD) over the data in the pixel and rejected high and low
 outliers at the 3-sigma level.  Pixels with too little data to compute
@@
 
-WRITTEN POORLY: 
+%WRITTEN POORLY: 
 The timestream data is made into a spatial map using the pointing data
-corresponding to each time point for each bolometer.  The data is weighted
-by inverse variance across a single scan and then drizzled into a map with
-$7.2$\farcs pixels using a nearest-neighbor algorithm.  The nearest-neighbor
-matching allows the map to be returned to a timestream in the same manner, 
-but with the S/N improved by averaging over all hits on a given pixel.
+corresponding to each time point for each bolometer.  The data is
+weighted by inverse variance across a single scan and then drizzled
+into a map with $7.2$\arcsec\ pixels using a nearest-neighbor
+algorithm.  The nearest-neighbor matching allows the map to be
+returned to a timestream in the same manner, but with the S/N improved
+by averaging over all hits on a given pixel.  It has the disadvantage
+that it accentuates the unevenness of the cross-scan sampling, since
+ech timestream point's value is assigned to an area much smaller than
+the beam.
+
+The resulting map is then subjected to a Hogbom-type CLEAN algorithm
+\citep{hogbom} using a specified kernel to produce a deconvolved
+image.  This has several advantages over the
 
@@
 noise levels obtained in the various fields of the BGPS also varies.
-
-\Figure{survey_depth}{The depth of the BGPS in the first quadrant
-as a function of Galactic longitude.  Black is the standard deviation
-of $0.9\arcdeg \times 0.9\arcdeg$ degree blocks centered on $b=0$ and
-the longitude indicated; red is similar, but the estimator is
-median(1/sqrt(weight map).}{fig:Depth}{1.0}
-
-The depth can be converted into an estimate of mass via standard
-estimates.
-
-\section{Photometry}
+However, the noise within a given $1\arcdeg \times 1\arcdeg$ field is
+fairly uniform in the absence of very bright sources.  We show the
+variation of the depth as a function of Galactic longitude in Figure
+\ref{fig:NoiseVsLongitude}.  The depth can be converted into an
+estimate of mass via standard estimates, i.e., under the assumption of
+a temperature, opacity, and distance.
+
+\Figure{survey_depth}{The depth of the BGPS in the first quadrant as a
+function of Galactic longitude.  Black is the standard deviation of
+$0.9\arcdeg \times 0.9\arcdeg$ degree blocks centered on $b=0$ and the
+longitude indicated for the error maps $E$; red is similar, but the
+estimator is median(1/sqrt(weight map).}{fig:NoiseVsLongitude}{1.0}
+
+\section{Effect of the Analysis on Photometry}
+\label{sec:Photometry}
 
@@
 understanding of the spatial filtering imposed by the observing
-strategy and the cleaning and mapping of the data.
+strategy and the cleaning and mapping of the data.  Quite apart from
+the issues discussed in this section are the issues of identifying
+sources with complex morphology and defining the regions over which to
+do the aperture.  This is discussed in \citet{rosolowsky09}.  Here we
+merely deal with the limitations on performing photometry imposed by
+the data analysis itself.
 
@@
 flux densities and sizes spread out through the map and summing the
-flux in an ellipse on the final cleaned map.
-
-Real data with the astrophysical source model removed were used as the
-background.  Because this is real data, at lower numbers of PCA components
-subtracted, the atmosphere still dominates the total measured flux, which is
-particularly evident for the largest sources.
+flux in an ellipse on the final cleaned map. Real data with the
+astrophysical source model removed were used as the background.
+
+The final reduction used 13 PCA components because this produced a
+reasonable compromise between attenuating extended structure and
+attaining high S/N on compact faint objects.
 
@@
 7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
-kernel for 13 PCA components subtracted }{fig:PCA_Filter}{1.0}
+kernel for 13 PCA components subtracted. \TBD\ {\it Remove sources
+with sizes smaller than the beam.  Are the sizes FWHM or something
+else?} }{fig:PCA_Filter}{1.0}
 
@@
 
-%\clearpage 
-%
-%\Figure{deconvolution_comparison}{The fractional flux lost as a function of
-%source size for well-separated Gaussian sources with the FWHM as
-%indicated.  Legend: Size of deconvolution kernel used to make model }{fig:deconv_filter}{1.0}
-
-\section{Final Maps}
+\section{Final Maps and Data Release}
+\label{sec:FinalMaps}
 
@@
 
-Noise maps are produced for each map, containing ...
-
-\section{Public Data Release}
+Noise maps are produced for each map, made from the residuals after
+removing the astrophysical signal model as well as the PCA component
+model.  These maps are useful for diagnosing the effect of the
+iterative process on bright sources and as a method of obtaining an
+estimate of the noise.
+
+%\section{Public Data Release}
 
@@
 
-\section{Summary}
+\section{Discussion}
+\label{sec:Discussion}
 

### 2009-04-11 methods/ms.tex
Yup.

@@
 % sec:Mapping
+% sec:Noise
+% sec:Photometry
+% sec:FinalMaps
+% sec:Discussion
 
@@
 \usepackage{subfigure}
+\usepackage{datetime}
+\usepackage{fmtcount}
+
+\newtimeformat{edttime}{\twodigit{\THEHOUR}:\twodigit{\THEMINUTE}~EDT}
+\settimeformat{edttime}
+\newdateformat{eurodate}{\dayofweekname{\THEDAY}{\THEMONTH}{\THEYEAR} \THEDAY \monthname[\THEMONTH] \THEYEAR}
 
@@
 
+% -----------------------------------------------------------------------------
+% BGPS specific definitions
 \def\bgps{BGPS}
@@
 \newcommand{\bcamfwhm}{31.2\arcsec}
-\newcommand{\ncores}{$10^4$}
+\newcommand{\ncores}{7628}
 \newcommand{\bgpsdepthlow}{20}
 \newcommand{\bgpsdepthhigh}{50}
+% -----------------------------------------------------------------------------
 
@@
 
-\slugcomment{DRAFT: \today}
+\slugcomment{DRAFT: \currenttime\ \eurodate\today}
 
@@
 
-\newpage
-\pagebreak
-
-\tableofcontents
-
-\newpage
-\pagebreak
+%\newpage
+%\pagebreak
+%
+%\tableofcontents
+%
+%\newpage
+%\pagebreak
+%
 
@@
 the 1st, 2nd, and 3rd quadrants.  The BGPS represents the first large
-area, systematic survey of the Galactic Plane in the (sub)millimeter
-continuum without pre-selected targets.  The survey has detected
-\ncores\ clumps to a limiting depth of between \bgpsdepthlow\ and
-\bgpsdepthhigh\ mJy RMS.  This paper details the survey observations
-and methods.  We treat carefully the comparison of the survey pointing
-and flux calibration and and serves as a companion to the public data
-release through NASA's Infrared Processing and Analysis Center (IPAC).
-We anticipate that the BGPS will be useful as a finder chart for ALMA
-and as a long-wavelength complement to {\em Herschel}-HiGAL.
+area, systematic survey of the Northern Galactic Plane in the
+(sub)millimeter continuum without pre-selected targets.  The survey
+has detected \ncores\ clumps to a limiting depth of between
+\bgpsdepthlow\ and \bgpsdepthhigh\ mJy RMS.  We include maps of 100
+contiguous square degrees from $l=-10.5$ to $l=86.5$ and $b=\pm0.5$
+with a resolution of 31\arcsec, as well as regions in IC1396, $l=111$
+(NGC7538), W3/4/5, and Gem OB1.  The most striking feature of the maps
+is the filamentary structure of cold dust throughout the Galaxy.
+
+This paper details the survey observations and methods.  We treat
+carefully the determination of pointing and flux calibration errors
+and compare our results to the literature.  Data processing algorithms
+that separate astronomical signals from time-variable atmospheric flux
+in the data time-stream are discussed.  The algorithms reproduce the
+structure of the astronomical sky on a limited range of angular scales
+and produce artifacts in the vicinity of bright sources. Specifically,
+extended emission smooth on scales larger than about 5\arcmin\ is not
+fully recovered in the images.  The spatial frequency response
+function of the Bolocam Galactic Plane Survey is discussed.
+
+This paper serves as a companion and guide to the public data release
+through NASA's Infrared Processing and Analysis Center (IPAC).  These
+images represent an important finder chart for future observations
+with ALMA and a long-wavelength spectral band complementary to
+imminent submillimeter surveys with SCUBA-2 and Herschel-SPIRE.
 
@@
 of the material most directly associated with the formation of
-planetary systems, stars, and star clusters
-\citep{johnstone06}.  Galactic dust continuum radiation at
-this wavelength is optically-thin almost everywhere, and at typical
-dust temperatures of order 10 K or more, is observed on the
-Rayleigh-Jeans tail of the Planck function.  Thus, the determination
-of column densities is relatively straight forward if the dust
-temperature is known.
+planetary systems, stars, and star clusters \citep{johnstone06}.
+Galactic dust continuum radiation at this wavelength is optically-thin
+almost everywhere, and at typical dust temperatures of order 10 K or
+more, is observed on the Rayleigh-Jeans tail of the Planck function.
+Thus, the determination of column densities is relatively straight
+forward if the dust temperature is known.
+
+Submillimeter observations of Galactic sources have been conducted by
+a variety of different groups focusing on small regions since
+bolometer technology was developed.  The Submillimeter Common-User
+Bolometer Array (SCUBA) on the 15 m James Clerk Maxwell Telescope
+mapped many significant regions in the galactic plane over its 8 year
+lifetime \citep{holland99,difrancesco08}, but never completed a
+contiguous survey of the galactic plane.  Bolocam and Mambo have
+previously been used to map large star forming regions at 1.1
+\citep{enoch06} and 1.2 mm \citep{motte07}, but again these were
+targeted observations.  A recent large area survey with the LABOCA
+instrument at 870 \mum\ has recently been reported \citep{schuller09}.
+
+Surveys of the galaxy in CO line emission \citep{dame01,FCRAO} have
+revealed much about galactic structure, but do not provide a complete
+picture of how star formation follows that structure.  Millimeter
+continuum more directly traces the cold dust associated with star
+formation.  Continuum data allows for accurate determinations of the
+mass of large, dense dust structures when combined with kinematic
+distances \citep[e.g.][]{RotationCurve}.
 
@@
 
-%\section{Overview of the Analysis}
-%\label{sec:Overview}
-
-{\it material from the Letter here}
-
-A number of different descriptions of the reduction of Bolocam data
-have been published \citep{laurent05,enoch06,sayers09}.  This work
-addresses the issues specific to the BGPS, significantly improving the
-method of \citet{enoch06} for generating maps and characterizing their
-properties.  It incorporates also some of the technical developments
-of \citet{sayers09}, though the exquisite control of systematics and
-noise of that analysis is neither necessary nor possible here.
+At the distances that we are observing these objects, we are likely
+observing aggregates of star forming cores found in a larger molecular
+cloud environment, which we will refer to as clumps
+\citep{williams00}.
 
@@
 on the coverage obtained via Bolocam raster scans.}{fig:Array}{1.0}
+
+\section{Overview of the Data Reduction}
+\label{sec:Overview}
+
+%{\it material from the Letter here}
+
+A number of different descriptions of the reduction of Bolocam data
+have been published \citep{laurent05,enoch06,sayers09}.  This work
+addresses the issues specific to the BGPS, significantly improving the
+method of \citet{enoch06} for generating maps and characterizing their
+properties.  It incorporates also some of the technical developments
+of \citet{sayers09}, though the exquisite control of systematics and
+noise of that analysis is neither necessary nor possible here.
+
+The data were reduced with a custom pipeline written specifically for
+the galactic plane survey based on \citet{enoch06} and
+\citet{Laurent2006}.  A key element of the reduction is the iterative
+estimation of the atmospheric fluctuations and the astrophysical
+signal.  The atmospheric model is developed from a set of principal
+components of the bolometer signal time series under the assumption
+that the bulk of the correlated signal is atmospheric.  The iterative
+estimation process then helps to restore correlated flux due to
+astrophysical emission \citep[details in][]{Aguirre2009}.
+
+The Bolocam observations are sensitive to structure between 31\arcsec\
+and about 400\arcsec\ (the array field of view).  An indicative
+analysis of the spatial filter function of the iterative mapping
+scheme is given in \citet{enoch06}.  The data were sampled onto a
+uniform 7\farcs2 grid.  Flux density calibrations were performed using
+observations of Mars, Uranus, and Neptune, and they are accurate to
+$\sim$20\%.
+
+%A calibration scheme capable of
+%5\% systematic and $<$5\% statistical errors is being implemented as outlined in
+%\citet{Sayers2009}.
+%To account for offsets between the observations, each observation was mapped
+%individually and aligned to a `master' field that has been tied to
+%pointing calibrators. 
+Noise properties across the survey are not completely uniform, but the
+measured $1\sigma$ level is $\approx43\pm7$ mJy/beam within the
+$b=\pm.5$ portion of the plane.
+%After the pipeline mapping, the fields were combined using the COMBINE
+%command in IRAF with WCS offsets.
+
+The absolute pointing accuracy of the survey has been measured to be
+$\sim$6\arcsec\ RMS.  A single $3^\circ \times 1^\circ$ observation of
+each region was registered to the pointing calibrators as a `master
+field,' and additional observations of that field were aligned to the
+master.
+
+Bright and large sources leave an impact on their surroundings when
+cleaned with a principal component subtraction.  \object{Sgr B2},
+\object{G 34.3+0.15}, and other sources with fluxes $\geq 10$ Jy are
+surrounded by substantial negative bowls.  Some flux is restored in
+these bowls using the iterative process described in
+\citet{Aguirre2009}, but around the brightest sources the impact of
+the source on the background estimation is too great to be fully
+recovered.
+
+Instrument glitches and cosmic ray hits have been removed by a
+combination of outlier rejection in each spatial pixel and hand
+flagging of the timestream data.  Streaking in the images results from
+incorrect determinations of the zero level across scans when a bright
+source is encountered.  Atmospheric noise in observations taken in
+poor weather may not be completely removed by the reduction
+procedures.
+%Particular bolometers may be noisy for a single observation and they may not
+%be adequately down-weighted.
 
@@
 IPAC\footnote{http://irsa.ipac.caltech.edu/Missions/bolocam.html}.
+IPAC provides a cutout service for the
 
@@
 gas most intimately associated with the earliest phases of star
-formation.
+formation.  Inspection of Figure \ref{fig:BGPSMontage}
+
+Figures 1 and 2 show the results of the BGPS.  Our images show
+excellent correspondence with SCUBA maps of small sub-fields
+throughout the plane \citep{SCUBAlegacy}.  BGPS contours overlaid on
+the GLIMPSE survey \citep{benjamin03} show excellent correlation with
+8\mum\ infrared dark clouds (IRDCs).  However, many features in the
+BGPS maps do not appear in the Spitzer observations, which suggests
+that the 1.1 mm emission traces dense clumps without a background to
+absorb.  A study of IRDC correlation with BGPS emission is underway
+\citep{Battersby2009}.
+
+% implies star forming....
+
+Filamentary structures with aspect ratios $\geq 10$ are present
+throughout the galactic plane.  The most crowded fields consist of
+frothy and clumpy structure.  There are 5000-10000 distinct sources,
+the majority of which are at least moderately resolved
+\citep{rosolowsky09}.  We suspect that higher resolution observations
+will resolve BGPS clumps into clusters of protostellar objects, as has
+been seen in Serpens \citep{enoch08,Testi1998} and OMC 1
+\citep{Beuther2004,johnstone99} where bolometer observations at low
+resolution have been complemented by interferometer observations at
+high resolution.
+
+There are clear maxima in the emission filling factor in the Galactic
+Center and in the region from $l=23$ to $l=31$, the line of sight
+through the densest part of the molecular ring.  Additional areas of
+high source density are seen at $l=10$ and $l=13$.  The filling factor
+of 1.1 mm continuum emission at the 100 mJy level is $\sim 20$\% per
+square degree from $l=-10$ to $l=20$ and $\sim 10$\% from $l=20$ to
+$l=50$.
+%In the range
+%$l=50$ to $l=75$, the filling factor is below 1\% and very few sources have
+%been detected.  
+This result is in contrast to CO filling factors $\sim1$ in the inner galactic
+plane \citep{dame01,FCRAO}, confirming that 1.1 mm continuum emission traces
+denser material than CO.  
+%The small filling factor of the 1.1 mm emission
+%compared to CO emission  shows that the continuum is directly associated with
+%star forming material, whereas the CO also traces less dense material not
+%directly associated with star formation.
+
+In some cases, distance to BGPS clumps can be determined by matching
+Galactic Ring Survey $^{13}$CO and 1.1 mm continuum morphology
+\citep{IRDCdistance,FCRAO}.  However, in other cases the association
+between the CO and 1.1 mm data is not clear, either because of
+confusion or because the BGPS sources are too compact to identify in
+$^{13}$CO morphology.  Heterodyne follow-up observations using dense
+gas tracers (NH$_3$, N$_2$H$^+$, HCO$^+$, and CS) are being conducted
+to provide radial velocity, density, chemistry, and temperature
+measurements \citep{schlingman09, battersby09, nordhaus09}.
+
+BGPS clumps are associated with the densest portions of giant
+molecular clouds (GMCs) traced by CO surveys
+\citep[e.g.,][]{dame01,FCRAO}.  The brightest clumps visible in our
+maps, e.g. \object{Sgr B2}, \object{G34.3+0.15}, \object{W 51},
+\object{W 43}, \object{W 49}, and \object{M 17}, correspond to well
+known star forming regions.
+%(the saturation is only a display artifact; the astrophysical sources are
+%always much fainter than the atmosphere and therefore do not saturate the
+%detectors).  
+These associations suggest that other bright sources of millimeter
+emission will prove to be massive star or cluster forming regions.
 

### 2009-04-11 methods/ms.tex
Yee haw!

@@
 % -----------------------------------------------------------------------------
+% Missions
+\def\spitzer{{\em Spitzer}}
+% -----------------------------------------------------------------------------
 
@@
 the mass column density is independent of the gas volume density.
-
-Using the same dust opacity as \TBD\ ({\it put in original references})
-%\citet{enoch06} and \citet{young06},
-and assuming a gas-to-dust mass ratio $X$ of 100, the mass sensitivity
-can be written as
-\begin{equation} 
-\label{eq:Mass}
-M_{gas}\approx
-0.22\left( e^{12.9/T_d}-1 \right) \left({S_\nu\over 15\; {\rm mJy}} \right)
-D^{2}_{kpc} \msol 
-\end{equation}
-where $D_{kpc}$ is the distance to the source in kpc.  (At $S_\nu =
-15$~mJy this corresponds to an RMS extinction sensitivity of $A_V\sim
-1$ mag, with the same $T_d$ dependence).  For Bolocam, $h\nu/k \approx
-13$~K, so for $T_d > XXX$ the dependence is approximately linear.  At
-the coldest temperatures expected, the mass changes a factor of 2.9
-between 20 and 10 K.  Far more important is the accurate determination
-of the distance to the clump.
-
 Thus it is thus possible with a wide area, relatively shallow 1.1~mm
@@
 multi-wavelength and high-resolution studies with existing telescopes
-and future facilities.  The clump catalog is described in a companion
-paper \citep{rosolowsky09}.
-
-At the distances that we are observing these objects, we are likely
-observing aggregates of star forming cores found in a larger molecular
-cloud environment, which we will refer to as clumps
-\citep{williams00}.
+and future facilities.  At the distances that we are observing these
+objects, we are likely observing aggregates of star forming cores
+found in a larger molecular cloud environment, which we will refer to
+as clumps \citep{williams00}.  The clump catalog is described in a
+companion paper \citep{rosolowsky09}.
 
@@
 describes the instrument and the observations.  Section
-\ref{sec:FluxCalibration} describes the flux calibration and errors.
-Section \ref{sec:Astrometry} describes the construction of an absolute
-reference frame for the observations and verification against other
-(sub)millimeter catalogs.  Section \ref{sec:Mapping}, \ref{sec:Noise},
-\ref{sec:Photometry}, \ref{sec:FinalMaps}, \ref{sec:Discussion}.
+\ref{sec:Overview} briefly describes the data reduction process, while
+Sections \ref{sec:FluxCalibration} to \ref{sec:FinalMaps} provide
+greater detail on flux calibration, astrometry, the mapping algorithm,
+noise, photometry, and the public data release.  We conclude in
+Section \ref{sec:Discussion} with brief discussion of the immediate
+implications of the emission revealed by the BGPS.
 
@@
     \begin{center}
- %     \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
+      \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
       \caption{$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
@@
     \begin{center}
- %     \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
+      \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
       \caption{$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
@@
     \begin{center}
-%      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
+      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
       \caption{$l=49.5$ to $l=74.5$.  \TBD\ Add annotations}
@@
   \hspace{-1in}
-%  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
+  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
   \caption{The Cygnus Arm. \TBD\ Add annotations}
@@
 \hspace{-0.5in}
-%  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
+  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
   \caption{Cloud complexes centered at $l=111$ in the Perseus Arm. \TBD\ Add annotations}
@@
   \hspace{-1in}
-%  \includegraphics[scale=0.8]{fig1_pg6_bw_inv_bar_label} 
+  \includegraphics[scale=0.8]{fig1_pg6_bw_inv_bar_label} 
   \caption{W3/4/5 \TBD\ Add annotations}
@@
 
-%\include{bgps_methods_observations}
 \section{Observations}
 \label{sec:Observations}
-
-%\subsection{Instrument}
 
@@
 
-%{\it material from the Letter here}
+{\it just stole material from the Letter here - needs a bit of cleaning up}
 
@@
 The data were reduced with a custom pipeline written specifically for
-the galactic plane survey based on \citet{enoch06} and
-\citet{Laurent2006}.  A key element of the reduction is the iterative
-estimation of the atmospheric fluctuations and the astrophysical
-signal.  The atmospheric model is developed from a set of principal
-components of the bolometer signal time series under the assumption
-that the bulk of the correlated signal is atmospheric.  The iterative
-estimation process then helps to restore correlated flux due to
-astrophysical emission \citep[details in][]{Aguirre2009}.
+A key element of the reduction is the iterative estimation of the
+atmospheric fluctuations and the astrophysical signal.  The
+atmospheric model is developed from a set of principal components of
+the bolometer signal time series under the assumption that the bulk of
+the correlated signal is atmospheric.  The iterative estimation
+process then helps to restore correlated flux due to astrophysical
+emission (Section \ref{sec:Mapping}).
 
@@
 observations of Mars, Uranus, and Neptune, and they are accurate to
-$\sim$20\%.
+$\sim$20\%.  This is described in \ref{sec:FluxCalibration}.
 
@@
 $\sim$6\arcsec\ RMS.  A single $3^\circ \times 1^\circ$ observation of
-each region was registered to the pointing calibrators as a `master
-field,' and additional observations of that field were aligned to the
-master.
+each region was registered to the pointing calibrators as a ``master
+field'', and additional observations of that field were aligned to the
+master (Section \ref{sec:Astrometry}).
 
@@
 surrounded by substantial negative bowls.  Some flux is restored in
-these bowls using the iterative process described in
-\citet{Aguirre2009}, but around the brightest sources the impact of
-the source on the background estimation is too great to be fully
-recovered.
+these bowls using the iterative process 
+%described in \citet{Aguirre2009}
+, but around the brightest sources the impact of the source on the
+background estimation is too great to be fully recovered (Section
+\ref{sec:Photometry}).
 
@@
 poor weather may not be completely removed by the reduction
-procedures.
+procedures (Section \ref{sec:Noise}).
 %Particular bolometers may be noisy for a single observation and they may not
@@
 Further details of the pointing calculation are given in Appendix
-\ref{sec:PointingCalculation}.
+\ref{app:PointingCalculation}.
 
@@
 \begin{equation}
+\label{eq:MapToTime}
 T[{\cal D}[\tilde{m}^{(n)}]] = \tilde{s}^{(n)}_i(t)
@@
 ech timestream point's value is assigned to an area much smaller than
-the beam.
+the beam.  In principle this can be addressed by various gridding
+algorithms, and may be a part of future reductions of the BGPS data.
 
 The resulting map is then subjected to a Hogbom-type CLEAN algorithm
-\citep{hogbom} using a specified kernel to produce a deconvolved
-image.  This has several advantages over the
+\citep{hogbom} using a specified kernel to produce a deconvolved image
+which is the one actually mapped back into the timestream to be
+subtracted (Equation \ref{eq:MapToTime}.  This has several advantages
+over using the original map directly, including rejecting artefacts
+smaller than the beam and decreasing the noise of the resulting
+timestream.  It is also better than a ``threshold'' method, which
+tends to produce discontinuities.
+
+In some fields, flux from certain source spread out over the course of
+the iterative process using certain kernel sizes.  The cause of this
+artifact are not yet well-understood, but using a different kernel
+size was an effective workaround and did little to change the
+properties of the final map.
 
@@
 
-% this is not true.  I can't do jackknifing....
-% To estimate the size of this
-% residual error, we also construct jackknife maps for each field, in
-% which the astrophysical signal is made to exactly cancel.  This
-% provides an estimate of the noise-only RMS in the maps, to which
-% deviations from the ``ghosts'' may be compared.
-
-In some fields, flux from certain source spread out over the course of
-the iterative process using certain kernel sizes.  The cause of this
-artifact are not yet well-understood, but using a different kernel
-size was an effective workaround and did little to change the
-properties of the final map.
-
-The noise is correlated between adjacent pixels.
-
-The final per-pixel error estimate is given as ...
+Noise maps are produced for each map, made from the residuals after
+removing the astrophysical signal model as well as the PCA component
+model.  These maps are useful for diagnosing the effect of the
+iterative process on bright sources and as a method of obtaining an
+estimate of the noise.
+
+The noise is correlated between adjacent spatial pixels due to
+residual atmospheric noise correlated in time..  We have completed
+ignored this effect in our analysis.
+
+The noise may be estimated either from the error maps, from the
+timestream PSDs of the detectors, or from the weight maps
+produced. The final per-pixel error estimate is given as \TBD.
 
@@
 a temperature, opacity, and distance.
+
+Using the same dust opacity as \TBD\ ({\it put in original references})
+%\citet{enoch06} and \citet{young06},
+and assuming a gas-to-dust mass ratio $X$ of 100, the mass sensitivity
+can be written as
+\begin{equation} 
+\label{eq:Mass}
+M_{gas}\approx
+0.22\left( e^{12.9/T_d}-1 \right) \left({S_\nu\over 15\; {\rm mJy}} \right)
+D^{2}_{kpc} \msol 
+\end{equation}
+where $D_{kpc}$ is the distance to the source in kpc.  (At $S_\nu =
+15$~mJy this corresponds to an RMS extinction sensitivity of $A_V\sim
+1$ mag, with the same $T_d$ dependence).  For Bolocam, $h\nu/k \approx
+13$~K, so for $T_d > XXX$ the dependence is approximately linear.  At
+the coldest temperatures expected, the mass changes a factor of 2.9
+between 20 and 10 K.  Far more important is the accurate determination
+of the distance to the clump.
 
@@
 
+To assess the effect of the mapping algorithm, we performed a series
+of simulations.
+
 Figure \ref{fig:PCA_Filter}a shows the fraction of flux recovered in
@@
 using both too large and too small a kernel.
+
+% -----------------------------------------------------------------------------
 
@@
 $(l_0,b_0)$.  The maps are made in Galactic coordinates using a plate
-carr\'{e} (FITS header CAR) projection.  As these maps are near the
-coordinate system equator, the difference between truly equiareal
-pixels and the pixels used is at most X\%.  The pixel size is
-7.2\arcsec, chosen to be much smaller than the Bolocam beam, and
-producing data squares 500 pixels on a side.
-
-Noise maps are produced for each map, made from the residuals after
-removing the astrophysical signal model as well as the PCA component
-model.  These maps are useful for diagnosing the effect of the
-iterative process on bright sources and as a method of obtaining an
-estimate of the noise.
+carr\'{e} (FITS header CAR) projection.  (This is the same projection
+used by the \spitzer-GLIMPSE and BU-FCRAO GRS surveys.)  As these maps
+are near the coordinate system equator, the difference between truly
+equiareal pixels and the pixels used is at most X\%.  The pixel size
+is 7.2\arcsec, chosen to be much smaller than the Bolocam beam.
+%, and
+%producing data squares 500 pixels on a side.
+The maps are written to standard FITS files.  An example of the FITS
+header for the BGPS images is given in Appendix \ref{app:FITS_Header}.
 
@@
 IPAC\footnote{http://irsa.ipac.caltech.edu/Missions/bolocam.html}.
-IPAC provides a cutout service for the
+IPAC provides a cutout service for the images as well as a searchable
+version of the catalog provided in \citep{rosolowsky09}.  The full
+release inclues
+\begin{enumerate}
+\item Calibrated maps for all regions observed (MAP)
+\item The MAP smoothed by the Bolocam PSF, which is helpful in bringing out extended structure (SMOOTHMAP)
+\item The deconvolved MAP (DECONVMAP)
+\item Maps of integration time per pixel (NHITSMAP)
+\item Maps of noise per pixel (NOISEMAP)
+\item Maps of the mask obtained for various regions from the cataloging algorithm (MASKMAP)
+\end{enumerate}
 
@@
 gas most intimately associated with the earliest phases of star
-formation.  Inspection of Figure \ref{fig:BGPSMontage}
-
-Figures 1 and 2 show the results of the BGPS.  Our images show
-excellent correspondence with SCUBA maps of small sub-fields
-throughout the plane \citep{SCUBAlegacy}.  BGPS contours overlaid on
-the GLIMPSE survey \citep{benjamin03} show excellent correlation with
-8\mum\ infrared dark clouds (IRDCs).  However, many features in the
-BGPS maps do not appear in the Spitzer observations, which suggests
-that the 1.1 mm emission traces dense clumps without a background to
-absorb.  A study of IRDC correlation with BGPS emission is underway
-\citep{Battersby2009}.
+formation.  Inspection of Figure \ref{fig:BGPSMontage} shows excellent
+correspondence with SCUBA maps of small sub-fields throughout the
+plane \citep{difrancesco08}.  BGPS contours overlaid on the GLIMPSE
+survey \citep{benjamin03} show excellent correlation with 8\mum\
+infrared dark clouds (IRDCs).  However, many features in the BGPS maps
+do not appear in the Spitzer observations, which suggests that the 1.1
+mm emission traces dense clumps without a background to absorb.  A
+study of IRDC correlation with BGPS emission is underway
+\citep{battersby09}.
 
@@
 emission will prove to be massive star or cluster forming regions.
+
+In conclusion, the BGPS is most awesome survey ever.
+
+\noindent---------------------------------
 
@@
 \section{Pointing Calculation}
-\label{sec:PointingCalculation}
+\label{app:PointingCalculation}
 

### 2009-04-12 methods/ms.tex
distmaps continued, minor ms.tex correction

@@
 
-The resulting map is then subjected to a Hogbom-type CLEAN algorithm
-\citep{hogbom} using a specified kernel to produce a deconvolved image
+The resulting map is then subjected to a maximum-entropy CLEAN algorithm
+%\citep{hogbom} 
+using a specified kernel to produce a deconvolved image
 which is the one actually mapped back into the timestream to be

### 2009-04-13 methods/ms.tex
Added Neal's introduction, John's cygnus comparison, and comment on distortion

@@
 
+\newcommand{\ammonia}{\mbox{{\rm NH}$_3$}}
+\newcommand{\form}{H$_2$CO}
+\newcommand{\td}{\mbox{$T_D$}}
+\newcommand{\jj}[2]{\mbox{$J = #1\rightarrow#2$}}
 \newcommand{\vdag}{(v)^\dagger}
@@
 Millimeter-wavelength continuum surveys of the Galactic plane provide
-the best way to identify high-column density clumps and clumps where
-planets, stars, and star clusters form.  Such data can locate and lead
-to the measurement of the physical properties of clumps un-biased by
-selection effects such as the presence of embedded stars, star
-clusters, infrared sources, masers, or radio continuum emission.
+the most efficient way to find molecular clumps that are the likely sites of
+formation for massive stars and star clusters. The development of
+detector arrays have made blind surveys of large areas possible.
+Such surveys can remove the selection effects used in previous surveyes,
+such as the presence of embedded stars or star clusters, infrared sources,
+masers, or radio continuum emission. In particular, they can locate
+molecular clumps before stars form, providing vital information on
+the initial conditions.  The surveys can also provide valuable constraints
+on the physical properties of the clumps, especially masses and mean densities.
+
 Galaxy-wide surveys are essential for measuring the impacts of the
-environment on clump properties and star formation activity.  Do clump
-properties vary with location in or out of spiral arms?  Do clump
-properties vary with Galactocentric distance?  Do they depend on the
-level of nearby star formation activity?  Galactic plane surveys of
-mm-wavelength dust continuum emission provide the most efficient tool
-for the identification of potential or active sites of star formation,
-including the rare objects where the most massive stars and cluster
-are, or soon will be, forming.  Dust continuum surveys of the Galaxy
-provide essential ``ground truth'' required for the analysis of distant
+environment on clump properties and star formation activity.
+Do clump properties vary with Galactocentric distance, or
+with location with respect to spiral arms?  Do they depend on the
+level of nearby star formation activity?
+Answering these questions in our Galaxy will provide the
+essential ``ground truth'' required for the analysis of distant
 galaxies where where individual clouds and clumps are not resolved and
@@
 
-Dust continuum emission near a wavelength of 1 mm is the best tracer
-of the material most directly associated with the formation of
-planetary systems, stars, and star clusters \citep{johnstone06}.
-Galactic dust continuum radiation at this wavelength is optically-thin
-almost everywhere, and at typical dust temperatures of order 10 K or
-more, is observed on the Rayleigh-Jeans tail of the Planck function.
-Thus, the determination of column densities is relatively straight
-forward if the dust temperature is known.
+Surveys of the galaxy in CO line emission \citep{dame01,FCRAO} have
+identified the locations of large molecular clouds and traced
+the transition from atomic to molecular gas as distance from the
+center of the galaxy decreases. Together with kinematic distances
+\citep[e.g.][]{RotationCurve} and, more recently, accurate distances
+from VLBI (add ref to Reid et al. work), these surveys have begun to
+reveal the spiral structure of the Milky Way. As this picture comes into
+sharper focus, we can begin to address the old question of the relationship
+between spiral density waves and star formation.
+
+To pursue this question, we need tracers of higher density material.
+Studies of nearby clouds have demonstrated that star formation is far
+from uniform over molecular clouds, but is concentrated in unusually dense
+regions called clumps or cores, which fill a small fraction of the area
+of most clouds [refs. E. Lada et al. Evans et al., Enoch et al.]
+Following \citet{williams00} and McKee-Ostriker (ARAA), we
+use the term core to refer to a very dense region destined to form an
+individual star or small multiple star systems and the term clump to
+refer to a
+region likely to form a group or cluster of stars. While clumps forming
+massive clusters may be denser than cores forming low mass stars
+[ref Mueller?],
+in general, clumps are larger and less dense. Clumps can be traced
+with line emission from molecules such as \ammonia, \form, CS, HCN, etc.
+Spectral lines also provide excellent diagnostics of
+line-of-sight motions, temperatures, and densities.
+However, the interpretation of these gas tracers is complicated by
+variations in tracer abundances caused by depletions and complex
+chemical processing, uncertainties in optical depths and excitation
+conditions, and the impacts of radiation fields and shocks. These
+complications make the derivation of column densities, masses, and
+other physical properties of star-forming clumps very difficult.
+A further limitation of spectral line studies is that the tracers of
+denser gas tend to be weak and multi-element receiver arrays have
+only a modest number of elements, making blind surveys very time-consuming.
+
+In contrast, focal-plane arrays containing hundreds of individual
+bolometers sensitive to millimeter and sub-millimeter (sub-mm)
+radiation are now available. This advance in technology enables
+blind surveys of the Galactic plane, providing a uniform inventory of massive
+star-forming and starless clumps.  Catalogs resulting
+from such surveys will provide the data base for subsequent observations
+in tracers such as hard-to-excite molecular lines and higher resolution
+studies with instruments like CARMA and ALMA.
+A further advantage of continuum observations of dust at long wavelengths
+is the low optical depth of the dust \citep{johnstone06},
+permitting a straight-forward estimate of the mass of the emitting region.
 
@@
 bolometer technology was developed.  The Submillimeter Common-User
-Bolometer Array (SCUBA) on the 15 m James Clerk Maxwell Telescope
+Bolometer Array (SCUBA) on the 15-m James Clerk Maxwell Telescope
 mapped many significant regions in the galactic plane over its 8 year
 lifetime \citep{holland99,difrancesco08}, but never completed a
-contiguous survey of the galactic plane.  Bolocam and Mambo have
-previously been used to map large star forming regions at 1.1
-\citep{enoch06} and 1.2 mm \citep{motte07}, but again these were
-targeted observations.  A recent large area survey with the LABOCA
-instrument at 870 \mum\ has recently been reported \citep{schuller09}.
-
-Surveys of the galaxy in CO line emission \citep{dame01,FCRAO} have
-revealed much about galactic structure, but do not provide a complete
-picture of how star formation follows that structure.  Millimeter
-continuum more directly traces the cold dust associated with star
-formation.  Continuum data allows for accurate determinations of the
-mass of large, dense dust structures when combined with kinematic
-distances \citep[e.g.][]{RotationCurve}.
-
-A crucial step in the observational study of star and cluster
-formation is identification and characterization of the cloud clumps
-which will soon form or are actively forming stars.  Massive stars and
-clusters form from high-density cloud clumps with very large column
-densities and extinctions $A_V > $ 100.  Thus, such cloud clumps are
-best investigated at millimeter and sub-millimeter wavelengths.
-However, the interpretation of various gas tracers that produce
-emission lines in this portion of the spectrum is very difficult.
-Although in principle, spectral lines provide excellent diagnostics of
-line-of-sight motions, temperatures, and densities in a cloud,
-variations in tracer abundances caused by depletions and complex
-chemical processing, uncertainties in excitation conditions, and the
-impacts of radiation fields and shocks make the derivation of column
-densities, masses, and other physical properties of cloud clumps very
-difficult.  The continuum emission from warm dust provides a more
-reliable tracer of the column densities and clump masses.
-
-The advent of focal plane arrays containing hundreds of individual
-bolometers sensitive to millimeter and sub-millimeter (sub-mm)
-radiation has enabled large-scale surveys of mm-wavelength continuum
-emission from Galactic interstellar dust.  The great advantage of
-continuum observations at 1.1mm is the low optical depth of the dust,
-permitting an estimate of the mass of the emitting region.  Further,
-the mass column density is independent of the gas volume density.
-Thus it is thus possible with a wide area, relatively shallow 1.1~mm
-survey to provide an unmatched, uniform inventory of massive
-star-forming and starless condensations.
-
-This survey presents the results of one of the first wide-area,
-untargeted surveys of the Galactic Plane in the millimeter continuum.
-We have used the 144 element Bolocam focal plane array, mounted at the
-Cassegrain focus of the 10 meter diameter sub-mm telescope at the
-Caltech Sub-millimeter Observatory (CSO), to survey over \bgpsarea\
+contiguous survey of the galactic plane.  The Bolocam instrument has been
+used on the 10.4-m Caltech Submiliimeter Observatory (CSO) to map nearby large
+molecular clouds at 1.1 mm and identify hundreds of cores \citep{enoch06}.
+Others have used MAMBO on the 30-m IRAM telescope at 1.2 mm to map
+more distant regions of more massive star formation \citep{motte07}.
+None of these surveys covered a significant fraction of the Galactic plane.
+
+Two large surveys of the Galactic plane are in progress.
+The ATLASGAL survey, using the LABOCA instrument at 870 \micron\
+on the APEX telescope in Chile, will cover the southern Galactic plane
+and extend somewhat into the north. Initial results from this survey
+have been reported by \citet{schuller09}. [say more]
+
+This paper presents the results of the Bolocam Galactic Plane Survey
+(BGPS).  (Give longitude and latitude coverage.)
+It is complementary to the survey by \citet{schuller09} in that
+it targets the part of the plane visible from the northern
+hemisphere and uses a somewhat longer wavelength, allowing
+comparison of properties in the region of overlap with the survey of
+\citet{schuller09}.
+At 870 \micron, $h\nu/k = 16.5$ K, compared to 13.1 K at 1.1 mm.
+Because starless clumps may be quite cold ($\td \approx 10$ K),
+the uncertainty in mass caused by uncertain temperature is less at 1.1 mm.
+For example, the mass estimate if the actual $\td = 20$ K, rather
+than 10 K, would decrease by a factor of 3.3 at 870 \micron\
+versus a factor of 2.9 at 1.1 mm. In addition, the Bolocam bandpass
+excludes the CO \jj{21} line, which can be a significant contaminant
+on top of the dust continuum emission.
+
+We have used the 144-element Bolocam focal plane array, mounted at the
+Cassegrain focus of the CSO, to survey over \bgpsarea\
 square degrees of the northern Galactic plane at a wavelength of 1.1
@@
 N46) and 17.9 Jy/beam in a 0.19 x 0.14 pc box, BGPS measures a peak
-flux of 15.5 Jy/beam (the beam being roughly 31\arcsec\ in diameter).
+flux of 17.5 Jy/beam (the beam being roughly 35\arcsec\ in diameter).
 Fluxes are best compared using sources compact as observed with the
@@
 Gaussian kernel that generates an approximately 35\arcsec\ beam,
-matched to our images (mapped without application of the distortion
-correction).  The results are shown in Figure
+matched to our images.  The results are shown in Figure
 \ref{fig:CygnusComparison}.
@@
 \Table
-{lll}
-{Flux density comparison with \citet{motte07}.}
+{llllll}
+{Note:  The \citet{motte07} integration box is given in terms of pc. 
+The assumed distance must be about 1.7 kpc \citep{schneider2006}  }
 {
-Source  &   BGPS           &  Motte \\
-        &   peak mJy/beam  &  mJy in box (see Motte+ Table 1)
+%Source  &   BGPS           &  Motte \\
+%        &   peak mJy/beam  &  mJy in box (see Motte+ Table 1)
+Motte Source Number &  Motte Table 1 integrated flux &  Motte scaled Jy/bm  & BGPS Jy/Bm &    Comments \\
 }
@@
 {
- N11    &   350 - 550      &  340 \\
- N12    &   1660-2200      &  1630 \\
- N16    &   613            &  550 \\
- N18    &   618            &  430 \\
- N26    &   314            &  340 \\
- N46    &   15500          &  17930  (DR21 S)
+3  &    1.59 [0.11x0.09] & 2.61      &  2.30  &  DR 17                               \\
+11 &    0.34 [0.11x0.06] & 0.48      &  0.50  &  West SW of DR21                     \\
+12 &    1.63 [0.11x0.09] & 2.60      &  2.20  &    "                                 \\
+16 &    0.55 [0.12x0.12] & 0.82      &  0.72  &    "                                 \\
+26 &    0.34 [0.20x0.10] & 0.48      &  0.44  &    "                                 \\
+29 &    0.54 [0.25x0.13] & 1.10      &  0.62  &    "                                 \\
+30 &   10.54 [0.15x0.10] &13.5       &  9.80  &  W75(N)                              \\
+44 &    8.43 [0.14x0.11] &14.5       & 12.7   &  DR21 (OH)                           \\
+46 &   17.90 [0.08x0.03] &18.4       & 15.8   &  DR21 f-f, maser (H2O)               \\
+48 &    3.72 [0.17x0.11] & 9.4       &  7.8   &  DR21 (OH)-S                         \\
+51 &    2.37 [0.24x0.03] & 5.5       &  4.1   &  DR21 FIR2                           \\
+53 &    1.60 [0.14x0.09] & 4.3       &  2.7   &  North of DR21  FIR3                 \\
+56 &    0.60 [0.12x0.08] & 0.81      &  0.75  &  SE of DR21 47                       \\
+58 &    2.73 [0.23x0.19] & 2.40      &  1.64  &  IRAS 20375+4109                     \\
+59 &    0.37 [0.12x0.05] & 1.3       &  0.93  &  East of IRAS 20375+4109             \\
+60 &    0.56 [0.16x0.13] & 1.00      &  0.78  &  East of IRAS 20375+4109             \\
+61 &    0.23 [0.12x0.09] & 0.60      &  0.49  &  MSX 81.5168+0.01926                 \\
+62 &    0.50 [0.18x0.12] & 1.23      &  0.80  &  between 63 \& IRAS 20375+4109       \\
+63 &    1.09 [0.08x0.05] & 1.60      &  1.50  &  DR22                                \\
+65 &    0.78 [0.16x0.12] & 1.15      &  1.10  &                                      \\
+66 &    0.25 [0.15x0.06] & 0.63      &  0.76  &                                      \\
+68 &    0.84 [0.10x0.10] & 1.01      &  0.94  &                                      \\
+69 &    1.28 [0.47x0.18] & 1.12      &  1.20  &                                      \\
+72 &    0.54 [0.28x0.13] & 0.58      &  0.47  &                                      \\
 }
@@
 bolometer individually.
+
+In our first release, these positions are made using the nominal positions
+without correction for optical distortion.  This results in a slightly blurred
+beam (35.6\farcs instead of 31.2\farcs).  Because this distortion is
+asymmetric, it can also result in a small pointing offset at the field edges
+where only bolometers with large offsets record data.  However, this effect is
+strongly mitigated by the low number of hits at field edges - this data is
+generally flagged out.  The residual offset is within the overall pointing
+model error, but caution should be used when measuring locations at the field
+edges.
 

### 2009-04-13 methods/ms.tex
Add_to_header updated

@@
 
-\affil{{$^\casa$}{\it{CASA, University of Colorado, CB 389, Boulder, CO 80309}}}
+\affil{{$^\casa$}{\it{CASA, University of Colorado, CB 389-UCB, Boulder, CO 80309}}}
 %, \email{John.Bally@casa.colorado.edu}
@@
 area, systematic survey of the Northern Galactic Plane in the
-(sub)millimeter continuum without pre-selected targets.  The survey
+millimeter continuum without pre-selected targets.  The survey
 has detected \ncores\ clumps to a limiting depth of between

### 2009-04-14 methods/ms.tex
mostly paper mods?

@@
 This paper details the survey observations and methods.  We treat
-carefully the determination of pointing and flux calibration errors
+carefully the determination of pointing and flux density calibration errors
 and compare our results to the literature.  Data processing algorithms
-that separate astronomical signals from time-variable atmospheric flux
+that separate astronomical signals from time-variable atmospheric flux density
 in the data time-stream are discussed.  The algorithms reproduce the
@@
 pointing towards Sgr B2 was from lines, and \citet{yoshida2005}
-reported $>40\%$ in Orion A from line emission. \TBD\ Other lines
+reported $>40\%$ in Orion A from line emission over the 260-328 GHz band. \TBD\ Other lines
 lying in the Bolocam passband include CS($5\to4$) and ($6\to5$) (245

### 2009-04-14 methods/ms.tex
made some figure caption changes

@@
 \newcommand{\solar}{\ensuremath{\odot}}
+\newcommand{\long}{\ensuremath{\ell}}
 
@@
 	51, W 43, W 49, and M 17 appear to be saturated, but this is
-	only a display artifact}
+	only a display artifact.  The $20 < \ell < 40$ region through the
+        4-8 kpc molecular ring and approximately the termination of the galactic
+        bar is particularly rich in clumps.}
     \end{center}
@@
       \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
-      \caption{$l=49.5$ to $l=74.5$.  \TBD\ Add annotations}
+      \caption{$l=49.5$ to $l=74.5$.  In comparison to the inner galaxy, the $65
+      < \ell < 75$ has a very sparse population of clumps}
     \end{center}
@@
   \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
-  \caption{The Cygnus Arm. \TBD\ Add annotations}
+  \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
+  1.5$\deg. The large scale 'peanut' shape including DR21 is suggestive of a
+  large wind-blown bubble, although.... [someone else must have commented on
+  this in the past?].  See section \ref{sec:motte} for a comparison with the
+  \citet{motte2007} IRAM study of this region. }
 \end{figure}
@@
 \subsection{Comparison to Other Surveys}
+\label{sec:motte}
 

### 2009-04-14 methods/ms.tex
Pointing plot - gauss

@@
 figure?}]
-{\label{fig:PointingModel-a}\includegraphics[scale=1.0]{pointing_model}}\\
+{\label{fig:PointingModel-a}\includegraphics[scale=1.0]{paper_models_0707}}\\
 
@@
 distribution.]
-{\label{fig:PointingModel-b}\includegraphics[scale=0.5]{pointing_model_residuals}}
+{\label{fig:PointingModel-b}\includegraphics[scale=0.5]{paper_gaussian_0707}}
 

### 2009-04-14 methods/ms.tex
Pointing plot - gauss

@@
 \newcommand{\solar}{\ensuremath{\odot}}
-\newcommand{\long}{\ensuremath{\ell}}
+\newcommand{\lon}{\ensuremath{\ell}}
 
@@
   \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
-  1.5$\deg. The large scale 'peanut' shape including DR21 is suggestive of a
+  1.5\deg$. The large scale 'peanut' shape including DR21 is suggestive of a
   large wind-blown bubble, although.... [someone else must have commented on
   this in the past?].  See section \ref{sec:motte} for a comparison with the
-  \citet{motte2007} IRAM study of this region. }
+  \citet{motte07} IRAM study of this region. }
 \end{figure}
@@
 distribution.]
-{\label{fig:PointingModel-b}\includegraphics[scale=0.5]{paper_gaussian_0707}}
+{\label{fig:PointingModel-b}\includegraphics[scale=1.0]{paper_gaussian_0707}}
 

### 2009-04-14 methods/ms.tex
changed pointing model figures

@@
 (right) for Epoch V, from which the master reference images were
-derived for subsequent alignment. {\em To be replaced with newer
-figure?}]
-{\label{fig:PointingModel-a}\includegraphics[scale=1.0]{paper_models_0707}}\\
+derived for subsequent alignment.  The red line indicates the fitted
+model. ]
+{\label{fig:PointingModel-a}\includegraphics[scale=0.9]{paper_models_0707}}\\
 
@@
 distribution.]
-{\label{fig:PointingModel-b}\includegraphics[scale=1.0]{paper_gaussian_0707}}
+{\label{fig:PointingModel-b}\includegraphics[scale=0.9]{paper_gaussian_0707}}
 

### 2009-04-14 plotting/plot_bolosens.py
bolosens plotting

@@ -5,14 +5,9 @@ from matplotlib.collections import PatchCollection
 import matplotlib
 
 uranus=[
-'050619_o23' ,
-'050619_o24' ,
-'050628_o33' ,
-'050628_o34' ,
-'050904_o31' ,
-'050904_o32' ,
-'050911_ob8' ,
-'070702_o41' 
+'050619_o23-4' ,
+'050628_o33-4' ,
+'050904_o31-2' 
 ]
 
 for obsdate in uranus:

### 2009-04-14 plotting/plot_bolosens.py
bolosens plotting

@@ -5,9 +5,9 @@ from matplotlib.collections import PatchCollection
 import matplotlib
 
 uranus=[
-'050619_o23-4' ,
-'050628_o33-4' ,
-'050904_o31-2' 
+'050619_o23-4_nofit' ,
+'050628_o33-4_nofit' ,
+'050904_o31-2_nofit' 
 ]
 
 for obsdate in uranus:

### 2009-04-14 plotting/plot_bolosens.py
bolosens plotting

@@ -14,7 +14,7 @@ for obsdate in uranus:
 
     d_angle = open('/scratch/adam_work/distmaps/uranus_'+obsdate+'.txt','r').readline().split().pop()
 
-    bolonum,base,amp,xwid,ywid,xcen,ycen,angle = readcol('/scratch/adam_work/distmaps/uranus_'+obsdate+'_bolofits.txt',twod=False)
+    bolonum,base,amp,xwid,ywid,xcen,ycen,angle = readcol('/scratch/adam_work/distmaps/uranus_'+obsdate+'_bolofits.txt',twod=False,skiplines=1)
 
     good = ((amp > (median(amp)-3*std(amp))) * (amp < (median(amp)+3*std(amp))))
 

### 2009-04-14 plotting/plot_bolosens.py
bolosens plotting

@@ -14,7 +14,7 @@ for obsdate in uranus:
 
     d_angle = open('/scratch/adam_work/distmaps/uranus_'+obsdate+'.txt','r').readline().split().pop()
 
-    bolonum,base,amp,xwid,ywid,xcen,ycen,angle = readcol('/scratch/adam_work/distmaps/uranus_'+obsdate+'_bolofits.txt',twod=False,skiplines=1)
+    bolonum,base,amp,xwid,ywid,xcen,ycen,angle = readcol('/scratch/adam_work/distmaps/uranus_'+obsdate+'_bolofits.txt',twod=False,skipline=1)
 
     good = ((amp > (median(amp)-3*std(amp))) * (amp < (median(amp)+3*std(amp))))
 

### 2009-04-14 plotting/plot_bolosens.py
bolosens plotting

@@ -6,9 +6,8 @@ import matplotlib
 
 uranus=[
 '050619_o23-4_nofit' ,
-'050628_o33-4_nofit' ,
-'050904_o31-2_nofit' 
-]
+'050628_o33-4_nofit' ]
+#'050904_o31-2_nofit' 
 
 for obsdate in uranus:
 

### 2009-04-15 methods/ms.tex
changed PCA figures and added new map demo figure

@@
     \begin{center}
-      \includegraphics[scale=0.8]{eachpca}
+      \includegraphics[angle=90,scale=0.6]{eachpca}
     \end{center}
@@
     \begin{center}
-      \includegraphics[scale=0.8]{eachpca_20iters}
+      \includegraphics[angle=90,scale=0.6]{eachpca_20iters}
     \end{center}
   \end{minipage}
-  \caption{{\it Top}: a grid of maps of the first 20 PCA components
+  \caption{Selected images to illustrate the PCA process.  The displays are in
+  Galactic coordinates with a color range from -.1 to 1.0 Jy/beam.
+  {\it Top}: a grid of maps of the first 20 PCA components
 displayed at the same scale.  It is clear that NCG 7538, the object
@@
 third being the most obvious atmospheric components.  Most of the
-other noise components are probably various bits of correlated
+other noise components are probably varieties of correlated
 detector noise. {\it Bottom}: The same figure, but after 20
@@
 
+Five image types will be released, each covering the same regions.  The maps
+are standard astrophysical maps subject to the caveats previously mentioned,
+the most important being the spatial filtering function (section \ref{sec:}).
+The model maps are deconvolved using the maximum-entropy method with kernels
+specified in the header.  The residual map is the map of the model timestream
+subtracted from the data timestream; it is close to but not identical to the
+map minus the model.  The weightmap shows the inverse-variance weighting of
+each pixel.  The nhitsmap shows how many recorded data points from the
+timestream have been assigned to each pixel; it is proportional to the dwell
+time per pixel (each 'hit' is .1s).  Examples of each (except the nhitsmap)
+are given in figure \ref{fig:sampleimages}.
+
+\Figure{image_types}{Examples of four of the image types being released.  Top
+left: MAP.  Top right: Residual.  Bottom left: Deconvolved.  Bottom right:
+Weight}{fig:sampleimages}{1.0}
+
 %\section{Public Data Release}
@@
 % first millimeter....
-The BGPS is the first (sub)millimeter survey of a substantial fraction
+The BGPS is the first millimeter survey of a substantial fraction
 of the Galactic Plane, providing an unbiased look at the high-density

### 2009-04-15 methods/ms.tex
changed PCA figures and added new map demo figure

@@
 are standard astrophysical maps subject to the caveats previously mentioned,
-the most important being the spatial filtering function (section \ref{sec:}).
+the most important being the spatial filtering function (section \ref{sec:Noise}).
 The model maps are deconvolved using the maximum-entropy method with kernels

### 2009-04-15 methods/ms.tex
distmap_centroids corrections

@@
 
-We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm
-continuum survey of \bgpsarea\ square degrees of the Galactic Plane in
-the 1st, 2nd, and 3rd quadrants.  The BGPS represents the first large
-area, systematic survey of the Northern Galactic Plane in the
-millimeter continuum without pre-selected targets.  The survey
-has detected \ncores\ clumps to a limiting depth of between
-\bgpsdepthlow\ and \bgpsdepthhigh\ mJy RMS.  We include maps of 100
-contiguous square degrees from $l=-10.5$ to $l=86.5$ and $b=\pm0.5$
-with a resolution of 31\arcsec, as well as regions in IC1396, $l=111$
-(NGC7538), W3/4/5, and Gem OB1.  The most striking feature of the maps
-is the filamentary structure of cold dust throughout the Galaxy.
-
-This paper details the survey observations and methods.  We treat
-carefully the determination of pointing and flux density calibration errors
-and compare our results to the literature.  Data processing algorithms
-that separate astronomical signals from time-variable atmospheric flux density
-in the data time-stream are discussed.  The algorithms reproduce the
-structure of the astronomical sky on a limited range of angular scales
-and produce artifacts in the vicinity of bright sources. Specifically,
-extended emission smooth on scales larger than about 5\arcmin\ is not
-fully recovered in the images.  The spatial frequency response
-function of the Bolocam Galactic Plane Survey is discussed.
-
-This paper serves as a companion and guide to the public data release
-through NASA's Infrared Processing and Analysis Center (IPAC).  These
-images represent an important finder chart for future observations
-with ALMA and a long-wavelength spectral band complementary to
-imminent submillimeter surveys with SCUBA-2 and Herschel-SPIRE.
+We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm continuum survey
+of \bgpsarea\ square degrees of the Galactic Plane primarily in the 1st
+quadrant with some coverage in the 2nd and 3rd quadrants.  The BGPS represents
+the first large area, systematic survey of the Northern Galactic Plane in the
+millimeter continuum without pre-selected targets.  The survey has detected
+\ncores\ clumps to a limiting depth of between \bgpsdepthlow\ and
+\bgpsdepthhigh\ mJy RMS.  We include maps of 100 contiguous square degrees from
+$l=-10.5$ to $l=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
+well as regions in IC1396, $l=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
+striking feature of the maps is the filamentary structure of cold dust
+throughout the Galaxy.
+
+This paper details the survey observations and methods.  We treat carefully the
+determination of pointing and flux density calibration errors and compare our
+results to the literature.  Data processing algorithms that separate
+astronomical signals from time-variable atmospheric flux density in the data
+time-stream are discussed.  The algorithms reproduce the structure of the
+astronomical sky on a limited range of angular scales and produce artifacts in
+the vicinity of bright sources. Specifically, extended emission smooth on
+scales larger than about 3\arcmin\ is not fully recovered in the images.  The
+spatial frequency response function of the Bolocam Galactic Plane Survey is
+discussed.
+
+This paper serves as a companion and guide to the public data release through
+NASA's Infrared Processing and Analysis Center (IPAC).  These images represent
+an important finder chart for future observations with ALMA and a
+long-wavelength spectral band complementary to imminent submillimeter surveys
+with SCUBA-2 and Herschel-SPIRE.
 

### 2009-04-15 methods/ms.tex
gaussian fits to offsets fixed

@@
 
+% Figure 3
 \Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright
@@
 
-\FigureTwo{bolosens050904_o32}{scan_10deg}{Left: the position,
-ellipticity and relative response of the detectors in the Bolocam
-focal plane as mapped to the sky.  Right: The effect of field rotation
-on the coverage obtained via Bolocam raster scans.}{fig:Array}{1.0}
+% Figure 4
+\FigureTwo{bolosens050904_o32}{scan_10deg}{Left: the position, ellipticity and
+relative response of the detectors in the Bolocam focal plane as mapped to the
+sky.  Right: The effect of field rotation on the coverage obtained via Bolocam
+raster scans.  The array is held fixed during a scan, but is rotated such that
+the sampling is most uniform.}{fig:Array}{1.0}
 
@@
 %{calibration_plot_2004}
-{Left: Average calibration curve [V/Jy] versus the mean detector
-voltage, a proxy for atmospheric loading.  Red points are observations
-of Mars and black of Uranus.  Right: Scaling of the relative
-calibration with atmospheric loading for a single
-detector.}{fig:CalibrationCurves}{1.0}
+{Left: Average calibration curve [V/Jy] versus the mean detector voltage, a
+proxy for atmospheric loading.  Red points are observations of Mars and black
+of Uranus.  The black line is a 2nd-order fit with 0,0 (no response if no
+measurable potential difference) forced.  Right: Scaling of the relative
+response to the atmosphere for a single detector compared to the array
+median.}{fig:CalibrationCurves}{1.0}
 
@@
 calibration using the atmosphere as a calibrator.  Black is the median
-over all bolometers (the atmosphere model), red and green are
+over all bolometers (the 1st-order atmosphere model), red and green are
 individual bolometers. a. before and b. after applying the relative
@@
 \Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
-in the same aperture from the \citet{motte07} MAMBO map and the
-Bolocam map of this paper.}{fig:CygnusComparison}{1.0}
+in the same aperture from the \citet{motte07} MAMBO map and the Bolocam map of
+this paper. THIS FIGURE IS A PLACEHOLDER}{fig:CygnusComparison}{1.0}
 

### 2009-04-15 plotting/plot_bolosens.py

@@ -9,11 +9,18 @@ uranus=[
 '050628_o33-4_nofit' ]
 #'050904_o31-2_nofit' 
 
-for obsdate in uranus:
+obs = [ { 'uranus':'050619_o23-4_nofit' } ,
+        { 'uranus':'050628_o33-4_nofit' } ,
+        { '3c279' :'050703_ob1-2' } ]
 
-    d_angle = open('/scratch/adam_work/distmaps/uranus_'+obsdate+'.txt','r').readline().split().pop()
+for o in obs:
 
-    bolonum,base,amp,xwid,ywid,xcen,ycen,angle = readcol('/scratch/adam_work/distmaps/uranus_'+obsdate+'_bolofits.txt',twod=False,skipline=1)
+    object = o.keys()[0]
+    obsdate = o[object]
+    
+    d_angle = open('/scratch/adam_work/distmaps/'+object+'_'+obsdate+'.txt','r').readline().split().pop()
+
+    bolonum,base,amp,xwid,ywid,xcen,ycen,angle = readcol('/scratch/adam_work/distmaps/'+object+'_'+obsdate+'_bolofits.txt',twod=False,skipline=1)
 
     good = ((amp > (median(amp)-3*std(amp))) * (amp < (median(amp)+3*std(amp))))
 

### 2009-04-15 methods/ms.tex
some more paper modifications plus.... crap, forgot to add plot_crs

@@
   \subfigure[The residuals of the pointing model.  Note the Gaussian
-distribution.]
+distribution. ($\sigma = 5.94,2.92$)]
 {\label{fig:PointingModel-b}\includegraphics[scale=0.9]{paper_gaussian_0707}}
@@
       \caption{An example of the change in the time series as
-      iterative mapping proceeds.}
+      iterative mapping proceeds.  1. Raw time series 2. After removal
+      of residual 60Hz signal 3. Exponential decay function at scan
+      turnarounds subtracted 4. A polynomial (with astrophysical source
+      rejection) is fit to remove large-scale variations across the scan. }
     \end{center}
@@
       \includegraphics[scale=0.9]{iterative_mapping2}
-      \caption{}
+      \caption{Panel 1 is the same as panel 4 in the previous figure.
+      Before the first cleaning, the raw data (black) and remainder data (green)
+      are equal because there is no model.  
+      Panel 2 shows the median-atmosphere subtraction, which is the first-
+      order correction.
+      Panel 3 shows the astrophysical signal left over from the PCA selection.
+      Panel 4 shows the total atmosphere model from PCA and median estimation}
     \end{center}
@@
       \includegraphics[scale=0.9]{iterative_mapping3}
-      \caption{}
+      \caption{Same as previous figure, except after 20 iterations.
+      Panel 1 - The deconvolved astrophysical map is returned to a timestream (red)
+      and subtracted from the 'raw' data (black). 
+      Panel 2 - The median of the remainder (green) is subtracted as the first
+      atmosphere estimation
+      Panel 3 - The cumulative astrophysical model (red) and the additional astrophysical
+      signal from iteration 20 (black)
+      Panel 4 - The atmosphere signal after 20 iterations}
     \end{center}
@@
   \end{minipage}
-  \caption{An illustration of the flagging process using the waterfall
-plot. Left: The glitch apparent at middle right is the same one whose
-time series is shown in Figure \ref{fig:CosmicRayGlitch}.  Because of
-the PCA subtraction, the effect of the glitch also propagates over the
-other bolometers, appearing as a horizontal stripe. Right: The same
-data displayed with the time point including the glitch flagged out
-and rescaled}
+  \caption{An illustration of the flagging process using the waterfall plot.
+  Left: The glitch apparent at middle right (bolometer 98, around 6.2s) is the
+  same one whose time series is shown in Figure \ref{fig:Flagger}b.  Because of
+  the PCA subtraction, the effect of the glitch also propagates over the other
+  bolometers, appearing as a horizontal stripe. Right: The same data displayed
+  with the time point including the glitch flagged out and rescaled}
 
@@
       \includegraphics[scale=0.5]{flagger_plots}
-      \caption{An illustration of a ``glitch'' in a single bolometer
-timestream (red) due to a cosmic ray strike.  Note the acausal ringing
-due to the application of the downsampling filter.  The time series
-for a physically adjacent bolometer is shown in blue, and a bolometer
-which does not pass over a source in green.  The PCA model has already
-been subtracted from the data.}
+      \caption{An illustration of a ``glitch'' in a single bolometer timestream
+      (red) due to a cosmic ray strike.  Note the acausal ringing due to the
+      application of the downsampling filter.  The time series for a physically
+      adjacent bolometer is shown in blue, and a bolometer which does not pass
+      over the source in green.  The PCA atmosphere estimation has already been
+      subtracted from the data.}
     \end{center}

### 2009-04-15 methods/ms.tex
changed plot_crs to a function

@@
 %
-\Figure{crs}{The distribution of glitch amplitudes flagged and removed
-from the data.  The expected contribution to the noise from the
-unremoved glitches below the detection threshold is
-\TBD.}{fig:GlitchDistribution}{1.0}
+\Figure{crs}{The distribution of glitch amplitudes flagged and removed from the
+data in the \lon=111 field.  Glitches below the detection threshold may
+contribute to the overall noise signal.}{fig:GlitchDistribution}{1.0}
 

### 2009-04-15 methods/ms.tex
Minor corrections to paper

@@
 % 19) fig:AperturePhotometry
+% 19) fig:sampleimages
 
@@
 \documentclass[12pt,preprint]{aastex}
-%{emulateapj}
+%\documentclass{emulateapj}
 
@@
 \bgpsdepthhigh\ mJy RMS.  We include maps of 100 contiguous square degrees from
-$l=-10.5$ to $l=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
-well as regions in IC1396, $l=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
+$\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
+well as regions in IC1396, $\lon=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
 striking feature of the maps is the filamentary structure of cold dust
@@
 
-Millimeter-wavelength continuum surveys of the Galactic plane provide
-the most efficient way to find molecular clumps that are the likely sites of
-formation for massive stars and star clusters. The development of
-detector arrays have made blind surveys of large areas possible.
-Such surveys can remove the selection effects used in previous surveyes,
-such as the presence of embedded stars or star clusters, infrared sources,
-masers, or radio continuum emission. In particular, they can locate
-molecular clumps before stars form, providing vital information on
-the initial conditions.  The surveys can also provide valuable constraints
-on the physical properties of the clumps, especially masses and mean densities.
+Millimeter-wavelength continuum surveys of the Galactic plane provide the most
+efficient way to find molecular clumps that are the likely sites of formation
+for massive stars and star clusters. The development of detector arrays have
+made blind surveys of large areas possible.  Such surveys bypass the need for
+selection based on the presence of embedded stars or star clusters, infrared
+sources, masers, or radio continuum emission. In particular, they can locate
+molecular clumps before stars form, providing vital information on the initial
+conditions of star formation.  These surveys can also provide valuable
+constraints on the physical properties of the clumps, especially masses and
+mean densities.
 
@@
 \citep[e.g.][]{RotationCurve} and, more recently, accurate distances
-from VLBI (add ref to Reid et al. work), these surveys have begun to
+from VLBI \citep{reid09}, these surveys have begun to
 reveal the spiral structure of the Milky Way. As this picture comes into
@@
 Following \citet{williams00} and McKee-Ostriker (ARAA), we
-use the term core to refer to a very dense region destined to form an
-individual star or small multiple star systems and the term clump to
+use the term `core' to refer to a very dense region destined to form an
+individual star or small multiple star systems and the term `clump' to
 refer to a
@@
 
-In contrast, focal-plane arrays containing hundreds of individual
-bolometers sensitive to millimeter and sub-millimeter (sub-mm)
-radiation are now available. This advance in technology enables
-blind surveys of the Galactic plane, providing a uniform inventory of massive
-star-forming and starless clumps.  Catalogs resulting
-from such surveys will provide the data base for subsequent observations
-in tracers such as hard-to-excite molecular lines and higher resolution
-studies with instruments like CARMA and ALMA.
+% redundant:
+% In contrast, focal-plane arrays containing hundreds of individual
+% bolometers sensitive to millimeter and sub-millimeter (sub-mm)
+% radiation are now available. This advance in technology enables
+% blind surveys of the Galactic plane, providing a uniform inventory of massive
+% star-forming and starless clumps.  Catalogs resulting
+% from such surveys will provide the data base for subsequent observations
+% in tracers such as hard-to-excite molecular lines and higher resolution
+% studies with instruments like CARMA and ALMA.
+(this line belongs somewhere)
 A further advantage of continuum observations of dust at long wavelengths
@@
 and extend somewhat into the north. Initial results from this survey
-have been reported by \citet{schuller09}. [say more]
-
-This paper presents the results of the Bolocam Galactic Plane Survey
-(BGPS).  (Give longitude and latitude coverage.)
-It is complementary to the survey by \citet{schuller09} in that
-it targets the part of the plane visible from the northern
-hemisphere and uses a somewhat longer wavelength, allowing
-comparison of properties in the region of overlap with the survey of
-\citet{schuller09}.
-At 870 \micron, $h\nu/k = 16.5$ K, compared to 13.1 K at 1.1 mm.
-Because starless clumps may be quite cold ($\td \approx 10$ K),
-the uncertainty in mass caused by uncertain temperature is less at 1.1 mm.
-For example, the mass estimate if the actual $\td = 20$ K, rather
-than 10 K, would decrease by a factor of 3.3 at 870 \micron\
-versus a factor of 2.9 at 1.1 mm. In addition, the Bolocam bandpass
-excludes the CO \jj{21} line, which can be a significant contaminant
-on top of the dust continuum emission.
+have been reported by \citet{schuller09}. [say more - overlap region?
+]
+
+This paper presents the results of the Bolocam Galactic Plane Survey (BGPS).
+The survey covers the contiguous range $-10.5 < \lon < 86.5, -.5 < b < .5$ with
+additional coverage to higher $|b|$ in the range $77 < \lon < 86.5$ and in the
+$\lon=111$, W3/4/5, Gem OB1, and IC 1396 regions.  It is complementary to the
+survey by \citet{schuller09} in that it targets the part of the plane visible
+from the northern hemisphere and uses a somewhat longer wavelength, allowing
+comparison of properties in the region of overlap with the ATLASGAL survey.
+At 870 \micron, $h\nu/k = 16.5$ K, compared to 13.1 K at 1.1 mm.  Because
+starless clumps may be quite cold ($\td \approx 10$ K), the uncertainty in mass
+caused by uncertain temperature is slightly less at 1.1 mm.  For example, the
+mass estimate if the actual $\td = 20$ K, rather than 10 K, would decrease by a
+factor of 3.3 at 870 \micron\ versus a factor of 2.9 at 1.1 mm. In addition,
+the Bolocam bandpass excludes the CO \jj{2}{1} line, which can be a significant
+contaminant on top of the dust continuum emission.
 
@@
 %\begin{figure}
-%  \subfigure[$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
-%	sources, e.g. Sgr B2, Sgr A, and sources near $l=10$ and
-%	$l=13$, appear to be saturated, but this is only a display
-%	artifact.  The noise is more pronounced from $l=-7$ to $l=-2$
+%  \subfigure[$\lon=-10.5$ to $\lon=19.5$ Units are Jy/Beam.  The brightest
+%	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
+%	$\lon=13$, appear to be saturated, but this is only a display
+%	artifact.  The noise is more pronounced from $\lon=-7$ to $\lon=-2$
 %	because this region was observed less.]{\label{fig:BGPSMontage-a}\includegraphics[scale=0.75]{fig1_pg1_bw_inv_bar_label}}\\
 %\pagebreak
-%\subfigure[$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
+%\subfigure[$\lon=19.5$ to $\lon=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
 %	51, W 43, W 49, and M 17 appear to be saturated, but this is
@@
       \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
-      \caption{$l=-10.5$ to $l=19.5$ Units are Jy/Beam.  The brightest
-	sources, e.g. Sgr B2, Sgr A, and sources near $l=10$ and
-	$l=13$, appear to be saturated, but this is only a display
-	artifact.  The noise is more pronounced from $l=-7$ to $l=-2$
+      \caption{$\lon=-10.5$ to $\lon=19.5$ Units are Jy/Beam.  The brightest
+	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
+	$\lon=13$, appear to be saturated, but this is only a display
+	artifact.  The noise is more pronounced from $\lon=-7$ to $\lon=-2$
 	because this region was observed less.}
@@
       \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
-      \caption{$l=19.5$ to $l=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
+      \caption{$\lon=19.5$ to $\lon=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
 	51, W 43, W 49, and M 17 appear to be saturated, but this is
@@
       \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
-      \caption{$l=49.5$ to $l=74.5$.  In comparison to the inner galaxy, the $65
+      \caption{$\lon=49.5$ to $\lon=74.5$.  In comparison to the inner galaxy, the $65
       < \ell < 75$ has a very sparse population of clumps}
@@
   \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
-  1.5\deg$. The large scale 'peanut' shape including DR21 is suggestive of a
+  1.5\deg$. The large scale `peanut' shape including DR21 is suggestive of a
   large wind-blown bubble, although.... [someone else must have commented on
@@
   \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
-  \caption{Cloud complexes centered at $l=111$ in the Perseus Arm. \TBD\ Add annotations}
+  \caption{Cloud complexes centered at $\lon=111$ in the Perseus Arm. \TBD\ Add annotations}
 \end{figure}
@@
 method of \citet{enoch06} for generating maps and characterizing their
-properties.  It incorporates also some of the technical developments
+properties.  It incorporates some of the technical developments
 of \citet{sayers09}, though the exquisite control of systematics and
@@
 {llllll}
-{Note:  The \citet{motte07} integration box is given in terms of pc. 
-The assumed distance must be about 1.7 kpc \citep{schneider2006}  }
+{Comparison of \citet{motte07} IRAM measurements to BGPS measurements
+in the Cygnus X region
+%Note:  The \citet{motte07} integration box is given in terms of pc. 
+%The assumed distance must be about 1.7 kpc \citep{schneider2006}    % no, it's 1.7kpc stated explicitly
+}
 {
@@
 
-TBD: In low s/n fields, specifically l=65 to 75, there was not enough signal to
+TBD: In low s/n fields, specifically \lon=65 to 75, there was not enough signal to
 acquire a pointing offset using cross-correlation.  In these fields the
@@
 
-  \subfigure[{\it Left}: the Bolocam map in a portion of the $l=30$
+  \subfigure[{\it Left}: the Bolocam map in a portion of the $\lon=30$
   field.  {\it Right}: the SLC maps in the same region.  The green
@@
     \begin{center}
-      \includegraphics[angle=90,scale=0.6]{eachpca}
+      \includegraphics[angle=270,scale=0.6]{eachpca}
     \end{center}
@@
     \begin{center}
-      \includegraphics[angle=90,scale=0.6]{eachpca_20iters}
+      \includegraphics[angle=270,scale=0.6]{eachpca_20iters}
     \end{center}
@@
   Galactic coordinates with a color range from -.1 to 1.0 Jy/beam.
-  {\it Top}: a grid of maps of the first 20 PCA components
-displayed at the same scale.  It is clear that NCG 7538, the object
-imaged, has correlated emission in each component.  There are varying
-levels of correlated noise in each component, with the first through
-third being the most obvious atmospheric components.  Most of the
-other noise components are probably varieties of correlated
-detector noise. {\it Bottom}: The same figure, but after 20
-iterations.  The figure is the breakdown of the atmosphere remainder
-(i.e. the raw data minus the astrophysical model) into eigenfunctions.
-Very little astrophysical flux remains at any level of correlation,
-though there is some at large (few arcminute) scales.}
+  {\it Top 4 rows}: a grid of maps of each of the first 20 PCA components displayed at
+  the same scale.  It is clear that NCG 7538, the object imaged, has emission
+  in each component.  There are varying levels of noise in each component, with
+  the first and second being the most obvious atmospheric components.  Most of
+  the other noise components are probably detector noise correlated among a
+  subset of the bolometers.  The streaks are residuals of the scan-turnaround
+  noise that was not removed by the exponential model fit.  {\it Bottom 4
+  rows}: The same figure, but after 20 iterations.  The figure is the breakdown
+  of the atmosphere remainder (i.e.  the raw data minus the astrophysical
+  model) into eigenfunctions.  Very little astrophysical flux remains at any
+  level of correlation, though there is some at large (few arcminute) scales.}
 \label{fig:PCA_Graphical}
@@
 on the iterative process can be seen in its effect on the
-residuals. From left to right: map, noise, smoothmap, model. Top to
+residuals. From left to right: map, noise, model. Top to
 bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
@@
 Sgr B2, and does not ``dig a hole'' in the residual map, as the
-7.2\arcsec\ kernel does.}{fig:Deconvolution}{1.0}
+7.2\arcsec\ kernel does.  The 7.2\arcsec\ kernel also lacks the
+noise-rejection features of the larger kernels, as can be seen in the
+last panel.}{fig:Deconvolution}{1.0}
 
@@
 
-Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered
-in the maps as a function of the deconvolution kernel used to create
-the astrophysical model maps.  The differences at large source sizes
-are not yet well-understood (!!!!!!), but at the smallest source size,
-it is evident that a deconvolution kernel smaller than the source size
-does not reliably recover the source flux.  Therefore we chose a
-deconvolution kernel smaller than the beam but larger than the pixel
-size used.  Figure \ref{fig:Deconvolution} demonstrates the effects of
-using both too large and too small a kernel.
+Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered in the
+maps as a function of the deconvolution kernel used to create the astrophysical
+model maps.  The differences at large source sizes are not well-understood
+(these size scales may be dominated by atmosphere), but at the smallest source
+size, it is evident that a deconvolution kernel smaller than the source size
+does not reliably recover the source flux.  Therefore we chose a deconvolution
+kernel smaller than the beam but larger than the pixel size used.  Figure
+\ref{fig:Deconvolution} demonstrates the effects of using both too large and
+too small a kernel.
 
@@
 
-\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The
+\FigureTwo{pca_comparison_nolegend_l111}{deconvolution_comparison_nolegend_l111}{The
 fractional flux recovered as a function of source size for
 well-separated Gaussian sources with the FWHM as indicated.
-\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13 (orange),16 (red),21
-(teal),26 (lime),31 (black) PCA components subtracted.  \emph{Right}:
-7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
-kernel for 13 PCA components subtracted. \TBD\ {\it Remove sources
-with sizes smaller than the beam.  Are the sizes FWHM or something
-else?} }{fig:PCA_Filter}{1.0}
+\emph{Left}: 3 (blue), 7 (green), 10 (yellow), 13 (orange), 16 (red), 21
+(teal), 26 (lime), 31 (black) PCA components subtracted.  
+Note that flux recovery drops to 50\% at 120\arcsec for the 13 PCA
+component cleaning used in the released data.  The 3 and 7 PCA cases
+show bumps because atmospheric noise is still present at large scales.
+The $>$100\% recovery for sources smaller than the deconvolution kernel is a
+side-effect; since the deconvolution kernel is smaller than the beam, no real
+source should ever be smaller than the kernel.
+\emph{Right}:
+7.2\arcsec (cyan), 14.4\arcsec (black), 21.6\arcsec (red), 31.2\arcsec (green)
+deconvolution kernel for 13 PCA components subtracted.  It is clear that the
+larger deconvolution kernels generate spurious signal at smaller scales, but
+the flux recovery is very close to 1 at the beam size
+(35\arcsec)}{fig:PCA_Filter}{1.0}
 
@@
 There are clear maxima in the emission filling factor in the Galactic
-Center and in the region from $l=23$ to $l=31$, the line of sight
+Center and in the region from $\lon=23$ to $\lon=31$, the line of sight
 through the densest part of the molecular ring.  Additional areas of
-high source density are seen at $l=10$ and $l=13$.  The filling factor
+high source density are seen at $\lon=10$ and $\lon=13$.  The filling factor
 of 1.1 mm continuum emission at the 100 mJy level is $\sim 20$\% per
-square degree from $l=-10$ to $l=20$ and $\sim 10$\% from $l=20$ to
-$l=50$.
+square degree from $\lon=-10$ to $\lon=20$ and $\sim 10$\% from $\lon=20$ to
+$\lon=50$.
 %In the range
-%$l=50$ to $l=75$, the filling factor is below 1\% and very few sources have
+%$\lon=50$ to $\lon=75$, the filling factor is below 1\% and very few sources have
 %been detected.  

### 2009-04-16 methods/ms.tex
Minor corrections to paper
cygnus comparison figure updated

@@
 \newcommand{\bgpsarea}{150}
-\newcommand{\bcamfwhm}{31.2\arcsec}
+\newcommand{\bcamfwhm}{35.6\arcsec}
 \newcommand{\ncores}{7628}
@@
 
-The data were reduced with a custom pipeline written specifically for
+The data were reduced with a custom pipeline written specifically for the BGPS.
 A key element of the reduction is the iterative estimation of the
@@
 
-The Bolocam observations are sensitive to structure between 31\arcsec\
-and about 400\arcsec\ (the array field of view).  An indicative
-analysis of the spatial filter function of the iterative mapping
-scheme is given in \citet{enoch06}.  The data were sampled onto a
-uniform 7\farcs2 grid.  Flux density calibrations were performed using
-observations of Mars, Uranus, and Neptune, and they are accurate to
-$\sim$20\%.  This is described in \ref{sec:FluxCalibration}.
+The Bolocam observations are sensitive to structure between 35\arcsec\ and
+about 200\arcsec\ (half the array field of view, see figure
+\ref{fig:PCA_filter}).  An indicative analysis of the spatial filter function
+of the iterative mapping scheme is given in \citet{enoch06}.  The data were
+sampled onto a uniform 7\farcs2 grid.  Flux density calibrations were performed
+using observations of Mars, Uranus, and Neptune, and they are accurate to
+$\sim$20\%.  The flux calibration is described in section \ref{sec:FluxCalibration}.
 
@@
 measured $1\sigma$ level is $\approx43\pm7$ mJy/beam within the
-$b=\pm.5$ portion of the plane.
+$b=\pm.5$ portion of the plane in the 1st quadrant.
 %After the pipeline mapping, the fields were combined using the COMBINE
@@
 The absolute pointing accuracy of the survey has been measured to be
-$\sim$6\arcsec\ RMS.  A single $3^\circ \times 1^\circ$ observation of
-each region was registered to the pointing calibrators as a ``master
-field'', and additional observations of that field were aligned to the
-master (Section \ref{sec:Astrometry}).
+$\sim$6\arcsec\ RMS (figure \ref{fig:PointingModel}.  A single $3^\circ \times
+1^\circ$ observation of each region was registered to the pointing calibrators
+as a ``master field'', and additional observations of that field were aligned
+to the master (Section \ref{sec:Astrometry}).
 
@@
 surrounded by substantial negative bowls.  Some flux is restored in
-these bowls using the iterative process 
-%described in \citet{Aguirre2009}
-, but around the brightest sources the impact of the source on the
+these bowls using the iterative process, 
+ but around the brightest sources the impact of the source on the
 background estimation is too great to be fully recovered (Section
@@
 
-Instrument glitches and cosmic ray hits have been removed by a
-combination of outlier rejection in each spatial pixel and hand
-flagging of the timestream data.  Streaking in the images results from
-incorrect determinations of the zero level across scans when a bright
-source is encountered.  Atmospheric noise in observations taken in
-poor weather may not be completely removed by the reduction
-procedures (Section \ref{sec:Noise}).
-%Particular bolometers may be noisy for a single observation and they may not
-%be adequately down-weighted.
+Instrument glitches and cosmic ray hits have been removed by a combination of
+outlier rejection in each spatial pixel and hand flagging of the timestream
+data.  Streaking in the images results from incorrect determinations of the
+zero level across scans when a bright source is encountered and variable noise
+in each strip from variable dwell time.  Atmospheric noise in observations
+taken in poor weather may not be completely removed by the reduction procedures
+because the atmospheric opacity can vary over timescales comparable to the time
+to scan astrophysical sources (Section \ref{sec:Noise}).
 
@@
 the BGPS fields, we make use of the following relation.  The
-calibration ${\cal S}$, referred to the detectors, is given by
+calibration ${\cal S}$, referenced to the detectors, is given by
 \begin{equation}
@@
 all observations.}  Note that this calibration curve folds in both the
-effects of changing atmospheric transmission, as well as changes in
+effects of changing atmospheric transmission and the changes in
 the detector response with optical loading.
@@
 The agreement between epochs was good, so a single combined
-calibration was used for all data here.
+calibration was used for all data.
 %We have found that the calibration can differ
@@
 Gaussian profile.  The beam area is that averaged over all detectors,
-and is ?$1.71\times10^{-6}$\TBD\ ($35.6$\farcs) steradians.  This
+and is $1.71\times10^{-6}$ steradians ($35.6$\farcs).  This
 allows conversion of the maps, calibrated in Jy beam$^{-1}$, into
-surface brightness (MJy sr$^{-1}$).  The uncertainty in the beam size
-is ?$.7\%$\TBD\ (number quoted is the uncertainty in the mean beam
-size), leading to an uncertainty in the surface brightness calibration
+surface brightness (MJy sr$^{-1}$).  The uncertainty in the mean beam size
+is $.7\%$, leading to an uncertainty in the surface brightness calibration
 of \TBD.
@@
 
-The figures of the Cygnus-X region presented by M07
-%Motte et al. (2009)
-, obtained at a central wavelength of 1.2 mm using the 30 meter IRAM
-telescope, appear nearly identical to the 1.1 mm Bolocam images.  The
-BGPS mapping strategy, larger beam, and field of view provides better
-recovery of the large scale structure of the dust continuum emission,
-but inferior angular resolution.  Nevertheless, there is excellent
-agreement between the structure revealed by the two data sets.
-
-The Bolocam and M07 data sets have flux calibration consistent within
-about 20\%.  However, direct comparison with the fluxes listed in M07
-is difficult due to the factor of three difference in the size of the
-beams used.  For example, the the brightest source in the Cyg-X region
-is DR 21.  While M07 quote a peak flux density per beam of
-4.2 Jy/beam for the brightest feature in the DR 21 complex (their peak
-N46) and 17.9 Jy/beam in a 0.19 x 0.14 pc box, BGPS measures a peak
-flux of 17.5 Jy/beam (the beam being roughly 35\arcsec\ in diameter).
-Fluxes are best compared using sources compact as observed with the
-beam of the IRAM 30 meter telescope.
+The figures of the Cygnus-X region presented by \citet{motte07}, obtained at a
+central wavelength of 1.2 mm using the 30 meter IRAM telescope, appear nearly
+identical to the 1.1 mm Bolocam images.  The BGPS mapping strategy, larger
+beam, and field of view provides better recovery of the large scale structure
+of the dust continuum emission, but inferior angular resolution.  The MAMBO
+filter is wider than the Bolocam filter and includes the CO 2-1 line.
+Nevertheless, there is excellent agreement between the structure revealed by
+the two data sets.
+
+The Bolocam and M07 data sets have flux calibration consistent within about
+20\%.  However, direct comparison with the fluxes listed in M07 is difficult
+due to the factor of three difference in the size of the beams used.  For
+example, the the brightest source in the Cyg-X region is DR 21.  While M07
+quote a peak flux density per beam of 4.2 Jy/beam for the brightest feature in
+the DR 21 complex (their peak N46) and 17.9 Jy/beam in a 0.19 x 0.14 pc box,
+BGPS measures a peak flux of 17.5 Jy/beam (the beam being roughly 35\arcsec\ in
+diameter).  Fluxes are best compared using sources that appear compact as
+observed with the beam of the IRAM 30 meter telescope.
 
@@
 in the same aperture from the \citet{motte07} MAMBO map and the Bolocam map of
-this paper. THIS FIGURE IS A PLACEHOLDER}{fig:CygnusComparison}{1.0}
+this paper. }{fig:CygnusComparison}{1.0}
 
@@
 
-\Figure{image_types}{Examples of four of the image types being released.  Top
-left: MAP.  Top right: Residual.  Bottom left: Deconvolved.  Bottom right:
+\Figure{image_types}{Examples of four of the image types being released.  Axes are offsets
+in arcminutes.  See section \ref{sec:FinalMaps}. Top
+left: Map.  Top right: Residual.  Bottom left: Deconvolved.  Bottom right:
 Weight}{fig:sampleimages}{1.0}

### 2009-04-16 methods/ms.tex
new tests for polynomial subtraction to try to get rid of bowls

@@
 CH$_3$OH lines are probably the dominant contributors to line flux in
-the passband.  \citet{nummelin1998} found that 22\% of the flux in one
+the passband.  \citet{nummelin1998} found that 22\% of the flux density in one
 pointing towards Sgr B2 was from lines, and \citet{yoshida2005}
@@
 
-We have convolved the fits files\footnote{{\tt
-ftp://cdsarc.u-strasbg.fr/pub/cats/J/A+A/476/1243/fits/}} with a
-Gaussian kernel that generates an approximately 35\arcsec\ beam,
-matched to our images.  The results are shown in Figure
+We have convolved the \citet{motte07} fits files\footnote{{\tt
+ftp://cdsarc.u-strasbg.fr/pub/cats/J/A+A/476/1243/fits/}} with a Gaussian
+kernel that generates an approximately 35\arcsec\ beam, and compared the
+measured fluxes with those from the BGPS.  The results are shown in Figure
 \ref{fig:CygnusComparison}.
@@
 {Comparison of \citet{motte07} IRAM measurements to BGPS measurements
-in the Cygnus X region
+in the Cygnus X region.  The IRAM data has been convolved to the BGPS beam
+to make the flux density measurements.
 %Note:  The \citet{motte07} integration box is given in terms of pc. 
@@
 %        &   peak mJy/beam  &  mJy in box (see Motte+ Table 1)
-Motte Source Number &  Motte Table 1 integrated flux &  Motte scaled Jy/bm  & BGPS Jy/Bm &    Comments \\
+Motte Source &  Motte Table 1   &  Motte scaled  & BGPS  &  Comments \\
+      Number &  integrated flux &  Jy/bm         & Jy/bm &           \\
 }
@@
 proxy for atmospheric loading.  Red points are observations of Mars and black
-of Uranus.  The black line is a 2nd-order fit with 0,0 (no response if no
-measurable potential difference) forced.  Right: Scaling of the relative
+of Uranus.  The black line is a 2nd-order fit with 0,0 forced (no response if no
+measurable potential difference) .  Right: Scaling of the relative
 response to the atmosphere for a single detector compared to the array
@@
 Pointing observations were performed approximately once every two
-hours over the night.  These sources were then mapped in alt/az
-coordinates relative to the nominal telescope boresight.  The
+hours over the night.   The
 elevation offsets showed a deviation from zero which was empirically
@@
 Nevertheless, an RMS scatter of $\sim 6\arcsec$ for the model over the
-entire observed range was achieved, with the scatter somewhat worse at
-the highest ZA.  A separate model was constructed for each epoch.  The
-residuals are nearly Gaussian, with an RMS of $\sim6\arcsec$.
+entire observed range was achieved, with the scatter somewhat worse at the
+highest ZA.  A separate model was constructed for each epoch, but epoch V was
+used as the primary pointing calibration and is shown in figure
+\ref{fig:PointingModel}.
 
@@
 coordinate system.  This is done by making observations which track
-all detectors across a bright source (a planet) and making maps from each
+all detectors across a bright source (e.g. a planet) and making maps from each
 bolometer individually.
@@
 run.  An elevation-dependent correction is applied via a
-CSO-determined look-up table between raster scans.  We do not see any
+CSO-determined look-up table between raster scans.  We did not see any
 evidence that more frequent focus checks improve the quality of the
@@
 relative alignment using the correlation maps is typically accurate to
-\TBD\ $<1\arcsec$.
-
-TBD: In low s/n fields, specifically \lon=65 to 75, there was not enough signal to
+ $<1\arcsec$.
+
+In low s/n fields, specifically \lon=65 to 75, there was not enough signal to
 acquire a pointing offset using cross-correlation.  In these fields the
@@
 uniform manner and made publicly available as the SCUBA Legacy Catalog
-(hereafter SLC).  These maps provide an excellent cross-check on the
+\citep[][hereafter SLC]{difrancesco08}.  These maps provide an excellent cross-check on the
 accuracy of the BGPS pointing model.  We have used the same
@@
 in wavlength between the surveys or due to the observing strategy) but
-rather makes use of all the information available.  In the event, the
+rather makes use of all the information available.  The
 morphological correlation between SCUBA and BGPS sources is generally

### 2009-04-17 methods/ms.tex
imagetypes -> negative

@@
 % sec:FinalMaps
-% sec:Discussion
+% sec:Analysis
 
@@
         Adam Ginsburg\altaffilmark{\casa},
-        Miranda Nordhaus\altaffilmark{\utexas},
+        Miranda K. Nordhaus\altaffilmark{\utexas},
 	Meredith Drosback\altaffilmark{\virginia},
@@
 time-stream are discussed.  The algorithms reproduce the structure of the
-astronomical sky on a limited range of angular scales and produce artifacts in
+astronomical sky on a \emph{limited range of angular scales} and produce artifacts in
 the vicinity of bright sources. Specifically, extended emission smooth on
@@
 
-Surveys of the galaxy in CO line emission \citep{dame01,FCRAO} have
+Surveys of the galaxy in CO line emission \citep{dame01,jackson06} have
 identified the locations of large molecular clouds and traced
@@
 noise, photometry, and the public data release.  We conclude in
-Section \ref{sec:Discussion} with brief discussion of the immediate
+Section \ref{sec:Analysis} with brief discussion of the immediate
 implications of the emission revealed by the BGPS.
@@
   \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
-  \caption{Cloud complexes centered at $\lon=111$ in the Perseus Arm. \TBD\ Add annotations}
+  \caption{Cloud complexes centered at $\lon=111$ in the Perseus Arm. 
+  The NGC 7538 complex is in the upper-left.}
 \end{figure}
@@
   \includegraphics[scale=0.8]{fig1_pg6_bw_inv_bar_label} 
-  \caption{W3/4/5 \TBD\ Add annotations}
+  \caption{W3/4/5.  The W3(OH)/W3 Main complex is the bright source
+  on the right side of the image.  W5 has one scan performed in RA/Dec
+  instead of Galactic coordinates and so has non-uniform noise properties
+  in each square degree}
 \end{figure}
@@
 % Figure 3
-\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright
-molecular emission lines are shown at their rest frequencies.  Note
-that the Bolocam passband rejects $>90\%$ of the $^{12}$CO flux,
-leaving our continuum measurements largely uncontaminated.  SO and
-CH$_3$OH lines are probably the dominant contributors to line flux in
-the passband.  \citet{nummelin1998} found that 22\% of the flux density in one
-pointing towards Sgr B2 was from lines, and \citet{yoshida2005}
-reported $>40\%$ in Orion A from line emission over the 260-328 GHz band. \TBD\ Other lines
-lying in the Bolocam passband include CS($5\to4$) and ($6\to5$) (245
-and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267 GHz).}
+\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright molecular
+emission lines are shown at their rest frequencies.  Note that the Bolocam
+passband rejects $>90\%$ of the $^{12}$CO flux, leaving our continuum
+measurements largely uncontaminated.  SO and CH$_3$OH lines are probably the
+dominant contributors to line flux in the passband.  \citet{nummelin1998} found
+that 22\% of the flux density in one pointing towards Sgr B2 was from lines,
+and \citet{yoshida2005} reported $>40\%$ in Orion A from line emission over the
+260-328 GHz band. Other lines lying in the Bolocam passband include CS($5\to4$)
+and ($6\to5$) (245 and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267
+GHz).  A follow-up project will attempt to determine the contribution of lines
+to the BGPS flux density measurements.}
 {fig:Bandpass}{1.0}
@@
 pointing model alone, where each individual observation would be
-coadded with tthe 6\arcsec\ RMS uncertainty of the model.  The
+coadded with the 6\arcsec\ RMS uncertainty of the model.  The
 relative alignment using the correlation maps is typically accurate to
@@
 
-All of the SCUBA 850 and 450 \mum\ data has been re-processed in a
-uniform manner and made publicly available as the SCUBA Legacy Catalog
-\citep[][hereafter SLC]{difrancesco08}.  These maps provide an excellent cross-check on the
-accuracy of the BGPS pointing model.  We have used the same
-cross-correlation procedure as that used to obtain the relative
-alignment of Bolocam observations to compare to the SLC.  A number of
-concerns might arise in comparing the Bolocam to the SCUBA maps,
-including the differing scan strategies (SCUBA maps were typically
-taken in jiggle-map mode, which tends to remove extended structure)
-and the often restricted range of positions measured within an
-extended cloud for the SLC.  The cross-correlation technique actually
-mitigates these effects, since it does not require the establishment
-of a single position for an object (which may differ due to the change
-in wavlength between the surveys or due to the observing strategy) but
-rather makes use of all the information available.  The
-morphological correlation between SCUBA and BGPS sources is generally
-excellent, giving a high degree of confidence to the comparison and to
-the results obtained from the pointing model.  An example is shown in
-Figure \ref{fig:SCUBAPointingComparison}.  We find that the RMS offset
-between BGPS and SLC positions within a $3\arcdeg \times 1\arcdeg$
-bloc defined by the BGPS is \TBD\ a few arcseconds, consistent with
-the errors derived for the Bolocam pointing model.
+All of the SCUBA 850 and 450 \mum\ data has been re-processed in a uniform
+manner and made publicly available as the SCUBA Legacy Catalog
+\citep[][hereafter SLC]{difrancesco08}.  These maps provide an excellent
+cross-check on the accuracy of the BGPS pointing model.  We have used the same
+cross-correlation procedure as that used to obtain the relative alignment of
+Bolocam observations to compare to the SLC.  A number of concerns might arise
+in comparing the Bolocam to the SCUBA maps, including the differing scan
+strategies (SCUBA maps were typically taken in jiggle-map mode, which tends to
+remove extended structure) and the often restricted range of positions measured
+within an extended cloud for the SLC.  The cross-correlation technique actually
+mitigates these effects, since it does not require the establishment of a
+single position for an object (which may differ due to the change in wavlength
+between the surveys or due to the observing strategy) but rather makes use of
+all the information available.  The morphological correlation between SCUBA and
+BGPS sources is generally excellent with some exceptions, giving a high degree
+of confidence to the comparison and to the results obtained from the pointing
+model.  An example is shown in Figure \ref{fig:SCUBAPointingComparison}.  We
+find that the RMS offset between BGPS and SLC positions within a $3\arcdeg
+\times 1\arcdeg$ block defined by the BGPS is $4.0\pm8.8$\arcsec, consistent
+with the errors derived for the Bolocam pointing model.  There were some BGPS
+fields that had larger offsets from SCUBA fields; these fields were excluded
+from the offset measurement above because of poor morpohological match.
 
@@
   contours on the Bolocam map indicate the positions of the SLC
-  sources.  \TBD\ {\it Do the negative bowls of either survey bunge up
-  the cross-correlation?  If not, how do we deal with them?  The SCUBA
-  image here has been somewhat doctored because of a large DC offset
-  in the diagonal filament at center}]
+  sources.  Negative bowls in the image are forced to zero before
+  cross-correlating.  ]
   {\label{fig:SCUBAPointingComparison-a}\includegraphics[scale=0.8]
@@
 there exists a linear operation which makes predictions about the
-observed timestreams, namely $d = A m$; this will be denoted $T[m] =
-d$.
+observed timestreams, namely $d_p = A m$; this will be denoted $T[m] =
+d_p$.
 
@@
 \end{equation}
-where $\tilde{s}^{(0)}_i(t)=0$.  This mean atmosphere model is then
-fit to each bolometer to obtain the relative gains (flat field) of the
-detectors
+where $\tilde{s}^{(0)}_i(t)=0$.   Each bolometer's timestream is then 
+fit to the mean atmosphere model to obtain the relative gains of the detectors.
 \begin{equation}
@@
 \end{equation}
-This is illustrated in Figure \ref{fig:Flatfield}.  The instrument
-errors, which are typically smaller than the atmosphere, are then
-estimated
-\begin{equation}
-\tilde{e}^{(n)}_i(t) = some models
-\end{equation}
-and both the atmosphere and instrument models are subtracted from the
+This is illustrated in Figure \ref{fig:Flatfield}.  
+% James - what's this section about?
+% The instrument
+% errors, which are typically smaller than the atmosphere, are then
+% estimated
+% \begin{equation}
+% \tilde{e}^{(n)}_i(t) = some models
+% \end{equation}
+Both the atmosphere and instrument models are subtracted from the
 raw time series
@@
 stage, the iterative process could begin again with Equation
-\ref{eq:FirstIterStep}, though it is highly useful to produce an
-``error map''
+\ref{eq:FirstIterStep}, though it is useful to produce a
+``residual map''
 \begin{equation}
@@
 \end{equation}
-This error map serves as a straightforward visualization of the
-progress of the iterative method, since in a perfect process it would
-be map of $\epsi$.
+This residual map serves as a visualization of the progress of the iterative
+method, since in a perfect process it would be map of $\epsi$.
 
@@
 To further remove the atmosphere (and other correlated instrument
-noise) without a detailed physical model, we use a principal component
+noise) without a detailed physical model, we use principal component
 analysis (PCA) as given in \citet{laurent05}.
@@
 
-\item Pickup from the 60 Hz AC power.  This appears as narrow lines in
-the PSD of the data.  The second harmonic of 60 Hz is aliased via
-beating against the 130 Hz bolometer bias frequency into 10 Hz with
-sidebands split at $\sim1$ Hz.
+\item Pickup from the 60 Hz AC power.  This appears as narrow lines in the PSD
+    of the data.  The second harmonic of 60 Hz is aliased via beating against
+    the 130 Hz bolometer bias frequency into 10 Hz with sidebands split at
+    $\sim1$ Hz.  It is removed by replacing components at these frequencies in
+    the fourier transform with gaussian noise matched to the local mean
+    amplitude.
 
@@
 
+% James - technical question: Why is there microphonic pickup?  What
+% does the term mean, exactly?
 \item Microphonic pickup due to vibrations of the receiver.  The most
@@
 low correlation with astrophysical signal, this step is performed only
-once and is not iterated (c.f. Figure XXX of \citet{sayers09}).
+once and is not iterated (c.f. Figure 1 of \citet{sayers09}).
 
@@
 degenerate with astrophysical signal and must be estimated as part of
-the iterative process.  Glitches are identified as large excursions
-from the RMS level after subtraction of the best atmosphere and bright
-source model, and the data there is excluded from inclusion in
-subsequent maps.  The turnaround microphonics are modeled as decaying
-exponentials at the beginnings and ends of scans.
+the iterative process.  
+% NOT TRUE - they are identified per-pixel most of the time
+% Glitches are identified as large excursions
+% from the RMS level after subtraction of the best atmosphere and bright
+% source model, and the data there is excluded from inclusion in
+% subsequent maps.
+The turnaround microphonics are modeled as decaying exponentials at the
+beginnings and ends of scans and are also removed by the PCA cleaning.
 
@@
 
-%WRITTEN POORLY: 
 The timestream data is made into a spatial map using the pointing data
@@
 that it accentuates the unevenness of the cross-scan sampling, since
-ech timestream point's value is assigned to an area much smaller than
-the beam.  In principle this can be addressed by various gridding
-algorithms, and may be a part of future reductions of the BGPS data.
-
-The resulting map is then subjected to a maximum-entropy CLEAN algorithm
-%\citep{hogbom} 
-using a specified kernel to produce a deconvolved image
-which is the one actually mapped back into the timestream to be
-subtracted (Equation \ref{eq:MapToTime}.  This has several advantages
-over using the original map directly, including rejecting artefacts
-smaller than the beam and decreasing the noise of the resulting
-timestream.  It is also better than a ``threshold'' method, which
-tends to produce discontinuities.
-
-In some fields, flux from certain source spread out over the course of
-the iterative process using certain kernel sizes.  The cause of this
-artifact are not yet well-understood, but using a different kernel
-size was an effective workaround and did little to change the
-properties of the final map.
+each timestream point's value is assigned to an area much smaller than
+the beam.
+%In principle this can be addressed by various gridding
+%algorithms, and may be a part of future reductions of the BGPS data.
+
+The resulting map is then subjected to a maximum-entropy clean algorithm
+\citep{hollis92} using a specified kernel to produce a deconvolved image which
+is mapped back into the timestream to be subtracted (Equation
+\ref{eq:MapToTime}).  This has several advantages over using the original map
+directly, including rejecting artifacts smaller than the kernel and decreasing
+the noise of the resulting timestream.  It is also better than a ``threshold''
+method, which tends to produce discontinuities and include noise outliers.
+
+In some fields, flux from some sources spread out over the course of the
+iterative process using certain kernel sizes.  The cause of this artifact is
+not yet well-understood, but using a different kernel size was an effective
+workaround and did little to change the properties of the final map.  The
+standard kernel size was 14.4\arcsec; a 21.6\arcsec kernel was used when
+artifacts were encountered.
 
@@
 data in the \lon=111 field.  Glitches below the detection threshold may
-contribute to the overall noise signal.}{fig:GlitchDistribution}{1.0}
+contribute to the overall noise.}{fig:GlitchDistribution}{1.0}
 
@@
 
-The error maps produced by the iterative mapping provide a natural way
-of estimating the systematic error resulting from imperfect
-subtraction of bright sources.  This results in ``ghosts'' of the
-bright sources in the error maps $E$.
-
-Noise maps are produced for each map, made from the residuals after
-removing the astrophysical signal model as well as the PCA component
-model.  These maps are useful for diagnosing the effect of the
-iterative process on bright sources and as a method of obtaining an
+The residual maps produced by the iterative mapping provide a natural way of
+estimating the systematic error resulting from imperfect subtraction of bright
+sources.  The imperfect subtraction results in ``ghosts'' of the bright sources
+in the error maps $E$.
+
+Residual maps are produced for each map from the residuals after
+removing the astrophysical signal model and the PCA atmosphere model.  These
+maps are useful for diagnosing the effect of the iterative process on bright
+sources and as a method of obtaining an
 estimate of the noise.
 
-The noise is correlated between adjacent spatial pixels due to
-residual atmospheric noise correlated in time..  We have completed
-ignored this effect in our analysis.
-
-The noise may be estimated either from the error maps, from the
-timestream PSDs of the detectors, or from the weight maps
-produced. The final per-pixel error estimate is given as \TBD.
+% ...ok, explain please?
+% The noise is correlated between adjacent spatial pixels due to
+% residual atmospheric noise correlated in time.  We have completed
+% ignored this effect in our analysis.
+
+The noise may be estimated either from the residual maps, from the timestream
+PSDs of the detectors, or from the weight maps produced. The final per-pixel
+error estimate is given as \TBD (this remains an open question - is the best
+per-pixel error a smoothed version of the residual map, e.g.  \citet{enoch06},
+1/weightmap$^2$, or some other estimate? Adam, James, Erik).
 
@@
 variation of the depth as a function of Galactic longitude in Figure
-\ref{fig:NoiseVsLongitude}.  The depth can be converted into an
+\ref{fig:NoiseVsLongitude}.
+
+The depth can be converted into an
 estimate of mass via standard estimates, i.e., under the assumption of
 a temperature, opacity, and distance.
-
-Using the same dust opacity as \TBD\ ({\it put in original references})
+Using dust opacity from \citet{ossenkopf94}
 %\citet{enoch06} and \citet{young06},
-and assuming a gas-to-dust mass ratio $X$ of 100, the mass sensitivity
+and assuming a gas-to-dust mass ratio 100, the mass sensitivity
 can be written as
@@
 M_{gas}\approx
-0.22\left( e^{12.9/T_d}-1 \right) \left({S_\nu\over 15\; {\rm mJy}} \right)
+0.22\left( e^{13.1/T_d}-1 \right) \left({S_\nu\over 15\; {\rm mJy}} \right)
 D^{2}_{kpc} \msol 
@@
 1$ mag, with the same $T_d$ dependence).  For Bolocam, $h\nu/k \approx
-13$~K, so for $T_d > XXX$ the dependence is approximately linear.  At
+13$~K, so for $T_d > 10$K the dependence is approximately linear.  At
 the coldest temperatures expected, the mass changes a factor of 2.9
-between 20 and 10 K.  Far more important is the accurate determination
-of the distance to the clump.
+between 20 and 10 K.  The distance to the clump is more important in most
+situations.
 
@@
 merely deal with the limitations on performing photometry imposed by
-the data analysis itself.
+the data itself.
 
@@
 primary beam $G(\xad)$, together with an effective high-pass
-spatial filter $F(\xad)$,
+spatial filter $F(\xad)$ (figure \ref{fig:PCA_filter}),
 \[
@@
 \]
+
+%James - please explain this to me, or explain it better here.  What
+%is the form of B(Omega) that it gives 0?
 The effect of the high pass filter is that the effective PSF $B=G
@@
 reasonable compromise between attenuating extended structure and
-attaining high S/N on compact faint objects.
-
-Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered in the
+cleaning the atmospheric contribution.  Note that this is a substantially
+more aggressive cleaning than that used in \citet{enoch06} largely because
+our mean integration time per pixel was $\sim$seconds, whereas theirs was
+$\sim$minutes, and therefore the atmospheric noise was much more likely to
+be correlated between observations.
+
+Figure \ref{fig:PCA_Filter}b shows the fraction of flux recovered in the
 maps as a function of the deconvolution kernel used to create the astrophysical
@@
 are near the coordinate system equator, the difference between truly
-equiareal pixels and the pixels used is at most X\%.  The pixel size
+equiareal pixels and the pixels used is at most (James: find this number?) X\%.  The pixel size
 is 7.2\arcsec, chosen to be much smaller than the Bolocam beam.
@@
 The model maps are deconvolved using the maximum-entropy method with kernels
-specified in the header.  The residual map is the map of the model timestream
+specified in the header (either 14.4\arcsec or 21.6\arcsec).  The residual map is the map of the model timestream
 subtracted from the data timestream; it is close to but not identical to the
@@
 timestream have been assigned to each pixel; it is proportional to the dwell
-time per pixel (each 'hit' is .1s).  Examples of each (except the nhitsmap)
+time per pixel (each `hit' is .1s).  Examples of each (except the nhitsmap)
 are given in figure \ref{fig:sampleimages}.
@@
 version of the catalog provided in \citep{rosolowsky09}.  The full
-release inclues
+release includes
 \begin{enumerate}
 \item Calibrated maps for all regions observed (MAP)
-\item The MAP smoothed by the Bolocam PSF, which is helpful in bringing out extended structure (SMOOTHMAP)
+% don't release smoothmaps? \item The MAP smoothed by the Bolocam PSF, which is helpful in bringing out extended structure (SMOOTHMAP)
 \item The deconvolved MAP (DECONVMAP)
@@
 
-\section{Discussion}
-\label{sec:Discussion}
-
-% first millimeter....
+\section{Analysis}
+\label{sec:Analysis}
+
 The BGPS is the first millimeter survey of a substantial fraction
@@
 gas most intimately associated with the earliest phases of star
-formation.  Inspection of Figure \ref{fig:BGPSMontage} shows excellent
+formation.
+
+Inspection of Figure \ref{fig:BGPSMontage} shows excellent
 correspondence with SCUBA maps of small sub-fields throughout the
@@
 do not appear in the Spitzer observations, which suggests that the 1.1
-mm emission traces dense clumps without a background to absorb.  A
-study of IRDC correlation with BGPS emission is underway
-\citep{battersby09}.
+mm emission traces dense clumps without a background to absorb.  [if we
+include this, we probably need a figure as an example, c.f. \citet{shuller09}]
+
+% No advertisements.
+% A
+% study of IRDC correlation with BGPS emission is underway
+% \citep{battersby09}.
 
@@
 square degree from $\lon=-10$ to $\lon=20$ and $\sim 10$\% from $\lon=20$ to
-$\lon=50$.
+$\lon=50$ (compare to figure \ref{fig:NoiseVsLongitude}.
 %In the range
@@
 This result is in contrast to CO filling factors $\sim1$ in the inner galactic
-plane \citep{dame01,FCRAO}, confirming that 1.1 mm continuum emission traces
+plane \citep{dame01,jackson06}, confirming that 1.1 mm continuum emission traces
 denser material than CO.  
@@
 Galactic Ring Survey $^{13}$CO and 1.1 mm continuum morphology
-\citep{IRDCdistance,FCRAO}.  However, in other cases the association
+\citep{IRDCdistance,jackson06}.  However, in other cases the association
 between the CO and 1.1 mm data is not clear, either because of
@@
 to provide radial velocity, density, chemistry, and temperature
-measurements \citep{schlingman09, battersby09, nordhaus09}.
+measurements. % no advertisements \citep{schlingman09, battersby09, nordhaus09}.
 
@@
 molecular clouds (GMCs) traced by CO surveys
-\citep[e.g.,][]{dame01,FCRAO}.  The brightest clumps visible in our
+\citep[e.g.,][]{dame01,jackson06}.  The brightest clumps visible in our
 maps, e.g. \object{Sgr B2}, \object{G34.3+0.15}, \object{W 51},
@@
 
+% James - it would be nice to include some numbers here, not just the process.
+
 \section{Pointing Calculation}
@@
 To calculate the position at which to point the telescope, the CSO
-antenna computer computes an alt/az derived from the RA/Dec J2000
+antenna computer computes an alt/az ($E$,$A$) derived from the RA/Dec J2000
 (heliocentric) catalog position.  It performs the following
@@
 
-\item A 11-term model (``$C$-terms'') based on the optical pointing of
-the telescope is then applied to $A$ and $Z$ along with $t$-terms (?),
+\item An 11-term model (``$C$-terms'') based on the optical pointing of
+the telescope is then applied to $A$ and $E$ along with $t$-terms (?), %James?
 the tilt of the alidade, and a refraction correction to obtain the

### 2009-04-17 methods/ms.tex
remove rms from plot header
introduction modified with Schuller materials

@@
 \newcommand{\solar}{\ensuremath{\odot}}
-\newcommand{\lon}{\ensuremath{\ell}}
+\newcommand{\lon}{\ensuremath{l}}
 
@@
 from uniform over molecular clouds, but is concentrated in unusually dense
-regions called clumps or cores, which fill a small fraction of the area
-of most clouds [refs. E. Lada et al. Evans et al., Enoch et al.]
-Following \citet{williams00} and McKee-Ostriker (ARAA), we
-use the term `core' to refer to a very dense region destined to form an
-individual star or small multiple star systems and the term `clump' to
-refer to a
-region likely to form a group or cluster of stars. While clumps forming
-massive clusters may be denser than cores forming low mass stars
-[ref Mueller?],
-in general, clumps are larger and less dense. Clumps can be traced
-with line emission from molecules such as \ammonia, \form, CS, HCN, etc.
-Spectral lines also provide excellent diagnostics of
-line-of-sight motions, temperatures, and densities.
-However, the interpretation of these gas tracers is complicated by
-variations in tracer abundances caused by depletions and complex
-chemical processing, uncertainties in optical depths and excitation
-conditions, and the impacts of radiation fields and shocks. These
-complications make the derivation of column densities, masses, and
-other physical properties of star-forming clumps very difficult.
-A further limitation of spectral line studies is that the tracers of
-denser gas tend to be weak and multi-element receiver arrays have
-only a modest number of elements, making blind surveys very time-consuming.
-
-% redundant:
-% In contrast, focal-plane arrays containing hundreds of individual
-% bolometers sensitive to millimeter and sub-millimeter (sub-mm)
-% radiation are now available. This advance in technology enables
-% blind surveys of the Galactic plane, providing a uniform inventory of massive
-% star-forming and starless clumps.  Catalogs resulting
-% from such surveys will provide the data base for subsequent observations
-% in tracers such as hard-to-excite molecular lines and higher resolution
-% studies with instruments like CARMA and ALMA.
-(this line belongs somewhere)
-A further advantage of continuum observations of dust at long wavelengths
-is the low optical depth of the dust \citep{johnstone06},
-permitting a straight-forward estimate of the mass of the emitting region.
+regions called clumps or cores, which fill a small fraction of the area of most
+clouds \citep{enoch06,evans09}[refs. E. Lada et al. Evans et al., Enoch et al.]
+(Neal, John, Jonathan) Following \citet{williams00} and \citep{mckee07}, we use
+the term `core' to refer to a very dense region destined to form an individual
+star or small multiple star systems and the term `clump' to refer to a region
+likely to form a group or cluster of stars. While clumps forming massive
+clusters may be denser than cores forming low mass stars [ref Mueller? (Neal,
+John, Jonathan)], in general, clumps are larger and less dense. Clumps can be
+traced with line emission from molecules such as \ammonia, \form, CS, HCN, etc.
+Spectral lines also provide excellent diagnostics of line-of-sight motions,
+temperatures, and densities.  However, the interpretation of these gas tracers
+is complicated by variations in tracer abundances caused by depletions and
+complex chemical processing, uncertainties in optical depths and excitation
+conditions, and the impacts of radiation fields and shocks. These complications
+make the derivation of column densities, masses, and other physical properties
+of star-forming clumps very difficult.  A limitation of spectral line studies
+is that the tracers of denser gas tend to be weak and multi-element receiver
+arrays have only a modest number of elements, making blind surveys very
+time-consuming.
+
+In contrast, focal-plane arrays containing hundreds of individual bolometers
+sensitive to millimeter and sub-millimeter (sub-mm) radiation are now
+available. This advance in technology enables blind surveys of the Galactic
+plane, providing a uniform inventory of massive star-forming and starless
+clumps.  Catalogs resulting from these surveys will provide the data base for
+subsequent observations in tracers such as hard-to-excite molecular lines and
+higher resolution studies with instruments like CARMA and ALMA.  A significant
+advantage of continuum observations of dust at long wavelengths is the low
+optical depth of the dust \citep{johnstone06}, permitting a straight-forward
+estimate of the mass of the emitting region.
 
@@
 
-Two large surveys of the Galactic plane are in progress.
-The ATLASGAL survey, using the LABOCA instrument at 870 \micron\
-on the APEX telescope in Chile, will cover the southern Galactic plane
-and extend somewhat into the north. Initial results from this survey
-have been reported by \citet{schuller09}. [say more - overlap region?
-]
+Two large surveys of the Galactic plane are in progress.  The ATLASGAL survey,
+using the LABOCA instrument at 870 \micron\  with 12\arcsec resolution on the
+APEX telescope in Chile, will cover the southern Galactic plane and some of the
+north.  Initial results from this survey have been reported by
+\citet{schuller09}. The overlap region between BGPS and ATLASGAL is in the
+region $-10.5 < \lon < 11.5$ and $15 < \lon < 21$, $-.5 < b < .5$, though
+ATLASGAL will eventually expand up to $\lon = 60$.  The two surveys provide
+complementary samples of the long-wavelength end of the spectral energy
+distribution in Galactic star forming regions.
 
@@
 \begin{figure}
-  \subfigure[The pointing model correction (left) and residuals
-(right) for Epoch V, from which the master reference images were
-derived for subsequent alignment.  The red line indicates the fitted
-model. ]
+  \subfigure[The pointing model correction (left) and residuals (right) for
+  Epoch V, from which the master reference images were derived for subsequent
+  alignment.  The red line indicates the fitted model. 510 pointing sources
+  were included, and the final RMS was 5.77\arcsec in altitude and 3.21\arcsec
+  in azimuth, or a total RMS offset of 6.6\arcsec]
 {\label{fig:PointingModel-a}\includegraphics[scale=0.9]{paper_models_0707}}\\

### 2009-04-17 methods/ms.tex
distmaps

@@
 The absolute pointing accuracy of the survey has been measured to be
-$\sim$6\arcsec\ RMS (figure \ref{fig:PointingModel}.  A single $3^\circ \times
-1^\circ$ observation of each region was registered to the pointing calibrators
-as a ``master field'', and additional observations of that field were aligned
-to the master (Section \ref{sec:Astrometry}).
+$\sim$6\arcsec\ RMS (figure \ref{fig:PointingModel}.  The Epoch V pointing model
+was used to make pointing reference fields which were then median combined
+using IRAF to make a higher S/N reference field with somewhat reduced pointing
+errors (Section \ref{sec:Astrometry}).
+
+% A single $3^\circ \times
+% 1^\circ$ observation of each region was registered to the pointing calibrators
+% as a ``master field'', and additional observations of that field were aligned
+% to the master (Section \ref{sec:Astrometry}).
 

### 2009-04-17 methods/ms.tex
distmaps

@@
 We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm continuum survey
-of \bgpsarea\ square degrees of the Galactic Plane primarily in the 1st
-quadrant with some coverage in the 2nd and 3rd quadrants.  The BGPS represents
+of \bgpsarea\ square degrees of the Galactic Plane with 130 in the 1st quadrant,
+31 in the 2nd, and 6 in the 3rd.  The BGPS represents
 the first large area, systematic survey of the Northern Galactic Plane in the
 millimeter continuum without pre-selected targets.  The survey has detected
-\ncores\ clumps to a limiting depth of between \bgpsdepthlow\ and
-\bgpsdepthhigh\ mJy RMS.  We include maps of 100 contiguous square degrees from
+\ncores\ clumps to a limiting non-uniform 1-$\sig$ noise level in the range \bgpsdepthlow\ and
+\bgpsdepthhigh\ mJy/beam RMS.  We present maps of 97 contiguous square degrees from
 $\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
 well as regions in IC1396, $\lon=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
-striking feature of the maps is the filamentary structure of cold dust
+striking feature of the maps is the filamentary structure of millimeter emission
 throughout the Galaxy.

### 2009-04-17 methods/ms.tex
distmaps

@@
 millimeter continuum without pre-selected targets.  The survey has detected
-\ncores\ clumps to a limiting non-uniform 1-$\sig$ noise level in the range \bgpsdepthlow\ and
+\ncores\ clumps to a limiting non-uniform 1-$\sigma$ noise level in the range \bgpsdepthlow\ and
 \bgpsdepthhigh\ mJy/beam RMS.  We present maps of 97 contiguous square degrees from
@@
 an important finder chart for future observations with ALMA and a
-long-wavelength spectral band complementary to imminent submillimeter surveys
-with SCUBA-2 and Herschel-SPIRE.
+long-wavelength spectral band complementary to ATLASGAL and imminent
+submillimeter surveys with SCUBA-2 and Herschel-SPIRE.
 
@@
 constraints on the physical properties of the clumps, especially masses and
-mean densities.
+mean densities, in conjunction with distance information.
 
@@
 clusters may be denser than cores forming low mass stars [ref Mueller? (Neal,
-John, Jonathan)], in general, clumps are larger and less dense. Clumps can be
+John, Jonathan)], in general, clumps are larger and have a lower mean density. Clumps can be
 traced with line emission from molecules such as \ammonia, \form, CS, HCN, etc.
@@
 molecular clouds at 1.1 mm and identify hundreds of cores \citep{enoch06}.
-Others have used MAMBO on the 30-m IRAM telescope at 1.2 mm to map
+MAMBO on the 30-m IRAM telescope has been used at 1.2 mm to map
 more distant regions of more massive star formation \citep{motte07}.
@@
 starless clumps may be quite cold ($\td \approx 10$ K), the uncertainty in mass
-caused by uncertain temperature is slightly less at 1.1 mm.  For example, the
-mass estimate if the actual $\td = 20$ K, rather than 10 K, would decrease by a
-factor of 3.3 at 870 \micron\ versus a factor of 2.9 at 1.1 mm. In addition,
+caused by uncertain temperature is slightly less at 1.1 mm.  For example, 
+if the actual $\td = 20$ K, rather than 10 K, the mass estimate would decrease by a
+factor of 3.3 at 870 \micron\ versus a factor of 2.9 at 1.1 mm.
+
+In addition,
 the Bolocam bandpass excludes the CO \jj{2}{1} line, which can be a significant
@@
 surveyed fields, providing an unbiased sample of clumps suitable for
-multi-wavelength and high-resolution studies with existing telescopes
-and future facilities.  At the distances that we are observing these
-objects, we are likely observing aggregates of star forming cores
-found in a larger molecular cloud environment, which we will refer to
-as clumps \citep{williams00}.  The clump catalog is described in a
-companion paper \citep{rosolowsky09}.
+multi-wavelength and high-resolution studies with existing telescopes and
+future facilities.  At the distances that we are likely to be observing these
+objects (assuming the majority are at distances greater than 2kpc....
+because?), we are likely observing aggregates of star forming cores found in a
+larger molecular cloud environment, which we will refer to as clumps
+\citep{williams00}.  The clump catalog is described in a companion paper
+\citep{rosolowsky09}.
 
@@
 \Figure{coverage_moll} {The coverage of the BGPS.  The background
-greyscale is IRAS 100 \mum.  
+greyscale is IRAS 100 \mum.  [James, team: is there a better figure 
+option?]
 %The Bolocam coverage is shown with white
@@
 
+\addtocounter{figure}{0}
 %\begin{sidewaysfigure}[h]
 \begin{figure}
+    \label{fig:BGPSMontage}
   \begin{minipage}{6.5in}
@@
       \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
-      \caption{$\lon=-10.5$ to $\lon=19.5$ Units are Jy/Beam.  The brightest
-	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
-	$\lon=13$, appear to be saturated, but this is only a display
-	artifact.  The noise is more pronounced from $\lon=-7$ to $\lon=-2$
+      \caption{$\lon=-10.5$ to $\lon=19.5$ Units are Jy/Beam. 
+%      The brightest
+%	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
+%	$\lon=13$, appear to be saturated, but this is only a display
+%	artifact.
+        The noise is more pronounced from $\lon=-7$ to $\lon=-2$
 	because this region was observed less.}
     \end{center}
-    \label{fig:BGPSMontage}
   \end{minipage}
@@
 
-\addtocounter{figure}{-1}
+\addtocounter{figure}{0}
 \addtocounter{subfig}{1}
@@
 
-  \addtocounter{figure}{-1} 
+  \addtocounter{figure}{0} 
   \addtocounter{subfig}{1}

### 2009-04-18 methods/ms.tex
distmaps

@@
       \caption{$\lon=49.5$ to $\lon=74.5$.  In comparison to the inner galaxy, the $65
-      < \ell < 75$ has a very sparse population of clumps}
+      < \ell < 75$ has a very sparse population of faint clumps}
     \end{center}
@@
   1.5\deg$. The large scale `peanut' shape including DR21 is suggestive of a
-  large wind-blown bubble, although.... [someone else must have commented on
-  this in the past?].  See section \ref{sec:motte} for a comparison with the
+  large wind-blown bubble, although.... [John: fill in discussion here or we'll
+  remove it].  See section \ref{sec:motte} for a comparison with the
   \citet{motte07} IRAM study of this region. }
@@
 Bolocam\footnote{{\tt http://www.cso.caltech.edu/bolocam}} is the
-facility 144-element bolometer array camera operating from the 10.4 m
+facility 144-element bolometer array camera operating on the 10.4 m
 dish of the Caltech Submillimeter Observatory (CSO) on the summit of
@@
 268~GHz (hereafter 1.1~mm) and fractional bandwidth $\Delta \nu/\nu =
-0.17$.  The passband is constructed to exclude the $^{12}\mathrm{CO}(2
+0.17$ (45.5 GHz).  The passband is constructed to exclude the $^{12}\mathrm{CO}(2
 \to 1)$ emission line.  Figure \ref{fig:Bandpass} shows the passband.
-We compute color corrections for sources of varying spectral index in
-Appendix \ref{app:ColorCorrections}.
+We compute color corrections in Appendix \ref{app:ColorCorrections}.
 

### 2009-04-18 methods/ms.tex
distmaps

@@
 \newcommand{\lon}{\ensuremath{l}}
+\newcommand\jyb{Jy~beam$^{-1}$}
 
@@
 \ncores\ clumps to a limiting non-uniform 1-$\sigma$ noise level in the range \bgpsdepthlow\ and
-\bgpsdepthhigh\ mJy/beam RMS.  We present maps of 97 contiguous square degrees from
+\bgpsdepthhigh\ m\jyb RMS.  We present maps of 97 contiguous square degrees from
 $\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
@@
 %\begin{figure}
-%  \subfigure[$\lon=-10.5$ to $\lon=19.5$ Units are Jy/Beam.  The brightest
+%  \subfigure[$\lon=-10.5$ to $\lon=19.5$ Units are \jyb.  The brightest
 %	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
@@
 %\pagebreak
-%\subfigure[$\lon=19.5$ to $\lon=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
+%\subfigure[$\lon=19.5$ to $\lon=49.5$.  Units are \jyb .  G34.3+0.15, W
 %	51, W 43, W 49, and M 17 appear to be saturated, but this is
@@
       \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
-      \caption{$\lon=-10.5$ to $\lon=19.5$ Units are Jy/Beam. 
+      \caption{$\lon=-10.5$ to $\lon=19.5$ Units are \jyb. 
 %      The brightest
@@
       \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
-      \caption{$\lon=19.5$ to $\lon=49.5$.  Units are Jy/Beam .  G34.3+0.15, W
+      \caption{$\lon=19.5$ to $\lon=49.5$.  Units are \jyb .  G34.3+0.15, W
 	51, W 43, W 49, and M 17 appear to be saturated, but this is
@@
 
-The observations described here were acquired during six separate
+The maps presented here were acquired during six separate
 observing sessions at the CSO over the course of two years.  The
@@
 corresponding ranges for the zenith opacity $\tau_{225}$ of the CSO
-tipper tau.  Because of the CSO weather multiplexing policy, Bolocam
+tipper tau.  Bolocam
 observations were typically scheduled when $\tau_{225} > 0.06$.
-Between each observing epoch, Bolocam was removed from its mount at
+Between observing epochs, Bolocam was removed from its mount at
 the re-imaged Cassegrain focus and stored warm.  Thus the flux
@@
 flux calibration did not in fact differ significantly between epochs.
-For the pointing model, we computed a well-constrained version for
-Epoch V and aligned all images to this.
+We observed additional pointing sources during Epoch V and therefore
+used it as the master pointing model.
 
@@
 
-Our basic observing strategy was to raster scan Bolocam by moving the
+[Reword section?] Our basic observing strategy was to raster scan Bolocam by moving the
 primary mirror of the CSO to modulate the astrophysical signal faster
 than fluctuations in atmospheric opacity.  Each field was scanned with
-alternating raster scans along $l$ and $b$.  Starting with Epoch III,
-the fundamental scan unit was a $3\arcdeg \times 1\arcdeg$ block.
-Each block was scanned with 23 scans along lines of constant $b$, and
-67 scans along lines of constant $l$.  In both cases, the spacing
-between adjacent rasters was 162\arcsec.  The total time for such a
-scan was between 39 and 48 minutes.  The data were electronically
-sampled at 10 Hz along the scan direction, slightly higher than the
-Nyquist rate for the scan speed of 120\arcsec\ s$^{-1}$.
+alternating raster scans along $l$ and $b$.  In Epoch I-II, the fundamental
+scan unit was a $1\arcdeg \times 1\arcdeg$ block, scanned 23 times in \lon and
+$b$.  Starting with Epoch III, the fundamental scan unit was changed to a
+$3\arcdeg \times 1\arcdeg$ block for increased mapping efficiency.  Each block
+was scanned with 23 scans along lines of constant $b$, and 67 scans along lines
+of constant $l$.  In both cases, the spacing between adjacent rasters was
+162\arcsec.  The total time for such a scan was between 39 and 48 minutes.  The
+data were electronically sampled at 10 Hz along the scan direction, slightly
+higher than the Nyquist rate for the scan speed of 120\arcsec\ s$^{-1}$.
 
@@
 in Figure \ref{fig:Array}.  Achieving good sampling is complicated by
-a number of missing pixels.  A simulation was performed to determine
+a number of missing bolometers.  A simulation was performed to determine
 the optimal angle to rotate the array with respect to the scan
-direction to account for the beam spacing and missing pixels.  During
+direction to account for the beam spacing and missing bolometers.  During
 the turnaround following a raster, the field rotator is adjusted to
@@
 atmospheric model is developed from a set of principal components of
-the bolometer signal time series under the assumption that the bulk of
-the correlated signal is atmospheric.  The iterative estimation
+the bolometer signal time series under the assumption that the bulk of the
+correlated signal is atmospheric (under this assumption, astrophysical extended
+structures are treated as atmospheric noise).  The iterative estimation
 process then helps to restore correlated flux due to astrophysical
@@
 \ref{fig:PCA_filter}).  An indicative analysis of the spatial filter function
-of the iterative mapping scheme is given in \citet{enoch06}.  The data were
+of the iterative mapping scheme is given in \citet{enoch06}, and we present a detailed analysis
+of the filter function in our survey in figure \ref{fig:PCA_filter}.  The data were
 sampled onto a uniform 7\farcs2 grid.  Flux density calibrations were performed
@@
 Noise properties across the survey are not completely uniform, but the
-measured $1\sigma$ level is $\approx43\pm7$ mJy/beam within the
+measured $1\sigma$ level is $\approx43\pm7$ m\jyb within the
 $b=\pm.5$ portion of the plane in the 1st quadrant.
@@
 
-The absolute pointing accuracy of the survey has been measured to be
-$\sim$6\arcsec\ RMS (figure \ref{fig:PointingModel}.  The Epoch V pointing model
-was used to make pointing reference fields which were then median combined
-using IRAF to make a higher S/N reference field with somewhat reduced pointing
-errors (Section \ref{sec:Astrometry}).
+A separate model was constructed for each epoch, but epoch V was used as the
+primary pointing calibration and is shown in figure \ref{fig:PointingModel}.
+In epoch V and VI, pointing sources were observed more frequently to obtain a
+better-constrained master pointing model. The absolute pointing accuracy was
+$\sim6\arcsec$ RMS.  The Epoch V pointing model was used to make pointing
+reference fields which were then median combined using IRAF to make a higher
+S/N reference field with somewhat reduced pointing errors (Section
+\ref{sec:Astrometry}).
 
@@
 
-The absolute flux calibration is obtained from observations of Mars
+The absolute flux calibration is derived from observations of Mars
 and Uranus
@@
 in-band atmosphere opacity.  Under the assumption that the only power
-variation on the detectors is due to the power from the atmosphere,
+variation on the detectors is due to the power from the atmosphere (i.e.
+that astronomical sources are faint relative to the atmosphere),
 which may be parameterized by $\tau$, ${\cal S}$ is a single-valued
@@
 
-A fit to the observed values for the primary calibrators was performed
-for the each epoch separately.
+A fit to the observed values (measured potential difference vs. known flux
+density) for the primary calibrators was performed for the each epoch
+separately.
 %CHECK
@@
 plane.  We do this by monitoring the response to the atmosphere
-emission in all bolometers.  Since the atmosphere is common to all
-detectors, any changes in response are due to the intrinsic properties
-of the detectors.  The change in relative response with loading for a
-typical detector is shown in Figure \ref{fig:CalibrationCurves}.  The
-actual application of the the method to the time series of the
-bolometer data is shown in Figure \ref{fig:Flatfield}, and is
-discussed further in Section \ref{sec:Mapping}.
+emission in all bolometers (astrophysical signal is negligible except at SgrB2).  Since the
+atmosphere is common to all detectors [Anyone - why is the atmosphere common across 7.5'
+at the mm?  Brief discussion of atmosphere physics would be helpful], any changes in response are due to the
+intrinsic properties of the detectors.  The change in relative response with
+loading for a typical detector is shown in Figure \ref{fig:CalibrationCurves}.
+The actual application of the method to the time series of the bolometer
+data is shown in Figure \ref{fig:Flatfield}, and is discussed further in
+Section \ref{sec:Mapping}.
+
+[move this?] In figure \ref{fig:Flatfield}, each step of the iterative cleaning process is illustrated.
 
@@
 \label{sec:motte}
-
-Comparison of the accuracy of the Bolocam flux density calibration
-with the SCUBA 850 \mum\ results is complicated by the unknown effect
+\bf{Claudia's comments:}
+In general, this section could use some reorganizing such that it sets out why
+this comparison field was chosen first (best available data?), describes any
+relevant differences in the datasets (eg filter bandpasses, CO possibly in
+MAMBO filter), describes how the comparison was done, and then represents the
+results.  It seems out of order at the moment.  A reference for CO
+contamination causing detectable contamination (at 850um, not 1mm) is
+Hatchell, J., \& Dunham, M.~M.\ 2009, arXiv:0904.1163
+
+Comparison of the BGPS flux density calibration
+with SCUBA 850 \mum\ results is complicated by the unknown effect
 of the dust spectral index.  However, there are several large-area
@@
 central wavelength of 1.2 mm using the 30 meter IRAM telescope, appear nearly
-identical to the 1.1 mm Bolocam images.  The BGPS mapping strategy, larger
-beam, and field of view provides better recovery of the large scale structure
-of the dust continuum emission, but inferior angular resolution.  The MAMBO
-filter is wider than the Bolocam filter and includes the CO 2-1 line.
-Nevertheless, there is excellent agreement between the structure revealed by
-the two data sets.
-
-The Bolocam and M07 data sets have flux calibration consistent within about
-20\%.  However, direct comparison with the fluxes listed in M07 is difficult
+identical to the 1.1 mm Bolocam images.  The MAMBO filter is wider than the
+Bolocam filter and includes the CO 2-1 line.  Nevertheless, there is excellent
+qualitative agreement between the structure revealed by the two data sets on size
+scales to which both are sensitive.
+
+[John - may want to remove N46 and other extended sources from comparison.  This 
+paragraph needs cleanup]
+Direct comparison with the fluxes listed in M07 is difficult
 due to the factor of three difference in the size of the beams used.  For
 example, the the brightest source in the Cyg-X region is DR 21.  While M07
-quote a peak flux density per beam of 4.2 Jy/beam for the brightest feature in
-the DR 21 complex (their peak N46) and 17.9 Jy/beam in a 0.19 x 0.14 pc box,
-BGPS measures a peak flux of 17.5 Jy/beam (the beam being roughly 35\arcsec\ in
+quote a peak flux density per beam of 4.2 \jyb for the brightest feature in
+the DR 21 complex (their peak N46) and 17.9 Jy in a 0.19 x 0.14 pc box,
+BGPS measures a peak flux of 17.5 \jyb (the beam being roughly 35\arcsec\ in
 diameter).  Fluxes are best compared using sources that appear compact as
-observed with the beam of the IRAM 30 meter telescope.
+observed with the beam of the IRAM 30 meter telescope. Although we list comparisons
+for non-compact sources, our flux calibratio comparison was made using compact sources.
+The Bolocam and M07 data sets have flux calibration consistent within about
+20\%.
 
@@
 \Table
-{llllll}
+{lllllll}
 {Comparison of \citet{motte07} IRAM measurements to BGPS measurements
 in the Cygnus X region.  The IRAM data has been convolved to the BGPS beam
-to make the flux density measurements.
+to make the flux density measurements. [John - what does `scaled' mean?]
 %Note:  The \citet{motte07} integration box is given in terms of pc. 
@@
 %Source  &   BGPS           &  Motte \\
-%        &   peak mJy/beam  &  mJy in box (see Motte+ Table 1)
-Motte Source &  Motte Table 1   &  Motte scaled  & BGPS  &  Comments \\
-      Number &  integrated flux &  Jy/bm         & Jy/bm &           \\
+%        &   peak m\jyb  &  mJy in box (see Motte+ Table 1)
+Motte Source &  Motte Table 1   &  Motte scaled  & BGPS  & Ratio &  Comments \\
+      Number &  integrated flux &  \jyb          & \jyb  &       &           \\
 }
@@
 {
-3  &    1.59 [0.11x0.09] & 2.61      &  2.30  &  DR 17                               \\
-11 &    0.34 [0.11x0.06] & 0.48      &  0.50  &  West SW of DR21                     \\
-12 &    1.63 [0.11x0.09] & 2.60      &  2.20  &    "                                 \\
-16 &    0.55 [0.12x0.12] & 0.82      &  0.72  &    "                                 \\
-26 &    0.34 [0.20x0.10] & 0.48      &  0.44  &    "                                 \\
-29 &    0.54 [0.25x0.13] & 1.10      &  0.62  &    "                                 \\
-30 &   10.54 [0.15x0.10] &13.5       &  9.80  &  W75(N)                              \\
-44 &    8.43 [0.14x0.11] &14.5       & 12.7   &  DR21 (OH)                           \\
-46 &   17.90 [0.08x0.03] &18.4       & 15.8   &  DR21 f-f, maser (H2O)               \\
-48 &    3.72 [0.17x0.11] & 9.4       &  7.8   &  DR21 (OH)-S                         \\
-51 &    2.37 [0.24x0.03] & 5.5       &  4.1   &  DR21 FIR2                           \\
-53 &    1.60 [0.14x0.09] & 4.3       &  2.7   &  North of DR21  FIR3                 \\
-56 &    0.60 [0.12x0.08] & 0.81      &  0.75  &  SE of DR21 47                       \\
-58 &    2.73 [0.23x0.19] & 2.40      &  1.64  &  IRAS 20375+4109                     \\
-59 &    0.37 [0.12x0.05] & 1.3       &  0.93  &  East of IRAS 20375+4109             \\
-60 &    0.56 [0.16x0.13] & 1.00      &  0.78  &  East of IRAS 20375+4109             \\
-61 &    0.23 [0.12x0.09] & 0.60      &  0.49  &  MSX 81.5168+0.01926                 \\
-62 &    0.50 [0.18x0.12] & 1.23      &  0.80  &  between 63 \& IRAS 20375+4109       \\
-63 &    1.09 [0.08x0.05] & 1.60      &  1.50  &  DR22                                \\
-65 &    0.78 [0.16x0.12] & 1.15      &  1.10  &                                      \\
-66 &    0.25 [0.15x0.06] & 0.63      &  0.76  &                                      \\
-68 &    0.84 [0.10x0.10] & 1.01      &  0.94  &                                      \\
-69 &    1.28 [0.47x0.18] & 1.12      &  1.20  &                                      \\
-72 &    0.54 [0.28x0.13] & 0.58      &  0.47  &                                      \\
+3  &    1.59 [0.11x0.09] & 2.61      &  2.30  & & DR 17                               \\
+11 &    0.34 [0.11x0.06] & 0.48      &  0.50  & & West SW of DR21                     \\
+12 &    1.63 [0.11x0.09] & 2.60      &  2.20  & &   "                                 \\
+16 &    0.55 [0.12x0.12] & 0.82      &  0.72  & &   "                                 \\
+26 &    0.34 [0.20x0.10] & 0.48      &  0.44  & &   "                                 \\
+29 &    0.54 [0.25x0.13] & 1.10      &  0.62  & &   "                                 \\
+30 &   10.54 [0.15x0.10] &13.5       &  9.80  & & W75(N)                              \\
+44 &    8.43 [0.14x0.11] &14.5       & 12.7   & & DR21 (OH)                           \\
+46 &   17.90 [0.08x0.03] &18.4       & 15.8   & & DR21 f-f, maser (H2O)               \\
+48 &    3.72 [0.17x0.11] & 9.4       &  7.8   & & DR21 (OH)-S                         \\
+51 &    2.37 [0.24x0.03] & 5.5       &  4.1   & & DR21 FIR2                           \\
+53 &    1.60 [0.14x0.09] & 4.3       &  2.7   & & North of DR21  FIR3                 \\
+56 &    0.60 [0.12x0.08] & 0.81      &  0.75  & & SE of DR21 47                       \\
+58 &    2.73 [0.23x0.19] & 2.40      &  1.64  & & IRAS 20375+4109                     \\
+59 &    0.37 [0.12x0.05] & 1.3       &  0.93  & & East of IRAS 20375+4109             \\
+60 &    0.56 [0.16x0.13] & 1.00      &  0.78  & & East of IRAS 20375+4109             \\
+61 &    0.23 [0.12x0.09] & 0.60      &  0.49  & & MSX 81.5168+0.01926                 \\
+62 &    0.50 [0.18x0.12] & 1.23      &  0.80  & & between 63 \& IRAS 20375+4109       \\
+63 &    1.09 [0.08x0.05] & 1.60      &  1.50  & & DR22                                \\
+65 &    0.78 [0.16x0.12] & 1.15      &  1.10  & &                                     \\
+66 &    0.25 [0.15x0.06] & 0.63      &  0.76  & &                                     \\
+68 &    0.84 [0.10x0.10] & 1.01      &  0.94  & &                                     \\
+69 &    1.28 [0.47x0.18] & 1.12      &  1.20  & &                                     \\
+72 &    0.54 [0.28x0.13] & 0.58      &  0.47  & &                                     \\
 }
@@
 measurable potential difference) .  Right: Scaling of the relative
-response to the atmosphere for a single detector compared to the array
-median.}{fig:CalibrationCurves}{1.0}
+response to the atmosphere for a single detector compared to the array median.
+Outliers are from noisy scans that are strongly
+downweighted.}{fig:CalibrationCurves}{1.0}
 
@@
 \startdata
-\label{tab:ErrorBudget}
+\label{tab:ErrorBudget} % categorize - which is systematic and which is random
 Pointing error uncertainty & 2\% \\
@@
 We constructed an absolute reference system for the BGPS by observing
-bright quasars and blazars near the Galactic Plane.  The distribution
-of sources over the sky is shown in Figure
+bright quasars and blazars near the Galactic Plane [with small raster maps?].  The distribution
+of pointing sources over the sky is shown in Figure
 \ref{fig:PointingCalibrators} and the list is given in Appendix
@@
 Pointing observations were performed approximately once every two
-hours over the night.   The
+hours over each night.   The
 elevation offsets showed a deviation from zero which was empirically
@@
 
-Because the Galactic Plane appears over much of the sky, the pointing
-model necessarily encompasses a large range of elevation and azimuth.
-Nevertheless, an RMS scatter of $\sim 6\arcsec$ for the model over the
+% Because the Galactic Plane appears over much of the sky, the pointing
+% model necessarily encompasses a large range of elevation and azimuth.
+An RMS scatter of $\sim 6\arcsec$ for the model over the
 entire observed range was achieved, with the scatter somewhat worse at the
-highest ZA.  A separate model was constructed for each epoch, but epoch V was
-used as the primary pointing calibration and is shown in figure
-\ref{fig:PointingModel}.
-
+highest ZA.  
 Further details of the pointing calculation are given in Appendix
@@
 In addition to the model for the pointing center, it is necessary to
-empirically determine actual projected pattern of the array on the
+empirically determine the actual projected pattern of the array on the
 sky, and measure the offset angle between the focal plane and the sky
@@
 
-In our first release, these positions are made using the nominal positions
-without correction for optical distortion.  This results in a slightly blurred
-beam (35.6\farcs instead of 31.2\farcs).  Because this distortion is
-asymmetric, it can also result in a small pointing offset at the field edges
-where only bolometers with large offsets record data.  However, this effect is
-strongly mitigated by the low number of hits at field edges - this data is
-generally flagged out.  The residual offset is within the overall pointing
-model error, but caution should be used when measuring locations at the field
-edges.
-
-A mean focus offset for the secondary is determined once per observing
+[I think this section needs to be checked on more.... I don't know what to say about it yet -Adam]
+In our first data release, the projected positions of the detectors on the sky
+are made using the nominal positions without correction for optical distortion.
+This results in a slightly blurred beam (35\farcs6 instead of 31\farcs2).
+Because this distortion is asymmetric, it can also result in a small pointing
+offset at the field edges where only bolometers with large offsets record data.
+However, this effect is strongly mitigated by the low number of hits at field
+edges - this data is generally flagged out.  The residual offset is within the
+overall pointing model error, but caution should be used when measuring
+locations at the field edges. [ Note - I haven't been able to measure this yet.  It's only marginally
+possible]
+
+A mean focus offset for the secondary was determined once per observing
 run.  An elevation-dependent correction is applied via a
@@
 evidence that more frequent focus checks improve the quality of the
-PSF.
+PSF. [Observers - what checks were done?]
 
@@
 
-Relative alignment between different observations of the same field
-was performed by finding the peak of the cross-correlation between
-images and a pointing master selected from the epoch with the
-best-constrained pointing model for that field. (In almost all cases,
-this was from Epoch V.)  Each observation was initially mapped
-individually, then all observations of a given field were
-cross-correlated with a selected master image of that field. The
-cross-correlation peak was fit with a gaussian and the difference
-between the gaussian peak and the image center was used as the pixel
-offset. 
-%The offsets were recorded and written to the
-%timestreams. 
-Finally, all observations of a field were merged into a single
-timestream with pointing offsets applied to create the field mosaic.
-
-This method of alignment avoids the ambiguities inherent in using
-extracted sources to align fields, as the Bolocam sources are rarely
-point-like.  It further avoids the pointing smearing and loss of peak
-flux density which would result if the the maps were coadded using the
-pointing model alone, where each individual observation would be
-coadded with the 6\arcsec\ RMS uncertainty of the model.  The
-relative alignment using the correlation maps is typically accurate to
- $<1\arcsec$.
+Relative alignment between different observations of the same field was
+performed by finding the peak of the cross-correlation between images and a
+pointing master constructed  from observations taken in the epoch with the
+best-constrained pointing model for that field (in most cases, this was from
+Epoch V, though in some cases Epoch VI was used).  Each observation was
+initially mapped individually, then all observations in the pointing epoch were
+median-combined to create a reference field.  Each observation was then
+cross-correlated with the reference image for that field. The cross-correlation
+peak was fit with a gaussian and the difference between the gaussian peak and
+the image center was used as the pixel offset.  Finally, all observations of a
+field were merged into a single timestream with pointing offsets applied to
+create the field mosaic.
+
+This method of alignment avoids the ambiguities inherent in using extracted
+sources to align fields, as the BGPS sources are rarely point-like.  It further
+avoids the pointing smearing and loss of peak flux density which would result
+if the the maps of individual observations were coadded using the pointing
+model alone, where each individual observation would be coadded with the
+6\arcsec\ RMS uncertainty of the model.  The relative alignment using the
+correlation maps is accurate to $<1\arcsec$ [I think this should be the
+Gaussian width of the cross-correlation fit?] where there is adequate signal.
 
@@
   \caption{Selected images to illustrate the PCA process.  The displays are in
-  Galactic coordinates with a color range from -.1 to 1.0 Jy/beam.
+  Galactic coordinates with a color range from -.1 to 1.0 \jyb.
   {\it Top 4 rows}: a grid of maps of each of the first 20 PCA components displayed at

### 2009-04-18 methods/ms.tex
claudia's corrections

@@
 
-\addtocounter{figure}{0}
+\addtocounter{figure}{-1}
 \addtocounter{subfig}{1}
@@
 
-All of the SCUBA 850 and 450 \mum\ data has been re-processed in a uniform
+All SCUBA 850 and 450 \mum\ data has been re-processed in a uniform
 manner and made publicly available as the SCUBA Legacy Catalog
-\citep[][hereafter SLC]{difrancesco08}.  These maps provide an excellent
-cross-check on the accuracy of the BGPS pointing model.  We have used the same
-cross-correlation procedure as that used to obtain the relative alignment of
-Bolocam observations to compare to the SLC.  A number of concerns might arise
-in comparing the Bolocam to the SCUBA maps, including the differing scan
+\citep[][hereafter SLC]{difrancesco08}.  These maps allow a 
+cross-check of the accuracy of the BGPS pointing model.  We have applied the same
+cross-correlation procedure used to obtain the relative alignment of
+BGPS observations to compare the BGPS images to the SLC.  Concerns might arise
+in comparing the Bolocam to the SCUBA maps, such as the differing scan
 strategies (SCUBA maps were typically taken in jiggle-map mode, which tends to
-remove extended structure) and the often restricted range of positions measured
-within an extended cloud for the SLC.  The cross-correlation technique actually
+remove extended structure).  The cross-correlation technique actually
 mitigates these effects, since it does not require the establishment of a
-single position for an object (which may differ due to the change in wavlength
+single position for an object (which may differ due to the change in wavelength
 between the surveys or due to the observing strategy) but rather makes use of
-all the information available.  The morphological correlation between SCUBA and
+all the information available.  The by-eye morphological comparison between SCUBA and
 BGPS sources is generally excellent with some exceptions, giving a high degree
-of confidence to the comparison and to the results obtained from the pointing
-model.  An example is shown in Figure \ref{fig:SCUBAPointingComparison}.  We
+of confidence to the comparison and to the results obtained from the BGPS pointing
+model [include Di Francesco pointing accuracy].  An example is shown in Figure \ref{fig:SCUBAPointingComparison}.  We
 find that the RMS offset between BGPS and SLC positions within a $3\arcdeg
@@
 Right: The distribution of the pointing calibration sources across the
-local sky in Hawaii during the July 2007 epoch when the pointing model
-was constructed.  Note the good sampling built up over the range of
-sky observed in the Survey.}{fig:PointingCalibrators}{1.0}
+local sky in Hawaii during July 2007 (epoch V) when the pointing model
+was constructed.  }{fig:PointingCalibrators}{1.0}
 % -----------------------------------------------------------------------------
@@
   were included, and the final RMS was 5.77\arcsec in altitude and 3.21\arcsec
-  in azimuth, or a total RMS offset of 6.6\arcsec]
+  in azimuth, or a total RMS offset of 6.6\arcsec.  No systematic offset with
+  altitude was found.]
 {\label{fig:PointingModel-a}\includegraphics[scale=0.9]{paper_models_0707}}\\
 
-  \subfigure[The residuals of the pointing model.  Note the Gaussian
-distribution. ($\sigma = 5.94,2.92$)]
+  \subfigure[The residuals of the pointing model.  The Gaussian fits have
+  $\sigma = 5.94,2.92$ in altitude offset and azimuth offset respectively.]
 {\label{fig:PointingModel-b}\includegraphics[scale=0.9]{paper_gaussian_0707}}
@@
 algorithm is the estimation and removal of a signal due to fluctuating
-atmosphere emission which is $>\sim$100's of times stronger than the typical
+atmospheric emission which is $>\sim$100's of times stronger than the typical
 sources in our maps.  We implement an iterative procedure for
@@
 noise) without a detailed physical model, we use principal component
-analysis (PCA) as given in \citet{laurent05}.
+analysis (PCA) as given in \citet{laurent05}. [more words]
+
+The mean across each scan is forced to zero by subtracting a polynomial
+fit to the scan after iteratively rejecting astrophysical sources.  This
+process helps reduce negative bowls in the scan direction near bright sources.
 
@@
 
-\item Pickup from the 60 Hz AC power.  This appears as narrow lines in the PSD
+\item Pickup from the 60 Hz AC power.  This appears as narrow lines in the power spectral density (PSD)
     of the data.  The second harmonic of 60 Hz is aliased via beating against
@@
 response (in Jy) at that time.  An example of this is shown in Figure
-\ref{fig:Flagger}.  With practice, anomalies such as the glitch shown
-can be detected and manually and iteractively flagged out.
+\ref{fig:Flagger}.  Anomalies such as the glitch shown
+can be detected and manually and interactively flagged out.
 
 An automated flagger was also created that flags out outlier data on a
-per-pixel basis.  In order to make a robust measurement of the
+per-map-pixel basis.  In order to make a robust measurement of the
 variance of the fluxes assigned to each pixel, we used the median
@@
   Left: The glitch apparent at middle right (bolometer 98, around 6.2s) is the
-  same one whose time series is shown in Figure \ref{fig:Flagger}b.  Because of
+  same one whose time series is shown in (\em{b}).  Because of
   the PCA subtraction, the effect of the glitch also propagates over the other
@@
 data in the \lon=111 field.  Glitches below the detection threshold may
-contribute to the overall noise.}{fig:GlitchDistribution}{1.0}
+contribute to the overall noise.  Each data point represents .1s of integration
+time.}{fig:GlitchDistribution}{1.0}
 
@@
 
-\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution
-on the iterative process can be seen in its effect on the
-residuals. From left to right: map, noise, model. Top to
-bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
-7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which
-has the result of leaving no flux in the residual at the location of
-Sgr B2, and does not ``dig a hole'' in the residual map, as the
-7.2\arcsec\ kernel does.  The 7.2\arcsec\ kernel also lacks the
-noise-rejection features of the larger kernels, as can be seen in the
-last panel.}{fig:Deconvolution}{1.0}
+\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution on the
+iterative process can be seen in its effect on the residuals in these images of
+Sgr B2, all displayed at the same scale. From left to right: map, residual,
+model. Top to bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
+7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which has the
+result of leaving no flux in the residual at the location of Sgr B2, and does
+not ``dig a hole'' in the residual map, as the 7.2\arcsec\ kernel does.  The
+7.2\arcsec\ kernel also lacks the noise-rejection features of the larger
+kernels, as can be seen in the last panel.}{fig:Deconvolution}{1.0}
 
@@
 estimating the systematic error resulting from imperfect subtraction of bright
-sources.  The imperfect subtraction results in ``ghosts'' of the bright sources
-in the error maps $E$.
-
-Residual maps are produced for each map from the residuals after
-removing the astrophysical signal model and the PCA atmosphere model.  These
-maps are useful for diagnosing the effect of the iterative process on bright
-sources and as a method of obtaining an
-estimate of the noise.
+sources.  The imperfect subtraction results in positive ``ghosts'' of the
+bright sources in the error maps $E$.  Smoothed residual maps also provide the
+best means of determining the pixel-to-pixel error near bright sources.  Near
+the scan edges, 1/sqrt(weightmap) provides a better estimate of the local noise.
+
+% Residual maps are produced for each map from the residuals after
+% removing the astrophysical signal model and the PCA atmosphere model.  These
+% maps are useful for diagnosing the effect of the iterative process on bright
+% sources and as a method of obtaining an
+% estimate of the noise.
 
@@
 
+[since we don't do any science in this paper, should this be held off for
+use in Erik's paper?]
 The depth can be converted into an
@@
 \Figure{survey_depth}{The depth of the BGPS in the first quadrant as a
-function of Galactic longitude.  Black is the standard deviation of
-$0.9\arcdeg \times 0.9\arcdeg$ degree blocks centered on $b=0$ and the
-longitude indicated for the error maps $E$; red is similar, but the
-estimator is median(1/sqrt(weight map).}{fig:NoiseVsLongitude}{1.0}
-
-\section{Effect of the Analysis on Photometry}
+function of Galactic longitude.  The black histogram plots the standard deviation as a 
+function of longitude binned in $0.9\arcdeg \times 0.9\arcdeg$ degree blocks
+(to avoid high-noise regions at scan edges) centered on $b=0$ for the error
+maps $E$.  Red is similar, but the estimator is median(1/sqrt(weight
+map).}{fig:NoiseVsLongitude}{1.0}
+
+\section{Effects of the Data Reduction Procedures on Photometry}
 \label{sec:Photometry}
@@
 understanding of the spatial filtering imposed by the observing
-strategy and the cleaning and mapping of the data.  Quite apart from
-the issues discussed in this section are the issues of identifying
-sources with complex morphology and defining the regions over which to
-do the aperture.  This is discussed in \citet{rosolowsky09}.  Here we
-merely deal with the limitations on performing photometry imposed by
-the data itself.
-
-The Bolocam maps produced are the convolution of the (nearly Gaussian)
-primary beam $G(\xad)$, together with an effective high-pass
+strategy and the cleaning and mapping of the data.  
+The additional
+complexities of defining ``sources'' in complicated regions are discussed in
+\citet{rosolowsky09}.  Here we restrict our discussion to the limitations
+on performing photometry imposed by the data reduction.
+
+The BGPS maps are the convolution of the (nearly Gaussian)
+primary beam $G(\xad)$ and an effective high-pass
 spatial filter $F(\xad)$ (figure \ref{fig:PCA_filter}),
@@
 To assess the effect of the mapping algorithm, we performed a series
-of simulations.
-
-Figure \ref{fig:PCA_Filter}a shows the fraction of flux recovered in
-the map as a function of source size for a range of different PCA
-components subtracted in the cleaning.  These measurements were
-produced by inserting simulated gaussian sources at a range of peak
-flux densities and sizes spread out through the map and summing the
-flux in an ellipse on the final cleaned map. Real data with the
-astrophysical source model removed were used as the background.
+of simulations.  Gaussian sources with a range of peak flux densities and sizes
+were inserted on top of a background consisting of real BGPS data with the
+astrophysical source model removed.  The recovered fluxes were measured in
+ellipses that included single well-separated sources.  Figure
+\ref{fig:PCA_Filter}a shows the fraction of flux recovered in the map as a
+function of source size for a range of different PCA components subtracted in
+the cleaning.
 
@@
 fractional flux recovered as a function of source size for
-well-separated Gaussian sources with the FWHM as indicated.
+well-separated Gaussian sources with FWHM as indicated.
 \emph{Left}: 3 (blue), 7 (green), 10 (yellow), 13 (orange), 16 (red), 21
@@
 show bumps because atmospheric noise is still present at large scales.
-The $>$100\% recovery for sources smaller than the deconvolution kernel is a
+The $>$100\% recovery for simulated sources smaller than the deconvolution kernel is a
 side-effect; since the deconvolution kernel is smaller than the beam, no real
-source should ever be smaller than the kernel.
+astrophysical source should ever be smaller than the kernel.
 \emph{Right}:
@@
 
-\Figure{aper_phot_hpf_beam}{The effect of performing aperture
+\Figure{aper_phot_hpf_beam}{[James - figure needs clarification] The effect of performing aperture
 photometry on a point source of unit flux observed with the effective
@@
 
-All processed maps are made available through
+All processed maps are available through
 IPAC\footnote{http://irsa.ipac.caltech.edu/Missions/bolocam.html}.
 IPAC provides a cutout service for the images as well as a searchable
-version of the catalog provided in \citep{rosolowsky09}.  The full
+version of the catalog provided in \citet{rosolowsky09}.  The full
 release includes
@@
 % don't release smoothmaps? \item The MAP smoothed by the Bolocam PSF, which is helpful in bringing out extended structure (SMOOTHMAP)
-\item The deconvolved MAP (DECONVMAP)
+\item The deconvolved MAP (MODEL)
 \item Maps of integration time per pixel (NHITSMAP)
-\item Maps of noise per pixel (NOISEMAP)
-\item Maps of the mask obtained for various regions from the cataloging algorithm (MASKMAP)
+\item Maps of residual noise per pixel (RESIDUAL)
+\item Maps of inverse variance per pixel (WEIGHTMAP)
+\item Maps of the mask obtained for various regions from the cataloging algorithm (MASKMAP) \citep{rosolowsky09}
 \end{enumerate}
@@
 \label{sec:Analysis}
+
+\bf{Claudia suggested that this section be removed or changed to an `advertisement' section
+where we indicate what follow-up work needs to be done - seems reasonable, since this
+is mostly junk pilfered from the `letter'.  However, we need to keep the last sentence around...}
 

### 2009-04-20 methods/ms.tex
added John's revision of the cygnus sectoin

@@
 \label{sec:motte}
-\bf{Claudia's comments:}
-In general, this section could use some reorganizing such that it sets out why
-this comparison field was chosen first (best available data?), describes any
-relevant differences in the datasets (eg filter bandpasses, CO possibly in
-MAMBO filter), describes how the comparison was done, and then represents the
-results.  It seems out of order at the moment.  A reference for CO
-contamination causing detectable contamination (at 850um, not 1mm) is
-Hatchell, J., \& Dunham, M.~M.\ 2009, arXiv:0904.1163
-
-Comparison of the BGPS flux density calibration
-with SCUBA 850 \mum\ results is complicated by the unknown effect
-of the dust spectral index.  However, there are several large-area
-surveys with the MAMBO instrument at 1.2 mm with which we can compare.
-Figure \ref{fig:CygnusComparison} shows the comparison of fluxes
-extracted from our map in the Cygnus Arm with those of
-\citet{motte07} (M07).
-
-The figures of the Cygnus-X region presented by \citet{motte07}, obtained at a
-central wavelength of 1.2 mm using the 30 meter IRAM telescope, appear nearly
-identical to the 1.1 mm Bolocam images.  The MAMBO filter is wider than the
-Bolocam filter and includes the CO 2-1 line.  Nevertheless, there is excellent
-qualitative agreement between the structure revealed by the two data sets on size
-scales to which both are sensitive.
-
-[John - may want to remove N46 and other extended sources from comparison.  This 
-paragraph needs cleanup]
-Direct comparison with the fluxes listed in M07 is difficult
-due to the factor of three difference in the size of the beams used.  For
-example, the the brightest source in the Cyg-X region is DR 21.  While M07
-quote a peak flux density per beam of 4.2 \jyb for the brightest feature in
-the DR 21 complex (their peak N46) and 17.9 Jy in a 0.19 x 0.14 pc box,
-BGPS measures a peak flux of 17.5 \jyb (the beam being roughly 35\arcsec\ in
-diameter).  Fluxes are best compared using sources that appear compact as
-observed with the beam of the IRAM 30 meter telescope. Although we list comparisons
-for non-compact sources, our flux calibratio comparison was made using compact sources.
-The Bolocam and M07 data sets have flux calibration consistent within about
-20\%.
+
+Comparison of the BGPS flux density calibration with SCUBA 850 \mum\
+or ATLASGAL 870 \mum\ results is complicated by the poorly determined
+variations in the dust spectral index produced by emissivity variations.
+However, there are several large-area surveys with the IRAM 30 meter
+telescope at 1.2 mm which can be used for comparison with BGPS to
+check overall image quality, pointing, and flux calibration.  The study
+of the Cygnus-X region by \citet{motte07} presents one of the largest
+fields in the Galactic plane that has been mapped with MABO which overlaps
+with the Bolocam survey fields.
+
+The Motte Cygnus-X study used both the 37 element MAMBO and 117 channel
+MAMBO-2 instrument on the IRAM 30-meter diameter telescope on Pico Veleta
+in Spain.   The FWHM beam size for the observations was 11\arcsec .
+The effective passband of the images presented by Motte et al.
+is about 70 GHz centered at 240 GHz and thus includes the bright
+J = 2--1 CO transition.
+
+The structure of the emission in the Cygnus-X region presented by
+\citet{motte07} appear nearly identical to the 1.1 mm Bolocam images
+of the same field despite the inclusion of the CO line, the slightly
+longer (by about 10\%) longer effective wavelength, and different beam
+sizes.   The peak positions also agree to within the errors of the
+BGPS survey discussed in this paper.
+
+Direct comparison with the fluxes listed in Motte et al. requires
+consideration of the factor of three difference in the size of the beams.
+For example, the the brightest source in the Cyg-X region is DR 21.
+While Motte et al. quote a peak flux density per beam of 4.2 \jyb for
+the brightest feature in the DR 21 complex (their peak N46) and 17.9 Jy
+in a $\sim$ 17\arcsec\ by 23\arcsec box (0.19 x 0.14 pc at an assumed
+distance of 1.7 kpc; see Motte et al. Table 1 in their Appendix).
+BGPS measures a peak flux of 17.5 \jyb in an effective beam roughly
+35\arcsec\ in diameter, indicating that the relative calibration is
+similar on the brightest source in common to both surveys.   However,
+DR 21 is an extended source.  Fluxes are best compared using sources
+that appear compact as observed with the beam of the IRAM 30 meter
+telescope.
 
@@
 kernel that generates an approximately 35\arcsec\ beam, and compared the
-measured fluxes with those from the BGPS.  The results are shown in Figure
-\ref{fig:CygnusComparison}.
+measured fluxes with those from the BGPS.  Additionally, the data values
+in Motte et al. are in units of Jankys per pixel, with each pixel subtending
+a 4\arcsec\ by 4\arcsec\ area on the sky.  In contrast, the data values
+in BGPS are in units of Janskys per beam where the beam is 31\arcsec\
+in diameter.   The conversion of units required multiplication of the
+convolved images by factor of 8.
+
+The Motte et al. images were convolved with IRAF task
+GAUSS using a 3.5 pixel convolution kernel to synthesize maps with an
+effective FWHM beam diameter of 35\arcsec ;  the BGPS maps have effective
+beam diameter 4\arcsec\ larger than the CSO beam diameter of 31\arcsec\
+because of the smearing effects of optical distortion at the edges of the
+Bolocam array.  This distortion has not been removed from the Version 1.0
+images.  The Bolocam flux calibration is based on the measurement of
+primary calibrators using the central pixels of the array which are not
+effected by distortion.   The results are shown  in Figure
+\ref{fig:CygnusComparison} and tabulated in Table 2.  This figure and
+the table shows that BGPS and \citet{motte07} clumps have fluxes
+consistent within about 20\% after convolution to a 35\arcsec\ beam and
+scaling to Jy/beam.
+
+The average Motte et al. fluxes are larger than the BGPS fluxes by a factor
+of 1.23 despite the longer wavelength.  Contamination by the bright
+CO J = 2-1 line may account for a few percent of the excess
+detected flux by MAMBO.    For a dust spectral index of $-3.5$, the
+MAMBO measurements should have detected a flux that is about 35\% lower
+than what was seen by BGPS.    If this is a typical spectral index for
+the sample of clumps, then the Motte et al. flux calibration may be as
+much as 45\% higher than the BGPS fluxes.
 
@@
 {lllllll}
-{Comparison of \citet{motte07} IRAM measurements to BGPS measurements
-in the Cygnus X region.  The IRAM data has been convolved to the BGPS beam
-to make the flux density measurements. [John - what does `scaled' mean?]
-%Note:  The \citet{motte07} integration box is given in terms of pc. 
-%The assumed distance must be about 1.7 kpc \citep{schneider2006}    % no, it's 1.7kpc stated explicitly
+{Comparison of \citet{motte07} IRAM and BGPS measurements
+in the Cygnus X region.  The IRAM data has been convolved
+to the BGPS beam and scaled so the units are in Jy/beam.
 }
@@
 }
+% 7
+\Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
+in the same aperture from the \citet{motte07} MAMBO map and the Bolocam map of
+this paper. }{fig:CygnusComparison}{1.0}
 

### 2009-04-20 methods/ms.tex
some more fixes

@@
 contiguous survey of the galactic plane.  The Bolocam instrument has been
-used on the 10.4-m Caltech Submiliimeter Observatory (CSO) to map nearby large
+used on the 10.4-m Caltech Submillimeter Observatory (CSO) to map nearby large
 molecular clouds at 1.1 mm and identify hundreds of cores \citep{enoch06}.
@@
 passband rejects $>90\%$ of the $^{12}$CO flux, leaving our continuum
-measurements largely uncontaminated.  SO and CH$_3$OH lines are probably the
-dominant contributors to line flux in the passband.  \citet{nummelin1998} found
+measurements largely uncontaminated.  SO$_2$ and CH$_3$OH lines are likely 
+strong contributors to line flux in the passband.  \citet{nummelin1998} found
 that 22\% of the flux density in one pointing towards Sgr B2 was from lines,
@@
 and ($6\to5$) (245 and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267
-GHz).  A follow-up project will attempt to determine the contribution of lines
-to the BGPS flux density measurements.}
+GHz).  } 
+% A follow-up project will attempt to determine the contribution of lines
+% to the BGPS flux density measurements.}
 {fig:Bandpass}{1.0}
@@
 about 200\arcsec\ (half the array field of view, see figure
-\ref{fig:PCA_filter}).  An indicative analysis of the spatial filter function
+\ref{fig:PCA_Filter}).  An indicative analysis of the spatial filter function
 of the iterative mapping scheme is given in \citet{enoch06}, and we present a detailed analysis
-of the filter function in our survey in figure \ref{fig:PCA_filter}.  The data were
+of the filter function in our survey in figure \ref{fig:PCA_Filter}.  The data were
 sampled onto a uniform 7\farcs2 grid.  Flux density calibrations were performed
@@
 primary beam $G(\xad)$ and an effective high-pass
-spatial filter $F(\xad)$ (figure \ref{fig:PCA_filter}),
+spatial filter $F(\xad)$ (figure \ref{fig:PCA_Filter}),
 \[
@@
 
-\bf{Claudia suggested that this section be removed or changed to an `advertisement' section
+{\bf Claudia suggested that this section be removed or changed to an `advertisement' section
 where we indicate what follow-up work needs to be done - seems reasonable, since this
 is mostly junk pilfered from the `letter'.  However, we need to keep the last sentence around...}
+
+TEST: \ref{fig:BGPSMontage}
 

### 2009-04-20 methods/ms.tex
some more fixes

@@
 \newcommand{\bgpsarea}{150}
-\newcommand{\bcamfwhm}{35.6\arcsec}
+\newcommand{\bcamfwhm}{31.2\arcsec}
 \newcommand{\ncores}{7628}
@@
 \bgpsdepthhigh\ m\jyb RMS.  We present maps of 97 contiguous square degrees from
-$\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$35\arcsec, as
+$\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$\bcamfwhm, as
 well as regions in IC1396, $\lon=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
@@
 
-The Bolocam observations are sensitive to structure between 35\arcsec\ and
+The Bolocam observations are sensitive to structure between \bcamfwhm\ and
 about 200\arcsec\ (half the array field of view, see figure
@@
 Gaussian profile.  The beam area is that averaged over all detectors,
-and is $1.71\times10^{-6}$ steradians ($35.6$\farcs).  This
+and is $1.71\times10^{-6}$ steradians (\bcamfwhm).  This
 allows conversion of the maps, calibrated in Jy beam$^{-1}$, into
@@
 BGPS measures a peak flux of 17.5 \jyb in an effective beam roughly
-35\arcsec\ in diameter, indicating that the relative calibration is
+\bcamfwhm\ in diameter, indicating that the relative calibration is
 similar on the brightest source in common to both surveys.   However,
@@
 ftp://cdsarc.u-strasbg.fr/pub/cats/J/A+A/476/1243/fits/}} with a Gaussian
-kernel that generates an approximately 35\arcsec\ beam, and compared the
+kernel that generates an approximately \bcamfwhm\ beam, and compared the
 measured fluxes with those from the BGPS.  Additionally, the data values
@@
 GAUSS using a 3.5 pixel convolution kernel to synthesize maps with an
-effective FWHM beam diameter of 35\arcsec ;  the BGPS maps have effective
+effective FWHM beam diameter of \bcamfwhm ;  the BGPS maps have effective
 beam diameter 4\arcsec\ larger than the CSO beam diameter of 31\arcsec\
@@
 the table shows that BGPS and \citet{motte07} clumps have fluxes
-consistent within about 20\% after convolution to a 35\arcsec\ beam and
+consistent within about 20\% after convolution to a \bcamfwhm\ beam and
 scaling to Jy/beam.
@@
 the flux recovery is very close to 1 at the beam size
-(35\arcsec)}{fig:PCA_Filter}{1.0}
+(\bcamfwhm)}{fig:PCA_Filter}{1.0}
 

### 2010-02-24 bgps_pipeline/methods/figures.tex
Creating r341: BGPS Pipeline V1.0

--- 2009-04-20 methods/ms.tex
@@
-% Figure list
-% 1) fig:Coverage
-% 2) fig:BGPSMontage
-% 3) fig:Bandpass
-% 4) fig:Array
-% 5) fig:CalibrationCurves
-% 6) fig:Flatfield
-% 7) fig:CygnusComparison
-% 8) fig:PointingCalibrators
-% 9) fig:PointingModel
-% 10) fig:SCUBAPointingComparison
-% 11) fig:IterativeMapping
-% 12) fig:Flagging
-% 13) fig:GlitchDistribution
-% 14) fig:PCA_Graphical
-% 15) fig:Deconvolution
-% 16) fig:Noise
-% 17) fig:NoiseVsLongitude
-% 18) fig:PCA_Filter
-% 19) fig:AperturePhotometry
-% 19) fig:sampleimages
-
-% Major Sections
-% sec:Introduction
-% sec:Observations
-% sec:FluxCalibration
-% sec:Astrometry
-% sec:Mapping
-% sec:Noise
-% sec:Photometry
-% sec:FinalMaps
-% sec:Analysis
-
-% calibration
-% you should look @ calibration/plot_dcfluxes.pro in my publish/ directory, and /usb/scratch1/planets/planet_dcfluxes.txt is the actual raw data
-%/home/milkyway/student/ginsbura/bgps_pipeline/calibration/plot_dcfluxes.pro?
-
-% glitches
-% I can't send you raw data for the glitches, but the best way I can think of dealing with them is taking one of my postiter.sav files in some directory and grabbing ac_bolos[where(flags)]......
-except that include hand-flagged stuff too
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                       % 
-%       Bolocam Galactic Plane Survey Description       %
-%                                                       % 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\documentclass[12pt,preprint]{aastex}
-%\documentclass{emulateapj}
-
-\usepackage{rotating}
-\usepackage{subfigure}
-\usepackage{datetime}
-\usepackage{fmtcount}
-
-\newtimeformat{edttime}{\twodigit{\THEHOUR}:\twodigit{\THEMINUTE}~EDT}
-\settimeformat{edttime}
-\newdateformat{eurodate}{\dayofweekname{\THEDAY}{\THEMONTH}{\THEYEAR} \THEDAY \monthname[\THEMONTH] \THEYEAR}
-
-\citestyle{aa}
-
-\bibliographystyle{apj_w_etal}
-
-\newcommand{\vect}[1]{\mathbf{#1}}
-\newcommand{\xad}{\vect{x}}
-
-\newcommand{\ammonia}{\mbox{{\rm NH}$_3$}}
-\newcommand{\form}{H$_2$CO}
-\newcommand{\td}{\mbox{$T_D$}}
-\newcommand{\jj}[2]{\mbox{$J = #1\rightarrow#2$}}
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand{\myemail}{{\tt jaguirre@sas.upenn.edu}}
-\newcommand{\lsim}{{_{<}\atop^{\sim}}}
-\newcommand{\gsim}{{_{>}\atop^{\sim}}}
-\newcommand{\etal}{{et al.\/}}
-\newcommand{\ie}{{\em ie.\/}}
-\newcommand{\cmq}{cm{$^{-3}$}}
-\newcommand{\per}{$^{\rm{-1}}$}
-\newcommand{\tc}{{$\theta^1$~Orionis~C}}
-%\newcommand{\msol}{M{$_{\odot}$}}
-\def\msol{\ifmmode {\>M_\odot}\else {$M_\odot$}\fi}
-\newcommand{\lsol}{L{$_{\odot}$}}
-\newcommand{\kms}{km~s{$^{-1}$}}
-\newcommand{\hii}{H~{\sc ii}}
-\newcommand{\Hii}{H~{\sc ii}}
-\newcommand{\Ha}{\mbox{H$\alpha$}}
-\newcommand{\sii}{S~{\sc ii}}
-\newcommand{\Feii}{Fe~{\sc ii}}
-\newcommand{\oi}{O~{\sc i}}
-\newcommand{\nii}{N~{\sc ii}}
-\newcommand{\oiii}{O~{\sc iii}}
-\newcommand{\mgii}{Mg~{\sc ii}}
-\newcommand{\tco}{{$^{13}$CO}}
-\newcommand{\CO}{{$^{12}$CO}}
-\newcommand{\Tco}{{$^{12}$CO}}
-\newcommand{\co}{C{$^{18}$O}}
-\newcommand{\Lsol}{L$_{\odot}$}
-\newcommand{\Msol}{M$_{\odot}$}
-%\newcommand{\C18o}{C$^{18}$O($1\rightarrow 0$)}
-\newcommand{\Check}{{\bf ???}}
-\newcommand{\mum}{\ensuremath{\mu \mathrm{m}}}
-\newcommand{\flux}{flux density}
-\newcommand{\solar}{\ensuremath{\odot}}
-\newcommand{\lon}{\ensuremath{l}}
-\newcommand\jyb{Jy~beam$^{-1}$}
-
-\newcommand{\epsi}{\varepsilon}
-
-% -----------------------------------------------------------------------------
-% BGPS specific definitions
-\def\bgps{BGPS}
-\newcommand{\bgpsarea}{150}
-\newcommand{\bcamfwhm}{31.2\arcsec}
-\newcommand{\ncores}{7628}
-\newcommand{\bgpsdepthlow}{20}
-\newcommand{\bgpsdepthhigh}{50}
-% -----------------------------------------------------------------------------
-% Missions
-\def\spitzer{{\em Spitzer}}
-% -----------------------------------------------------------------------------
-
-\newcommand{\TBD}{{\bf TBD}}
-
-\def\Figure#1#2#3#4{
-\begin{figure}[htb]
-\epsscale{#4}
-\plotone{#1}
-\caption{#2}
-\label{#3}
-\end{figure}
-}
-
-\def\FigureTwo#1#2#3#4#5{
-\begin{figure}[htb]
-\epsscale{#5}
-\plottwo{#1}{#2}
-\caption{#3}
-\label{#4}
-\end{figure}
-}
-
-\def\Table#1#2#3#4#5{
-\begin{deluxetable}{#1}
-\tablewidth{0pt}
-\tablecaption{#2}
-\tablehead{#3}
-\startdata
-\label{#4}
-#5
-\enddata
-\end{deluxetable}
-}
-
-\newcommand{\penn}{1}
-\newcommand{\casa}{2}
-\newcommand{\utexas}{3}
-\newcommand{\virginia}{4}
-\newcommand{\ucf}{5}
-\newcommand{\wisc}{6}
-\newcommand{\jpl}{7}
-\newcommand{\ubc}{8}
-\newcommand{\hawaiihilo}{9}
-\newcommand{\hawaiimain}{10}
-\newcommand{\arizona}{11}
-
-	% End definitions
-
-\slugcomment{DRAFT: \currenttime\ \eurodate\today}
-
-\shorttitle{BGPS}
-\shortauthors{Aguirre et al.}
-
-\begin{document}
-
-\title{The Bolocam Galactic Plane Survey: Survey Description and Data
-Reduction}
-
-%\newpage
-%\pagebreak
-%
-%\tableofcontents
-%
-%\newpage
-%\pagebreak
-%
-
-\author{James Aguirre\altaffilmark{\penn},
-        Adam Ginsburg\altaffilmark{\casa},
-        Miranda K. Nordhaus\altaffilmark{\utexas},
-	Meredith Drosback\altaffilmark{\virginia},
-        John Bally\altaffilmark{\casa}, 
-	Cara Battersby\altaffilmark{\casa},
-	Eric Todd Bradley\altaffilmark{\ucf},
-%        Richard Chamberlin\altaffilmark{\cso},
-	Claudia Cyganowski\altaffilmark{\wisc},
-	Darren Dowell\altaffilmark{\jpl}
-	Neal J. Evans II\altaffilmark{\utexas},
-        Jason Glenn\altaffilmark{\casa},
-        Paul Harvey\altaffilmark{\utexas,\casa},
-        Erik Rosolowsky\altaffilmark{\ubc},
-%        Wayne Schlingman\altaffilmark{9},
-%        Yancy Shirley\altaffilmark{9},
-        Guy S. Stringfellow\altaffilmark{\casa},
-        Josh Walawender\altaffilmark{\hawaiihilo}, and 
-        Jonathan Williams\altaffilmark{\hawaiimain}
-}
-
-\affil{{$^\penn$}{\it{Department of Physics and Astronomy, University of
-      Pennsylvania, Philadelphia, PA }}}
-\email{\myemail}
-
-\affil{{$^\casa$}{\it{CASA, University of Colorado, CB 389-UCB, Boulder, CO 80309}}}
-%, \email{John.Bally@casa.colorado.edu}
-%      \email{adam.ginsburg@colorado.edu}
-%      \email{cara.battersby@colorado.edu}
-%      \email{Jason.Glenn@colorado.edu} \email{pmh@astro.as.utexas.edu}
-%      \email{Guy.Stringfellow@colorado.edu} }}
-
-\affil{{$^\utexas$}{\it{Department of Astronomy, University of Texas,
-      1 University Station C1400, Austin, TX 78712}}}
-%,            
-%      \email{nje@astro.utexas.edu},
-%      \email{nordhaus@astro.utexas.edu}}}
-
-\affil{{$^\virginia$}{\it{Department of Astronomy, University of
-Virginia, P.O. Box 400325, Charlottesville, VA 22904}}}
-%, 
-%    \email{meredith.drosback@origins.colorado.edu}}}
-
-\affil{{$^\ucf$}{\it{Department of Physics, University of Central
-Florida}}}
-%,           
-%                                              } ,   \email{tbradley@physics.ucf.edu}} }
-
-\affil{{$^\wisc$}{\it{Department of Astronomy, University of Wisconsin,
-       Madison, WI 53706}}}
-% , \email{cyganow@astro.wisc.edu}}}
-
-\affil{{$^\jpl$}{\it{Jet Propulsion Laboratory, California Institute
-   of Technology, 4800 Oak Grove Dr., Pasadena, CA 91104}}}
-%,
-%       \email{cdd@submm.caltech.edu}}}
-
-\affil{{$^{\ubc}$}{\it{Department of Physics and Astronomy, University
-       of British Columbia, Okanagan }}}
-% ,               \email{erik.rosolowsky@ubc.ca}}}
-
-%\affil{{$^{\arizona}$}{\it{ Steward Observatory, University of
-%Arizona, 933 North Cherry Avenue, Tucson, AZ 85721 }}}
-%%\email{yshirley@as.arizona.edu} \email{wschlingman@as.arizona.edu}}}
-
-\affil{{$^{\hawaiihilo}$}{\it{Institute for Astronomy, University of
-        Hawaii,640 N. Aohoku Pl., Hilo, HI 96720}}}
-%\email{joshw@ifa.hawaii.edu} }}
-
-\affil{{$^{\hawaiimain}$}{\it{Institute for Astronomy, University of
-Hawaii,680 Woodlawn Drive, Honolulu, HI 96822}}}
-%\email{jpw@ifa.hawaii.edu}}
-
-%\altaffiltext{\penn}{University of Pennsylvania, Philadelphia, PA 19104}
-%%Jansky Fellow, National Radio Astronomy Observatory} 
-%\altaffiltext{\casa}{CASA, University of Colorado, CB 389, Boulder, CO 80309}
-%\altaffiltext{\utexas}{Department of Astronomy, University of Texas, 
-%       1 University Station C1400, Austin, TX 78712}
-%\altaffiltext{4}{Caltech Submillimeter Observatory, Hilo, HI}
-%\altaffiltext{5}{Institute for Astronomy (IfA), University of Hawaii
-%640 N. Aohoku Pl., Hilo, HI 96720}
-%
-\begin{abstract}
-
-We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm continuum survey
-of \bgpsarea\ square degrees of the Galactic Plane with 130 in the 1st quadrant,
-31 in the 2nd, and 6 in the 3rd.  The BGPS represents
-the first large area, systematic survey of the Northern Galactic Plane in the
-millimeter continuum without pre-selected targets.  The survey has detected
-\ncores\ clumps to a limiting non-uniform 1-$\sigma$ noise level in the range \bgpsdepthlow\ and
-\bgpsdepthhigh\ m\jyb RMS.  We present maps of 97 contiguous square degrees from
-$\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$\bcamfwhm, as
-well as regions in IC1396, $\lon=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
-striking feature of the maps is the filamentary structure of millimeter emission
-throughout the Galaxy.
-
-This paper details the survey observations and methods.  We treat carefully the
-determination of pointing and flux density calibration errors and compare our
-results to the literature.  Data processing algorithms that separate
-astronomical signals from time-variable atmospheric flux density in the data
-time-stream are discussed.  The algorithms reproduce the structure of the
-astronomical sky on a \emph{limited range of angular scales} and produce artifacts in
-the vicinity of bright sources. Specifically, extended emission smooth on
-scales larger than about 3\arcmin\ is not fully recovered in the images.  The
-spatial frequency response function of the Bolocam Galactic Plane Survey is
-discussed.
-
-This paper serves as a companion and guide to the public data release through
-NASA's Infrared Processing and Analysis Center (IPAC).  These images represent
-an important finder chart for future observations with ALMA and a
-long-wavelength spectral band complementary to ATLASGAL and imminent
-submillimeter surveys with SCUBA-2 and Herschel-SPIRE.
-
-\end{abstract}
-
-\keywords{
-ISM: - molecular clouds --
-stars: formation -- high mass
-millimeter continuum
-}
-
-%\include{bgps_methods_introduction}
-
-\section{Introduction}
-\label{sec:Introduction}
-
-Millimeter-wavelength continuum surveys of the Galactic plane provide the most
-efficient way to find molecular clumps that are the likely sites of formation
-for massive stars and star clusters. The development of detector arrays have
-made blind surveys of large areas possible.  Such surveys bypass the need for
-selection based on the presence of embedded stars or star clusters, infrared
-sources, masers, or radio continuum emission. In particular, they can locate
-molecular clumps before stars form, providing vital information on the initial
-conditions of star formation.  These surveys can also provide valuable
-constraints on the physical properties of the clumps, especially masses and
-mean densities, in conjunction with distance information.
-
-Galaxy-wide surveys are essential for measuring the impacts of the
-environment on clump properties and star formation activity.
-Do clump properties vary with Galactocentric distance, or
-with location with respect to spiral arms?  Do they depend on the
-level of nearby star formation activity?
-Answering these questions in our Galaxy will provide the
-essential ``ground truth'' required for the analysis of distant
-galaxies where where individual clouds and clumps are not resolved and
-only galaxy-wide average quantities can be measured.
-
-Surveys of the galaxy in CO line emission \citep{dame01,jackson06} have
-identified the locations of large molecular clouds and traced
-the transition from atomic to molecular gas as distance from the
-center of the galaxy decreases. Together with kinematic distances
-\citep[e.g.][]{RotationCurve} and, more recently, accurate distances
-from VLBI \citep{reid09}, these surveys have begun to
-reveal the spiral structure of the Milky Way. As this picture comes into
-sharper focus, we can begin to address the old question of the relationship
-between spiral density waves and star formation.
-
-To pursue this question, we need tracers of higher density material.
-Studies of nearby clouds have demonstrated that star formation is far
-from uniform over molecular clouds, but is concentrated in unusually dense
-regions called clumps or cores, which fill a small fraction of the area of most
-clouds \citep{enoch06,evans09}[refs. E. Lada et al. Evans et al., Enoch et al.]
-(Neal, John, Jonathan) Following \citet{williams00} and \citep{mckee07}, we use
-the term `core' to refer to a very dense region destined to form an individual
-star or small multiple star systems and the term `clump' to refer to a region
-likely to form a group or cluster of stars. While clumps forming massive
-clusters may be denser than cores forming low mass stars [ref Mueller? (Neal,
-John, Jonathan)], in general, clumps are larger and have a lower mean density. Clumps can be
-traced with line emission from molecules such as \ammonia, \form, CS, HCN, etc.
-Spectral lines also provide excellent diagnostics of line-of-sight motions,
-temperatures, and densities.  However, the interpretation of these gas tracers
-is complicated by variations in tracer abundances caused by depletions and
-complex chemical processing, uncertainties in optical depths and excitation
-conditions, and the impacts of radiation fields and shocks. These complications
-make the derivation of column densities, masses, and other physical properties
-of star-forming clumps very difficult.  A limitation of spectral line studies
-is that the tracers of denser gas tend to be weak and multi-element receiver
-arrays have only a modest number of elements, making blind surveys very
-time-consuming.
-
-In contrast, focal-plane arrays containing hundreds of individual bolometers
-sensitive to millimeter and sub-millimeter (sub-mm) radiation are now
-available. This advance in technology enables blind surveys of the Galactic
-plane, providing a uniform inventory of massive star-forming and starless
-clumps.  Catalogs resulting from these surveys will provide the data base for
-subsequent observations in tracers such as hard-to-excite molecular lines and
-higher resolution studies with instruments like CARMA and ALMA.  A significant
-advantage of continuum observations of dust at long wavelengths is the low
-optical depth of the dust \citep{johnstone06}, permitting a straight-forward
-estimate of the mass of the emitting region.
-
-Submillimeter observations of Galactic sources have been conducted by
-a variety of different groups focusing on small regions since
-bolometer technology was developed.  The Submillimeter Common-User
-Bolometer Array (SCUBA) on the 15-m James Clerk Maxwell Telescope
-mapped many significant regions in the galactic plane over its 8 year
-lifetime \citep{holland99,difrancesco08}, but never completed a
-contiguous survey of the galactic plane.  The Bolocam instrument has been
-used on the 10.4-m Caltech Submillimeter Observatory (CSO) to map nearby large
-molecular clouds at 1.1 mm and identify hundreds of cores \citep{enoch06}.
-MAMBO on the 30-m IRAM telescope has been used at 1.2 mm to map
-more distant regions of more massive star formation \citep{motte07}.
-None of these surveys covered a significant fraction of the Galactic plane.
-
-Two large surveys of the Galactic plane are in progress.  The ATLASGAL survey,
-using the LABOCA instrument at 870 \micron\  with 12\arcsec resolution on the
-APEX telescope in Chile, will cover the southern Galactic plane and some of the
-north.  Initial results from this survey have been reported by
-\citet{schuller09}. The overlap region between BGPS and ATLASGAL is in the
-region $-10.5 < \lon < 11.5$ and $15 < \lon < 21$, $-.5 < b < .5$, though
-ATLASGAL will eventually expand up to $\lon = 60$.  The two surveys provide
-complementary samples of the long-wavelength end of the spectral energy
-distribution in Galactic star forming regions.
-
-This paper presents the results of the Bolocam Galactic Plane Survey (BGPS).
-The survey covers the contiguous range $-10.5 < \lon < 86.5, -.5 < b < .5$ with
-additional coverage to higher $|b|$ in the range $77 < \lon < 86.5$ and in the
-$\lon=111$, W3/4/5, Gem OB1, and IC 1396 regions.  It is complementary to the
-survey by \citet{schuller09} in that it targets the part of the plane visible
-from the northern hemisphere and uses a somewhat longer wavelength, allowing
-comparison of properties in the region of overlap with the ATLASGAL survey.
-At 870 \micron, $h\nu/k = 16.5$ K, compared to 13.1 K at 1.1 mm.  Because
-starless clumps may be quite cold ($\td \approx 10$ K), the uncertainty in mass
-caused by uncertain temperature is slightly less at 1.1 mm.  For example, 
-if the actual $\td = 20$ K, rather than 10 K, the mass estimate would decrease by a
-factor of 3.3 at 870 \micron\ versus a factor of 2.9 at 1.1 mm.
-
-In addition,
-the Bolocam bandpass excludes the CO \jj{2}{1} line, which can be a significant
-contaminant on top of the dust continuum emission.
-
-We have used the 144-element Bolocam focal plane array, mounted at the
-Cassegrain focus of the CSO, to survey over \bgpsarea\
-square degrees of the northern Galactic plane at a wavelength of 1.1
-mm in the dust continuum.  Figure \ref{fig:Coverage} shows the
-coverage of the \bgps.  Maps of the entire BGPS are presented in
-Figure \ref{fig:BGPSMontage}.  We have detected \ncores\ clumps in the
-surveyed fields, providing an unbiased sample of clumps suitable for
-multi-wavelength and high-resolution studies with existing telescopes and
-future facilities.  At the distances that we are likely to be observing these
-objects (assuming the majority are at distances greater than 2kpc....
-because?), we are likely observing aggregates of star forming cores found in a
-larger molecular cloud environment, which we will refer to as clumps
-\citep{williams00}.  The clump catalog is described in a companion paper
-\citep{rosolowsky09}.
-
-The outline of the paper is as follows. Section \ref{sec:Observations}
-describes the instrument and the observations.  Section
-\ref{sec:Overview} briefly describes the data reduction process, while
-Sections \ref{sec:FluxCalibration} to \ref{sec:FinalMaps} provide
-greater detail on flux calibration, astrometry, the mapping algorithm,
-noise, photometry, and the public data release.  We conclude in
-Section \ref{sec:Analysis} with brief discussion of the immediate
-implications of the emission revealed by the BGPS.
-
-%BGPS will identify regions of high-mass star and cluster formation
-%throughout the Galaxy and sites of low-mass star formation within a
-%few kpc of the Sun (Figure 1).  Their physical properties may then be
-%constrained by comparison with data in other wavebands.  The
-%distribution of these regions will be compared with other tracers of
-%the interstellar medium (ISM) such as molecular clouds, supershells,
-%HII regions, supernova remnants, and supershells.  The 1.1 mm data
-%together with dust continuum maps at shorter wavelengths taken by us
-%with SHARC~II or with other telescopes will constrain temperature and
-%reveal what surrounding material may be feeding the formation of dense
-%cores. Star formation efficiencies may be obtained by detailed
-%comparison of the NIR-MIR observations of stars with the BGPS
-%observations.  This will also constrain the extinction law and dust
-%properties, essential to refining mass estimates.  By comparing the
-%distribution of 1.1mm cores with HII regions, supernova remnants, and
-%IR emission as seen by {\it Spitzer}, we will constrain the mode of
-%core and star formation, i.e., is it predominantly triggered by
-%advancing shock and ionization fronts, by converging flows in a
-%turbulent medium, or by spontaneous gravitational collapse?  The
-%former models predict a close correlation between fronts and cores
-%while the latter predicts the correlation will be poor.
-
-%\Figure{mass_limits}{The limiting gas mass of cores detectable
-%with at a flux limit of 15 mJy RMS. Detection thresholds at 3 (dashed)
-%and 5 (solid) $\sigma$ are shown for a range of dust temperatures.
-%Dust temperatures $<20$~K are most interesting for this survey, since
-%these are the sources most likely to be pre- or proto-stellar
-%condensations.}{fig:mass_limits}{1.0}
-%
 \Figure{coverage_moll} {The coverage of the BGPS.  The background
-greyscale is IRAS 100 \mum.  [James, team: is there a better figure 
-option?]
-%The Bolocam coverage is shown with white
-%solid lines in the top two panels and black in the bottom three.
-%Major regions of Galactic star formation are labeled.  The coverage of
-%{\em Spitzer}-GLIMPSE \citep{benjamin03} and the FCRAO $^{13}$CO GRS
-%\citep{jackson06} are shown.
+greyscale is IRAS 100 \mum.  
+%[James, team: is there a better figure 
+%option?]
+%[I think this is fine. For print, you can try a black line instead
+%of red. NJE]
 }{fig:Coverage}{1.0}
 
-% TEST
-% Useful, but not here
-%\begin{figure}
-%  \subfigure[$\lon=-10.5$ to $\lon=19.5$ Units are \jyb.  The brightest
-%	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
-%	$\lon=13$, appear to be saturated, but this is only a display
-%	artifact.  The noise is more pronounced from $\lon=-7$ to $\lon=-2$
-%	because this region was observed less.]{\label{fig:BGPSMontage-a}\includegraphics[scale=0.75]{fig1_pg1_bw_inv_bar_label}}\\
-%\pagebreak
-%\subfigure[$\lon=19.5$ to $\lon=49.5$.  Units are \jyb .  G34.3+0.15, W
-%	51, W 43, W 49, and M 17 appear to be saturated, but this is
-%	only a display artifact.]
-%{\label{fig:BGPSMontage-b}\includegraphics[scale=0.75]{fig1_pg2_bw_inv_bar_label}}
-%
-%\end{figure}
-%% --------------------------------
-%
-
-\newcounter{subfig}
-\setcounter{subfig}{1}
-\renewcommand{\thefigure}{\arabic{figure}\alph{subfig}}
-
-\addtocounter{figure}{0}
-%\begin{sidewaysfigure}[h]
-\begin{figure}
-  \label{fig:BGPSMontage}
-  \begin{minipage}{6.5in}
-    \begin{center}
-      \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
-      \caption{$\lon=-10.5$ to $\lon=19.5$ Units are \jyb. 
-%      The brightest
-%	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
-%	$\lon=13$, appear to be saturated, but this is only a display
-%	artifact.
-        The noise is more pronounced from $\lon=-7$ to $\lon=-2$
-	because this region was observed less.}
-    \end{center}
-  \end{minipage}
-\end{figure}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \begin{minipage}{6.5in} 
-    \begin{center}
-      \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
-      \caption{$\lon=19.5$ to $\lon=49.5$.  Units are \jyb .  G34.3+0.15, W
-	51, W 43, W 49, and M 17 appear to be saturated, but this is
-	only a display artifact.  The $20 < \ell < 40$ region through the
-        4-8 kpc molecular ring and approximately the termination of the galactic
-        bar is particularly rich in clumps.}
-    \end{center}
-  \end{minipage}
-\end{figure}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \begin{minipage}{6.5in} 
-    \begin{center}
-      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
-      \caption{$\lon=49.5$ to $\lon=74.5$.  In comparison to the inner galaxy, the $65
-      < \ell < 75$ has a very sparse population of faint clumps}
-    \end{center}
-  \end{minipage}
-\end{figure}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \hspace{-1in}
-  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
-  \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
-  1.5\deg$. The large scale `peanut' shape including DR21 is suggestive of a
-  large wind-blown bubble, although.... [John: fill in discussion here or we'll
-  remove it].  See section \ref{sec:motte} for a comparison with the
-  \citet{motte07} IRAM study of this region. }
-\end{figure}
-%  \vspace{-4in}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-\hspace{-0.5in}
-  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
-  \caption{Cloud complexes centered at $\lon=111$ in the Perseus Arm. 
-  The NGC 7538 complex is in the upper-left.}
-\end{figure}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \hspace{-1in}
-  \includegraphics[scale=0.8]{fig1_pg6_bw_inv_bar_label} 
-  \caption{W3/4/5.  The W3(OH)/W3 Main complex is the bright source
-  on the right side of the image.  W5 has one scan performed in RA/Dec
-  instead of Galactic coordinates and so has non-uniform noise properties
-  in each square degree}
-\end{figure}
-
-\renewcommand{\thefigure}{\arabic{figure}}
-
-\clearpage
-
-\section{Observations}
-\label{sec:Observations}
-
-Bolocam\footnote{{\tt http://www.cso.caltech.edu/bolocam}} is the
-facility 144-element bolometer array camera operating on the 10.4 m
-dish of the Caltech Submillimeter Observatory (CSO) on the summit of
-Mauna Kea.  We used the filter configuration with a bandcenter of
-268~GHz (hereafter 1.1~mm) and fractional bandwidth $\Delta \nu/\nu =
-0.17$ (45.5 GHz).  The passband is constructed to exclude the $^{12}\mathrm{CO}(2
-\to 1)$ emission line.  Figure \ref{fig:Bandpass} shows the passband.
-We compute color corrections in Appendix \ref{app:ColorCorrections}.
-
-The array field-of-view is 7\arcmin.5, with individual detectors
-having nearly Gaussian beams of \bcamfwhm\ FWHM.  The spacing of the
-pixels at 1.1 mm is 1.6$f\lambda$, so the focal plane is not
-instantaneously sampled.  The Bolocam instrument is described in greater
-detail in \citet{haig04} and \citet{glenn03}.
-
-%\subsection{Observations}
-
-The maps presented here were acquired during six separate
-observing sessions at the CSO over the course of two years.  The
-observing epochs are given in Table \ref{tab:Observing}, along with
-corresponding ranges for the zenith opacity $\tau_{225}$ of the CSO
-tipper tau.  Bolocam
-observations were typically scheduled when $\tau_{225} > 0.06$.
-Between observing epochs, Bolocam was removed from its mount at
-the re-imaged Cassegrain focus and stored warm.  Thus the flux
-calibration and pointing model must be re-computed for each epoch to
-allow for variations in the instrument and optics.  We found that the
-flux calibration did not in fact differ significantly between epochs.
-We observed additional pointing sources during Epoch V and therefore
-used it as the master pointing model.
-
-%\subsection{Observing Strategy}
-
-% xraster 120 11280 23 /step_size=162 /equatorial /position_angle=36.753118 /alternate_direction /rot /settling_time = 03
-
-[Reword section?] Our basic observing strategy was to raster scan Bolocam by moving the
-primary mirror of the CSO to modulate the astrophysical signal faster
-than fluctuations in atmospheric opacity.  Each field was scanned with
-alternating raster scans along $l$ and $b$.  In Epoch I-II, the fundamental
-scan unit was a $1\arcdeg \times 1\arcdeg$ block, scanned 23 times in \lon and
-$b$.  Starting with Epoch III, the fundamental scan unit was changed to a
-$3\arcdeg \times 1\arcdeg$ block for increased mapping efficiency.  Each block
-was scanned with 23 scans along lines of constant $b$, and 67 scans along lines
-of constant $l$.  In both cases, the spacing between adjacent rasters was
-162\arcsec.  The total time for such a scan was between 39 and 48 minutes.  The
-data were electronically sampled at 10 Hz along the scan direction, slightly
-higher than the Nyquist rate for the scan speed of 120\arcsec\ s$^{-1}$.
-
-In order to fill in the instanteously undersampled focal plane, we
-began using in Epoch II a field rotator to mechanically align the
-focal plane at an optimal orientation along the scan direction to
-improve the sampling orthogonal to the scan direction.  This is shown
-in Figure \ref{fig:Array}.  Achieving good sampling is complicated by
-a number of missing bolometers.  A simulation was performed to determine
-the optimal angle to rotate the array with respect to the scan
-direction to account for the beam spacing and missing bolometers.  During
-the turnaround following a raster, the field rotator is adjusted to
-this optimum angle.
-%CHECK
-% per Adam, 2009/3/26
-Without the field rotator, the coverage shows variations of 100\% from
-pixel to pixel in a single raster of a field.  With the rotator, this
-is reduced to $\sim40\%$.
-
-% FIGURES AND TABLES
-
 % Figure 3
-\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright molecular
-emission lines are shown at their rest frequencies.  Note that the Bolocam
-passband rejects $>90\%$ of the $^{12}$CO flux, leaving our continuum
-measurements largely uncontaminated.  SO$_2$ and CH$_3$OH lines are likely 
-strong contributors to line flux in the passband.  \citet{nummelin1998} found
-that 22\% of the flux density in one pointing towards Sgr B2 was from lines,
-and \citet{yoshida2005} reported $>40\%$ in Orion A from line emission over the
-260-328 GHz band. Other lines lying in the Bolocam passband include CS($5\to4$)
-and ($6\to5$) (245 and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267
-GHz).  } 
+\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass (thick line).  Bright
+molecular emission lines are shown at their rest frequencies.  For
+comparison, the MAMBO-2 bandpass is shown as a thin line.  Note that
+the Bolocam passband rejects $>90\%$ of the $^{12}$CO flux, leaving
+our continuum measurements largely uncontaminated.  SO$_2$ and
+CH$_3$OH lines are likely strong contributors to line flux in the
+passband.  \citet{nummelin1998} found that 22\% of the flux density in
+one pointing towards Sgr B2 was from lines, and \citet{yoshida2005}
+reported $>40\%$ in Orion A from line emission over the 260-328 GHz
+band. Other lines lying in the Bolocam passband include CS($5\to4$)
+and ($6\to5$) (245 and 293 GHz), HCN($3\to2$) (265 GHz) and
+HCO$^+(3\to2)$ (267 GHz).  }
 % A follow-up project will attempt to determine the contribution of lines
@@
 
-\Table
-{lllll}
-{Observing Epochs for the BGPS}
-{Number & Begin (UT) & End (UT) & Nights & $\tau_{225}$ }
-{tab:Observing}
-{
-I   & 2005 Jul 03 & 2005 Jul 13 & 5 & 0.1 \\
-II  & 2005 Sep 04 & 2005 Sep 12 & 5 & 0.1 \\
-III & 2006 Jul 01 & 2006 Jul 13 & 5 & 0.1 \\
-IV  & 2006 Sep 01 & 2006 Sep 09 & 5 & 0.1 \\
-V   & 2007 Jul 01 & 2007 Jul 13 & 5 & 0.1 \\
-VI  & 2007 Sep 01 & 2007 Sep 09 & 5 & 0.1 \\
-}
-
 % Figure 4
-\FigureTwo{bolosens050904_o32}{scan_10deg}{Left: the position, ellipticity and
-relative response of the detectors in the Bolocam focal plane as mapped to the
-sky.  Right: The effect of field rotation on the coverage obtained via Bolocam
-raster scans.  The array is held fixed during a scan, but is rotated such that
-the sampling is most uniform.}{fig:Array}{1.0}
-
-\section{Overview of the Data Reduction}
-\label{sec:Overview}
-
-{\it just stole material from the Letter here - needs a bit of cleaning up}
-
-A number of different descriptions of the reduction of Bolocam data
-have been published \citep{laurent05,enoch06,sayers09}.  This work
-addresses the issues specific to the BGPS, significantly improving the
-method of \citet{enoch06} for generating maps and characterizing their
-properties.  It incorporates some of the technical developments
-of \citet{sayers09}, though the exquisite control of systematics and
-noise of that analysis is neither necessary nor possible here.
-
-The data were reduced with a custom pipeline written specifically for the BGPS.
-A key element of the reduction is the iterative estimation of the
-atmospheric fluctuations and the astrophysical signal.  The
-atmospheric model is developed from a set of principal components of
-the bolometer signal time series under the assumption that the bulk of the
-correlated signal is atmospheric (under this assumption, astrophysical extended
-structures are treated as atmospheric noise).  The iterative estimation
-process then helps to restore correlated flux due to astrophysical
-emission (Section \ref{sec:Mapping}).
-
-The Bolocam observations are sensitive to structure between \bcamfwhm\ and
-about 200\arcsec\ (half the array field of view, see figure
-\ref{fig:PCA_Filter}).  An indicative analysis of the spatial filter function
-of the iterative mapping scheme is given in \citet{enoch06}, and we present a detailed analysis
-of the filter function in our survey in figure \ref{fig:PCA_Filter}.  The data were
-sampled onto a uniform 7\farcs2 grid.  Flux density calibrations were performed
-using observations of Mars, Uranus, and Neptune, and they are accurate to
-$\sim$20\%.  The flux calibration is described in section \ref{sec:FluxCalibration}.
-
-%A calibration scheme capable of
-%5\% systematic and $<$5\% statistical errors is being implemented as outlined in
-%\citet{Sayers2009}.
-%To account for offsets between the observations, each observation was mapped
-%individually and aligned to a `master' field that has been tied to
-%pointing calibrators. 
-Noise properties across the survey are not completely uniform, but the
-measured $1\sigma$ level is $\approx43\pm7$ m\jyb within the
-$b=\pm.5$ portion of the plane in the 1st quadrant.
-%After the pipeline mapping, the fields were combined using the COMBINE
-%command in IRAF with WCS offsets.
-
-A separate model was constructed for each epoch, but epoch V was used as the
-primary pointing calibration and is shown in figure \ref{fig:PointingModel}.
-In epoch V and VI, pointing sources were observed more frequently to obtain a
-better-constrained master pointing model. The absolute pointing accuracy was
-$\sim6\arcsec$ RMS.  The Epoch V pointing model was used to make pointing
-reference fields which were then median combined using IRAF to make a higher
-S/N reference field with somewhat reduced pointing errors (Section
-\ref{sec:Astrometry}).
-
-% A single $3^\circ \times
-% 1^\circ$ observation of each region was registered to the pointing calibrators
-% as a ``master field'', and additional observations of that field were aligned
-% to the master (Section \ref{sec:Astrometry}).
-
-Bright and large sources leave an impact on their surroundings when
-cleaned with a principal component subtraction.  \object{Sgr B2},
-\object{G 34.3+0.15}, and other sources with fluxes $\geq 10$ Jy are
-surrounded by substantial negative bowls.  Some flux is restored in
-these bowls using the iterative process, 
- but around the brightest sources the impact of the source on the
-background estimation is too great to be fully recovered (Section
-\ref{sec:Photometry}).
-
-Instrument glitches and cosmic ray hits have been removed by a combination of
-outlier rejection in each spatial pixel and hand flagging of the timestream
-data.  Streaking in the images results from incorrect determinations of the
-zero level across scans when a bright source is encountered and variable noise
-in each strip from variable dwell time.  Atmospheric noise in observations
-taken in poor weather may not be completely removed by the reduction procedures
-because the atmospheric opacity can vary over timescales comparable to the time
-to scan astrophysical sources (Section \ref{sec:Noise}).
-
-\section{Flux Density and Surface Brightness Calibration}
-\label{sec:FluxCalibration}
-
-The absolute flux calibration is derived from observations of Mars
-and Uranus
-% no good observations, per AG
-%and Neptune 
-(the ``primary calibrators'').  The millimeter-wave flux of these
-planets is known to $\sim 5\%$ \citep{orton86,griffin93}.
-Calibrations at (sub)millimeter wavelengths are strongly affected by
-atmospheric opacity corrections.  Further, the detector responsivity
-of Bolocam's bolometers is a non-linear function of the mean
-atmospheric loading.
-
-To relate observations of the primary calibrators to observations of
-the BGPS fields, we make use of the following relation.  The
-calibration ${\cal S}$, referenced to the detectors, is given by
-\begin{equation}
-\label{eq:Calibration}
-{\cal S} \, \left[\mathrm{\frac{V}{Jy}}\right] = 
-S(\tau) \eta A \exp{(-\tau)} \Delta\nu
-\end{equation}
-where $S$ is the bolometer responsivity ([V/W]), $\eta$ is the system
-optical efficiency, $A$ is the effective telescope collecting area,
-$\Delta \nu$ is the bandwidth, and $\tau$ is the line-of-sight,
-in-band atmosphere opacity.  Under the assumption that the only power
-variation on the detectors is due to the power from the atmosphere (i.e.
-that astronomical sources are faint relative to the atmosphere),
-which may be parameterized by $\tau$, ${\cal S}$ is a single-valued
-function of $\tau$.  We have used the mean bolometer resistance as a
-proxy for $\tau$, since the bolometer resistance is a single-valued
-function of loading.  {\it This quantity is monitored continuously for
-all observations.}  Note that this calibration curve folds in both the
-effects of changing atmospheric transmission and the changes in
-the detector response with optical loading.
-
-%Multiple observations of secondary calibrators suffice to give the
-%shape of the curve.  To reference it to the absolute calibrators, the
-%fluxes of the planets were held fixed and the fluxes of the secondary
-%calibrators allowed to float to produce the best agreement with a
-%second-order polynomial for all sources.  The values for the secondary
-%calibrators agree well with previously obtained Bolocam values and
-%with values in the literature \citep{sandell94,jenness02}.  
-%%A fit of Equation \ref{eq:Calibration} 
-%
-
-A fit to the observed values (measured potential difference vs. known flux
-density) for the primary calibrators was performed for the each epoch
-separately.
-%CHECK
-The agreement between epochs was good, so a single combined
-calibration was used for all data.
-%We have found that the calibration can differ
-%between successive cooldowns of the instrument by $\sim10\%$ \Check\
-%but is generally stable over the period of order a month which
-%constitutes each of the observing epochs.  
-The calibration curve is shown in Figure \ref{fig:CalibrationCurves}.  The
-resulting error on the calibration curve fit is less than 
-%CHECK
-$5\%$ (statistical) over the observed range of $\tau$.  A tally of all
-contributions to the flux density error is given in Table
-\ref{tab:ErrorBudget}.
-
-The above flux density calibration only accounts for the average
-calibration of bolometer Volts to Janskys.  It is also necessary to
-account for the variation of bolometer response across the focal
-plane.  We do this by monitoring the response to the atmosphere
-emission in all bolometers (astrophysical signal is negligible except at SgrB2).  Since the
-atmosphere is common to all detectors [Anyone - why is the atmosphere common across 7.5'
-at the mm?  Brief discussion of atmosphere physics would be helpful], any changes in response are due to the
-intrinsic properties of the detectors.  The change in relative response with
-loading for a typical detector is shown in Figure \ref{fig:CalibrationCurves}.
-The actual application of the method to the time series of the bolometer
-data is shown in Figure \ref{fig:Flatfield}, and is discussed further in
-Section \ref{sec:Mapping}.
-
-[move this?] In figure \ref{fig:Flatfield}, each step of the iterative cleaning process is illustrated.
-
-The instrument beam size (PSF) is measured using the planets Uranus
-and Neptune which are nearly point sources for Bolocam.
-%The semi-diameter of
-%Mars over this period ranged from 2.3\arcsec\ to 2.9\arcsec, with
-%Neptune $\sim1.1\arcsec$.  Relative to the \bcamfwhm~FWHM Bolocam
-%beam, these may be regarded as point sources; the finite size of Mars
-%results in a $< 1.5\%$ correction of the observed flux.
-The maps of the planets, including all detectors, are fit to a
-Gaussian profile.  The beam area is that averaged over all detectors,
-and is $1.71\times10^{-6}$ steradians (\bcamfwhm).  This
-allows conversion of the maps, calibrated in Jy beam$^{-1}$, into
-surface brightness (MJy sr$^{-1}$).  The uncertainty in the mean beam size
-is $.7\%$, leading to an uncertainty in the surface brightness calibration
-of \TBD.
-
-\subsection{Comparison to Other Surveys}
-\label{sec:motte}
-
-Comparison of the BGPS flux density calibration with SCUBA 850 \mum\
-or ATLASGAL 870 \mum\ results is complicated by the poorly determined
-variations in the dust spectral index produced by emissivity variations.
-However, there are several large-area surveys with the IRAM 30 meter
-telescope at 1.2 mm which can be used for comparison with BGPS to
-check overall image quality, pointing, and flux calibration.  The study
-of the Cygnus-X region by \citet{motte07} presents one of the largest
-fields in the Galactic plane that has been mapped with MABO which overlaps
-with the Bolocam survey fields.
-
-The Motte Cygnus-X study used both the 37 element MAMBO and 117 channel
-MAMBO-2 instrument on the IRAM 30-meter diameter telescope on Pico Veleta
-in Spain.   The FWHM beam size for the observations was 11\arcsec .
-The effective passband of the images presented by Motte et al.
-is about 70 GHz centered at 240 GHz and thus includes the bright
-J = 2--1 CO transition.
-
-The structure of the emission in the Cygnus-X region presented by
-\citet{motte07} appear nearly identical to the 1.1 mm Bolocam images
-of the same field despite the inclusion of the CO line, the slightly
-longer (by about 10\%) longer effective wavelength, and different beam
-sizes.   The peak positions also agree to within the errors of the
-BGPS survey discussed in this paper.
-
-Direct comparison with the fluxes listed in Motte et al. requires
-consideration of the factor of three difference in the size of the beams.
-For example, the the brightest source in the Cyg-X region is DR 21.
-While Motte et al. quote a peak flux density per beam of 4.2 \jyb for
-the brightest feature in the DR 21 complex (their peak N46) and 17.9 Jy
-in a $\sim$ 17\arcsec\ by 23\arcsec box (0.19 x 0.14 pc at an assumed
-distance of 1.7 kpc; see Motte et al. Table 1 in their Appendix).
-BGPS measures a peak flux of 17.5 \jyb in an effective beam roughly
-\bcamfwhm\ in diameter, indicating that the relative calibration is
-similar on the brightest source in common to both surveys.   However,
-DR 21 is an extended source.  Fluxes are best compared using sources
-that appear compact as observed with the beam of the IRAM 30 meter
-telescope.
-
-We have convolved the \citet{motte07} fits files\footnote{{\tt
-ftp://cdsarc.u-strasbg.fr/pub/cats/J/A+A/476/1243/fits/}} with a Gaussian
-kernel that generates an approximately \bcamfwhm\ beam, and compared the
-measured fluxes with those from the BGPS.  Additionally, the data values
-in Motte et al. are in units of Jankys per pixel, with each pixel subtending
-a 4\arcsec\ by 4\arcsec\ area on the sky.  In contrast, the data values
-in BGPS are in units of Janskys per beam where the beam is 31\arcsec\
-in diameter.   The conversion of units required multiplication of the
-convolved images by factor of 8.
-
-The Motte et al. images were convolved with IRAF task
-GAUSS using a 3.5 pixel convolution kernel to synthesize maps with an
-effective FWHM beam diameter of \bcamfwhm ;  the BGPS maps have effective
-beam diameter 4\arcsec\ larger than the CSO beam diameter of 31\arcsec\
-because of the smearing effects of optical distortion at the edges of the
-Bolocam array.  This distortion has not been removed from the Version 1.0
-images.  The Bolocam flux calibration is based on the measurement of
-primary calibrators using the central pixels of the array which are not
-effected by distortion.   The results are shown  in Figure
-\ref{fig:CygnusComparison} and tabulated in Table 2.  This figure and
-the table shows that BGPS and \citet{motte07} clumps have fluxes
-consistent within about 20\% after convolution to a \bcamfwhm\ beam and
-scaling to Jy/beam.
-
-The average Motte et al. fluxes are larger than the BGPS fluxes by a factor
-of 1.23 despite the longer wavelength.  Contamination by the bright
-CO J = 2-1 line may account for a few percent of the excess
-detected flux by MAMBO.    For a dust spectral index of $-3.5$, the
-MAMBO measurements should have detected a flux that is about 35\% lower
-than what was seen by BGPS.    If this is a typical spectral index for
-the sample of clumps, then the Motte et al. flux calibration may be as
-much as 45\% higher than the BGPS fluxes.
-
-\Table
-{lllllll}
-{Comparison of \citet{motte07} IRAM and BGPS measurements
-in the Cygnus X region.  The IRAM data has been convolved
-to the BGPS beam and scaled so the units are in Jy/beam.
-}
-{
-%Source  &   BGPS           &  Motte \\
-%        &   peak m\jyb  &  mJy in box (see Motte+ Table 1)
-Motte Source &  Motte Table 1   &  Motte scaled  & BGPS  & Ratio &  Comments \\
-     Number &  integrated flux &  \jyb          & \jyb  &       &           \\
-}
-{tab:CygnusComparison}
-{
-3  &    1.59 [0.11x0.09] & 2.61      &  2.30  & & DR 17                               \\
-11 &    0.34 [0.11x0.06] & 0.48      &  0.50  & & West SW of DR21                     \\
-12 &    1.63 [0.11x0.09] & 2.60      &  2.20  & &   "                                 \\
-16 &    0.55 [0.12x0.12] & 0.82      &  0.72  & &   "                                 \\
-26 &    0.34 [0.20x0.10] & 0.48      &  0.44  & &   "                                 \\
-29 &    0.54 [0.25x0.13] & 1.10      &  0.62  & &   "                                 \\
-30 &   10.54 [0.15x0.10] &13.5       &  9.80  & & W75(N)                              \\
-44 &    8.43 [0.14x0.11] &14.5       & 12.7   & & DR21 (OH)                           \\
-46 &   17.90 [0.08x0.03] &18.4       & 15.8   & & DR21 f-f, maser (H2O)               \\
-48 &    3.72 [0.17x0.11] & 9.4       &  7.8   & & DR21 (OH)-S                         \\
-51 &    2.37 [0.24x0.03] & 5.5       &  4.1   & & DR21 FIR2                           \\
-53 &    1.60 [0.14x0.09] & 4.3       &  2.7   & & North of DR21  FIR3                 \\
-56 &    0.60 [0.12x0.08] & 0.81      &  0.75  & & SE of DR21 47                       \\
-58 &    2.73 [0.23x0.19] & 2.40      &  1.64  & & IRAS 20375+4109                     \\
-59 &    0.37 [0.12x0.05] & 1.3       &  0.93  & & East of IRAS 20375+4109             \\
-60 &    0.56 [0.16x0.13] & 1.00      &  0.78  & & East of IRAS 20375+4109             \\
-61 &    0.23 [0.12x0.09] & 0.60      &  0.49  & & MSX 81.5168+0.01926                 \\
-62 &    0.50 [0.18x0.12] & 1.23      &  0.80  & & between 63 \& IRAS 20375+4109       \\
-63 &    1.09 [0.08x0.05] & 1.60      &  1.50  & & DR22                                \\
-65 &    0.78 [0.16x0.12] & 1.15      &  1.10  & &                                     \\
-66 &    0.25 [0.15x0.06] & 0.63      &  0.76  & &                                     \\
-68 &    0.84 [0.10x0.10] & 1.01      &  0.94  & &                                     \\
-69 &    1.28 [0.47x0.18] & 1.12      &  1.20  & &                                     \\
-72 &    0.54 [0.28x0.13] & 0.58      &  0.47  & &                                     \\
-}
-% 7
-\Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
-in the same aperture from the \citet{motte07} MAMBO map and the Bolocam map of
-this paper. }{fig:CygnusComparison}{1.0}
+\FigureTwo{bolosens050904_o32}{scan_10deg}{Left: the position,
+ellipticity and relative response of the detectors in the Bolocam
+focal plane as mapped to the sky.  Right: The effect of field rotation
+on the coverage obtained via Bolocam raster scans.  The array is held
+fixed during a scan, but is rotated relative to the scan direction
+such that the sampling is most uniform by attaining the best sampling
+in the cross-scan direction.}{fig:Array}{1.0}
 
@@
 %{calibration_plot_2004}
-{Left: Average calibration curve [V/Jy] versus the mean detector voltage, a
-proxy for atmospheric loading.  Red points are observations of Mars and black
-of Uranus.  The black line is a 2nd-order fit with 0,0 forced (no response if no
-measurable potential difference) .  Right: Scaling of the relative
-response to the atmosphere for a single detector compared to the array median.
-Outliers are from noisy scans that are strongly
-downweighted.}{fig:CalibrationCurves}{1.0}
+{Left: Average calibration curve [V/Jy] versus the mean detector
+voltage, a proxy for atmospheric loading.  Red points are observations
+of Mars and black of Uranus.  The black line is a 2nd-order fit with
+0,0 forced (no response if no measurable potential difference) .
+Right: Scaling of the relative response to the atmosphere for a single
+detector compared to the array median.  Outliers are from noisy scans
+that are strongly downweighted.}{fig:CalibrationCurves}{1.0}
 
@@
 \Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
-in the same aperture from the \citet{motte07} MAMBO map and the Bolocam map of
-this paper. }{fig:CygnusComparison}{1.0}
-
-\begin{deluxetable}{lc}
-\tablewidth{0pt}
-\tablecaption{Flux density error budget}
-\tablehead{
-\colhead{Source} & \colhead{Contribution}
-}
-\startdata
-\label{tab:ErrorBudget} % categorize - which is systematic and which is random
-Pointing error uncertainty & 2\% \\
-Calibration curve (Eq. \ref{eq:Calibration}) uncertainty & $<5\%$ \\  % formal statistical error is probably less than real effect...?
-PCA flux reduction uncertainty & 4\% \\   % is this an uncertainty?  Or systematic loss?
-Absolute Mars flux uncertainty &  5\% \\
-Beam size uncertainty (surface brightness) & X\% \\
-\hline
-Total & 7\% (random) + 5\% (systematic)
-\enddata
-\end{deluxetable}
-
-\section{Astrometry}
-\label{sec:Astrometry}
-
-\subsection{Absolute Reference Sources and Pointing Model}
-
-We constructed an absolute reference system for the BGPS by observing
-bright quasars and blazars near the Galactic Plane [with small raster maps?].  The distribution
-of pointing sources over the sky is shown in Figure
-\ref{fig:PointingCalibrators} and the list is given in Appendix
-\ref{app:PointingCalibrators}.
-
-Pointing observations were performed approximately once every two
-hours over each night.   The
-elevation offsets showed a deviation from zero which was empirically
-well-modeled by a quadratic function of elevation and a linear
-function of azimuth.  No systematic deviation was observed for the
-azimuth offsets.
-
-% Because the Galactic Plane appears over much of the sky, the pointing
-% model necessarily encompasses a large range of elevation and azimuth.
-An RMS scatter of $\sim 6\arcsec$ for the model over the
-entire observed range was achieved, with the scatter somewhat worse at the
-highest ZA.  
-Further details of the pointing calculation are given in Appendix
-\ref{app:PointingCalculation}.
-
-\subsection{Pixel Positions in the FOV}
-
-In addition to the model for the pointing center, it is necessary to
-empirically determine the actual projected pattern of the array on the
-sky, and measure the offset angle between the focal plane and the sky
-coordinate system.  This is done by making observations which track
-all detectors across a bright source (e.g. a planet) and making maps from each
-bolometer individually.
-
-[I think this section needs to be checked on more.... I don't know what to say about it yet -Adam]
-In our first data release, the projected positions of the detectors on the sky
-are made using the nominal positions without correction for optical distortion.
-This results in a slightly blurred beam (35\farcs6 instead of 31\farcs2).
-Because this distortion is asymmetric, it can also result in a small pointing
-offset at the field edges where only bolometers with large offsets record data.
-However, this effect is strongly mitigated by the low number of hits at field
-edges - this data is generally flagged out.  The residual offset is within the
-overall pointing model error, but caution should be used when measuring
-locations at the field edges. [ Note - I haven't been able to measure this yet.  It's only marginally
-possible]
-
-A mean focus offset for the secondary was determined once per observing
-run.  An elevation-dependent correction is applied via a
-CSO-determined look-up table between raster scans.  We did not see any
-evidence that more frequent focus checks improve the quality of the
-PSF. [Observers - what checks were done?]
-
-\subsection{Relative Alignment and Mosaicing}
-
-Relative alignment between different observations of the same field was
-performed by finding the peak of the cross-correlation between images and a
-pointing master constructed  from observations taken in the epoch with the
-best-constrained pointing model for that field (in most cases, this was from
-Epoch V, though in some cases Epoch VI was used).  Each observation was
-initially mapped individually, then all observations in the pointing epoch were
-median-combined to create a reference field.  Each observation was then
-cross-correlated with the reference image for that field. The cross-correlation
-peak was fit with a gaussian and the difference between the gaussian peak and
-the image center was used as the pixel offset.  Finally, all observations of a
-field were merged into a single timestream with pointing offsets applied to
-create the field mosaic.
-
-This method of alignment avoids the ambiguities inherent in using extracted
-sources to align fields, as the BGPS sources are rarely point-like.  It further
-avoids the pointing smearing and loss of peak flux density which would result
-if the the maps of individual observations were coadded using the pointing
-model alone, where each individual observation would be coadded with the
-6\arcsec\ RMS uncertainty of the model.  The relative alignment using the
-correlation maps is accurate to $<1\arcsec$ [I think this should be the
-Gaussian width of the cross-correlation fit?] where there is adequate signal.
-
-In low s/n fields, specifically \lon=65 to 75, there was not enough signal to
-acquire a pointing offset using cross-correlation.  In these fields the
-relative pointing offset is larger and the beam is slightly larger.
-
-\subsection{Comparison to SCUBA Legacy Catalog Source Positions}
-\label{sec:SCUBAPointingComparison}
-%and SHARC-II Positions}
-
-All SCUBA 850 and 450 \mum\ data has been re-processed in a uniform
-manner and made publicly available as the SCUBA Legacy Catalog
-\citep[][hereafter SLC]{difrancesco08}.  These maps allow a 
-cross-check of the accuracy of the BGPS pointing model.  We have applied the same
-cross-correlation procedure used to obtain the relative alignment of
-BGPS observations to compare the BGPS images to the SLC.  Concerns might arise
-in comparing the Bolocam to the SCUBA maps, such as the differing scan
-strategies (SCUBA maps were typically taken in jiggle-map mode, which tends to
-remove extended structure).  The cross-correlation technique actually
-mitigates these effects, since it does not require the establishment of a
-single position for an object (which may differ due to the change in wavelength
-between the surveys or due to the observing strategy) but rather makes use of
-all the information available.  The by-eye morphological comparison between SCUBA and
-BGPS sources is generally excellent with some exceptions, giving a high degree
-of confidence to the comparison and to the results obtained from the BGPS pointing
-model [include Di Francesco pointing accuracy].  An example is shown in Figure \ref{fig:SCUBAPointingComparison}.  We
-find that the RMS offset between BGPS and SLC positions within a $3\arcdeg
-\times 1\arcdeg$ block defined by the BGPS is $4.0\pm8.8$\arcsec, consistent
-with the errors derived for the Bolocam pointing model.  There were some BGPS
-fields that had larger offsets from SCUBA fields; these fields were excluded
-from the offset measurement above because of poor morpohological match.
-
-For the purposes of future comparison of both flux and pointing with
-other surveys, we present in Appendix \ref{app:ReferenceSources} a
-selection of bright, compact, relatively isolated sources.
-
-%{\em Miranda's data here}
+in the same aperture from the \citet{motte07} MAMBO map and the
+Bolocam map of this paper. }{fig:CygnusComparison}{1.0}
 
@@
 % -----------------------------------------------------------------------------
-
-\section{Mapping Algorithm}
-\label{sec:Mapping}
-
-The essential signal-processing problem to be solved by the mapping
-algorithm is the estimation and removal of a signal due to fluctuating
-atmospheric emission which is $>\sim$100's of times stronger than the typical
-sources in our maps.  We implement an iterative procedure for
-estimating both the atmosphere fluctuations and the astrophysical
-signal without {\it a priori} knowledge of either.
-
-We assume the raw timestream data $d$ for each bolometer (indexed by
-$i$) can be written as
-\begin{equation}
-d_i(t) = s_i(t)+a_i(t)+e_i(t)+\epsi_i(t)
-\end{equation}
-where $s$ is the astrophysical signal, $a$ is atmospheric fluctuation
-noise, $e$ are non-random signals due to the instrument itself, and
-$\epsi$ is irreducible Gaussian noise due to photon shot and detector
-noise.  The process of making a maximum likelihood map in the presence
-of Gaussian noise is well-understood, and if the only contributions to
-the data were $s$ and $\epsi$, then the minimum variance estimator of
-the true astrophysical map is given by
-\begin{equation}
-\label{eq:LSMap}
-m = (A^T W A) A^T W d
-\end{equation}
-where $A$ encodes the pointing information and $W$ is the inverse of
-the covariance matrix of the time domain noise $\epsi$,
-\begin{equation}
-W = {\langle \epsi_i \epsi_j \rangle}^{-1}
-\end{equation}
-In this case, the mapping from data to map is a linear operator, $M
-=(A^T W A) A^T W$.  For compactness, Equation \ref{eq:LSMap} will be
-written as $M[d] = m$.  Note that the mapping operation is not
-invertible.  However, given a map $m$ and an observing matrix $A$,
-there exists a linear operation which makes predictions about the
-observed timestreams, namely $d_p = A m$; this will be denoted $T[m] =
-d_p$.
-
-The goal is to produce a time series for each bolometer which as
-closely as possible approximates $s + \epsi$ so that we may produce
-the best estimate of the astrophysical signal $m = M[s+\epsi] = S + N$.
-
-We proceed iteratively, estimating $a$ and $e$ in the order of their
-relative strengths, beginning with the atmosphere.  The first
-iteration step is then
-\begin{equation}
-\label{eq:FirstIterStep}
-\tilde{a}^{(n)}(t) = 
-\sum_i{d_i(t)-\tilde{s}^{(n)}_i(t) - \tilde{e}^{(n)}_i(t)}
-\end{equation}
-where $\tilde{s}^{(0)}_i(t)=0$.   Each bolometer's timestream is then 
-fit to the mean atmosphere model to obtain the relative gains of the detectors.
-\begin{equation}
-\tilde{a}^{(n)}_i(t) = \frac{d_i(t) \cdot a(t)}{d_i(t)^2} a(t) = r_i a(t)
-\end{equation}
-This is illustrated in Figure \ref{fig:Flatfield}.  
-% James - what's this section about?
-% The instrument
-% errors, which are typically smaller than the atmosphere, are then
-% estimated
-% \begin{equation}
-% \tilde{e}^{(n)}_i(t) = some models
-% \end{equation}
-Both the atmosphere and instrument models are subtracted from the
-raw time series
-\begin{equation}
-d_i(t) - \tilde{a}^{(n)}_i(t) - \tilde{e}^{(n)}_i(t)
-\approx s_i(t) + \epsi_i(t)
-\end{equation}
-This is the best estimate of signal plus irreducible noise at
-iteration step $n$, and is made into a map
-\begin{equation}
-M[d_i(t) - \tilde{a}^{(n)}_i(t) - \tilde{e}^{(n)}_i(t)] = \tilde{m}^{(n)}
-\end{equation}
-The current best map $\tilde{m}^{(n)}$ is then deconvolved to provide
-a relatively low-noise, smooth map from which to generate a timestream
-\begin{equation}
-\label{eq:MapToTime}
-T[{\cal D}[\tilde{m}^{(n)}]] = \tilde{s}^{(n)}_i(t)
-\end{equation}
-where ${\cal D}$ represents the deconvolution operation.  At this
-stage, the iterative process could begin again with Equation
-\ref{eq:FirstIterStep}, though it is useful to produce a
-``residual map''
-\begin{equation}
-E = M[d_i(t) - \tilde{s}^{(n)}_i(t) - \tilde{a}^{(n)}_i(t) - 
-\tilde{e}^{(n)}_i(t)]
-\end{equation}
-This residual map serves as a visualization of the progress of the iterative
-method, since in a perfect process it would be map of $\epsi$.
-
-\subsection{Atmosphere Fluctuation Noise Model}
-
-The simplest model for the atmosphere fluctations makes use of the
-fact that the beams for all of the detectors pass through a nearly
-identical atmosphere, thus implying that atmosphere fluctuations will
-be highly correlated between detectors.
-
-To further remove the atmosphere (and other correlated instrument
-noise) without a detailed physical model, we use principal component
-analysis (PCA) as given in \citet{laurent05}. [more words]
-
-The mean across each scan is forced to zero by subtracting a polynomial
-fit to the scan after iteratively rejecting astrophysical sources.  This
-process helps reduce negative bowls in the scan direction near bright sources.
-
-\subsection{Instrument Error Signals}
-
-Most of the instrument error signals have characteristic features
-which allow them to be identified, though not always removed.  The
-error signals include the following:
-\begin{enumerate}
-
-\item Pickup from the 60 Hz AC power.  This appears as narrow lines in the power spectral density (PSD)
-    of the data.  The second harmonic of 60 Hz is aliased via beating against
-    the 130 Hz bolometer bias frequency into 10 Hz with sidebands split at
-    $\sim1$ Hz.  It is removed by replacing components at these frequencies in
-    the fourier transform with gaussian noise matched to the local mean
-    amplitude.
-
-\item Spikes in voltage due to cosmic ray strikes on the bolometers
-(``glitches'').
-
-% James - technical question: Why is there microphonic pickup?  What
-% does the term mean, exactly?
-\item Microphonic pickup due to vibrations of the receiver.  The most
-noticeable microphonics occur at the end of each scan when the
-telescope is turning around and the field rotator is adjusting.  This
-leads to broad spikes in the time series, whose long decay must be
-removed from the data, particularly during the beginnings of scans.
-
-%\item Others?
-
-\end{enumerate}
-
-Fortunately, most of the AC powerline pick-up occurs at frequencies
-where there is no astrophysical signal, given the beam size and scan
-speed.  Thus this error is dealt with by first notch filtering at the
-line frequencies and then low-pass filtering the data.  Because of the
-low correlation with astrophysical signal, this step is performed only
-once and is not iterated (c.f. Figure 1 of \citet{sayers09}).
-
-Both glitches and microphonic pickup from the scan turnarounds are
-degenerate with astrophysical signal and must be estimated as part of
-the iterative process.  
-% NOT TRUE - they are identified per-pixel most of the time
-% Glitches are identified as large excursions
-% from the RMS level after subtraction of the best atmosphere and bright
-% source model, and the data there is excluded from inclusion in
-% subsequent maps.
-The turnaround microphonics are modeled as decaying exponentials at the
-beginnings and ends of scans and are also removed by the PCA cleaning.
-
-\subsection{Data Flagging}
-
-Due to the large volume of data generated by the survey, it was
-necessary to develop new tools to quickly visualize the data and
-ensure data quality.  A common tool in radio astronomy is the
-so-called ``waterfall'' plot, which is an image with frequency on the
-x-axis, time on the y, and an intensity proportional to the
-interferometer visibility amplitude or phase.  We have used a variant
-on this to visualize the Bolocam data by displaying bolometer number
-(related to the bolometer position in the focal plane) on the x-axis
-and time on the y, with the intensity given by the bolometer's
-response (in Jy) at that time.  An example of this is shown in Figure
-\ref{fig:Flagger}.  Anomalies such as the glitch shown
-can be detected and manually and interactively flagged out.
-
-An automated flagger was also created that flags out outlier data on a
-per-map-pixel basis.  In order to make a robust measurement of the
-variance of the fluxes assigned to each pixel, we used the median
-average deviation (MAD) over the data in the pixel and rejected high and low
-outliers at the 3-sigma level.  Pixels with too little data to compute
-a deviation, i.e. those with $<3$ data points, were also flagged out -
-these scan-edge pixels are the dominant contribution to the total
-number of flagged data points.
-
-\subsection{Creation of the Astrophysical Model}
-
-The timestream data is made into a spatial map using the pointing data
-corresponding to each time point for each bolometer.  The data is
-weighted by inverse variance across a single scan and then drizzled
-into a map with $7.2$\arcsec\ pixels using a nearest-neighbor
-algorithm.  The nearest-neighbor matching allows the map to be
-returned to a timestream in the same manner, but with the S/N improved
-by averaging over all hits on a given pixel.  It has the disadvantage
-that it accentuates the unevenness of the cross-scan sampling, since
-each timestream point's value is assigned to an area much smaller than
-the beam.
-%In principle this can be addressed by various gridding
-%algorithms, and may be a part of future reductions of the BGPS data.
-
-The resulting map is then subjected to a maximum-entropy clean algorithm
-\citep{hollis92} using a specified kernel to produce a deconvolved image which
-is mapped back into the timestream to be subtracted (Equation
-\ref{eq:MapToTime}).  This has several advantages over using the original map
-directly, including rejecting artifacts smaller than the kernel and decreasing
-the noise of the resulting timestream.  It is also better than a ``threshold''
-method, which tends to produce discontinuities and include noise outliers.
-
-In some fields, flux from some sources spread out over the course of the
-iterative process using certain kernel sizes.  The cause of this artifact is
-not yet well-understood, but using a different kernel size was an effective
-workaround and did little to change the properties of the final map.  The
-standard kernel size was 14.4\arcsec; a 21.6\arcsec kernel was used when
-artifacts were encountered.
 
@@
 
-%\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of
-%the flagging process using the waterfall plot. Left: The glitch
-%apparent at middle right is the same one whose time series is shown in
-%Figure \ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the
-%effect of the glitch also propagates over the other bolometers,
-%appearing as a horizontal stripe. Right: The same data displayed with
-%the time point including the glitch flagged out and rescaled}
-%{fig:Flaggin}{1.0}
-%
 \Figure{crs}{The distribution of glitch amplitudes flagged and removed from the
@@
   \end{minipage}
-  \caption{Selected images to illustrate the PCA process.  The displays are in
-  Galactic coordinates with a color range from -.1 to 1.0 \jyb.
-  {\it Top 4 rows}: a grid of maps of each of the first 20 PCA components displayed at
-  the same scale.  It is clear that NCG 7538, the object imaged, has emission
-  in each component.  There are varying levels of noise in each component, with
-  the first and second being the most obvious atmospheric components.  Most of
-  the other noise components are probably detector noise correlated among a
-  subset of the bolometers.  The streaks are residuals of the scan-turnaround
-  noise that was not removed by the exponential model fit.  {\it Bottom 4
-  rows}: The same figure, but after 20 iterations.  The figure is the breakdown
-  of the atmosphere remainder (i.e.  the raw data minus the astrophysical
-  model) into eigenfunctions.  Very little astrophysical flux remains at any
-  level of correlation, though there is some at large (few arcminute) scales.}
+  \caption{Selected images to illustrate the PCA process.  The
+  displays are in Galactic coordinates with a color range from -.1 to
+  1.0 \jyb.  {\it Top 4 rows}: a grid of maps of each of the first 20
+  PCA components displayed at the same scale.  It is clear that NCG
+  7538, the object imaged, has emission in each component.  There are
+  varying levels of noise in each component, with the first and second
+  being the most obvious atmospheric components.  Most of the other
+  noise components are probably detector noise correlated among a
+  subset of the bolometers.  The streaks are residuals of the
+  scan-turnaround noise that was not removed by the exponential model
+  fit.  {\it Bottom 4 rows}: The same figure, but after 20 iterations.
+  The figure is the breakdown of the atmosphere remainder (i.e.  the
+  raw data minus the astrophysical model) into eigenfunctions.  Very
+  little astrophysical flux remains at any level of correlation,
+  though there is some at large (few arcminute) scales.}
 \label{fig:PCA_Graphical}
@@
 
-\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution on the
-iterative process can be seen in its effect on the residuals in these images of
-Sgr B2, all displayed at the same scale. From left to right: map, residual,
-model. Top to bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
-7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which has the
-result of leaving no flux in the residual at the location of Sgr B2, and does
-not ``dig a hole'' in the residual map, as the 7.2\arcsec\ kernel does.  The
-7.2\arcsec\ kernel also lacks the noise-rejection features of the larger
-kernels, as can be seen in the last panel.}{fig:Deconvolution}{1.0}
+\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution
+on the iterative process can be seen in its effect on the residuals in
+these images of Sgr B2, all displayed at the same scale. From left to
+right: map, residual, model. Top to bottom kernel size: 14.4\arcsec,
+21.6\arcsec, 31.2\arcsec, 7.2\arcsec. The final version of the
+pipeline uses 14.4\arcsec, which has the result of leaving no flux in
+the residual at the location of Sgr B2, and does not ``dig a hole'' in
+the residual map, as the 7.2\arcsec\ kernel does.  The 7.2\arcsec\
+kernel also lacks the noise-rejection features of the larger kernels,
+as can be seen in the last panel.}{fig:Deconvolution}{1.0}
+
+\Figure{survey_depth}{The depth of the BGPS in the first quadrant as a
+function of Galactic longitude.  The black histogram plots the
+standard deviation as a function of longitude binned in $0.9\arcdeg
+\times 0.9\arcdeg$ degree blocks (to avoid high-noise regions at scan
+edges) centered on $b=0$ for the error maps $E$.  Red is similar, but
+the estimator is median(1/sqrt(weight
+map).}{fig:NoiseVsLongitude}{1.0}
+
+% -----------------------------------------------------------------------------
 
@@
 
-\section{Noise and Systematic Effects}
-\label{sec:Noise}
-
-The residual maps produced by the iterative mapping provide a natural way of
-estimating the systematic error resulting from imperfect subtraction of bright
-sources.  The imperfect subtraction results in positive ``ghosts'' of the
-bright sources in the error maps $E$.  Smoothed residual maps also provide the
-best means of determining the pixel-to-pixel error near bright sources.  Near
-the scan edges, 1/sqrt(weightmap) provides a better estimate of the local noise.
-
-% Residual maps are produced for each map from the residuals after
-% removing the astrophysical signal model and the PCA atmosphere model.  These
-% maps are useful for diagnosing the effect of the iterative process on bright
-% sources and as a method of obtaining an
-% estimate of the noise.
-
-% ...ok, explain please?
-% The noise is correlated between adjacent spatial pixels due to
-% residual atmospheric noise correlated in time.  We have completed
-% ignored this effect in our analysis.
-
-The noise may be estimated either from the residual maps, from the timestream
-PSDs of the detectors, or from the weight maps produced. The final per-pixel
-error estimate is given as \TBD (this remains an open question - is the best
-per-pixel error a smoothed version of the residual map, e.g.  \citet{enoch06},
-1/weightmap$^2$, or some other estimate? Adam, James, Erik).
-
-Because observing conditions varied widely during the survey, the RMS
-noise levels obtained in the various fields of the BGPS also varies.
-However, the noise within a given $1\arcdeg \times 1\arcdeg$ field is
-fairly uniform in the absence of very bright sources.  We show the
-variation of the depth as a function of Galactic longitude in Figure
-\ref{fig:NoiseVsLongitude}.
-
-[since we don't do any science in this paper, should this be held off for
-use in Erik's paper?]
-The depth can be converted into an
-estimate of mass via standard estimates, i.e., under the assumption of
-a temperature, opacity, and distance.
-Using dust opacity from \citet{ossenkopf94}
-%\citet{enoch06} and \citet{young06},
-and assuming a gas-to-dust mass ratio 100, the mass sensitivity
-can be written as
-\begin{equation} 
-\label{eq:Mass}
-M_{gas}\approx
-0.22\left( e^{13.1/T_d}-1 \right) \left({S_\nu\over 15\; {\rm mJy}} \right)
-D^{2}_{kpc} \msol 
-\end{equation}
-where $D_{kpc}$ is the distance to the source in kpc.  (At $S_\nu =
-15$~mJy this corresponds to an RMS extinction sensitivity of $A_V\sim
-1$ mag, with the same $T_d$ dependence).  For Bolocam, $h\nu/k \approx
-13$~K, so for $T_d > 10$K the dependence is approximately linear.  At
-the coldest temperatures expected, the mass changes a factor of 2.9
-between 20 and 10 K.  The distance to the clump is more important in most
-situations.
-
-\Figure{survey_depth}{The depth of the BGPS in the first quadrant as a
-function of Galactic longitude.  The black histogram plots the standard deviation as a 
-function of longitude binned in $0.9\arcdeg \times 0.9\arcdeg$ degree blocks
-(to avoid high-noise regions at scan edges) centered on $b=0$ for the error
-maps $E$.  Red is similar, but the estimator is median(1/sqrt(weight
-map).}{fig:NoiseVsLongitude}{1.0}
-
-\section{Effects of the Data Reduction Procedures on Photometry}
-\label{sec:Photometry}
-
-To do accurate and meaningful photometry on the Bolocam maps requires
-a good estimate of the noise (Section \ref{sec:Noise}) but also an
-understanding of the spatial filtering imposed by the observing
-strategy and the cleaning and mapping of the data.  
-The additional
-complexities of defining ``sources'' in complicated regions are discussed in
-\citet{rosolowsky09}.  Here we restrict our discussion to the limitations
-on performing photometry imposed by the data reduction.
-
-The BGPS maps are the convolution of the (nearly Gaussian)
-primary beam $G(\xad)$ and an effective high-pass
-spatial filter $F(\xad)$ (figure \ref{fig:PCA_Filter}),
-\[
-M'(\xad) = (G(\xad) \otimes F(\xad)) \otimes M(\xad)
-\]
-
-%James - please explain this to me, or explain it better here.  What
-%is the form of B(Omega) that it gives 0?
-The effect of the high pass filter is that the effective PSF $B=G
-\otimes F$ has the non-intuitive property that its area is {\em zero}:
-\[
-\int{B(\Omega) d\Omega} = 0
-\]
-Clearly, this complicates the definition of surface brightness, and
-also imposes a limit on the size of features for which photometry may
-be meaningfully performed.
-
-To assess the effect of the mapping algorithm, we performed a series
-of simulations.  Gaussian sources with a range of peak flux densities and sizes
-were inserted on top of a background consisting of real BGPS data with the
-astrophysical source model removed.  The recovered fluxes were measured in
-ellipses that included single well-separated sources.  Figure
-\ref{fig:PCA_Filter}a shows the fraction of flux recovered in the map as a
-function of source size for a range of different PCA components subtracted in
-the cleaning.
-
-The final reduction used 13 PCA components because this produced a
-reasonable compromise between attenuating extended structure and
-cleaning the atmospheric contribution.  Note that this is a substantially
-more aggressive cleaning than that used in \citet{enoch06} largely because
-our mean integration time per pixel was $\sim$seconds, whereas theirs was
-$\sim$minutes, and therefore the atmospheric noise was much more likely to
-be correlated between observations.
-
-Figure \ref{fig:PCA_Filter}b shows the fraction of flux recovered in the
-maps as a function of the deconvolution kernel used to create the astrophysical
-model maps.  The differences at large source sizes are not well-understood
-(these size scales may be dominated by atmosphere), but at the smallest source
-size, it is evident that a deconvolution kernel smaller than the source size
-does not reliably recover the source flux.  Therefore we chose a deconvolution
-kernel smaller than the beam but larger than the pixel size used.  Figure
-\ref{fig:Deconvolution} demonstrates the effects of using both too large and
-too small a kernel.
-
-% -----------------------------------------------------------------------------
-
 \FigureTwo{pca_comparison_nolegend_l111}{deconvolution_comparison_nolegend_l111}{The
 fractional flux recovered as a function of source size for
-well-separated Gaussian sources with FWHM as indicated.
-\emph{Left}: 3 (blue), 7 (green), 10 (yellow), 13 (orange), 16 (red), 21
-(teal), 26 (lime), 31 (black) PCA components subtracted.  
-Note that flux recovery drops to 50\% at 120\arcsec for the 13 PCA
-component cleaning used in the released data.  The 3 and 7 PCA cases
-show bumps because atmospheric noise is still present at large scales.
-The $>$100\% recovery for simulated sources smaller than the deconvolution kernel is a
-side-effect; since the deconvolution kernel is smaller than the beam, no real
-astrophysical source should ever be smaller than the kernel.
-\emph{Right}:
-7.2\arcsec (cyan), 14.4\arcsec (black), 21.6\arcsec (red), 31.2\arcsec (green)
-deconvolution kernel for 13 PCA components subtracted.  It is clear that the
-larger deconvolution kernels generate spurious signal at smaller scales, but
-the flux recovery is very close to 1 at the beam size
+well-separated Gaussian sources with FWHM as indicated.  \emph{Left}:
+3 (blue), 7 (green), 10 (yellow), 13 (orange), 16 (red), 21 (teal), 26
+(lime), 31 (black) PCA components subtracted.  Note that flux recovery
+drops to 50\% at 120\arcsec for the 13 PCA component cleaning used in
+the released data.  The 3 and 7 PCA cases show bumps because
+atmospheric noise is still present at large scales.  The $>$100\%
+recovery for simulated sources smaller than the deconvolution kernel
+is a side-effect; since the deconvolution kernel is smaller than the
+beam, no real astrophysical source should ever be smaller than the
+kernel.  \emph{Right}: 7.2\arcsec (cyan), 14.4\arcsec (black),
+21.6\arcsec (red), 31.2\arcsec (green) deconvolution kernel for 13 PCA
+components subtracted.  It is clear that the larger deconvolution
+kernels generate spurious signal at smaller scales, but the flux
+recovery is very close to 1 at the beam size
 (\bcamfwhm)}{fig:PCA_Filter}{1.0}
 
-\Figure{aper_phot_hpf_beam}{[James - figure needs clarification] The effect of performing aperture
-photometry on a point source of unit flux observed with the effective
-Bolocam PSF $B$.  The black curve shows the area (measured in pixels)
-as a function of the aperture radius for the filter measured via
-simulation.  This is compared to the equivalent case for a Gaussian
-beam (green).  The vertical lines show radii of $n/2 \times FWHM$ for
-$n=1,2,3$.  One can see that the Gaussian beam has nearly reached a
-constant area of $2 \pi \sigma^2$ by a radius of $3/2 \times FWHM$, at
-which point any larger aperture would recover the full flux of the
-source.  The actual Bolocam beam reaches its maximum effective area
-sooner, and then drops precipitously as the size of the aperture is
-increased.  }{fig:ESF}{1.0}
+\Figure{image_types}{Examples of four of the image types being
+released.  Axes are offsets in arcminutes.  See section
+\ref{sec:FinalMaps}. Top left: Map.  Top right: Residual.  Bottom
+left: Deconvolved.  Bottom right: Weight}{fig:sampleimages}{1.0}
 
@@
 
-\section{Final Maps and Data Release}
-\label{sec:FinalMaps}
+% -----------------------------------------------------------------------------
+%\begin{sidewaysfigure}[h]
+\begin{figure}
+% This assigns the correct label to the *entire* Figure 2.
+  \caption{Images from the BGPS.}
+  \label{fig:BGPSMontage}
+  \addtocounter{figure}{-1}
+  \renewcommand{\thefigure}{\arabic{figure}\alph{subfig}}  
+  \begin{minipage}{6.5in}
+    \begin{center}
+      \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
+      \caption{$\lon=-10.5$ to $\lon=19.5$ Units are \jyb.  The
+      brightest sources, e.g. Sgr B2, Sgr A, and sources near
+      $\lon=10$ and $\lon=13$, appear to be saturated, but this is
+      only a display artifact.  The noise is more pronounced from
+      $\lon=-7$ to $\lon=-2$ because this region was observed less.}
+    \end{center}
+  \end{minipage}
+\end{figure}
 
-The final maps are produced by coadding all observations of a single
-square degree centered on a particular Galactic coordinate
-$(l_0,b_0)$.  The maps are made in Galactic coordinates using a plate
-carr\'{e} (FITS header CAR) projection.  (This is the same projection
-used by the \spitzer-GLIMPSE and BU-FCRAO GRS surveys.)  As these maps
-are near the coordinate system equator, the difference between truly
-equiareal pixels and the pixels used is at most (James: find this number?) X\%.  The pixel size
-is 7.2\arcsec, chosen to be much smaller than the Bolocam beam.
-%, and
-%producing data squares 500 pixels on a side.
-The maps are written to standard FITS files.  An example of the FITS
-header for the BGPS images is given in Appendix \ref{app:FITS_Header}.
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
 
-Five image types will be released, each covering the same regions.  The maps
-are standard astrophysical maps subject to the caveats previously mentioned,
-the most important being the spatial filtering function (section \ref{sec:Noise}).
-The model maps are deconvolved using the maximum-entropy method with kernels
-specified in the header (either 14.4\arcsec or 21.6\arcsec).  The residual map is the map of the model timestream
-subtracted from the data timestream; it is close to but not identical to the
-map minus the model.  The weightmap shows the inverse-variance weighting of
-each pixel.  The nhitsmap shows how many recorded data points from the
-timestream have been assigned to each pixel; it is proportional to the dwell
-time per pixel (each `hit' is .1s).  Examples of each (except the nhitsmap)
-are given in figure \ref{fig:sampleimages}.
+\begin{figure}
+  \begin{minipage}{6.5in} 
+    \begin{center}
+      \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
+      \caption{$\lon=19.5$ to $\lon=49.5$.  Units are \jyb .
+	G34.3+0.15, W 51, W 43, W 49, and M 17 appear to be saturated,
+	but this is only a display artifact.  The $20 < \ell < 40$
+	region through the 4-8 kpc molecular ring and approximately
+	the termination of the galactic bar is particularly rich in
+	clumps.}
+    \end{center}
+  \end{minipage}
+\end{figure}
 
-\Figure{image_types}{Examples of four of the image types being released.  Axes are offsets
-in arcminutes.  See section \ref{sec:FinalMaps}. Top
-left: Map.  Top right: Residual.  Bottom left: Deconvolved.  Bottom right:
-Weight}{fig:sampleimages}{1.0}
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
 
-%\section{Public Data Release}
+\begin{figure}
+  \begin{minipage}{6.5in} 
+    \begin{center}
+      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
+      \caption{$\lon=49.5$ to $\lon=74.5$.  In comparison to the inner galaxy, the $65
+      < \ell < 75$ has a very sparse population of faint clumps}
+    \end{center}
+  \end{minipage}
+\end{figure}
 
-All processed maps are available through
-IPAC\footnote{http://irsa.ipac.caltech.edu/Missions/bolocam.html}.
-IPAC provides a cutout service for the images as well as a searchable
-version of the catalog provided in \citet{rosolowsky09}.  The full
-release includes
-\begin{enumerate}
-\item Calibrated maps for all regions observed (MAP)
-% don't release smoothmaps? \item The MAP smoothed by the Bolocam PSF, which is helpful in bringing out extended structure (SMOOTHMAP)
-\item The deconvolved MAP (MODEL)
-\item Maps of integration time per pixel (NHITSMAP)
-\item Maps of residual noise per pixel (RESIDUAL)
-\item Maps of inverse variance per pixel (WEIGHTMAP)
-\item Maps of the mask obtained for various regions from the cataloging algorithm (MASKMAP) \citep{rosolowsky09}
-\end{enumerate}
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
 
-%\citet{moore07}
-%\citet{zinchenko97}
+\begin{figure}
+  \hspace{-1in}
+  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
+  \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
+  1.5\deg$. The large scale `peanut' shape including DR21 is suggestive of a
+  large wind-blown bubble, although.... [John: fill in discussion here or we'll
+  remove it].  See section \ref{sec:motte} for a comparison with the
+  \citet{motte07} IRAM study of this region. }
+\end{figure}
+%  \vspace{-4in}
 
-\section{Analysis}
-\label{sec:Analysis}
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
 
-{\bf Claudia suggested that this section be removed or changed to an `advertisement' section
-where we indicate what follow-up work needs to be done - seems reasonable, since this
-is mostly junk pilfered from the `letter'.  However, we need to keep the last sentence around...}
+\begin{figure}
+\hspace{-0.5in}
+  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
+  \caption{Cloud complexes centered at $\lon=111$ in the Perseus Arm. 
+  The NGC 7538 complex is in the upper-left.}
+\end{figure}
 
-TEST: \ref{fig:BGPSMontage}
+\addtocounter{figure}{-1}
+\addtocounter{subfig}{1}
 
-The BGPS is the first millimeter survey of a substantial fraction
-of the Galactic Plane, providing an unbiased look at the high-density
-gas most intimately associated with the earliest phases of star
-formation.
+\begin{figure}
+  \hspace{-1in}
+  \includegraphics[scale=0.8]{fig1_pg6_bw_inv_bar_label} 
+  \caption{W3/4/5.  The W3(OH)/W3 Main complex is the bright source
+  on the right side of the image.  W5 has one scan performed in RA/Dec
+  instead of Galactic coordinates and so has non-uniform noise properties
+  in each square degree}
+\end{figure}
 
-Inspection of Figure \ref{fig:BGPSMontage} shows excellent
-correspondence with SCUBA maps of small sub-fields throughout the
-plane \citep{difrancesco08}.  BGPS contours overlaid on the GLIMPSE
-survey \citep{benjamin03} show excellent correlation with 8\mum\
-infrared dark clouds (IRDCs).  However, many features in the BGPS maps
-do not appear in the Spitzer observations, which suggests that the 1.1
-mm emission traces dense clumps without a background to absorb.  [if we
-include this, we probably need a figure as an example, c.f. \citet{shuller09}]
-
-% No advertisements.
-% A
-% study of IRDC correlation with BGPS emission is underway
-% \citep{battersby09}.
-
-% implies star forming....
-
-Filamentary structures with aspect ratios $\geq 10$ are present
-throughout the galactic plane.  The most crowded fields consist of
-frothy and clumpy structure.  There are 5000-10000 distinct sources,
-the majority of which are at least moderately resolved
-\citep{rosolowsky09}.  We suspect that higher resolution observations
-will resolve BGPS clumps into clusters of protostellar objects, as has
-been seen in Serpens \citep{enoch08,Testi1998} and OMC 1
-\citep{Beuther2004,johnstone99} where bolometer observations at low
-resolution have been complemented by interferometer observations at
-high resolution.
-
-There are clear maxima in the emission filling factor in the Galactic
-Center and in the region from $\lon=23$ to $\lon=31$, the line of sight
-through the densest part of the molecular ring.  Additional areas of
-high source density are seen at $\lon=10$ and $\lon=13$.  The filling factor
-of 1.1 mm continuum emission at the 100 mJy level is $\sim 20$\% per
-square degree from $\lon=-10$ to $\lon=20$ and $\sim 10$\% from $\lon=20$ to
-$\lon=50$ (compare to figure \ref{fig:NoiseVsLongitude}.
-%In the range
-%$\lon=50$ to $\lon=75$, the filling factor is below 1\% and very few sources have
-%been detected.  
-This result is in contrast to CO filling factors $\sim1$ in the inner galactic
-plane \citep{dame01,jackson06}, confirming that 1.1 mm continuum emission traces
-denser material than CO.  
-%The small filling factor of the 1.1 mm emission
-%compared to CO emission  shows that the continuum is directly associated with
-%star forming material, whereas the CO also traces less dense material not
-%directly associated with star formation.
-
-In some cases, distance to BGPS clumps can be determined by matching
-Galactic Ring Survey $^{13}$CO and 1.1 mm continuum morphology
-\citep{IRDCdistance,jackson06}.  However, in other cases the association
-between the CO and 1.1 mm data is not clear, either because of
-confusion or because the BGPS sources are too compact to identify in
-$^{13}$CO morphology.  Heterodyne follow-up observations using dense
-gas tracers (NH$_3$, N$_2$H$^+$, HCO$^+$, and CS) are being conducted
-to provide radial velocity, density, chemistry, and temperature
-measurements. % no advertisements \citep{schlingman09, battersby09, nordhaus09}.
-
-BGPS clumps are associated with the densest portions of giant
-molecular clouds (GMCs) traced by CO surveys
-\citep[e.g.,][]{dame01,jackson06}.  The brightest clumps visible in our
-maps, e.g. \object{Sgr B2}, \object{G34.3+0.15}, \object{W 51},
-\object{W 43}, \object{W 49}, and \object{M 17}, correspond to well
-known star forming regions.
-%(the saturation is only a display artifact; the astrophysical sources are
-%always much fainter than the atmosphere and therefore do not saturate the
-%detectors).  
-These associations suggest that other bright sources of millimeter
-emission will prove to be massive star or cluster forming regions.
-
-In conclusion, the BGPS is most awesome survey ever.
-
-\noindent---------------------------------
-
-\acknowledgments
-
-We would like to acknowledge the staff and day crew of the CSO for their
-assistance. The BGPS project is supported by the National Science Foundation
-through NSF grant AST-0708403. J.A. was supported by a Jansky Fellowship from
-the National Radio Astronomy Observatory (NRAO). The first observing runs for
-BGPS were supported by travel funds provided by NRAO. Support for the
-development of Bolocam was provided by NSF grants AST-9980846 and AST-0206158.
-Team support was provided in part by NSF grant AST-0607793 to the
-University of Texas at Austin.
-
-We recognize and acknowledge the cultural role and reverence that the
-summit of Mauna Kea has within the Hawaiian community. We are
-fortunate to conduct observations from this mountain.
-
-{\it Facilities:} \facility{CSO (Bolocam)}
-
-\appendix
-
-\section{Calculation of Color Corrections}
-\label{app:ColorCorrections}
-
-If an experiment has finite bandwidth ($t(\nu) \ne \delta(\nu -
-\nu_c)$), to report a source surface brightness at a single
-frequency, one must assume a source spectrum.  The power detected from
-that source is assumed to be
-\begin{equation}
-P_{in} = \eta \; A \Omega \; \int I_0(\nu) t(\nu) d \nu
-\end{equation}
-(Here $\eta$ and $A \Omega$ are the optical efficiency and throughput
-of the instrument, $I_0(\nu)$ is the nominal (assumed) surface
-brightness of the source, and $t(\nu)$ is the bandpass transmission
-normalized to $1.0$ at its peak.)  The effective band center $\nu_c$
-is usually chosen such that
-\begin{equation}
-I_0(\nu_c) \simeq \frac{\int I_0(\nu) t(\nu) d \nu}
-{\int t(\nu) d \nu} 
-\end{equation}
-The band centers for Bolocam are calculated assuming a Rayleigh-Jeans
-(RJ) source spectrum
-\begin{eqnarray}
-I_0(\nu_c) & = & I_{RJ}(\nu_c) \\
-\nonumber & = & \tau \; 2 k T \; \frac{\nu_c^2}{c^2},
-\end{eqnarray}
-where $\tau$ is the optical depth of the source and $k$ is Boltzmann's
-constant.  Since the detected power is assumed to be
-\begin{equation}
-P_{in} = \eta \; A \Omega \; \int \tau \; 2 k T \; \frac{\nu^2}{c^2}
-\; t(\nu) d \nu,
-\end{equation}
-we can write
-\begin{equation}
-I_0(\nu_c) = \frac{P_{in}}{\eta \; A \Omega \int \nu^2 \; t(\nu) d \nu} \; \nu_c^2
-\end{equation}
-Now if we assume a different source spectrum, for example a greybody
-with power-law emissivity, the assumed input power is
-\begin{eqnarray}
-P_{in} & = & \eta \; A \Omega \; \int I_{GB}(\nu) t(\nu) d \nu \\
-\nonumber & = & \eta \; A \Omega \; \int \tau(\nu_0) (\nu / \nu_0)^\alpha B_\nu(T) t(\nu) d \nu
-\end{eqnarray}
-and the source spectrum inferred from the detected power is
-\begin{eqnarray}
-I_{GB}(\nu_c) & = & \tau(\nu_0) (\nu_c / \nu_0)^\alpha B_{\nu_c}(T) \\
-\nonumber & = & \frac{P_{in}}{\eta \; A \Omega \int \nu^\alpha B_\nu(T) t(\nu) d \nu} \; \nu_c^\alpha B_{\nu_c}(T) \\
-\nonumber & = & \frac{\int \nu^2 t(\nu) d \nu}{\int \nu^\alpha B_\nu(T) t(\nu) d \nu} \; \nu_c^{\alpha-2} B_{\nu_c}(T) \; I_{RJ}(\nu_c) \\
-\nonumber & \equiv & \frac{I_{RJ}(\nu_c)}{K}.
-\end{eqnarray}
-This defines the color correction $K$ to apply to the reported Bolocam
-flux from a source if the source is assumed to have a greybody
-spectrum with power-law emissivity.
-
-%We make a similar calculation for DIRBE, for which the band centers are 
-%computed assuming a spectrum with $\nu I(\nu)$ constant.  In this case, 
-%the correction is given by 
-%\begin{eqnarray}
-%K &=& \frac{\nu_c^{-1}}{\int \nu^{-1} t(\nu) d \nu} \left[\frac{\tau(\nu_0) (\nu_c / \nu_0)^\alpha B_{\nu_c}(T)}{\int \tau(\nu_0) (\nu / \nu_0)^\alpha B_{\nu}(T) t(\nu) d \nu} \right]^{-1} \\
-%\nonumber &=& \frac{\int \nu^\alpha B_{\nu}(T) t(\nu) d \nu}{\int \nu^{-1} t(\nu) d \nu} \; \nu_c^{-(\alpha+1)} B_{\nu_c}(T)
-%\end{eqnarray}
-%
-We note that for an arbitrary experiment with bandpass $t(\nu)$ that
-reports its surface brightness measurements assuming a spectrum
-$I_0(\nu)$, the surface brightness assuming a different source
-spectrum $I_1(\nu)$ is given by
-\begin{eqnarray}
-I_1(\nu_c) &=& I_0(\nu_c) / K \\
-\nonumber &=& I_0(\nu_c) \frac{I_1(\nu_c)}{\int I_1(\nu) t(\nu) d \nu} \left[\frac{I_0(\nu_c)}{\int I_0(\nu) t(\nu) d \nu} \right]^{-1}
-\end{eqnarray}
-
-% James - it would be nice to include some numbers here, not just the process.
-
-\section{Pointing Calculation}
-\label{app:PointingCalculation}
-
-To calculate the position at which to point the telescope, the CSO
-antenna computer computes an alt/az ($E$,$A$) derived from the RA/Dec J2000
-(heliocentric) catalog position.  It performs the following
-calculation:
-
-\begin{enumerate}
-
-\item Precess catalog coordinates to current epoch.  The CSO by
-default stores catalog positions in B1950.
-
-\item Add aberration and nutation corrections.  This is the
-``requested apparent'' RA and Dec reported by the antenna computer.
-
-\item The equatorial coordinates are transformed to horizon
-coordinates using the current local apparent sidereal time.
-
-\item An 11-term model (``$C$-terms'') based on the optical pointing of
-the telescope is then applied to $A$ and $E$ along with $t$-terms (?), %James?
-the tilt of the alidade, and a refraction correction to obtain the
-necessary mechanical pointing of the telescope to acquire the source.
-
-\item The telescope then attempts to follow this track; the difference
-between the requested $A$,$Z$ and the actual, measured angles of the
-encoders (a result of servo errors) are also reported.
-
-% are c4 and c5 different from the alidade_x,y tilt that are in the RPC file?
-
-%char	32   pointing_file_name
-%double	11   pointing_constant
-%double	6    t_term_constant
-%double	1    alidade_x_tilt
-%double	1    alidade_y_tilt
-%double	1    azimuth_t_term_offset
-%double	1    elevation_t_term_offset
-%double	1    tropospheric_refraction
-
-\end{enumerate}
-
-The CSO antenna computer reports this pointing information, including
-geocentric RA/Dec, at a rate of 100 Hz.  This time series, along with
-the field rotator encoder information from Bolocam is merged with the
-bolometer time series and aligned.
-
-To calculate the pointing used in the map from the telescope inputs,
-the Bolocam software does the following:
-
-\begin{enumerate}
-
-\item Start with the reported $\alpha',\delta'$ from the CSO.  Remove
-aberration and nutation corrections.  Precess from current epoch to
-J2000.  This gives $\alpha,\delta$.
-
-\item Apply the $\Delta A,\Delta E$ terms to $\alpha,\delta$ to
-account for the difference between commanded and actual positions of
-the telescope.
-
-\end{enumerate}
-
-\section{Table of Absolute Pointing Sources}
-\label{app:PointingCalibrators}
-
-The absolute reference frame for the BGPS pointing model was chosen
-from a selection of bright quasars near the Galactic Plane.  Table
-\ref{tab:PointingCalibrators} gives the pointing sources used for this
-purpose.
-
-\Table
-{llrrrrc}
-{Absolute Pointing Calibrators}
-{Number & Alias & RA(J2000) & Dec(J2000) & l & b  & Flux (Jy)}
-{tab:PointingCalibrators}
-{
-         1 &   1622-253 & 16 25 46.9 & -25 27 38.3 & 352.14 &  16.32 &  0.18 \\
-         2 & 16293-2422 & 16 32 22.9 & -24 28 35.6 & 353.94 &  15.84 &  8.40 \\
-         3 &   1657-261 & 17 00 53.2 & -26 10 51.7 & 356.70 &   9.75 &  0.07 \\
-         4 &   NGC6334I & 17 20 53.4 & -35 47  1.7 & 351.42 &   0.64 &  2.50 \\
-         5 &    NRAO530 & 17 33 02.7 & -13 04 49.5 &  12.03 &  10.81 &  2.70 \\
-         6 &   1741-038 & 17 43 58.8 &  -3 50  4.6 &  21.59 &  13.13 &  1.44 \\
-         7 &   1749+096 & 17 51 32.8 &   9 39  0.7 &  34.92 &  17.65 &  2.70 \\
-         8 &      G5.89 & 18 00 30.4 & -24 04  0.5 &   5.89 &  -0.39 &  3.57 \\
-         9 &        M8E & 18 04 53.0 & -24 26 39.4 &   6.05 &  -1.45 &  3.92 \\
-        10 &     G10.62 & 18 10 28.7 & -19 55 49.8 &  10.62 &  -0.38 & 17.20 \\
-        11 &   1830-211 & 18 33 39.9 & -21 03 40.0 &  12.17 &  -5.71 &  1.70 \\
-        12 &      G34.3 & 18 53 18.6 &   1 14 58.3 &  34.26 &   0.15 & 31.30 \\
-        13 &   1908-202 & 19 11 09.6 & -20 06 55.0 &  16.87 & -13.22 &  1.00 \\
-        14 &      G45.1 & 19 13 22.1 &  10 50 53.4 &  45.07 &   0.13 &  3.70 \\
-        15 &      OV236 & 19 24 51.0 & -29 14 29.8 &   9.34 & -19.61 &  8.60 \\
-        16 &   1923+210 & 19 25 59.6 &  21 06 26.1 &  55.56 &   2.26 &  0.32 \\
-        17 &   1954+513 & 19 55 42.7 &  51 31 48.6 &  85.30 &  11.76 &  0.60 \\
-        18 &       CYGA & 19 59 28.5 &  40 44  1.7 &  76.19 &   5.75 &  0.25 \\
-        19 &      K3-50 & 20 01 45.7 &  33 32 43.5 &  70.29 &   1.60 &  8.45 \\
-        20 &   2005+403 & 20 07 44.9 &  40 29 48.6 &  76.82 &   4.30 &  0.40 \\
-        21 &        ON1 & 20 10 09.1 &  31 31 37.7 &  69.54 &  -0.98 &  2.90 \\
-        22 &    2013+37 & 20 15 28.7 &  37 10 59.6 &  74.87 &   1.22 &  1.40 \\
-        23 &   2021+317 & 20 23 19.0 &  31 53  2.4 &  71.40 &  -3.10 &  0.54 \\
-        24 &   2023+336 & 20 25 10.8 &  33 43  0.3 &  73.13 &  -2.37 &  0.92 \\
-        25 &     GL2591 & 20 29 24.7 &  40 11 18.9 &  78.89 &   0.71 &  2.07 \\
-        26 &    MWC 349 & 20 32 45.5 &  40 39 36.7 &  79.64 &   0.47 &  1.67 \\
-        27 &       W75N & 20 38 36.4 &  42 37 34.5 &  81.87 &   0.78 &  4.46 \\
-        28 &      3C418 & 20 38 37.0 &  51 19 12.7 &  88.81 &   6.04 &  0.62 \\
-        29 &   CRL 2688 & 21 02 18.8 &  36 41 37.7 &  80.17 &  -6.50 &  1.90 \\
-        30 &    NGC7027 & 21 07 01.6 &  42 14 10.2 &  84.93 &  -3.50 &  9.27 \\
-        31 &   2201+315 & 22 03 15.0 &  31 45 38.4 &  85.96 & -18.78 &  0.35 \\
-}
+\renewcommand{\thefigure}{\arabic{figure}}
 
@@
 
-\section{Table of Reference Sources}
-\label{app:ReferenceSources}
+\Figure{bgps_glimpse_vgps_28_5}
+{An RGB image of a portion of the Galactic Plane, combining Bolocam
+(red), VGPS 20 cm continuum (green) and Spitzer GLIMPSE 8 \mum\
+(blue).}  {fig:Science}{1.0}
 
-\Table
-{llrrrrc}
-{In-plane Millimeter Sources}
-{Number & Alias & RA(J2000) & Dec(J2000) & l & b  & Flux (mJy)}
-{tab:PPS}
-{
-   l351pps &            & 17 23 50.2 & -36 38 58.8 & 351.04 &  -0.34 &  -999.0 \\
-   l354pps &            & 18 00 50.0 & -23 20 33.0 &   6.55 &  -0.10 &  -999.0 \\
-   l357pps &            & 17 40 57.3 & -31 10 48.0 & 357.56 &  -0.32 &  -999.0 \\
-   l000pps &            & 17 46 37.1 & -29 10 21.5 & 359.91 &  -0.31 &  -999.0 \\
-  l000pps2 &            & 17 47 10.3 & -28 46 11.8 &   0.32 &  -0.20 &  -999.0 \\
-   l002pps &            & 17 50 36.3 & -27 06  2.8 &   2.14 &   0.01 &  -999.0 \\
-   l006pps &            & 17 57 34.4 & -23 58 12.0 &   5.64 &   0.24 &   989.0 \\
-   l009pps &            & 18 06 14.2 & -20 31 58.0 &   9.61 &   0.19 &  1187.0 \\
-  l009pps2 &            & 18 06 15.5 & -20 32  8.0 &   9.61 &   0.19 &  1189.0 \\
-   l012pps &            & 18 10 50.5 & -17 55 54.0 &  12.42 &   0.51 &  1205.0 \\
-   l015pps &            & 18 14 35.3 & -16 45 45.0 &  13.87 &   0.28 &  1085.0 \\
-  l015pps2 &            & 18 21 08.5 & -14 31 48.0 &  16.58 &  -0.05 &   748.0 \\
-   l018pps &            & 18 25 42.0 & -13 10 13.0 &  18.30 &  -0.39 &  1544.0 \\
-   l020pps &            & 18 28 09.9 & -11 28 47.0 &  20.08 &  -0.13 &  1650.0 \\
-   l021pps &            & 18 30 34.0 &  -9 34 54.0 &  22.04 &   0.22 &   993.0 \\
-   l023pps &            & 18 34 54.6 &  -8 49 18.0 &  23.20 &  -0.38 &  1681.0 \\
-   l024pps &            & 18 36 05.1 &  -7 31 21.0 &  24.49 &  -0.04 &  1851.0 \\
-   l025pps &            & 18 36 16.7 &  -6 43  8.7 &  25.23 &   0.29 &  -999.0 \\
-   l026pps &            & 18 37 18.4 &  -6 38 38.4 &  25.41 &   0.10 &  -999.0 \\
-  l026pps2 &            & 18 39 04.9 &  -6 24 23.6 &  25.82 &  -0.18 &  -999.0 \\
-   l027pps &            & 18 41 51.1 &  -5 01 48.0 &  27.36 &  -0.17 &  3478.0 \\
-   l028pps &            & 18 44 19.0 &  -4 40 52.0 &  27.95 &  -0.55 &  -999.0 \\
-  l028pps2 &            & 18 42 51.8 &  -4 00  1.9 &  28.39 &   0.08 &  -999.0 \\
-   l029pps &            & 18 42 15.6 &  -3 34 44.5 &  28.70 &   0.41 &  -999.0 \\
-  l028pps2 &            & 18 42 50.8 &  -3 59 46.1 &  28.40 &   0.09 &  -999.0 \\
-   l033pps &            & 18 52 25.1 &   0 14 53.0 &  33.26 &  -0.11 &  -999.0 \\
-   l035pps &            & 18 53 39.1 &   1 50 32.0 &  34.82 &   0.35 &   756.0 \\
-   l037pps &            & 18 59 10.0 &   4 12 10.0 &  37.55 &   0.20 &  1045.0 \\
-   l038pps &            & 19 01 53.2 &   4 12 51.0 &  37.87 &  -0.40 &  1487.0 \\
-   l040pps &            & 19 05 40.9 &   6 26  5.0 &  40.28 &  -0.22 &  1700.0 \\
-   l042pps &            & 19 10 33.5 &   9 08  7.0 &  43.23 &  -0.05 &  1247.0 \\
-   l044pps &            & 19 11 54.4 &   9 35 53.0 &  43.80 &  -0.13 &  1829.0 \\
-  l044pps2 &            & 19 13 28.4 &  10 53 41.0 &  45.12 &   0.13 &  1999.0 \\
-   l048pps &            & 19 23 10.8 &  14 26 31.0 &  49.37 &  -0.30 &  1903.0 \\
-   l050pps &            & 19 23 11.1 &  14 26 34.0 &  49.37 &  -0.30 &  2088.0 \\
-   l079pps &            & 20 29 25.3 &  40 11 28.0 &  78.89 &   0.71 &  1390.0 \\
-   l079pps &            & 20 29 25.2 &  40 11 30.0 &  78.89 &   0.71 &  2014.0 \\
-  l079pps2 &            & 20 31 13.3 &  40 03 33.0 &  78.99 &   0.35 &   790.0 \\
-   l080pps &            & 20 34 42.8 &  39 44 45.0 &  79.13 &  -0.37 &  1104.0 \\
-  l080pps2 &            & 20 40 05.3 &  41 31 48.0 &  81.17 &  -0.11 &   961.0 \\
-   l080pps &            & 20 30 28.7 &  41 16  6.0 &  79.88 &   1.18 &  1024.0 \\
-   l082pps &            & 20 40 26.8 &  41 56 54.0 &  81.54 &   0.10 &   805.0 \\
-l110.5npps &            & 23 05 10.7 &  60 14 50.6 & 110.11 &   0.05 &  -999.0 \\
-   l111pps &            & 23 15 31.5 &  61 07 39.7 & 111.62 &   0.38 &  -999.0 \\
-    l134p1 &            & 02 29 02.8 &  61 33 31.2 & 134.28 &   0.86 &  -999.0 \\
-  l134p1-2 &            & 02 27 06.9 &  61 52 20.8 & 133.95 &   1.07 &  -999.0 \\
-  l134p1-3 &            & 02 27 02.4 &  61 52 32.9 & 133.94 &   1.07 &  -999.0 \\
-    l135p1 &            & 02 34 45.1 &  61 46 23.0 & 134.83 &   1.31 &  -999.0 \\
-   l136p15 &            & 02 50 08.4 &  61 59 56.7 & 136.38 &   2.27 &  -999.0 \\
-   l137p15 &            & 02 29 03.2 &  60 43 26.9 & 134.59 &   0.08 &  -999.0 \\
-    IC1396 &            & 21 40 11.5 &  58 16 11.7 &  99.93 &   4.21 &  -999.0 \\
-  IC1396-2 &            & 21 36 36.8 &  57 30 50.0 &  99.07 &   3.97 &  -999.0 \\
-  IC1396-3 &            & 21 35 38.4 &  57 26 40.5 &  98.93 &   4.00 &  -999.0 \\
-   l189pps &            & 06 08 50.1 &  21 38 19.0 & 188.94 &   0.87 &  -999.0 \\
- l189pps-2 &            & 06 08 49.7 &  21 38  5.7 & 188.95 &   0.87 &  -999.0 \\
-   l192pps &            & 06 12 51.5 &  18 00 39.3 & 192.58 &  -0.05 &  -999.0 \\
- l192pps-2 &            & 06 12 51.5 &  17 59 36.3 & 192.59 &  -0.05 &  -999.0 \\
- l192pps-3 &            & 06 12 50.1 &  18 00 35.8 & 192.58 &  -0.05 &  -999.0 \\
- l192pps-4 &            & 06 12 50.3 &  17 59 28.8 & 192.59 &  -0.06 &  -999.0 \\
- l192pps-5 &            & 06 07 43.9 &  20 39 29.6 & 189.67 &   0.17 &  -999.0 \\
-}
-
-\section{FITS Header Information}
-\label{app:FITS_Header}
-
-\begin{verbatim}
-
-SIMPLE  =                    T / Written by IDL:  Sun Jan 18 01:21:05 2009      
-BITPIX  =                  -32 / Number of bits per data pixel                  
-NAXIS   =                    2 / Number of data axes                            
-NAXIS1  =                 3134 /                                                
-NAXIS2  =                  883 /                                                
-DATE    = '2009-01-18'         / Creation UTC (CCCC-MM-DD) date of FITS header  
-LONPOLE2=            180.00000 /lonpole                                         
-LATPOLE2=            0.0000000 /latpole                                         
-PPBEAM  =            21.276915 /pixels per beam                                 
-CALIB_0 =          -0.00333379 / 0th coefficient for flux cal                   
-CALIB_1 =             -2.92617 / 1st coefficient for flux cal                   
-CALIB_2 =              6.97269 / 2nd coefficient for flux cal                   
-ITERNUM =                    0 /Iteration number                                
-N_PCA   =                    0 /number of PCA components subtracted             
-COMMENT FITS (Flexible Image Transport System) format is defined in 'Astronomy  
-COMMENT and Astrophysics', volume 376, page 359; bibcode 2001A&A...376..359H    
-CTYPE1  = 'GLON-CAR'           / Coordinate Type                                
-CTYPE2  = 'GLAT-CAR'           / Coordinate Type                                
-EQUINOX =              2000.00 / Equinox of Ref. Coord.                         
-CD1_1   =    -0.00199999986216 / Degrees / Pixel                                
-CD2_1   =        0.00000000000 / Degrees / Pixel                                
-CD1_2   =       -0.00000000000 / Degrees / Pixel                                
-CD2_2   =     0.00199999986216 / Degrees / Pixel                                
-CRPIX1  =              1270.52 / Reference Pixel in X                           
-CRPIX2  =              366.367 / Reference Pixel in Y                           
-CRVAL1  =        191.092003456 / Galactic longitude of reference pixel          
-CRVAL2  =      0.0993870183708 / Galactic latitude of reference pixel           
-PV2_1   =        0.00000000000 /Projection parameter 1                          
-HISTORY PUTAST: Jan 18 01:10:42 2009 World Coordinate System parameters written 
-END
-
-\end{verbatim}
-
-\bibliography{milkyway}
-
-\end{document}
+\clearpage

### 2010-02-24 bgps_pipeline/methods/ms.tex
Creating r341: BGPS Pipeline V1.0

--- 2009-04-20 methods/ms.tex
@@
 % sec:FinalMaps
-% sec:Analysis
+% sec:Discussion
 
@@
 
-\documentclass[12pt,preprint]{aastex}
-%\documentclass{emulateapj}
+%\documentclass[12pt,preprint]{aastex}
+\documentclass{emulateapj}
+
+%%% THIS ACHIEVES THE HOLY GRAIL OF 1 IN MARGINS ALL AROUND!!! %%%
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\oddsidemargin  0.0in
+	\evensidemargin 0.0in
+	\textwidth      6.5in
+	\headheight     0.0in
+	\topmargin      0.375in
+	\textheight=9in
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %\newcommand{\C18o}{C$^{18}$O($1\rightarrow 0$)}
-\newcommand{\Check}{{\bf ???}}
+\def\Check#1{{\tt #1}}
 \newcommand{\mum}{\ensuremath{\mu \mathrm{m}}}
@@
 \newcommand{\bgpsarea}{150}
-\newcommand{\bcamfwhm}{31.2\arcsec}
+\newcommand{\bcamfwhm}{33\arcsec}
 \newcommand{\ncores}{7628}
@@
 
+\newcounter{subfig}
+\setcounter{subfig}{1}
+
 \title{The Bolocam Galactic Plane Survey: Survey Description and Data
@@
 	Claudia Cyganowski\altaffilmark{\wisc},
-	Darren Dowell\altaffilmark{\jpl}
+	Darren Dowell\altaffilmark{\jpl},
 	Neal J. Evans II\altaffilmark{\utexas},
@@
 
-We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm continuum survey
-of \bgpsarea\ square degrees of the Galactic Plane with 130 in the 1st quadrant,
-31 in the 2nd, and 6 in the 3rd.  The BGPS represents
-the first large area, systematic survey of the Northern Galactic Plane in the
-millimeter continuum without pre-selected targets.  The survey has detected
-\ncores\ clumps to a limiting non-uniform 1-$\sigma$ noise level in the range \bgpsdepthlow\ and
-\bgpsdepthhigh\ m\jyb RMS.  We present maps of 97 contiguous square degrees from
-$\lon=-10.5$ to $\lon=86.5$ and $b=\pm0.5$ with a resolution of $\sim$\bcamfwhm, as
-well as regions in IC1396, $\lon=111$ (NGC7538), W3/4/5, and Gem OB1.  The most
-striking feature of the maps is the filamentary structure of millimeter emission
-throughout the Galaxy.
-
-This paper details the survey observations and methods.  We treat carefully the
-determination of pointing and flux density calibration errors and compare our
-results to the literature.  Data processing algorithms that separate
-astronomical signals from time-variable atmospheric flux density in the data
-time-stream are discussed.  The algorithms reproduce the structure of the
-astronomical sky on a \emph{limited range of angular scales} and produce artifacts in
-the vicinity of bright sources. Specifically, extended emission smooth on
-scales larger than about 3\arcmin\ is not fully recovered in the images.  The
-spatial frequency response function of the Bolocam Galactic Plane Survey is
-discussed.
-
-This paper serves as a companion and guide to the public data release through
-NASA's Infrared Processing and Analysis Center (IPAC).  These images represent
-an important finder chart for future observations with ALMA and a
-long-wavelength spectral band complementary to ATLASGAL and imminent
-submillimeter surveys with SCUBA-2 and Herschel-SPIRE.
+We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm
+continuum survey of \bgpsarea\ square degrees of the Galactic Plane
+with 130 in the 1st quadrant, 31 in the 2nd, and 6 in the 3rd.  The
+BGPS represents the first large area, systematic survey of the
+Northern Galactic Plane in the millimeter continuum without
+pre-selected targets.  The survey has detected \ncores\ clumps to a
+limiting non-uniform 1-$\sigma$ noise level in the range
+\bgpsdepthlow\ and \bgpsdepthhigh\ m\jyb RMS.  We present maps of 97
+contiguous square degrees from $\lon=-10.5$ to $\lon=86.5$ and
+$b=\pm0.5$ with a resolution of $\sim$\bcamfwhm, as well as regions in
+IC1396, $\lon=111$ (NGC7538), W3/4/5, and Gem OB1.  The most striking
+feature of the maps is the filamentary structure of millimeter
+emission throughout the Galaxy.
+
+This paper details the survey observations and data reduction methods.
+We treat carefully the determination of pointing and flux density
+calibration errors and compare our results to the literature.  Data
+processing algorithms that separate astronomical signals from
+time-variable atmospheric flux density in the data time-stream are
+discussed.  The algorithms reproduce the structure of the astronomical
+sky over a limited range of angular scales and produce artifacts in
+the vicinity of bright sources. Specifically, extended emission smooth
+on scales larger than about 3\arcmin\ is not fully recovered in the
+images.  The spatial frequency response function of the Bolocam
+Galactic Plane Survey is discussed.
+
+This paper serves as a companion and guide to the public data release
+through NASA's Infrared Processing and Analysis Center (IPAC).  These
+images represent an important finder chart for future observations
+with ALMA and a long-wavelength spectral band complementary to
+ATLASGAL and imminent submillimeter surveys with SCUBA-2 and
+Herschel-SPIRE.
 
@@
 
-Millimeter-wavelength continuum surveys of the Galactic plane provide the most
-efficient way to find molecular clumps that are the likely sites of formation
-for massive stars and star clusters. The development of detector arrays have
-made blind surveys of large areas possible.  Such surveys bypass the need for
-selection based on the presence of embedded stars or star clusters, infrared
-sources, masers, or radio continuum emission. In particular, they can locate
-molecular clumps before stars form, providing vital information on the initial
+Millimeter-wavelength continuum surveys of the Galactic plane provide
+the most efficient way to find molecular clumps that are the likely
+sites of formation for massive stars and star clusters. The
+development of detector arrays has made blind surveys of large areas
+possible.  Such surveys bypass the need for selection based on the
+presence of embedded stars or star clusters, infrared sources, masers,
+or radio continuum emission. In particular, they can locate molecular
+clumps before stars form, providing vital information on the initial
 conditions of star formation.  These surveys can also provide valuable
-constraints on the physical properties of the clumps, especially masses and
-mean densities, in conjunction with distance information.
+constraints on the physical properties of the clumps, especially
+masses and mean densities, in conjunction with distance information.
 
 Galaxy-wide surveys are essential for measuring the impacts of the
-environment on clump properties and star formation activity.
-Do clump properties vary with Galactocentric distance, or
-with location with respect to spiral arms?  Do they depend on the
-level of nearby star formation activity?
-Answering these questions in our Galaxy will provide the
-essential ``ground truth'' required for the analysis of distant
-galaxies where where individual clouds and clumps are not resolved and
-only galaxy-wide average quantities can be measured.
-
-Surveys of the galaxy in CO line emission \citep{dame01,jackson06} have
-identified the locations of large molecular clouds and traced
-the transition from atomic to molecular gas as distance from the
-center of the galaxy decreases. Together with kinematic distances
+environment on clump properties and star formation activity.  Do clump
+properties vary with Galactocentric distance, or with location with
+respect to spiral arms?  Do they depend on the level of nearby star
+formation activity?  Answering these questions in our Galaxy will
+provide the essential ``ground truth'' required for the analysis of
+distant galaxies where individual clouds and clumps are not resolved
+and only galaxy-wide average quantities can be measured.
+
+Surveys of the galaxy in CO line emission \citep{dame01,jackson06}
+have identified the locations of large molecular clouds and traced the
+transition from atomic gas in the outer galaxy to molecular gas in the
+inner galaxy.  Together with kinematic distances
 \citep[e.g.][]{RotationCurve} and, more recently, accurate distances
-from VLBI \citep{reid09}, these surveys have begun to
-reveal the spiral structure of the Milky Way. As this picture comes into
-sharper focus, we can begin to address the old question of the relationship
+from VLBI \citep{reid09}, these surveys have begun to reveal the
+spiral structure of the Milky Way. As this picture comes into sharper
+focus, we can begin to address the old question of the relationship
 between spiral density waves and star formation.
@@
 Studies of nearby clouds have demonstrated that star formation is far
-from uniform over molecular clouds, but is concentrated in unusually dense
-regions called clumps or cores, which fill a small fraction of the area of most
-clouds \citep{enoch06,evans09}[refs. E. Lada et al. Evans et al., Enoch et al.]
-(Neal, John, Jonathan) Following \citet{williams00} and \citep{mckee07}, we use
+from uniform over molecular clouds, but is concentrated in unusually
+dense regions called clumps or cores, which fill a small fraction of
+the area of most clouds \citep{lada91,enoch07,evans09}.
+%[added ref to Lada and changed ref to Enoch to the summary paper. NJE]
+Following \citet{williams00} and \citet{mckee07}, we use
 the term `core' to refer to a very dense region destined to form an individual
-star or small multiple star systems and the term `clump' to refer to a region
+star or small multiple star system and the term `clump' to refer to a region
 likely to form a group or cluster of stars. While clumps forming massive
-clusters may be denser than cores forming low mass stars [ref Mueller? (Neal,
-John, Jonathan)], in general, clumps are larger and have a lower mean density. Clumps can be
+clusters may be even denser than cores forming low mass stars 
+\citep{mueller02}, in general, clumps are larger and have a lower mean 
+density \citep{mckee07}. Clumps can be
 traced with line emission from molecules such as \ammonia, \form, CS, HCN, etc.
@@
 temperatures, and densities.  However, the interpretation of these gas tracers
-is complicated by variations in tracer abundances caused by depletions and
-complex chemical processing, uncertainties in optical depths and excitation
-conditions, and the impacts of radiation fields and shocks. These complications
+is complicated by variations in tracer abundances caused by freeze-out onto
+grains, sublimation caused by star formation, and subsequent
+complex chemical processing \citep{vandishoeck98}. Interpretation is
+further complicated by uncertainties in optical depths and excitation
+conditions and the impacts of radiation fields and shocks. These complications
 make the derivation of column densities, masses, and other physical properties
-of star-forming clumps very difficult.  A limitation of spectral line studies
+of star-forming clumps very difficult.  A limitation of spectral line surveys
 is that the tracers of denser gas tend to be weak and multi-element receiver
 arrays have only a modest number of elements, making blind surveys very
-time-consuming.
-
-In contrast, focal-plane arrays containing hundreds of individual bolometers
-sensitive to millimeter and sub-millimeter (sub-mm) radiation are now
-available. This advance in technology enables blind surveys of the Galactic
-plane, providing a uniform inventory of massive star-forming and starless
-clumps.  Catalogs resulting from these surveys will provide the data base for
-subsequent observations in tracers such as hard-to-excite molecular lines and
-higher resolution studies with instruments like CARMA and ALMA.  A significant
-advantage of continuum observations of dust at long wavelengths is the low
-optical depth of the dust \citep{johnstone06}, permitting a straight-forward
-estimate of the mass of the emitting region.
+time-consuming. Consequently, no blind surveys of the Galaxy have been done
+in lines that trace the molecular clumps.
+
+In contrast, focal-plane arrays containing hundreds of individual
+bolometers sensitive to millimeter and sub-millimeter (sub-mm)
+radiation are now available. This advance in technology enables blind
+surveys of the Galactic plane, providing a uniform inventory of
+massive star-forming and starless clumps.  Catalogs resulting from
+these surveys will provide the data base for subsequent observations
+in tracers such as hard-to-excite molecular lines and higher
+resolution studies with instruments like CARMA and ALMA.  A
+significant advantage of continuum observations of dust at long
+wavelengths is the low optical depth of the dust \citep{johnstone06},
+permitting a straight-forward estimate of the mass of the emitting
+region.
 
 Submillimeter observations of Galactic sources have been conducted by
-a variety of different groups focusing on small regions since
-bolometer technology was developed.  The Submillimeter Common-User
-Bolometer Array (SCUBA) on the 15-m James Clerk Maxwell Telescope
-mapped many significant regions in the galactic plane over its 8 year
-lifetime \citep{holland99,difrancesco08}, but never completed a
-contiguous survey of the galactic plane.  The Bolocam instrument has been
-used on the 10.4-m Caltech Submillimeter Observatory (CSO) to map nearby large
-molecular clouds at 1.1 mm and identify hundreds of cores \citep{enoch06}.
-MAMBO on the 30-m IRAM telescope has been used at 1.2 mm to map
-more distant regions of more massive star formation \citep{motte07}.
-None of these surveys covered a significant fraction of the Galactic plane.
-
-Two large surveys of the Galactic plane are in progress.  The ATLASGAL survey,
-using the LABOCA instrument at 870 \micron\  with 12\arcsec resolution on the
-APEX telescope in Chile, will cover the southern Galactic plane and some of the
-north.  Initial results from this survey have been reported by
-\citet{schuller09}. The overlap region between BGPS and ATLASGAL is in the
-region $-10.5 < \lon < 11.5$ and $15 < \lon < 21$, $-.5 < b < .5$, though
-ATLASGAL will eventually expand up to $\lon = 60$.  The two surveys provide
-complementary samples of the long-wavelength end of the spectral energy
-distribution in Galactic star forming regions.
-
-This paper presents the results of the Bolocam Galactic Plane Survey (BGPS).
-The survey covers the contiguous range $-10.5 < \lon < 86.5, -.5 < b < .5$ with
-additional coverage to higher $|b|$ in the range $77 < \lon < 86.5$ and in the
-$\lon=111$, W3/4/5, Gem OB1, and IC 1396 regions.  It is complementary to the
-survey by \citet{schuller09} in that it targets the part of the plane visible
-from the northern hemisphere and uses a somewhat longer wavelength, allowing
-comparison of properties in the region of overlap with the ATLASGAL survey.
-At 870 \micron, $h\nu/k = 16.5$ K, compared to 13.1 K at 1.1 mm.  Because
-starless clumps may be quite cold ($\td \approx 10$ K), the uncertainty in mass
-caused by uncertain temperature is slightly less at 1.1 mm.  For example, 
-if the actual $\td = 20$ K, rather than 10 K, the mass estimate would decrease by a
-factor of 3.3 at 870 \micron\ versus a factor of 2.9 at 1.1 mm.
-
-In addition,
-the Bolocam bandpass excludes the CO \jj{2}{1} line, which can be a significant
-contaminant on top of the dust continuum emission.
+a variety of different groups focusing on small regions.  The
+Submillimeter Common-User Bolometer Array (SCUBA) on the 15-m James
+Clerk Maxwell Telescope mapped many significant regions in the
+galactic plane over its 8 year lifetime
+\citep{holland99,difrancesco08}, but never completed a contiguous
+survey of the galactic plane.  The Bolocam instrument has been used on
+the 10.4-m Caltech Submiliimeter Observatory (CSO) to map nearby large
+molecular clouds at 1.1 mm and identify hundreds of cores
+\citep{enoch06}.  MAMBO on the 30-m IRAM telescope has been used at
+1.2 mm to map both small, nearby cores \citep{kauffmann08} and more
+distant regions of more massive star formation \citep{motte07}.  None
+of these surveys covered a significant fraction of the Galactic plane.
+
+Two large surveys of the Galactic plane are in progress.  The ATLASGAL
+survey, using the LABOCA instrument at 870 \micron\ with 12\arcsec\
+resolution on the APEX telescope in Chile, will cover the southern
+Galactic plane and some of the north.  Initial results from this
+survey have been reported by \citet{schuller09}. The overlap region
+between BGPS and ATLASGAL is in the region $-10.5 < \lon < 11.5$ and
+$15 < \lon < 21$, $-0.5 < b < 0.5$, though ATLASGAL will eventually
+expand up to $\lon = 60$.  The two surveys provide complementary
+samples of the long-wavelength end of the spectral energy distribution
+in Galactic star forming regions.
+
+This paper presents the results of the Bolocam Galactic Plane Survey
+(BGPS).  The survey covers the contiguous range $-10.5 < \lon < 86.5,
+-0.5 < b < 0.5$ with additional coverage to higher $|b|$ in the range
+$77 < \lon < 86.5$ and in the $\lon=111$, W3/4/5, Gem OB1, and IC 1396
+regions.  It is complementary to the survey by \citet{schuller09} in
+that it targets the part of the plane visible from the northern
+hemisphere and uses a somewhat longer wavelength, allowing comparison
+of properties in the region of overlap with the ATLASGAL survey.  In
+addition, the BGPS covers the Galactic anti-center region, allowing
+consistent comparison of very different parts of the Galaxy.  At 870
+\micron, $h\nu/k = 16.5$ K, compared to 13.1 K at 1.1 mm.  Because
+starless clumps may be quite cold ($\td \approx 10$ K), the
+uncertainty in mass caused by uncertain temperature is slightly less
+at 1.1 mm.  For example, if the actual $\td = 20$ K, rather than 10 K,
+the mass estimate would decrease by a factor of 3.3 at 870 \micron\
+versus a factor of 2.9 at 1.1 mm.  In addition, the Bolocam bandpass
+excludes the CO \jj{2}{1} line, which can be a significant contaminant
+on top of the dust continuum emission.
 
 We have used the 144-element Bolocam focal plane array, mounted at the
-Cassegrain focus of the CSO, to survey over \bgpsarea\
-square degrees of the northern Galactic plane at a wavelength of 1.1
-mm in the dust continuum.  Figure \ref{fig:Coverage} shows the
-coverage of the \bgps.  Maps of the entire BGPS are presented in
-Figure \ref{fig:BGPSMontage}.  We have detected \ncores\ clumps in the
-surveyed fields, providing an unbiased sample of clumps suitable for
-multi-wavelength and high-resolution studies with existing telescopes and
-future facilities.  At the distances that we are likely to be observing these
-objects (assuming the majority are at distances greater than 2kpc....
-because?), we are likely observing aggregates of star forming cores found in a
-larger molecular cloud environment, which we will refer to as clumps
-\citep{williams00}.  The clump catalog is described in a companion paper
-\citep{rosolowsky09}.
+Cassegrain focus of the CSO, to survey over \bgpsarea\ square degrees
+of the northern Galactic plane at a wavelength of 1.1 mm in the dust
+continuum.  Figure \ref{fig:Coverage} shows the coverage of the \bgps.
+%[Note: ref to figure 2 with our images is commented, needs to be called
+%in Section 9. NJE]
+We have detected \ncores\ clumps in the surveyed fields, providing a
+sample of clumps suitable for multi-wavelength and high-resolution
+studies with existing telescopes and future facilities.  This sample
+is free of the usual biases associated with observing only regions
+with signposts of star formation, such as HII regions or masers. While
+sensitivity limits will bias the survey against distant, low-mass
+objects, follow-up studies indicate that many sources are more
+massive, distant objects \citep{bally09,nordhaus09, rosolowsky09}.
+%[refs to papers in prep by John, Miranda, and Erik, where distance is
+%discussed a bit. Erik's last version had more discussion of this
+%topic, so need to coordinate with that. NJE] 
+These objects are likely to be aggregates of star forming cores found
+in a larger molecular cloud environment, which we will refer to as
+clumps \citep{williams00}.  The clump catalog is described in a
+companion paper \citep{rosolowsky09}.
 
@@
 noise, photometry, and the public data release.  We conclude in
-Section \ref{sec:Analysis} with brief discussion of the immediate
+Section \ref{sec:Discussion} with brief discussion of the immediate
 implications of the emission revealed by the BGPS.
-
-%BGPS will identify regions of high-mass star and cluster formation
-%throughout the Galaxy and sites of low-mass star formation within a
-%few kpc of the Sun (Figure 1).  Their physical properties may then be
-%constrained by comparison with data in other wavebands.  The
-%distribution of these regions will be compared with other tracers of
-%the interstellar medium (ISM) such as molecular clouds, supershells,
-%HII regions, supernova remnants, and supershells.  The 1.1 mm data
-%together with dust continuum maps at shorter wavelengths taken by us
-%with SHARC~II or with other telescopes will constrain temperature and
-%reveal what surrounding material may be feeding the formation of dense
-%cores. Star formation efficiencies may be obtained by detailed
-%comparison of the NIR-MIR observations of stars with the BGPS
-%observations.  This will also constrain the extinction law and dust
-%properties, essential to refining mass estimates.  By comparing the
-%distribution of 1.1mm cores with HII regions, supernova remnants, and
-%IR emission as seen by {\it Spitzer}, we will constrain the mode of
-%core and star formation, i.e., is it predominantly triggered by
-%advancing shock and ionization fronts, by converging flows in a
-%turbulent medium, or by spontaneous gravitational collapse?  The
-%former models predict a close correlation between fronts and cores
-%while the latter predicts the correlation will be poor.
-
-%\Figure{mass_limits}{The limiting gas mass of cores detectable
-%with at a flux limit of 15 mJy RMS. Detection thresholds at 3 (dashed)
-%and 5 (solid) $\sigma$ are shown for a range of dust temperatures.
-%Dust temperatures $<20$~K are most interesting for this survey, since
-%these are the sources most likely to be pre- or proto-stellar
-%condensations.}{fig:mass_limits}{1.0}
-%
-\Figure{coverage_moll} {The coverage of the BGPS.  The background
-greyscale is IRAS 100 \mum.  [James, team: is there a better figure 
-option?]
-%The Bolocam coverage is shown with white
-%solid lines in the top two panels and black in the bottom three.
-%Major regions of Galactic star formation are labeled.  The coverage of
-%{\em Spitzer}-GLIMPSE \citep{benjamin03} and the FCRAO $^{13}$CO GRS
-%\citep{jackson06} are shown.
-}{fig:Coverage}{1.0}
 
@@
 
-\newcounter{subfig}
-\setcounter{subfig}{1}
-\renewcommand{\thefigure}{\arabic{figure}\alph{subfig}}
-
-\addtocounter{figure}{0}
-%\begin{sidewaysfigure}[h]
-\begin{figure}
-  \label{fig:BGPSMontage}
-  \begin{minipage}{6.5in}
-    \begin{center}
-      \includegraphics[scale=0.9]{fig1_pg1_bw_inv_bar_label}
-      \caption{$\lon=-10.5$ to $\lon=19.5$ Units are \jyb. 
-%      The brightest
-%	sources, e.g. Sgr B2, Sgr A, and sources near $\lon=10$ and
-%	$\lon=13$, appear to be saturated, but this is only a display
-%	artifact.
-        The noise is more pronounced from $\lon=-7$ to $\lon=-2$
-	because this region was observed less.}
-    \end{center}
-  \end{minipage}
-\end{figure}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \begin{minipage}{6.5in} 
-    \begin{center}
-      \includegraphics[scale=0.9]{fig1_pg2_bw_inv_bar_label} 
-      \caption{$\lon=19.5$ to $\lon=49.5$.  Units are \jyb .  G34.3+0.15, W
-	51, W 43, W 49, and M 17 appear to be saturated, but this is
-	only a display artifact.  The $20 < \ell < 40$ region through the
-        4-8 kpc molecular ring and approximately the termination of the galactic
-        bar is particularly rich in clumps.}
-    \end{center}
-  \end{minipage}
-\end{figure}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \begin{minipage}{6.5in} 
-    \begin{center}
-      \includegraphics[scale=0.9]{fig1_pg3_bw_inv_bar_label}
-      \caption{$\lon=49.5$ to $\lon=74.5$.  In comparison to the inner galaxy, the $65
-      < \ell < 75$ has a very sparse population of faint clumps}
-    \end{center}
-  \end{minipage}
-\end{figure}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \hspace{-1in}
-  \includegraphics[scale=0.8]{fig1_pg5_bw_inv_bar_label} 
-  \caption{The Cygnus Arm. Note that coverage in \emph{b} is extended to $\pm
-  1.5\deg$. The large scale `peanut' shape including DR21 is suggestive of a
-  large wind-blown bubble, although.... [John: fill in discussion here or we'll
-  remove it].  See section \ref{sec:motte} for a comparison with the
-  \citet{motte07} IRAM study of this region. }
-\end{figure}
-%  \vspace{-4in}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-\hspace{-0.5in}
-  \includegraphics[scale=0.8]{fig1_pg4_bw_inv_bar_label} 
-  \caption{Cloud complexes centered at $\lon=111$ in the Perseus Arm. 
-  The NGC 7538 complex is in the upper-left.}
-\end{figure}
-
-\addtocounter{figure}{-1}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \hspace{-1in}
-  \includegraphics[scale=0.8]{fig1_pg6_bw_inv_bar_label} 
-  \caption{W3/4/5.  The W3(OH)/W3 Main complex is the bright source
-  on the right side of the image.  W5 has one scan performed in RA/Dec
-  instead of Galactic coordinates and so has non-uniform noise properties
-  in each square degree}
-\end{figure}
-
-\renewcommand{\thefigure}{\arabic{figure}}
-
-\clearpage
-
 \section{Observations}
@@
 268~GHz (hereafter 1.1~mm) and fractional bandwidth $\Delta \nu/\nu =
-0.17$ (45.5 GHz).  The passband is constructed to exclude the $^{12}\mathrm{CO}(2
-\to 1)$ emission line.  Figure \ref{fig:Bandpass} shows the passband.
-We compute color corrections in Appendix \ref{app:ColorCorrections}.
+0.17$ (45.5 GHz).  The passband is constructed to exclude the
+$^{12}\mathrm{CO}(2 \to 1)$ emission line.  Figure \ref{fig:Bandpass}
+shows the passband.  We compute color corrections in Appendix
+\ref{app:ColorCorrections}.
 
@@
 pixels at 1.1 mm is 1.6$f\lambda$, so the focal plane is not
-instantaneously sampled.  The Bolocam instrument is described in greater
-detail in \citet{haig04} and \citet{glenn03}.
+instantaneously sampled.  The Bolocam instrument is described in
+greater detail in \citet{haig04} and \citet{glenn03}.
 
@@
 
-The maps presented here were acquired during six separate
-observing sessions at the CSO over the course of two years.  The
-observing epochs are given in Table \ref{tab:Observing}, along with
+The maps presented here were acquired during six separate observing
+sessions at the CSO over the course of two years.  The observing
+epochs are given in Table \ref{tab:Observing}, along with
 corresponding ranges for the zenith opacity $\tau_{225}$ of the CSO
-tipper tau.  Bolocam
-observations were typically scheduled when $\tau_{225} > 0.06$.
-Between observing epochs, Bolocam was removed from its mount at
-the re-imaged Cassegrain focus and stored warm.  Thus the flux
-calibration and pointing model must be re-computed for each epoch to
-allow for variations in the instrument and optics.  We found that the
-flux calibration did not in fact differ significantly between epochs.
-We observed additional pointing sources during Epoch V and therefore
-used it as the master pointing model.
+tipper tau.  Bolocam observations were typically scheduled when
+$\tau_{225} > 0.06$.  Between observing epochs, Bolocam was removed
+from its mount at the re-imaged Cassegrain focus and stored warm.
+Thus the flux calibration and pointing model must be re-computed for
+each epoch to allow for variations in the instrument and optics.  We
+found that the flux calibration did not in fact differ significantly
+between epochs.  We observed additional pointing sources during Epoch
+V and therefore used it as the master pointing model.
 
@@
 
-[Reword section?] Our basic observing strategy was to raster scan Bolocam by moving the
+%[Reword section?] 
+Our basic observing strategy was to raster scan Bolocam by moving the
 primary mirror of the CSO to modulate the astrophysical signal faster
 than fluctuations in atmospheric opacity.  Each field was scanned with
-alternating raster scans along $l$ and $b$.  In Epoch I-II, the fundamental
-scan unit was a $1\arcdeg \times 1\arcdeg$ block, scanned 23 times in \lon and
-$b$.  Starting with Epoch III, the fundamental scan unit was changed to a
-$3\arcdeg \times 1\arcdeg$ block for increased mapping efficiency.  Each block
-was scanned with 23 scans along lines of constant $b$, and 67 scans along lines
-of constant $l$.  In both cases, the spacing between adjacent rasters was
-162\arcsec.  The total time for such a scan was between 39 and 48 minutes.  The
-data were electronically sampled at 10 Hz along the scan direction, slightly
-higher than the Nyquist rate for the scan speed of 120\arcsec\ s$^{-1}$.
+alternating raster scans along $l$ and $b$.  In Epoch I-II, the
+fundamental scan unit was a $1\arcdeg \times 1\arcdeg$ block, scanned
+23 times in \lon\ and $b$.  Starting with Epoch III, the fundamental
+scan unit was changed to a $3\arcdeg \times 1\arcdeg$ block for
+increased mapping efficiency.  Each block was scanned with 23 scans
+along lines of constant $b$, and 67 scans along lines of constant $l$.
+In both cases, the spacing between adjacent rasters was 162\arcsec.
+The total time for such a scan was 39 (48) minutes for the $b$ ($l$)
+scans.  The data were electronically sampled at 10 Hz along the scan
+direction, slightly higher than the Nyquist rate for the scan speed of
+120\arcsec\ s$^{-1}$.
 
@@
 in Figure \ref{fig:Array}.  Achieving good sampling is complicated by
-a number of missing bolometers.  A simulation was performed to determine
-the optimal angle to rotate the array with respect to the scan
-direction to account for the beam spacing and missing bolometers.  During
-the turnaround following a raster, the field rotator is adjusted to
-this optimum angle.
+a number of missing bolometers.  A simulation was performed to
+determine the optimal angle to rotate the array with respect to the
+scan direction to account for the beam spacing and missing bolometers.
+During the turnaround following a raster, the field rotator is
+adjusted to this optimum angle.
 %CHECK
@@
 
-% FIGURES AND TABLES
-
-% Figure 3
-\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright molecular
-emission lines are shown at their rest frequencies.  Note that the Bolocam
-passband rejects $>90\%$ of the $^{12}$CO flux, leaving our continuum
-measurements largely uncontaminated.  SO$_2$ and CH$_3$OH lines are likely 
-strong contributors to line flux in the passband.  \citet{nummelin1998} found
-that 22\% of the flux density in one pointing towards Sgr B2 was from lines,
-and \citet{yoshida2005} reported $>40\%$ in Orion A from line emission over the
-260-328 GHz band. Other lines lying in the Bolocam passband include CS($5\to4$)
-and ($6\to5$) (245 and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267
-GHz).  } 
-% A follow-up project will attempt to determine the contribution of lines
-% to the BGPS flux density measurements.}
-{fig:Bandpass}{1.0}
-
-\Table
-{lllll}
-{Observing Epochs for the BGPS}
-{Number & Begin (UT) & End (UT) & Nights & $\tau_{225}$ }
-{tab:Observing}
-{
-I   & 2005 Jul 03 & 2005 Jul 13 & 5 & 0.1 \\
-II  & 2005 Sep 04 & 2005 Sep 12 & 5 & 0.1 \\
-III & 2006 Jul 01 & 2006 Jul 13 & 5 & 0.1 \\
-IV  & 2006 Sep 01 & 2006 Sep 09 & 5 & 0.1 \\
-V   & 2007 Jul 01 & 2007 Jul 13 & 5 & 0.1 \\
-VI  & 2007 Sep 01 & 2007 Sep 09 & 5 & 0.1 \\
-}
-
-% Figure 4
-\FigureTwo{bolosens050904_o32}{scan_10deg}{Left: the position, ellipticity and
-relative response of the detectors in the Bolocam focal plane as mapped to the
-sky.  Right: The effect of field rotation on the coverage obtained via Bolocam
-raster scans.  The array is held fixed during a scan, but is rotated such that
-the sampling is most uniform.}{fig:Array}{1.0}
-
 \section{Overview of the Data Reduction}
 \label{sec:Overview}
-
-{\it just stole material from the Letter here - needs a bit of cleaning up}
 
@@
 method of \citet{enoch06} for generating maps and characterizing their
-properties.  It incorporates some of the technical developments
-of \citet{sayers09}, though the exquisite control of systematics and
-noise of that analysis is neither necessary nor possible here.
-
-The data were reduced with a custom pipeline written specifically for the BGPS.
-A key element of the reduction is the iterative estimation of the
-atmospheric fluctuations and the astrophysical signal.  The
+properties and is similar in many respects to the methods presented in
+\citet{cotton09} or \citet{kovacs08}.  It incorporates some of the
+technical developments of \citet{sayers09}, though the exquisite
+control of systematics and noise of that analysis is neither necessary
+nor possible here.
+
+The data were reduced with a custom pipeline written specifically for
+the BGPS.  A key element of the reduction is the iterative estimation
+of the atmospheric fluctuations and the astrophysical signal.  The
 atmospheric model is developed from a set of principal components of
-the bolometer signal time series under the assumption that the bulk of the
-correlated signal is atmospheric (under this assumption, astrophysical extended
-structures are treated as atmospheric noise).  The iterative estimation
-process then helps to restore correlated flux due to astrophysical
-emission (Section \ref{sec:Mapping}).
-
-The Bolocam observations are sensitive to structure between \bcamfwhm\ and
-about 200\arcsec\ (half the array field of view, see figure
-\ref{fig:PCA_Filter}).  An indicative analysis of the spatial filter function
-of the iterative mapping scheme is given in \citet{enoch06}, and we present a detailed analysis
-of the filter function in our survey in figure \ref{fig:PCA_Filter}.  The data were
-sampled onto a uniform 7\farcs2 grid.  Flux density calibrations were performed
-using observations of Mars, Uranus, and Neptune, and they are accurate to
-$\sim$20\%.  The flux calibration is described in section \ref{sec:FluxCalibration}.
+the bolometer signal time series under the assumption that the bulk of
+the correlated signal is atmospheric (under this assumption,
+astrophysical extended structures are treated as atmospheric noise).
+The iterative estimation process then helps to restore correlated flux
+due to astrophysical emission (Section \ref{sec:Mapping}).
+
+The Bolocam observations are sensitive to structure between \bcamfwhm\
+and about 200\arcsec\ (half the array field of view, see figure
+\ref{fig:PCA_Filter}).  We present a detailed analysis of the filter
+function in our survey in figure \ref{fig:PCA_Filter}.  The data were
+sampled onto a uniform 7\farcs2 grid.  Flux density calibrations were
+performed using observations of Mars and Uranus, and the overall
+calibration accuracy is estimated to be $\sim$15\%.  The flux
+calibration is described in section \ref{sec:FluxCalibration}.
 
@@
 
-A separate model was constructed for each epoch, but epoch V was used as the
-primary pointing calibration and is shown in figure \ref{fig:PointingModel}.
-In epoch V and VI, pointing sources were observed more frequently to obtain a
-better-constrained master pointing model. The absolute pointing accuracy was
-$\sim6\arcsec$ RMS.  The Epoch V pointing model was used to make pointing
-reference fields which were then median combined using IRAF to make a higher
-S/N reference field with somewhat reduced pointing errors (Section
-\ref{sec:Astrometry}).
+A separate model was constructed for each epoch, but epoch V was used
+as the primary pointing calibration and is shown in figure
+\ref{fig:PointingModel}.  In epoch V and VI, pointing sources were
+observed more frequently to obtain a better-constrained master
+pointing model. The absolute pointing accuracy was $\sim6\arcsec$ RMS.
+The Epoch V pointing model was used to make pointing reference fields
+to which all other fields were aligned using a cross-correlation
+algorithm (Section \ref{sec:Astrometry}).
 
@@
 surrounded by substantial negative bowls.  Some flux is restored in
-these bowls using the iterative process, 
- but around the brightest sources the impact of the source on the
-background estimation is too great to be fully recovered (Section
-\ref{sec:Photometry}).
-
-Instrument glitches and cosmic ray hits have been removed by a combination of
-outlier rejection in each spatial pixel and hand flagging of the timestream
-data.  Streaking in the images results from incorrect determinations of the
-zero level across scans when a bright source is encountered and variable noise
-in each strip from variable dwell time.  Atmospheric noise in observations
-taken in poor weather may not be completely removed by the reduction procedures
-because the atmospheric opacity can vary over timescales comparable to the time
-to scan astrophysical sources (Section \ref{sec:Noise}).
+these bowls using the iterative process, but around the brightest
+sources the impact of the source on the background estimation is too
+great to be fully recovered (Section \ref{sec:Photometry}).
+
+Instrument glitches and cosmic ray hits have been removed by a
+combination of outlier rejection in each spatial pixel and hand
+flagging of the timestream data.  Streaking in the images results from
+incorrect determinations of the zero level across scans when a bright
+source is encountered and variable noise in each strip from variable
+dwell time.  Atmospheric noise in observations taken in poor weather
+may not be completely removed by the reduction procedures because the
+atmospheric opacity can vary over timescales comparable to the time to
+scan astrophysical sources (Section \ref{sec:Noise}).
 
@@
 
-The absolute flux calibration is derived from observations of Mars
-and Uranus
+The absolute flux calibration is derived from observations of Mars and
+Uranus
 % no good observations, per AG
@@
 in-band atmosphere opacity.  Under the assumption that the only power
-variation on the detectors is due to the power from the atmosphere (i.e.
-that astronomical sources are faint relative to the atmosphere),
-which may be parameterized by $\tau$, ${\cal S}$ is a single-valued
-function of $\tau$.  We have used the mean bolometer resistance as a
-proxy for $\tau$, since the bolometer resistance is a single-valued
-function of loading.  {\it This quantity is monitored continuously for
-all observations.}  Note that this calibration curve folds in both the
-effects of changing atmospheric transmission and the changes in
-the detector response with optical loading.
+variation on the detectors is due to the power from the atmosphere
+(i.e.  that astronomical sources are faint relative to the
+atmosphere), which may be parameterized by $\tau$, ${\cal S}$ is a
+single-valued function of $\tau$.  We have used the mean bolometer
+resistance as a proxy for $\tau$, since the bolometer resistance is a
+single-valued function of loading.  {\it This quantity is monitored
+continuously for all observations.}  Note that this calibration curve
+folds in both the effects of changing atmospheric transmission and the
+changes in the detector response with optical loading.
 
@@
 
-A fit to the observed values (measured potential difference vs. known flux
-density) for the primary calibrators was performed for the each epoch
-separately.
+A fit to the observed values (measured potential difference vs. known
+flux density) for the primary calibrators was performed for the each
+epoch separately.
 %CHECK
@@
 %constitutes each of the observing epochs.  
-The calibration curve is shown in Figure \ref{fig:CalibrationCurves}.  The
-resulting error on the calibration curve fit is less than 
+The calibration curve is shown in Figure \ref{fig:CalibrationCurves}.
+The resulting error on the calibration curve fit is less than
 %CHECK
@@
 plane.  We do this by monitoring the response to the atmosphere
-emission in all bolometers (astrophysical signal is negligible except at SgrB2).  Since the
-atmosphere is common to all detectors [Anyone - why is the atmosphere common across 7.5'
-at the mm?  Brief discussion of atmosphere physics would be helpful], any changes in response are due to the
-intrinsic properties of the detectors.  The change in relative response with
-loading for a typical detector is shown in Figure \ref{fig:CalibrationCurves}.
-The actual application of the method to the time series of the bolometer
-data is shown in Figure \ref{fig:Flatfield}, and is discussed further in
-Section \ref{sec:Mapping}.
-
-[move this?] In figure \ref{fig:Flatfield}, each step of the iterative cleaning process is illustrated.
+emission in all bolometers (astrophysical signal is negligible except
+at SgrB2).  Being in the near field, the atmosphere is common to all
+detectors, and thus this serves as a common relative reference to
+calibrate out variation in the individual detector responsivities and
+optical efficiencies.  The properties of atmospheric noise above Mauna
+Kea as inferred from the Bolocam data are discussed in
+\citet{sayers09b}.  The change in relative response with loading for a
+typical detector is shown in Figure \ref{fig:CalibrationCurves}.  The
+actual application of the method to the time series of the bolometer
+data is shown in Figure \ref{fig:Flatfield}, where it is clear that
+correlation of the timestreams is indeed improved by the application
+of a single multiplicative factor.  The implementation of this
+calibration in the context of the larger mapping algorithm is
+discussed further in Section \ref{sec:Mapping}.
 
@@
 Gaussian profile.  The beam area is that averaged over all detectors,
-and is $1.71\times10^{-6}$ steradians (\bcamfwhm).  This
-allows conversion of the maps, calibrated in Jy beam$^{-1}$, into
-surface brightness (MJy sr$^{-1}$).  The uncertainty in the mean beam size
-is $.7\%$, leading to an uncertainty in the surface brightness calibration
-of \TBD.
+and is $1.71\times10^{-6}$ steradians (\bcamfwhm).  This allows
+conversion of the maps, calibrated in Jy beam$^{-1}$, into surface
+brightness (MJy sr$^{-1}$).  The uncertainty in the mean beam size is
+$3\%$, leading to a corresponding additional uncertainty in the
+surface brightness calibration.
 
@@
 or ATLASGAL 870 \mum\ results is complicated by the poorly determined
-variations in the dust spectral index produced by emissivity variations.
-However, there are several large-area surveys with the IRAM 30 meter
-telescope at 1.2 mm which can be used for comparison with BGPS to
-check overall image quality, pointing, and flux calibration.  The study
-of the Cygnus-X region by \citet{motte07} presents one of the largest
-fields in the Galactic plane that has been mapped with MABO which overlaps
-with the Bolocam survey fields.
-
-The Motte Cygnus-X study used both the 37 element MAMBO and 117 channel
-MAMBO-2 instrument on the IRAM 30-meter diameter telescope on Pico Veleta
-in Spain.   The FWHM beam size for the observations was 11\arcsec .
-The effective passband of the images presented by Motte et al.
-is about 70 GHz centered at 240 GHz and thus includes the bright
-J = 2--1 CO transition.
+variations in the dust spectral index produced by emissivity
+variations.  However, there are several large-area surveys with the
+IRAM 30 meter telescope at 1.2 mm which can be used for comparison
+with BGPS to check overall image quality, pointing, and flux
+calibration.  The study of the Cygnus-X region by \citet{motte07}
+(hereafter M07) presents one of the largest fields in the Galactic
+plane that has been mapped with MAMBO which overlaps with the Bolocam
+survey fields.
+
+The M07 Cygnus-X study used both the 37 element MAMBO and 117 channel
+MAMBO-2 instrument on the IRAM 30-meter diameter telescope on Pico
+Veleta in Spain.  The FWHM beam size for the observations was
+11\arcsec .  The effective passband of the images presented by M07 is
+about 70 GHz centered at 240 GHz and thus includes the bright J = 2--1
+CO transition (see Figure \ref{fig:Bandpass}).
 
 The structure of the emission in the Cygnus-X region presented by
-\citet{motte07} appear nearly identical to the 1.1 mm Bolocam images
+\citet{motte07} appears nearly identical to the 1.1 mm Bolocam images
 of the same field despite the inclusion of the CO line, the slightly
@@
 sizes.  The peak positions also agree to within the errors of the
-BGPS survey discussed in this paper.
-
-Direct comparison with the fluxes listed in Motte et al. requires
-consideration of the factor of three difference in the size of the beams.
-For example, the the brightest source in the Cyg-X region is DR 21.
-While Motte et al. quote a peak flux density per beam of 4.2 \jyb for
-the brightest feature in the DR 21 complex (their peak N46) and 17.9 Jy
-in a $\sim$ 17\arcsec\ by 23\arcsec box (0.19 x 0.14 pc at an assumed
-distance of 1.7 kpc; see Motte et al. Table 1 in their Appendix).
-BGPS measures a peak flux of 17.5 \jyb in an effective beam roughly
+BGPS, as discussed in this paper.
+
+Direct comparison with the fluxes listed in M07 requires consideration
+of the factor of three difference in the size of the beams.  For
+example, the the brightest source in the Cyg-X region is DR 21.  While
+M07 quote a peak flux density per beam of 4.2 \jyb for the
+brightest feature in the DR 21 complex (their peak N46) and 17.9 Jy in
+a $\sim$ 17\arcsec\ by 23\arcsec box (0.19 x 0.14 pc at an assumed
+distance of 1.7 kpc; see M07 Table 1 in their Appendix).
+BGPS measures a peak flux of 17.5 \jyb\ in an effective beam roughly
 \bcamfwhm\ in diameter, indicating that the relative calibration is
@@
 measured fluxes with those from the BGPS.  Additionally, the data values
-in Motte et al. are in units of Jankys per pixel, with each pixel subtending
+in M07 are in units of Jankys per pixel, with each pixel subtending
 a 4\arcsec\ by 4\arcsec\ area on the sky.  In contrast, the data values
@@
 
-The Motte et al. images were convolved with IRAF task
+The M07 images were convolved with IRAF task
 GAUSS using a 3.5 pixel convolution kernel to synthesize maps with an
@@
 
-The average Motte et al. fluxes are larger than the BGPS fluxes by a factor
+The average M07 fluxes are larger than the BGPS fluxes by a factor
 of 1.23 despite the longer wavelength.  Contamination by the bright
@@
 than what was seen by BGPS.    If this is a typical spectral index for
-the sample of clumps, then the Motte et al. flux calibration may be as
+the sample of clumps, then the M07 flux calibration may be as
 much as 45\% higher than the BGPS fluxes.
-
-\Table
-{lllllll}
-{Comparison of \citet{motte07} IRAM and BGPS measurements
-in the Cygnus X region.  The IRAM data has been convolved
-to the BGPS beam and scaled so the units are in Jy/beam.
-}
-{
-%Source  &   BGPS           &  Motte \\
-%        &   peak m\jyb  &  mJy in box (see Motte+ Table 1)
-Motte Source &  Motte Table 1   &  Motte scaled  & BGPS  & Ratio &  Comments \\
-     Number &  integrated flux &  \jyb          & \jyb  &       &           \\
-}
-{tab:CygnusComparison}
-{
-3  &    1.59 [0.11x0.09] & 2.61      &  2.30  & & DR 17                               \\
-11 &    0.34 [0.11x0.06] & 0.48      &  0.50  & & West SW of DR21                     \\
-12 &    1.63 [0.11x0.09] & 2.60      &  2.20  & &   "                                 \\
-16 &    0.55 [0.12x0.12] & 0.82      &  0.72  & &   "                                 \\
-26 &    0.34 [0.20x0.10] & 0.48      &  0.44  & &   "                                 \\
-29 &    0.54 [0.25x0.13] & 1.10      &  0.62  & &   "                                 \\
-30 &   10.54 [0.15x0.10] &13.5       &  9.80  & & W75(N)                              \\
-44 &    8.43 [0.14x0.11] &14.5       & 12.7   & & DR21 (OH)                           \\
-46 &   17.90 [0.08x0.03] &18.4       & 15.8   & & DR21 f-f, maser (H2O)               \\
-48 &    3.72 [0.17x0.11] & 9.4       &  7.8   & & DR21 (OH)-S                         \\
-51 &    2.37 [0.24x0.03] & 5.5       &  4.1   & & DR21 FIR2                           \\
-53 &    1.60 [0.14x0.09] & 4.3       &  2.7   & & North of DR21  FIR3                 \\
-56 &    0.60 [0.12x0.08] & 0.81      &  0.75  & & SE of DR21 47                       \\
-58 &    2.73 [0.23x0.19] & 2.40      &  1.64  & & IRAS 20375+4109                     \\
-59 &    0.37 [0.12x0.05] & 1.3       &  0.93  & & East of IRAS 20375+4109             \\
-60 &    0.56 [0.16x0.13] & 1.00      &  0.78  & & East of IRAS 20375+4109             \\
-61 &    0.23 [0.12x0.09] & 0.60      &  0.49  & & MSX 81.5168+0.01926                 \\
-62 &    0.50 [0.18x0.12] & 1.23      &  0.80  & & between 63 \& IRAS 20375+4109       \\
-63 &    1.09 [0.08x0.05] & 1.60      &  1.50  & & DR22                                \\
-65 &    0.78 [0.16x0.12] & 1.15      &  1.10  & &                                     \\
-66 &    0.25 [0.15x0.06] & 0.63      &  0.76  & &                                     \\
-68 &    0.84 [0.10x0.10] & 1.01      &  0.94  & &                                     \\
-69 &    1.28 [0.47x0.18] & 1.12      &  1.20  & &                                     \\
-72 &    0.54 [0.28x0.13] & 0.58      &  0.47  & &                                     \\
-}
-% 7
-\Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
-in the same aperture from the \citet{motte07} MAMBO map and the Bolocam map of
-this paper. }{fig:CygnusComparison}{1.0}
-
-\FigureTwo{fluxcal_errorbars}{calib_vs_dc}
-%{rel_flux_cal_050303_ob3_to_050405_o66}
-%{calibration_plot_2004}
-{Left: Average calibration curve [V/Jy] versus the mean detector voltage, a
-proxy for atmospheric loading.  Red points are observations of Mars and black
-of Uranus.  The black line is a 2nd-order fit with 0,0 forced (no response if no
-measurable potential difference) .  Right: Scaling of the relative
-response to the atmosphere for a single detector compared to the array median.
-Outliers are from noisy scans that are strongly
-downweighted.}{fig:CalibrationCurves}{1.0}
-
-% 6
-\Figure{relsens_cal}{An illustration of the relative sensitivity
-calibration using the atmosphere as a calibrator.  Black is the median
-over all bolometers (the 1st-order atmosphere model), red and green are
-individual bolometers. a. before and b. after applying the relative
-calibration.  Note the improved agreement.}{fig:Flatfield}{1.0}
-
-% 7
-\Figure{cygnus_flux_comparison}{A comparison of the fluxes extracted
-in the same aperture from the \citet{motte07} MAMBO map and the Bolocam map of
-this paper. }{fig:CygnusComparison}{1.0}
-
-\begin{deluxetable}{lc}
-\tablewidth{0pt}
-\tablecaption{Flux density error budget}
-\tablehead{
-\colhead{Source} & \colhead{Contribution}
-}
-\startdata
-\label{tab:ErrorBudget} % categorize - which is systematic and which is random
-Pointing error uncertainty & 2\% \\
-Calibration curve (Eq. \ref{eq:Calibration}) uncertainty & $<5\%$ \\  % formal statistical error is probably less than real effect...?
-PCA flux reduction uncertainty & 4\% \\   % is this an uncertainty?  Or systematic loss?
-Absolute Mars flux uncertainty &  5\% \\
-Beam size uncertainty (surface brightness) & X\% \\
-\hline
-Total & 7\% (random) + 5\% (systematic)
-\enddata
-\end{deluxetable}
 
@@
 We constructed an absolute reference system for the BGPS by observing
-bright quasars and blazars near the Galactic Plane [with small raster maps?].  The distribution
-of pointing sources over the sky is shown in Figure
-\ref{fig:PointingCalibrators} and the list is given in Appendix
+bright quasars and blazars near the Galactic Plane [with small raster
+maps?].  The distribution of pointing sources over the sky is shown in
+Figure \ref{fig:PointingCalibrators} and the list is given in Appendix
 \ref{app:PointingCalibrators}.
@@
 Pointing observations were performed approximately once every two
-hours over each night.   The
-elevation offsets showed a deviation from zero which was empirically
-well-modeled by a quadratic function of elevation and a linear
-function of azimuth.  No systematic deviation was observed for the
-azimuth offsets.
+hours over each night.  The elevation offsets showed a deviation from
+zero which was empirically well-modeled by a quadratic function of
+elevation and a linear function of azimuth.  No systematic deviation
+was observed for the azimuth offsets.
 
@@
 coordinate system.  This is done by making observations which track
-all detectors across a bright source (e.g. a planet) and making maps from each
-bolometer individually.
-
-[I think this section needs to be checked on more.... I don't know what to say about it yet -Adam]
-In our first data release, the projected positions of the detectors on the sky
-are made using the nominal positions without correction for optical distortion.
-This results in a slightly blurred beam (35\farcs6 instead of 31\farcs2).
+all detectors across a bright source (e.g. a planet) and making maps
+from each bolometer individually.
+
+%[I think this section needs to be checked on more.... I don't know
+%what to say about it yet -Adam] In our first data release, the
+%projected positions of the detectors on the sky are made using the
+%nominal positions without correction for optical distortion.  This
+%results in a slightly blurred beam (35\farcs6 instead of 31\farcs2).
+%Because this distortion is asymmetric, it can also result in a small
+%pointing offset at the field edges where only bolometers with large
+%offsets record data.  However, this effect is strongly mitigated by
+%the low number of hits at field edges - this data is generally flagged
+%out.  The residual offset is within the overall pointing model error,
+%but caution should be used when measuring locations at the field
+%edges. [ Note - I haven't been able to measure this yet.  It's only
+%marginally possible]
+%
+
+In our first data release, the projected positions of the detectors on
+the sky are made using the nominal positions without correction for
+optical distortion.  This results in a slightly blurred beam
+(\bcamfwhm instead of 31\farcs2).  Since a different subset of the
+array is used to map each portion of the scanned field, the effective
+beam size will vary slightly across the field, ranging from
+$\sim31\farcs$ to $\sim33\farcs$, and it may be asymmetric.  The
+effective beam size was measured from fully-sampled beam-mapping
+observations of planets, while the variation in beam size with
+sampling was measured from flux calibration observations of planets.
+The beam size at each position cannot be measured until distortion
+correction is performed in a later release.
+
+Because this distortion is asymmetric, it can also result in a small
+pointing offset at the field edges where only bolometers with large
+offsets record data.  However, this effect is strongly mitigated by
+the low number of hits at field edges - this data is generally flagged
+out.  The residual offset is within the overall pointing model error,
+but caution should be used when measuring source locations at the
+field edges.
+
 Because this distortion is asymmetric, it can also result in a small pointing
@@
 overall pointing model error, but caution should be used when measuring
-locations at the field edges. [ Note - I haven't been able to measure this yet.  It's only marginally
-possible]
-
-A mean focus offset for the secondary was determined once per observing
-run.  An elevation-dependent correction is applied via a
+source locations at the field edges.
+
+A mean focus offset for the secondary was determined once per
+observing run.  An elevation-dependent correction is applied via a
 CSO-determined look-up table between raster scans.  We did not see any
 evidence that more frequent focus checks improve the quality of the
-PSF. [Observers - what checks were done?]
-
-\subsection{Relative Alignment and Mosaicing}
-
-Relative alignment between different observations of the same field was
-performed by finding the peak of the cross-correlation between images and a
-pointing master constructed  from observations taken in the epoch with the
-best-constrained pointing model for that field (in most cases, this was from
-Epoch V, though in some cases Epoch VI was used).  Each observation was
-initially mapped individually, then all observations in the pointing epoch were
-median-combined to create a reference field.  Each observation was then
-cross-correlated with the reference image for that field. The cross-correlation
-peak was fit with a gaussian and the difference between the gaussian peak and
-the image center was used as the pixel offset.  Finally, all observations of a
-field were merged into a single timestream with pointing offsets applied to
-create the field mosaic.
-
-This method of alignment avoids the ambiguities inherent in using extracted
-sources to align fields, as the BGPS sources are rarely point-like.  It further
-avoids the pointing smearing and loss of peak flux density which would result
-if the the maps of individual observations were coadded using the pointing
-model alone, where each individual observation would be coadded with the
-6\arcsec\ RMS uncertainty of the model.  The relative alignment using the
-correlation maps is accurate to $<1\arcsec$ [I think this should be the
-Gaussian width of the cross-correlation fit?] where there is adequate signal.
-
-In low s/n fields, specifically \lon=65 to 75, there was not enough signal to
-acquire a pointing offset using cross-correlation.  In these fields the
-relative pointing offset is larger and the beam is slightly larger.
+PSF.
+%[Observers - what checks were done?]
+
+\subsection{Relative Alignment and Mosaicking}
+
+Relative alignment between different observations of the same field
+was performed by finding the peak of the cross-correlation between
+images and a pointing master constructed from observations taken in
+the epoch with the best-constrained pointing model for that field (in
+most cases, this was from Epoch V, though in some cases Epoch VI was
+used).  Each observation was initially mapped individually, then all
+observations in the pointing epoch were median-combined to create a
+reference field.  Each observation was then cross-correlated with the
+reference image for that field. The cross-correlation peak was fit
+with a gaussian and the difference between the gaussian peak and the
+image center was used as the pixel offset.  Finally, all observations
+of a field were merged into a single timestream with pointing offsets
+applied to create the field mosaic.
+
+This method of alignment avoids the ambiguities inherent in using
+extracted sources to align fields, as the BGPS sources are rarely
+point-like.  It further avoids the pointing smearing and loss of peak
+flux density which would result if the the maps of individual
+observations were coadded using the pointing model alone, where each
+individual observation would be coadded with the 6\arcsec\ RMS
+uncertainty of the model.  The relative alignment using the
+correlation maps may be determined accurately to the error in finding
+the peak of the gaussian, typically $<1\arcsec$ where there is
+adequate signal.  In a few low S/N fields, specifically \lon=65 to 75,
+there was not enough signal to acquire a pointing offset using
+cross-correlation.  In these fields, the pointing model was used
+directly.  This results in a slightly larger effective beam since the
+pointing error of 6\arcsec\ is convolved with the instrument PSF.
 
@@
 \citep[][hereafter SLC]{difrancesco08}.  These maps allow a
-cross-check of the accuracy of the BGPS pointing model.  We have applied the same
-cross-correlation procedure used to obtain the relative alignment of
-BGPS observations to compare the BGPS images to the SLC.  Concerns might arise
-in comparing the Bolocam to the SCUBA maps, such as the differing scan
-strategies (SCUBA maps were typically taken in jiggle-map mode, which tends to
-remove extended structure).  The cross-correlation technique actually
-mitigates these effects, since it does not require the establishment of a
-single position for an object (which may differ due to the change in wavelength
-between the surveys or due to the observing strategy) but rather makes use of
-all the information available.  The by-eye morphological comparison between SCUBA and
-BGPS sources is generally excellent with some exceptions, giving a high degree
-of confidence to the comparison and to the results obtained from the BGPS pointing
-model [include Di Francesco pointing accuracy].  An example is shown in Figure \ref{fig:SCUBAPointingComparison}.  We
-find that the RMS offset between BGPS and SLC positions within a $3\arcdeg
-\times 1\arcdeg$ block defined by the BGPS is $4.0\pm8.8$\arcsec, consistent
-with the errors derived for the Bolocam pointing model.  There were some BGPS
-fields that had larger offsets from SCUBA fields; these fields were excluded
-from the offset measurement above because of poor morpohological match.
+cross-check of the accuracy of the BGPS pointing model.  We have
+applied the same cross-correlation procedure used to obtain the
+relative alignment of BGPS observations to compare the BGPS images to
+the SLC.  Concerns might arise in comparing the Bolocam to the SCUBA
+maps, such as the differing scan strategies (SCUBA maps were typically
+taken in jiggle-map mode, which tends to remove extended structure).
+The cross-correlation technique actually mitigates these effects,
+since it does not require the establishment of a single position for
+an object (which may differ due to the change in wavelength between
+the surveys or due to the observing strategy) but rather makes use of
+all the information available.  The by-eye morphological comparison
+between SCUBA and BGPS sources is generally excellent with some
+exceptions, giving a high degree of confidence to the comparison and
+to the results obtained from the BGPS pointing model [include Di
+Francesco pointing accuracy].  An example is shown in Figure
+\ref{fig:SCUBAPointingComparison}.  We find that the RMS offset
+between BGPS and SLC positions within a $3\arcdeg \times 1\arcdeg$
+block defined by the BGPS is $4.0\pm8.8$\arcsec, consistent with the
+errors derived for the Bolocam pointing model.  There were some BGPS
+fields that had larger offsets from SCUBA fields; these fields were
+excluded from the offset measurement above because of poor
+morpohological match.
 
@@
 %{\em Miranda's data here}
-
-% 8
-% -----------------------------------------------------------------------------
-\FigureTwo{plane_astrometry}{pointing_model_skydist}{Left: The
-distribution of absolute reference sources (crosses) in the Galactic
-Plane (Appendix \ref{app:PointingCalibrators}).  Also shown (crosses)
-are the locations of bright, isolated, compact sources for comparison
-with other surveys, as given in Appendix \ref{app:ReferenceSources}.
-Right: The distribution of the pointing calibration sources across the
-local sky in Hawaii during July 2007 (epoch V) when the pointing model
-was constructed.  }{fig:PointingCalibrators}{1.0}
-% -----------------------------------------------------------------------------
-
-% 9
-% -----------------------------------------------------------------------------
-\begin{figure}
-  \subfigure[The pointing model correction (left) and residuals (right) for
-  Epoch V, from which the master reference images were derived for subsequent
-  alignment.  The red line indicates the fitted model. 510 pointing sources
-  were included, and the final RMS was 5.77\arcsec in altitude and 3.21\arcsec
-  in azimuth, or a total RMS offset of 6.6\arcsec.  No systematic offset with
-  altitude was found.]
-{\label{fig:PointingModel-a}\includegraphics[scale=0.9]{paper_models_0707}}\\
-
-  \subfigure[The residuals of the pointing model.  The Gaussian fits have
-  $\sigma = 5.94,2.92$ in altitude offset and azimuth offset respectively.]
-{\label{fig:PointingModel-b}\includegraphics[scale=0.9]{paper_gaussian_0707}}
-
-\caption{The Bolocam pointing model for Epoch V.}
-\label{fig:PointingModel}
-\end{figure}
-% -----------------------------------------------------------------------------
-
-% 10
-% -----------------------------------------------------------------------------
-\begin{figure}
-
-  \subfigure[{\it Left}: the Bolocam map in a portion of the $\lon=30$
-  field.  {\it Right}: the SLC maps in the same region.  The green
-  contours on the Bolocam map indicate the positions of the SLC
-  sources.  Negative bowls in the image are forced to zero before
-  cross-correlating.  ]
-  {\label{fig:SCUBAPointingComparison-a}\includegraphics[scale=0.8]
-  {scuba_bolocam_l030}}
-
-  \begin{tabular}{cc}
-
-  \subfigure[The cross-correlation map of the BGPS and SLC maps in
-  Figure \ref{fig:SCUBAPointingComparison-a}. {\bf to be replaced with
-  correct map}]
-  {\label{fig:SCUBAPointingComparison-b}\includegraphics[scale=0.45]
-  {xcorr_standin}}
-
-  \subfigure[The measured offset between Bolocam and SCUBA Legacy
-sources \citep{difrancesco08}, using the method described in Setion
-\ref{sec:SCUBAPointingComparison}.  The circle indicates the $1\sigma$
-region, which is also consistent with the error derived from the
-internal Bolocam pointing model.]
-{\label{fig:SCUBAPointingComparison-c}\includegraphics[scale=0.45]
-{scuba_pointing_offsets}}
-
-\end{tabular}
-
-\caption{Comparing the Bolocam positions to those of the SCUBA Legacy Catalog.}
-\label{fig:SCUBAPointingComparison}
-\end{figure}
-% -----------------------------------------------------------------------------
 
@@
 there exists a linear operation which makes predictions about the
-observed timestreams, namely $d_p = A m$; this will be denoted $T[m] =
-d_p$.
-
-The goal is to produce a time series for each bolometer which as
+observed timestreams, namely $d = A m$; this will be denoted $T[m] =
+d$. The goal is to produce a time series for each bolometer which as
 closely as possible approximates $s + \epsi$ so that we may produce
-the best estimate of the astrophysical signal $m = M[s+\epsi] = S + N$.
+the best estimate of the astrophysical signal $m = M[s+\epsi] = S +
+N$.
 
@@
 where $\tilde{s}^{(0)}_i(t)=0$.   Each bolometer's timestream is then 
-fit to the mean atmosphere model to obtain the relative gains of the detectors.
+fit to the mean atmosphere model 
 \begin{equation}
+\label{eq:MeanAtmosphere}
 \tilde{a}^{(n)}_i(t) = \frac{d_i(t) \cdot a(t)}{d_i(t)^2} a(t) = r_i a(t)
 \end{equation}
-This is illustrated in Figure \ref{fig:Flatfield}.  
+This is illustrated in Figure \ref{fig:Flatfield}.  The $r_i$ are then
+used as the relative gains of the detectors.
 % James - what's this section about?
@@
 \begin{equation}
+\label{eq:SignalEstimate}
 d_i(t) - \tilde{a}^{(n)}_i(t) - \tilde{e}^{(n)}_i(t)
@@
 \begin{equation}
+\label{eq:ResidualMap}
 E = M[d_i(t) - \tilde{s}^{(n)}_i(t) - \tilde{a}^{(n)}_i(t) - 
@@
 \end{equation}
-This residual map serves as a visualization of the progress of the iterative
-method, since in a perfect process it would be map of $\epsi$.
+This residual map serves as a visualization of the progress of the
+iterative method, since in a perfect process it would be map of
+$\epsi$.
 
@@
 
-The simplest model for the atmosphere fluctations makes use of the
-fact that the beams for all of the detectors pass through a nearly
-identical atmosphere, thus implying that atmosphere fluctuations will
-be highly correlated between detectors.
-
-To further remove the atmosphere (and other correlated instrument
-noise) without a detailed physical model, we use principal component
-analysis (PCA) as given in \citet{laurent05}. [more words]
-
-The mean across each scan is forced to zero by subtracting a polynomial
-fit to the scan after iteratively rejecting astrophysical sources.  This
-process helps reduce negative bowls in the scan direction near bright sources.
+By construction, the Bolocam beams as they pass through the dominant
+layer of atmospheric water vapor at $\sim1$~km altitude are still
+highly overlapped, and therefore sample a nearly identical region of
+atmosphere.  The simplest model for the atmosphere fluctations makes
+use of this fact by assuming that the largest correlated signals
+between detectors are due to to the atmosphere correlations.  However,
+the simple common mode subtraction of Equation \ref{eq:MeanAtmosphere}
+does not remove all of the correlated signal.  To further remove the
+atmosphere (and other correlated instrument noise) without a detailed
+physical model, we use principal component analysis (PCA) as given in
+\citet{laurent05}.
+%[more words]
+While lacking the physical motivation of the polynomial subtraction
+used for the 2.1 mm Bolocam data by \citet{sayers09b}, the 1.1 mm data
+seems to have a large number of correlated components that are not
+simply described by low-order polynomials in the focal plane.  Figure
+\ref{fig:PCA_Graphical} shows an example of the modes removed by the
+PCA model.  In addition to the PCA model, after iteratively
+subtracting the astrophysical model, each scan has a polynomial fit in
+time removed to deal with the longest time scale modes.
+
+%The mean across each scan is forced to zero by subtracting a
+%polynomial fit to the scan after iteratively rejecting astrophysical
+%sources.  This process helps reduce negative bowls in the scan
+%direction near bright sources.
 
@@
 
-\item Pickup from the 60 Hz AC power.  This appears as narrow lines in the power spectral density (PSD)
-    of the data.  The second harmonic of 60 Hz is aliased via beating against
-    the 130 Hz bolometer bias frequency into 10 Hz with sidebands split at
-    $\sim1$ Hz.  It is removed by replacing components at these frequencies in
-    the fourier transform with gaussian noise matched to the local mean
+\item Pickup from the 60 Hz AC power.  This appears as narrow lines in
+    the power spectral density (PSD) of the data.  The second harmonic
+    of 60 Hz is aliased via beating against the 130 Hz bolometer bias
+    frequency into 10 Hz with sidebands split at $\sim1$ Hz.  It is
+    removed by replacing components at these frequencies in the
+    fourier transform with gaussian noise matched to the local mean
     amplitude.
@@
 each timestream point's value is assigned to an area much smaller than
-the beam.
-%In principle this can be addressed by various gridding
-%algorithms, and may be a part of future reductions of the BGPS data.
-
-The resulting map is then subjected to a maximum-entropy clean algorithm
-\citep{hollis92} using a specified kernel to produce a deconvolved image which
-is mapped back into the timestream to be subtracted (Equation
-\ref{eq:MapToTime}).  This has several advantages over using the original map
-directly, including rejecting artifacts smaller than the kernel and decreasing
-the noise of the resulting timestream.  It is also better than a ``threshold''
-method, which tends to produce discontinuities and include noise outliers.
-
-In some fields, flux from some sources spread out over the course of the
-iterative process using certain kernel sizes.  The cause of this artifact is
-not yet well-understood, but using a different kernel size was an effective
-workaround and did little to change the properties of the final map.  The
-standard kernel size was 14.4\arcsec; a 21.6\arcsec kernel was used when
-artifacts were encountered.
-
-\setcounter{subfig}{1}
-\renewcommand{\thefigure}{\arabic{figure}\alph{subfig}}
-
-\begin{figure}
-  \begin{minipage}{6.5in}
-    \begin{center}
-      \includegraphics[scale=0.9]{iterative_mapping1}
-      \caption{An example of the change in the time series as
-      iterative mapping proceeds.  1. Raw time series 2. After removal
-      of residual 60Hz signal 3. Exponential decay function at scan
-      turnarounds subtracted 4. A polynomial (with astrophysical source
-      rejection) is fit to remove large-scale variations across the scan. }
-    \end{center}
-    \label{fig:IterativeMapping}
-  \end{minipage}
-\end{figure}
-
-\addtocounter{figure}{0}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \begin{minipage}{6.5in}
-    \begin{center}
-      \includegraphics[scale=0.9]{iterative_mapping2}
-      \caption{Panel 1 is the same as panel 4 in the previous figure.
-      Before the first cleaning, the raw data (black) and remainder data (green)
-      are equal because there is no model.  
-      Panel 2 shows the median-atmosphere subtraction, which is the first-
-      order correction.
-      Panel 3 shows the astrophysical signal left over from the PCA selection.
-      Panel 4 shows the total atmosphere model from PCA and median estimation}
-    \end{center}
-    \label{fig:IterativeMapping-b}
-  \end{minipage}
-\end{figure}
-
-\addtocounter{figure}{0}
-\addtocounter{subfig}{1}
-
-\begin{figure}
-  \begin{minipage}{6.5in}
-    \begin{center}
-      \includegraphics[scale=0.9]{iterative_mapping3}
-      \caption{Same as previous figure, except after 20 iterations.
-      Panel 1 - The deconvolved astrophysical map is returned to a timestream (red)
-      and subtracted from the 'raw' data (black). 
-      Panel 2 - The median of the remainder (green) is subtracted as the first
-      atmosphere estimation
-      Panel 3 - The cumulative astrophysical model (red) and the additional astrophysical
-      signal from iteration 20 (black)
-      Panel 4 - The atmosphere signal after 20 iterations}
-    \end{center}
-    \label{fig:IterativeMapping-c}
-  \end{minipage}
-\end{figure}
-
-% -----------------------------------------------------------------------------
-\setcounter{subfig}{1}
-\begin{figure}
-  \begin{minipage}{3.25in}
-    \begin{center}
-      \includegraphics[scale=0.5]{flagger_withglitch}
-    \end{center}
-  \end{minipage}
-  \begin{minipage}{3.25in}
-    \begin{center}
-      \includegraphics[scale=0.5]{flagger_glitchgone}
-    \end{center}
-  \end{minipage}
-  \caption{An illustration of the flagging process using the waterfall plot.
-  Left: The glitch apparent at middle right (bolometer 98, around 6.2s) is the
-  same one whose time series is shown in (\em{b}).  Because of
-  the PCA subtraction, the effect of the glitch also propagates over the other
-  bolometers, appearing as a horizontal stripe. Right: The same data displayed
-  with the time point including the glitch flagged out and rescaled}
-
-  \label{fig:Flagger}
-
-  \addtocounter{figure}{0} 
-  \addtocounter{subfig}{1}
-
-  \begin{minipage}{6.5in}
-    \begin{center}
-      \includegraphics[scale=0.5]{flagger_plots}
-      \caption{An illustration of a ``glitch'' in a single bolometer timestream
-      (red) due to a cosmic ray strike.  Note the acausal ringing due to the
-      application of the downsampling filter.  The time series for a physically
-      adjacent bolometer is shown in blue, and a bolometer which does not pass
-      over the source in green.  The PCA atmosphere estimation has already been
-      subtracted from the data.}
-    \end{center}
-  \end{minipage}
-
-\end{figure}
-
-% -----------------------------------------------------------------------------
-
-\renewcommand{\thefigure}{\arabic{figure}}
-
-%\FigureTwo{flagger_withglitch}{flagger_glitchgone}{An illustration of
-%the flagging process using the waterfall plot. Left: The glitch
-%apparent at middle right is the same one whose time series is shown in
-%Figure \ref{fig:CosmicRayGlitch}.  Because of the PCA subtraction, the
-%effect of the glitch also propagates over the other bolometers,
-%appearing as a horizontal stripe. Right: The same data displayed with
-%the time point including the glitch flagged out and rescaled}
-%{fig:Flaggin}{1.0}
-%
-\Figure{crs}{The distribution of glitch amplitudes flagged and removed from the
-data in the \lon=111 field.  Glitches below the detection threshold may
-contribute to the overall noise.  Each data point represents .1s of integration
-time.}{fig:GlitchDistribution}{1.0}
-
-\begin{figure}
-  \begin{minipage}{6.5in}
-    \begin{center}
-      \includegraphics[angle=270,scale=0.6]{eachpca}
-    \end{center}
-  \end{minipage}
-\vspace{0.25in}
-  \begin{minipage}{6.5in}
-    \begin{center}
-      \includegraphics[angle=270,scale=0.6]{eachpca_20iters}
-    \end{center}
-  \end{minipage}
-  \caption{Selected images to illustrate the PCA process.  The displays are in
-  Galactic coordinates with a color range from -.1 to 1.0 \jyb.
-  {\it Top 4 rows}: a grid of maps of each of the first 20 PCA components displayed at
-  the same scale.  It is clear that NCG 7538, the object imaged, has emission
-  in each component.  There are varying levels of noise in each component, with
-  the first and second being the most obvious atmospheric components.  Most of
-  the other noise components are probably detector noise correlated among a
-  subset of the bolometers.  The streaks are residuals of the scan-turnaround
-  noise that was not removed by the exponential model fit.  {\it Bottom 4
-  rows}: The same figure, but after 20 iterations.  The figure is the breakdown
-  of the atmosphere remainder (i.e.  the raw data minus the astrophysical
-  model) into eigenfunctions.  Very little astrophysical flux remains at any
-  level of correlation, though there is some at large (few arcminute) scales.}
-\label{fig:PCA_Graphical}
-
-\end{figure}
-
-\Figure{l001_deconvolutionkernelcompare}{The effect of deconvolution on the
-iterative process can be seen in its effect on the residuals in these images of
-Sgr B2, all displayed at the same scale. From left to right: map, residual,
-model. Top to bottom kernel size: 14.4\arcsec, 21.6\arcsec, 31.2\arcsec,
-7.2\arcsec. The final version of the pipeline uses 14.4\arcsec, which has the
-result of leaving no flux in the residual at the location of Sgr B2, and does
-not ``dig a hole'' in the residual map, as the 7.2\arcsec\ kernel does.  The
-7.2\arcsec\ kernel also lacks the noise-rejection features of the larger
-kernels, as can be seen in the last panel.}{fig:Deconvolution}{1.0}
-
-\clearpage
+the beam.  In principle this can be addressed by various gridding
+algorithms, and may be a part of future reductions of the BGPS data.
+
+The resulting map is then subjected to a maximum-entropy clean
+algorithm \citep{hollis92} using a specified kernel to produce a
+deconvolved image which is mapped back into the timestream to be
+subtracted (Equation \ref{eq:MapToTime}).  This has several advantages
+over using the original map directly, including rejecting artifacts
+smaller than the kernel and decreasing the noise of the resulting
+timestream.  It is also better than a ``threshold'' method, which
+tends to produce discontinuities and include noise outliers.
+
+In some fields, flux from some sources spread out over the course of
+the iterative process using certain kernel sizes.  The cause of this
+artifact is not yet well-understood, but using a different kernel size
+was an effective workaround and did little to change the properties of
+the final map.  The standard kernel size was 14.4\arcsec; a
+21.6\arcsec kernel was used when artifacts were encountered.
+Simulations indicate that this change in kernel has a negligible
+effect on the flux of the source; see Figure \ref{fig:PCA_Filter}.
 
@@
 
-The residual maps produced by the iterative mapping provide a natural way of
-estimating the systematic error resulting from imperfect subtraction of bright
-sources.  The imperfect subtraction results in positive ``ghosts'' of the
-bright sources in the error maps $E$.  Smoothed residual maps also provide the
-best means of determining the pixel-to-pixel error near bright sources.  Near
-the scan edges, 1/sqrt(weightmap) provides a better estimate of the local noise.
-
-% Residual maps are produced for each map from the residuals after
-% removing the astrophysical signal model and the PCA atmosphere model.  These
-% maps are useful for diagnosing the effect of the iterative process on bright
-% sources and as a method of obtaining an
-% estimate of the noise.
-
+The residual maps $E$ (Equation \ref{eq:ResidualMap}) form the basis
+for the noise estimation and also provide a way of estimating the
+systematic error resulting from imperfect subtraction of bright
+sources.  These maps are produced for each region from the data
+residuals after removing the astrophysical signal model and the PCA
+atmosphere model.  An example of an error map is shown in Figure
+\ref{fig:sampleimages}.  In an ideal case, the residual map $E$
+represents a map of a realization of the underlying irreducible noise
+$\epsi$.  However, the imperfect estimation of the signal results in
+positive ``ghosts'' of bright sources.  We have found that smoothed
+versions of the residual maps provide the best means of determining
+the pixel-to-pixel error that account for the local variations in the
+noise, including those due to such artifacts.
+%Near the scan edges,
+%1/sqrt(weightmap) provides a better estimate of the local noise.
 % ...ok, explain please?
-% The noise is correlated between adjacent spatial pixels due to
-% residual atmospheric noise correlated in time.  We have completed
-% ignored this effect in our analysis.
-
-The noise may be estimated either from the residual maps, from the timestream
-PSDs of the detectors, or from the weight maps produced. The final per-pixel
-error estimate is given as \TBD (this remains an open question - is the best
-per-pixel error a smoothed version of the residual map, e.g.  \citet{enoch06},
-1/weightmap$^2$, or some other estimate? Adam, James, Erik).
+Our pixel noise estimate assumes the noise is uncorrelated between
+adjacent pixels, but of course adjacent spatial pixels are correlated
+due to residual atmospheric noise correlated in time.  We have ignored
+this effect in our analysis under the assumption that the remaining
+correlations after subtracting the PCA model are small.
 
@@
 
-[since we don't do any science in this paper, should this be held off for
-use in Erik's paper?]
-The depth can be converted into an
-estimate of mass via standard estimates, i.e., under the assumption of
-a temperature, opacity, and distance.
-Using dust opacity from \citet{ossenkopf94}
+\section{Effects of the Data Reduction Procedures on Photometry}
+\label{sec:Photometry}
+
+To do accurate and meaningful photometry on the Bolocam maps requires
+a good estimate of the noise (Section \ref{sec:Noise}) but also an
+understanding of the spatial filtering imposed by the observing
+strategy and the cleaning and mapping of the data.  The additional
+complexities of defining ``sources'' in complicated regions are
+discussed in \citet{rosolowsky09}.  Here we restrict our discussion to
+the limitations on performing photometry imposed by the data
+reduction.
+
+The fundamental feature of the data is that there is a degeneracy
+between large spatial scale astrophysical emission and the atmosphere
+and other signals with long spatial or temporal variations.
+Consequently, there are limits to ability of the algorithm to separate
+the signal $s$ from the atmosphere $a$ and instrument terms $e$ in
+Equation \ref{eq:SignalEstimate}.  Inevitably, some of the signal
+which should be present in $s$ is mixed into these terms and is thus
+not present in the final map $m$.  Because $s$ is generated from a
+deconvolution algorithm, it has non-zero mean by construction, but
+importantly, it does {\it not} contain an unbiased estimate of the
+astrophysical signal on all spatial scales: large spatial scales are
+preferentially missing.
+
+To assess the effect of the mapping algorithm on the flux recovered as
+a function of angular scale, we performed a series of simulations.
+Gaussian sources with a range of peak flux densities and sizes were
+inserted on top of a background consisting of real BGPS data with the
+astrophysical source model removed.  The recovered fluxes were
+measured in ellipses that included single well-separated sources.
+Figure \ref{fig:PCA_Filter}a shows the fraction of flux recovered in
+the map as a function of source size for a range of different PCA
+components subtracted in the cleaning.
+
+The final reduction used 13 PCA components because this produced a
+reasonable compromise between attenuating extended structure and
+cleaning the atmospheric contribution.  Note that this is a
+substantially more aggressive cleaning than that used in
+\citet{enoch06} largely because our mean integration time per pixel
+was $\sim$seconds, whereas theirs was $\sim$minutes.  
+%, and therefore the
+%atmospheric noise was much more likely to be correlated between
+%observations.
+
+Figure \ref{fig:PCA_Filter}b shows the fraction of flux recovered in
+the maps as a function of the deconvolution kernel used to create the
+astrophysical model maps.  The differences at large source sizes are
+not well-understood (these size scales may be dominated by
+atmosphere), but at the smallest source size, it is evident that a
+deconvolution kernel smaller than the source size does not reliably
+recover the source flux.  Therefore we chose a deconvolution kernel
+smaller than the beam but larger than the pixel size used.  Figure
+\ref{fig:Deconvolution} demonstrates the effects of using both too
+large and too small a kernel.
+
+\section{Final Maps and Data Release}
+\label{sec:FinalMaps}
+
+The final maps are produced by coadding all observations of a single
+square degree centered on a particular Galactic coordinate
+$(l_0,b_0)$.  The maps are made in Galactic coordinates using a plate
+carr\'{e} (FITS header CAR) projection.  (This is the same projection
+used by the \spitzer-GLIMPSE and BU-FCRAO GRS surveys.)  As these maps
+are near the coordinate system equator, the difference between truly
+equiareal pixels and the pixels used is at most even at 5\arcdeg out
+of the plane (as for IC1396) is 0.4\%.  The pixel size is 7.2\arcsec,
+chosen to be much smaller than the Bolocam beam.  The maps are written
+to standard FITS files.  An example of the FITS header for the BGPS
+images is given in Appendix \ref{app:FITS_Header}.
+
+Five image types will be released, each covering the same regions.
+The maps are standard astrophysical maps subject to the caveats
+previously mentioned, the most important being the spatial filtering
+function (section \ref{sec:Noise}).
+
+All processed maps are available through
+IPAC\footnote{http://irsa.ipac.caltech.edu/Missions/bolocam.html}.
+IPAC provides a cutout service for the images as well as a searchable
+version of the catalog provided in \citet{rosolowsky09}.  The full
+release includes:
+
+\begin{enumerate}
+\item Calibrated maps for all regions observed (MAP).
+
+% don't release smoothmaps? \item The MAP smoothed by the Bolocam PSF, which is helpful in bringing out extended structure (SMOOTHMAP)
+
+\item The deconvolved MAP (MODEL).  The model maps are deconvolved
+using the maximum-entropy method with kernels specified in the header
+(either 14.4\arcsec or 21.6\arcsec).  {\tt After deconvolution, the maps
+are smoothed to the beam size of \bcamfwhm.}
+
+\item Maps of integration time per pixel (NHITSMAP).  The nhitsmap
+shows how many recorded data points from the timestream have been
+assigned to each pixel; it is proportional to the dwell time per pixel
+(each `hit' is .1s).
+
+\item Maps of residual noise per pixel (RESIDUAL).  The residual map
+is the map of the model timestream subtracted from the data
+timestream; it is close to but not identical to the map minus the
+model.
+
+\item Maps of inverse variance per pixel (WEIGHTMAP).  The weightmap
+shows the inverse-variance weighting of each pixel.
+
+\item Maps of the mask obtained for various regions from the
+cataloging algorithm (MASKMAP) \citep{rosolowsky09}
+
+\end{enumerate}
+
+Examples of each (except the nhitsmap) are given in figure
+\ref{fig:sampleimages}.
+
+\section{Discussion}
+\label{sec:Discussion}
+
+%{\bf Claudia suggested that this section be removed or changed to an
+%`advertisement' section where we indicate what follow-up work needs to
+%be done - seems reasonable, since this is mostly junk pilfered from
+%the `letter'.  However, we need to keep the last sentence around...}
+
+The BGPS is the first millimeter survey of a substantial fraction of
+the Galactic Plane, providing an unbiased look at the high-density gas
+most intimately associated with the earliest phases of star formation.
+Maps of the entire BGPS are presented in Figure \ref{fig:BGPSMontage}.
+
+Inspection of Figure \ref{fig:BGPSMontage} shows excellent
+correspondence with SCUBA maps of small sub-fields throughout the
+plane \citep{difrancesco08}.  BGPS contours overlaid on the GLIMPSE
+survey \citep{benjamin03} show excellent correlation with 8\mum\
+infrared dark clouds (IRDCs).  However, many features in the BGPS maps
+do not appear in the Spitzer observations, which suggests that the 1.1
+mm emission traces dense clumps without a background to absorb; see
+Figure \ref{fig:Science}.
+
+% No advertisements.
+% A
+% study of IRDC correlation with BGPS emission is underway
+% \citep{battersby09}.
+
+% implies star forming....
+
+Filamentary structures with aspect ratios $\geq 10$ are present
+throughout the galactic plane.  The most crowded fields consist of
+frothy and clumpy structure.  There are 5000-10000 distinct sources,
+the majority of which are at least moderately resolved
+\citep{rosolowsky09}.  We suspect that higher resolution observations
+will resolve BGPS clumps into clusters of protostellar objects, as has
+been seen in Serpens \citep{enoch08,Testi1998}, OMC 1
+\citep{beuther04,johnstone99}, and S255N \citep{cyganowski07} where
+bolometer observations at low resolution have been complemented by
+interferometer observations at high resolution.
+
+There are clear maxima in the emission filling factor in the Galactic
+Center and in the region from $\lon=23$ to $\lon=31$, the line of
+sight through the densest part of the molecular ring.  Additional
+areas of high source density are seen at $\lon=10$ and $\lon=13$.  The
+filling factor of 1.1 mm continuum emission at the 100 mJy level is
+$\sim 20$\% per square degree from $\lon=-10$ to $\lon=20$ and $\sim
+10$\% from $\lon=20$ to $\lon=50$ (compare to figure
+\ref{fig:NoiseVsLongitude}.  In the range $\lon=50$ to $\lon=75$, the
+filling factor is below 1\% and very few sources have been detected.
+This result is in contrast to CO filling factors $\sim1$ in the inner
+galactic plane \citep{dame01,jackson06}, confirming that 1.1 mm
+continuum emission traces denser material than CO.  The small filling
+factor of the 1.1 mm emission compared to CO emission shows that the
+continuum is directly associated with star forming material, whereas
+the CO also traces less dense material not directly associated with
+star formation.
+
+In some cases, distance to BGPS clumps can be determined by matching
+Galactic Ring Survey $^{13}$CO and 1.1 mm continuum morphology
+\citep{IRDCdistance,jackson06}.  However, in other cases the
+association between the CO and 1.1 mm data is not clear, either
+because of confusion or because the BGPS sources are too compact to
+identify in $^{13}$CO morphology.  Heterodyne follow-up observations
+using dense gas tracers (NH$_3$, N$_2$H$^+$, HCO$^+$, and CS) are
+being conducted to provide radial velocity, density, chemistry, and
+temperature measurements \citep{schlingman09,battersby09, nordhaus09}.
+
+The depth can be converted into an estimate of mass via standard
+estimates, i.e., under the assumption of a temperature, opacity, and
+distance.  Using dust opacity from \citet{ossenkopf94}
 %\citet{enoch06} and \citet{young06},
@@
 
-\Figure{survey_depth}{The depth of the BGPS in the first quadrant as a
-function of Galactic longitude.  The black histogram plots the standard deviation as a 
-function of longitude binned in $0.9\arcdeg \times 0.9\arcdeg$ degree blocks
-(to avoid high-noise regions at scan edges) centered on $b=0$ for the error
-maps $E$.  Red is similar, but the estimator is median(1/sqrt(weight
-map).}{fig:NoiseVsLongitude}{1.0}
-
-\section{Effects of the Data Reduction Procedures on Photometry}
-\label{sec:Photometry}
-
-To do accurate and meaningful photometry on the Bolocam maps requires
-a good estimate of the noise (Section \ref{sec:Noise}) but also an
-understanding of the spatial filtering imposed by the observing
-strategy and the cleaning and mapping of the data.  
-The additional
-complexities of defining ``sources'' in complicated regions are discussed in
-\citet{rosolowsky09}.  Here we restrict our discussion to the limitations
-on performing photometry imposed by the data reduction.
-
-The BGPS maps are the convolution of the (nearly Gaussian)
-primary beam $G(\xad)$ and an effective high-pass
-spatial filter $F(\xad)$ (figure \ref{fig:PCA_Filter}),
-\[
-M'(\xad) = (G(\xad) \otimes F(\xad)) \otimes M(\xad)
-\]
-
-%James - please explain this to me, or explain it better here.  What
-%is the form of B(Omega) that it gives 0?
-The effect of the high pass filter is that the effective PSF $B=G
-\otimes F$ has the non-intuitive property that its area is {\em zero}:
-\[
-\int{B(\Omega) d\Omega} = 0
-\]
-Clearly, this complicates the definition of surface brightness, and
-also imposes a limit on the size of features for which photometry may
-be meaningfully performed.
-
-To assess the effect of the mapping algorithm, we performed a series
-of simulations.  Gaussian sources with a range of peak flux densities and sizes
-were inserted on top of a background consisting of real BGPS data with the
-astrophysical source model removed.  The recovered fluxes were measured in
-ellipses that included single well-separated sources.  Figure
-\ref{fig:PCA_Filter}a shows the fraction of flux recovered in the map as a
-function of source size for a range of different PCA components subtracted in
-the cleaning.
-
-The final reduction used 13 PCA components because this produced a
-reasonable compromise between attenuating extended structure and
-cleaning the atmospheric contribution.  Note that this is a substantially
-more aggressive cleaning than that used in \citet{enoch06} largely because
-our mean integration time per pixel was $\sim$seconds, whereas theirs was
-$\sim$minutes, and therefore the atmospheric noise was much more likely to
-be correlated between observations.
-
-Figure \ref{fig:PCA_Filter}b shows the fraction of flux recovered in the
-maps as a function of the deconvolution kernel used to create the astrophysical
-model maps.  The differences at large source sizes are not well-understood
-(these size scales may be dominated by atmosphere), but at the smallest source
-size, it is evident that a deconvolution kernel smaller than the source size
-does not reliably recover the source flux.  Therefore we chose a deconvolution
-kernel smaller than the beam but larger than the pixel size used.  Figure
-\ref{fig:Deconvolution} demonstrates the effects of using both too large and
-too small a kernel.
-
-% -----------------------------------------------------------------------------
-
-\FigureTwo{pca_comparison_nolegend_l111}{deconvolution_comparison_nolegend_l111}{The
-fractional flux recovered as a function of source size for
-well-separated Gaussian sources with FWHM as indicated.
-\emph{Left}: 3 (blue), 7 (green), 10 (yellow), 13 (orange), 16 (red), 21
-(teal), 26 (lime), 31 (black) PCA components subtracted.  
-Note that flux recovery drops to 50\% at 120\arcsec for the 13 PCA
-component cleaning used in the released data.  The 3 and 7 PCA cases
-show bumps because atmospheric noise is still present at large scales.
-The $>$100\% recovery for simulated sources smaller than the deconvolution kernel is a
-side-effect; since the deconvolution kernel is smaller than the beam, no real
-astrophysical source should ever be smaller than the kernel.
-\emph{Right}:
-7.2\arcsec (cyan), 14.4\arcsec (black), 21.6\arcsec (red), 31.2\arcsec (green)
-deconvolution kernel for 13 PCA components subtracted.  It is clear that the
-larger deconvolution kernels generate spurious signal at smaller scales, but
-the flux recovery is very close to 1 at the beam size
-(\bcamfwhm)}{fig:PCA_Filter}{1.0}
-
-\Figure{aper_phot_hpf_beam}{[James - figure needs clarification] The effect of performing aperture
-photometry on a point source of unit flux observed with the effective
-Bolocam PSF $B$.  The black curve shows the area (measured in pixels)
-as a function of the aperture radius for the filter measured via
-simulation.  This is compared to the equivalent case for a Gaussian
-beam (green).  The vertical lines show radii of $n/2 \times FWHM$ for
-$n=1,2,3$.  One can see that the Gaussian beam has nearly reached a
-constant area of $2 \pi \sigma^2$ by a radius of $3/2 \times FWHM$, at
-which point any larger aperture would recover the full flux of the
-source.  The actual Bolocam beam reaches its maximum effective area
-sooner, and then drops precipitously as the size of the aperture is
-increased.  }{fig:ESF}{1.0}
-
-\clearpage
-
-\section{Final Maps and Data Release}
-\label{sec:FinalMaps}
-
-The final maps are produced by coadding all observations of a single
-square degree centered on a particular Galactic coordinate
-$(l_0,b_0)$.  The maps are made in Galactic coordinates using a plate
-carr\'{e} (FITS header CAR) projection.  (This is the same projection
-used by the \spitzer-GLIMPSE and BU-FCRAO GRS surveys.)  As these maps
-are near the coordinate system equator, the difference between truly
-equiareal pixels and the pixels used is at most (James: find this number?) X\%.  The pixel size
-is 7.2\arcsec, chosen to be much smaller than the Bolocam beam.
-%, and
-%producing data squares 500 pixels on a side.
-The maps are written to standard FITS files.  An example of the FITS
-header for the BGPS images is given in Appendix \ref{app:FITS_Header}.
-
-Five image types will be released, each covering the same regions.  The maps
-are standard astrophysical maps subject to the caveats previously mentioned,
-the most important being the spatial filtering function (section \ref{sec:Noise}).
-The model maps are deconvolved using the maximum-entropy method with kernels
-specified in the header (either 14.4\arcsec or 21.6\arcsec).  The residual map is the map of the model timestream
-subtracted from the data timestream; it is close to but not identical to the
-map minus the model.  The weightmap shows the inverse-variance weighting of
-each pixel.  The nhitsmap shows how many recorded data points from the
-timestream have been assigned to each pixel; it is proportional to the dwell
-time per pixel (each `hit' is .1s).  Examples of each (except the nhitsmap)
-are given in figure \ref{fig:sampleimages}.
-
-\Figure{image_types}{Examples of four of the image types being released.  Axes are offsets
-in arcminutes.  See section \ref{sec:FinalMaps}. Top
-left: Map.  Top right: Residual.  Bottom left: Deconvolved.  Bottom right:
-Weight}{fig:sampleimages}{1.0}
-
-%\section{Public Data Release}
-
-All processed maps are available through
-IPAC\footnote{http://irsa.ipac.caltech.edu/Missions/bolocam.html}.
-IPAC provides a cutout service for the images as well as a searchable
-version of the catalog provided in \citet{rosolowsky09}.  The full
-release includes
-\begin{enumerate}
-\item Calibrated maps for all regions observed (MAP)
-% don't release smoothmaps? \item The MAP smoothed by the Bolocam PSF, which is helpful in bringing out extended structure (SMOOTHMAP)
-\item The deconvolved MAP (MODEL)
-\item Maps of integration time per pixel (NHITSMAP)
-\item Maps of residual noise per pixel (RESIDUAL)
-\item Maps of inverse variance per pixel (WEIGHTMAP)
-\item Maps of the mask obtained for various regions from the cataloging algorithm (MASKMAP) \citep{rosolowsky09}
-\end{enumerate}
-
-%\citet{moore07}
-%\citet{zinchenko97}
-
-\section{Analysis}
-\label{sec:Analysis}
-
-{\bf Claudia suggested that this section be removed or changed to an `advertisement' section
-where we indicate what follow-up work needs to be done - seems reasonable, since this
-is mostly junk pilfered from the `letter'.  However, we need to keep the last sentence around...}
-
-TEST: \ref{fig:BGPSMontage}
-
-The BGPS is the first millimeter survey of a substantial fraction
-of the Galactic Plane, providing an unbiased look at the high-density
-gas most intimately associated with the earliest phases of star
-formation.
-
-Inspection of Figure \ref{fig:BGPSMontage} shows excellent
-correspondence with SCUBA maps of small sub-fields throughout the
-plane \citep{difrancesco08}.  BGPS contours overlaid on the GLIMPSE
-survey \citep{benjamin03} show excellent correlation with 8\mum\
-infrared dark clouds (IRDCs).  However, many features in the BGPS maps
-do not appear in the Spitzer observations, which suggests that the 1.1
-mm emission traces dense clumps without a background to absorb.  [if we
-include this, we probably need a figure as an example, c.f. \citet{shuller09}]
-
-% No advertisements.
-% A
-% study of IRDC correlation with BGPS emission is underway
-% \citep{battersby09}.
-
-% implies star forming....
-
-Filamentary structures with aspect ratios $\geq 10$ are present
-throughout the galactic plane.  The most crowded fields consist of
-frothy and clumpy structure.  There are 5000-10000 distinct sources,
-the majority of which are at least moderately resolved
-\citep{rosolowsky09}.  We suspect that higher resolution observations
-will resolve BGPS clumps into clusters of protostellar objects, as has
-been seen in Serpens \citep{enoch08,Testi1998} and OMC 1
-\citep{Beuther2004,johnstone99} where bolometer observations at low
-resolution have been complemented by interferometer observations at
-high resolution.
-
-There are clear maxima in the emission filling factor in the Galactic
-Center and in the region from $\lon=23$ to $\lon=31$, the line of sight
-through the densest part of the molecular ring.  Additional areas of
-high source density are seen at $\lon=10$ and $\lon=13$.  The filling factor
-of 1.1 mm continuum emission at the 100 mJy level is $\sim 20$\% per
-square degree from $\lon=-10$ to $\lon=20$ and $\sim 10$\% from $\lon=20$ to
-$\lon=50$ (compare to figure \ref{fig:NoiseVsLongitude}.
-%In the range
-%$\lon=50$ to $\lon=75$, the filling factor is below 1\% and very few sources have
-%been detected.  
-This result is in contrast to CO filling factors $\sim1$ in the inner galactic
-plane \citep{dame01,jackson06}, confirming that 1.1 mm continuum emission traces
-denser material than CO.  
-%The small filling factor of the 1.1 mm emission
-%compared to CO emission  shows that the continuum is directly associated with
-%star forming material, whereas the CO also traces less dense material not
-%directly associated with star formation.
-
-In some cases, distance to BGPS clumps can be determined by matching
-Galactic Ring Survey $^{13}$CO and 1.1 mm continuum morphology
-\citep{IRDCdistance,jackson06}.  However, in other cases the association
-between the CO and 1.1 mm data is not clear, either because of
-confusion or because the BGPS sources are too compact to identify in
-$^{13}$CO morphology.  Heterodyne follow-up observations using dense
-gas tracers (NH$_3$, N$_2$H$^+$, HCO$^+$, and CS) are being conducted
-to provide radial velocity, density, chemistry, and temperature
-measurements. % no advertisements \citep{schlingman09, battersby09, nordhaus09}.
-
 BGPS clumps are associated with the densest portions of giant
 molecular clouds (GMCs) traced by CO surveys
-\citep[e.g.,][]{dame01,jackson06}.  The brightest clumps visible in our
-maps, e.g. \object{Sgr B2}, \object{G34.3+0.15}, \object{W 51},
+\citep[e.g.,][]{dame01,jackson06}.  The brightest clumps visible in
+our maps, e.g. \object{Sgr B2}, \object{G34.3+0.15}, \object{W 51},
 \object{W 43}, \object{W 49}, and \object{M 17}, correspond to well
@@
 
-In conclusion, the BGPS is most awesome survey ever.
+We anticipate that the public release of the BGPS data will serve as
+an important first look to help guide HIGAL, JPS, ...
 
 \noindent---------------------------------
+
+{\it Facilities:} \facility{CSO (Bolocam)}
 
@@
 fortunate to conduct observations from this mountain.
-
-{\it Facilities:} \facility{CSO (Bolocam)}
 
@@
 % James - it would be nice to include some numbers here, not just the process.
+
+\Table
+{llll}
+{Comparison of band centers and flux ratios for Bolocam and MAMBO.}
+{         & MAMBO         & Bolocam       & $S_{\rm BOLOCAM}/$ \\
+ $\alpha$ & $\nu_c$ [GHz] & $\nu_c$ [GHz] & $S_{\rm MAMBO}$ }
+{tab:ColorCorrections}
+{
+1.0 & 254.8 & 267.8 & 1.051 \\
+1.5 & 256.4 & 268.6 & 1.072 \\
+2.0 & 258.0 & 269.4 & 1.090 \\
+2.5 & 259.5 & 270.0 & 1.104 \\
+3.0 & 261.1 & 270.7 & 1.115 \\
+3.5 & 262.5 & 271.4 & 1.124 \\
+4.0 & 264.0 & 272.2 & 1.130 \\
+4.5 & 265.4 & 272.9 & 1.134 \\
+5.0 & 266.8 & 273.8 & 1.137 \\
+}
 
@@
 
+\include{tables}
+
+\include{figures}
+
 \bibliography{milkyway}

### 2010-02-24 bgps_pipeline/cleaning/flagging/pyflagger.py

@@ -1,0 +1,688 @@
+
+import math
+
+import pylab
+from pylab import *
+import matplotlib
+import pyfits
+from numpy import isnan
+from mad import MAD,nanmedian
+#from matplotlib import patches
+from matplotlib.patches import Rectangle,FancyArrow
+from matplotlib.lines import Line2D
+from matplotlib.widgets import Cursor, MultiCursor
+import matplotlib.cm as cm
+from Scientific.IO import NetCDF
+import time
+import re
+import os
+import copy
+
+
+matplotlib.defaultParams['image.origin']='lower'
+matplotlib.defaultParams['image.interpolation']='nearest'
+matplotlib.defaultParams['image.aspect']=.1
+
+class Flagger:
+  """
+  Write out a file with appropriate flagging commands for use in IDL / later editing
+  Example:
+
+      import pyflagger
+      f = pyflagger.Flagger('050906_o11_raw_ds5.nc')
+      f.plotscan(0)
+      f.close()
+  """
+
+  def __init__(self, filename, ncfilename='', flagfile='', mapnum='', axis=None):
+    fnsearch = re.compile(
+            '([0-9]{6}_o[0-9b][0-9]_raw_ds5.nc)(_indiv[0-9]{1,2}pca)(_MARS)?').search(filename)
+    ncsearch = re.compile(
+            '[0-9]{6}_o[0-9b][0-9]_raw_ds5.nc').search(ncfilename)
+    if fnsearch is None:
+        print "Couldn't find the correct prefix in the filename" \
+                +" - expected form like 050906_o11_raw_ds5.nc_indiv13pca_timestream00.fits"
+        return
+    mapnumsearch = re.compile('([0-9]{2})(\.fits)').search(filename)
+    if mapnumsearch is not None and mapnum=='':
+        mapnum = mapnumsearch.groups()[0]
+    elif mapnum=='':
+        mapnum = '01'
+
+    self.fileprefix = fnsearch.group()
+    self.pathprefix = filename[:fnsearch.start()]
+
+    if ncsearch is not None and fnsearch.groups()[0] == ncsearch.group():
+        self.ncfilename = ncfilename # self.pathprefix+fnsearch.groups()[0]
+        self.readncfile()
+    else:
+        print "Warning: the NCDF filename doesn't match the input fits file name."\
+                + "You'll probably get errors and your work won't be saved."
[…]

### 2010-02-24 bgps_pipeline/methods/paperfigs/example_waterfalls.py

@@ -1,0 +1,40 @@
+import pyflagger
+
+# change this path if you want
+figure_path = '/home/milkyway/student/ginsbura/paper_figures/'
+
+f = pyflagger.Flagger('/usb/scratch1/super_gc/050703_o15_raw_ds5.nc_indiv13pca',mapnum='01',ncfilename='/scratch/sliced/l000/050703_o15_raw_ds5.nc')
+
+f.scannum = 12
+f.flags[f.scannum,:,:] -= (f.flags[f.scannum,:,:] > 0) * f.flags[f.scannum,:,:]
+
+f.plotscan(12,seconds=1)
+figure(1); savefig(figure_path+'flagger_withglitch.ps')
+
+#f.flag_box(97,123,97,132,1)
+f.flag_time(123,'t')
+f.flag_time(124,'t')
+f.flag_time(125,'t')
+f.flag_time(126,'t')
+f.flag_time(127,'t')
+f.flag_time(128,'t')
+f.flag_time(129,'t')
+f.flag_time(130,'t')
+f.flag_time(131,'t')
+f.flag_time(132,'t')
+figure(1); savefig(figure_path+'flagger_glitchboxflagged.ps')
+
+f.plotscan(12,seconds=1)
+figure(1); savefig(figure_path+'flagger_glitchgone.ps')
+
+figure(3)
+xax = arange(f.data.shape[1])/20.  # assuming sample rate is 20 Hz or .05 s
+plot(xax,f.data[12,:,10])  # timestream with no glitch but with sources
+plot(xax,f.data[12,:,27])  # timestream with no glitch or sources
+plot(xax,f.data[12,:,97])  # timestream with glitch
+xlabel("Time (s)")
+ylabel("Amplitude (Jy)")
+savefig(figure_path+'flagger_plots.ps')
+
+f.close()
+

### 2010-02-24 bgps_pipeline/methods/paperfigs/plot_bolosens.py

@@ -1,0 +1,64 @@
+from readcol import readcol
+from pylab import *
+from matplotlib.patches import Ellipse
+from matplotlib.collections import PatchCollection
+import matplotlib
+import os
+
+uranus=[
+'050619_o23-4_nofit' ,
+'050628_o33-4_nofit' ]
+#'050904_o31-2_nofit' 
+
+obs = [ { 'uranus':'050619_o23-4_nofit' } ,
+        { 'uranus':'050628_o33-4_nofit' } ,
+        ]
+#        { '3c279' :'050703_ob1-2' } ]
+
+for o in obs:
+
+    object = o.keys()[0]
+    obsdate = o[object]
+    
+#    d_angle = open(os.environ['workingdir']+'/distmaps/'+object+'_'+obsdate+'.txt','r').readline().split().pop()
+#    d_angle = 0 # I think that was a hack to rotate back to array frame
+
+    bolonum,base,amp,xwid,ywid,xcen,ycen,angle = readcol(os.environ['workingdir']+'/distmaps/'+object+'_'+obsdate+'_bolofits.txt',twod=False,skipline=1)
+
+    good = ((amp > (median(amp)-3*std(amp))) * (amp < (median(amp)+3*std(amp))))
+    low  = amp[good] < median(amp)-std(amp)
+    high = amp[good] > median(amp)+std(amp)
+
+    amplot = amp[good]
+    amplot[low]  = median(amp)-std(amp)
+    amplot[high] = median(amp)+std(amp)
+    colorscale = (amplot-min(amplot))/max(amplot-min(amplot))
+    xwid = xwid[good] / max(xcen[good]-min(xcen[good]))
+    ywid = ywid[good] / max(ycen[good]-min(ycen[good]))
+    xcen = (xcen[good]-min(xcen[good]))/max(xcen[good]-min(xcen[good]))
+    ycen = (ycen[good]-min(ycen[good]))/max(ycen[good]-min(ycen[good]))
+    angle= angle[good] # + float(d_angle)/180*pi
+
+    rad = (xwid+ywid)/2
+    ells = [Ellipse(xy=[xcen[i],ycen[i]], width=xwid[i], height=ywid[i], angle=angle[i]) for i in xrange(good.sum())]
+    lowells = [Ellipse(xy=[xcen[i],ycen[i]], width=xwid[i], height=ywid[i], angle=angle[i]) for i in where(low)[0].tolist()]
[…]
